### 2018-10-23 paper/data-exploration/turnover.Rmd
Initial exploration of Web of Life report
Issue #7

---
title: "Turnover of species and interactions"
author: "Fernando Cagua"
date: "10/23/2018"
output:
  md_document:
    variant: markdown_github
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

The research question is to investigate whether species interact differently in the core of their range versus at the fringes of their distribution, where one would expect it to be harder.

The aim of this document is to explore whetherthe interaction data available in the Bascompte's Web of Life is adequate to answer this question or not.

We start by checking wether species (and interactions) are reflected in enough localities to be able to detect a signal of change across the habitat.

# Species turnover

```{r}
require(ggplot2)
drake::loadd(species_list)

get_sp_freq_by_group <- function(species_list, group){
  group_var <- dplyr::enquo(group)
  species_list %>%
    dplyr::group_by(!!group_var, guild) %>%
    dplyr::summarise(n_net = dplyr::n_distinct(net_name), 
                     n_loc = dplyr::n_distinct(loc_name)) %>%
    dplyr::group_by(guild) %>%
    dplyr::mutate(n_net_rank = dplyr::row_number(dplyr::desc(n_net)),
                  n_loc_rank = dplyr::row_number(dplyr::desc(n_loc)))
}

plot_freq_step <- function(freq_df){
  if ("guild" %in% names(freq_df)){
    p <- freq_df %>%
      ggplot(aes(x = n_loc_rank, y = n_loc, colour = guild)) 
  } else {
    p <- freq_df %>%
      ggplot(aes(x = n_loc_rank, y = n_loc)) 
  }
  p +
  geom_step(size = 1) +
  scale_x_log10() +
  theme_bw() +
  scale_color_brewer(palette = "Paired", 
                     labels = c("plants", "pollinators")) +
  labs(x = "rank", 
       y = "# locations") +
  theme(legend.position = c(0.99, 0.99), 
        legend.justification = c(1,1))
}
species_list %>%
  remove_unknown_species() %>% 
  get_sp_freq_by_group(sp_name) %>% 
  plot_freq_step() +
  ggtitle("number of locations per species")

species_list %>%
  remove_unknown_species() %>% 
  get_sp_freq_by_group(genus) %>%
  plot_freq_step()+
  ggtitle("number of locations per genus")
```

```{r}
require(ggplot2)
drake::loadd(interaction_list)

get_int_freq_by_group <- function(interaction_list, pla_group, pol_group){
  pla_group_var <- dplyr::enquo(pla_group)
  pol_group_var <- dplyr::enquo(pol_group)

  interaction_list %>%
    dplyr::group_by(!!pla_group_var, !!pol_group_var) %>%
    dplyr::summarise(n_net = dplyr::n_distinct(net_name), 
                     n_loc = dplyr::n_distinct(loc_name)) %>%
    dplyr::group_by() %>%
    dplyr::mutate(n_net_rank = dplyr::row_number(dplyr::desc(n_net)),
                  n_loc_rank = dplyr::row_number(dplyr::desc(n_loc)))
}

interaction_list %>%
  remove_unknown_species() %>% 
  get_int_freq_by_group(pla_name, pol_name) %>% 
  plot_freq_step() +
  ggtitle("locations per interactions (species)")

interaction_list %>% 
  remove_unknown_species() %>% 
  get_int_freq_by_group(pla_genus, pol_genus) %>% 
  plot_freq_step() +
  ggtitle("locations per interactions (genus)")
```

# Interactions turnover

### 2018-10-23 main.R

@@ -16,7 +16,9 @@ read_data_plan <- drake::drake_plan(
 
 exploration_plan <- drake::drake_plan(
   species_list = get_species_list(networks, metadata), 
-  interaction_list = get_interaction_list(networks, metadata)
+  interaction_list = get_interaction_list(networks, metadata),
+  rmarkdown::render(input = drake::knitr_in("paper/data-exploration/turnover.Rmd"), 
+                    output_file = drake::file_out("paper/data-exploration/turnover.md"))
 )
 
 full_plan <- rbind(

### 2018-10-26 paper/data-exploration/turnover.Rmd
move functions to calculate frequency to the exploration.R file

@@
 drake::loadd(species_list)
-
-get_sp_freq_by_group <- function(species_list, group){
-  group_var <- dplyr::enquo(group)
-  species_list %>%
-    dplyr::group_by(!!group_var, guild) %>%
-    dplyr::summarise(n_net = dplyr::n_distinct(net_name), 
-                     n_loc = dplyr::n_distinct(loc_name)) %>%
-    dplyr::group_by(guild) %>%
-    dplyr::mutate(n_net_rank = dplyr::row_number(dplyr::desc(n_net)),
-                  n_loc_rank = dplyr::row_number(dplyr::desc(n_loc)))
-}
 
@@
 
-get_int_freq_by_group <- function(interaction_list, pla_group, pol_group){
-  pla_group_var <- dplyr::enquo(pla_group)
-  pol_group_var <- dplyr::enquo(pol_group)
-
   interaction_list %>%

### 2018-10-26 code/exploration.R

@@ -41,3 +41,29 @@ interactions_as_df <- function(x){
     dplyr::mutate_if(is.factor, as.character) %>% 
     `names<-`(c("pla_name", "pol_name", "int_weight"))
 }
+
+# get frequency of group (eg sp_name or genus)
+get_sp_freq_by_group <- function(species_list, group){
+  group_var <- dplyr::enquo(group)
+  species_list %>%
+    dplyr::group_by(!!group_var, guild) %>%
+    dplyr::summarise(n_net = dplyr::n_distinct(net_name), 
+                     n_loc = dplyr::n_distinct(loc_name)) %>%
+    dplyr::group_by(guild) %>%
+    dplyr::mutate(n_net_rank = dplyr::row_number(dplyr::desc(n_net)),
+                  n_loc_rank = dplyr::row_number(dplyr::desc(n_loc)))
+}
+
+# get frequency of interactions by group (eg pla_name & pol_name or pla_genus $pol_genus)
+get_int_freq_by_group <- function(interaction_list, pla_group, pol_group){
+  pla_group_var <- dplyr::enquo(pla_group)
+  pol_group_var <- dplyr::enquo(pol_group)
+  
+  interaction_list %>%
+    dplyr::group_by(!!pla_group_var, !!pol_group_var) %>%
+    dplyr::summarise(n_net = dplyr::n_distinct(net_name), 
+                     n_loc = dplyr::n_distinct(loc_name)) %>%
+    dplyr::group_by() %>%
+    dplyr::mutate(n_net_rank = dplyr::row_number(dplyr::desc(n_net)),
+                  n_loc_rank = dplyr::row_number(dplyr::desc(n_loc)))
+}

### 2018-10-26 paper/data-exploration/turnover.Rmd
Add explanation & tables and use only species data (not genus)
Genus is too broad and probably not useful for the research question

@@
 
-The research question is to investigate whether species interact differently in the core of their range versus at the fringes of their distribution, where one would expect it to be harder.
+We want to investigate whether species interact differently at the core of their range compared to the fringes of their distribution. 
+One could expect species to diversify their interactions as interaction parters become less common/available.
+Alternatively, one could expect species to interact with only a subset of the interaction partners, as they cannot develop new interactions when environemntal conditions are close to the limits of where possitive groth rates occur.
 
-The aim of this document is to explore whetherthe interaction data available in the Bascompte's Web of Life is adequate to answer this question or not.
+The aim of this document is to explore whether the interaction data available in the Bascompte's Web of Life could be adequate to answer this question or not.
 
-We start by checking wether species (and interactions) are reflected in enough localities to be able to detect a signal of change across the habitat.
+We start by checking wether species (and interactions) occur in enough localities to be able to detect a change across the species ranges.
 
-# Species turnover
+## Species & interaction turnover
+
+### Species turnover
 
@@
 }
+
 species_list %>%
@@
   plot_freq_step() +
-  ggtitle("number of locations per species")
+  labs(title = "number of locations per species", 
+       subtitle = "turnover of species in the Web of Life database")
 
+# species_list %>%
+#   remove_unknown_species() %>% 
+#   get_sp_freq_by_group(genus) %>%
+#   plot_freq_step()+
+#   ggtitle("number of locations per genus")
+```
+
+```{r}
 species_list %>%
   remove_unknown_species() %>% 
-  get_sp_freq_by_group(genus) %>%
-  plot_freq_step()+
-  ggtitle("number of locations per genus")
+  get_sp_freq_by_group(sp_name) %>%
+  dplyr::filter(n_loc_rank <= 10) %>%
+  dplyr::select(n_loc_rank, guild, sp_name, n_loc) %>%
+  dplyr::arrange(guild, n_loc_rank) %>%
+  knitr::kable(col.names = c("", "guild", "species", "# locations"))
 ```
+
+### Interaction turnover
 
@@
 interaction_list %>%
-    dplyr::group_by(!!pla_group_var, !!pol_group_var) %>%
-    dplyr::summarise(n_net = dplyr::n_distinct(net_name), 
-                     n_loc = dplyr::n_distinct(loc_name)) %>%
-    dplyr::group_by() %>%
-    dplyr::mutate(n_net_rank = dplyr::row_number(dplyr::desc(n_net)),
-                  n_loc_rank = dplyr::row_number(dplyr::desc(n_loc)))
-}
+  remove_unknown_species() %>% 
+  get_int_freq_by_group(pla_name, pol_name) %>% 
+  plot_freq_step() +
+  labs(litle = "locations per interactions", 
+       subtitle = "turnover of interactions in the Web of Life database")
+# 
+# interaction_list %>% 
+#   remove_unknown_species() %>% 
+#   get_int_freq_by_group(pla_genus, pol_genus) %>% 
+#   plot_freq_step() +
+#   ggtitle("locations per interactions (genus)")
+```
 
+```{r}
 interaction_list %>%
@@
   get_int_freq_by_group(pla_name, pol_name)  %>%
-  plot_freq_step() +
-  ggtitle("locations per interactions (species)")
-
-interaction_list %>% 
-  remove_unknown_species() %>% 
-  get_int_freq_by_group(pla_genus, pol_genus) %>% 
-  plot_freq_step() +
-  ggtitle("locations per interactions (genus)")
+  dplyr::filter(n_loc_rank <= 20) %>% 
+  dplyr::select(n_loc_rank, pla_name, pol_name, n_loc) %>%
+  dplyr::arrange(n_loc_rank) %>%
+  knitr::kable(col.names = c("", "plant", "pollinator", "# locations"), 
+               caption = 'Top 20 most "widespread" interactions')
 ```
-
-# Interactions turnover

### 2018-10-26 main.R
Adjust output directory of the markdown file

@@ -18,7 +18,8 @@ exploration_plan <- drake::drake_plan(
   species_list = get_species_list(networks, metadata), 
   interaction_list = get_interaction_list(networks, metadata),
   rmarkdown::render(input = drake::knitr_in("paper/data-exploration/turnover.Rmd"), 
-                    output_file = drake::file_out("paper/data-exploration/turnover.md"))
+                    output_file = drake::file_out("paper/data-exploration/turnover.md"),
+                    output_dir = "paper/data-exploration/")
 )
 
 full_plan <- rbind(

### 2018-10-26 paper/data-exploration/turnover.Rmd
Fix broken figures in exploration report

@@
   labs(title = "number of locations per species", 
-       subtitle = "turnover of species in the Web of Life database")
+       subtitle = "species turnover in the Web of Life database")
 
@@
   plot_freq_step() +
-  labs(litle = "locations per interactions", 
-       subtitle = "turnover of interactions in the Web of Life database")
+  labs(title = "locations per interactions", 
+       subtitle = "interactions turnover in the Web of Life database")
 # 

### 2018-10-26 main.R

@@ -17,9 +17,8 @@ read_data_plan <- drake::drake_plan(
 exploration_plan <- drake::drake_plan(
   species_list = get_species_list(networks, metadata), 
   interaction_list = get_interaction_list(networks, metadata),
-  rmarkdown::render(input = drake::knitr_in("paper/data-exploration/turnover.Rmd"), 
-                    output_file = drake::file_out("paper/data-exploration/turnover.md"),
-                    output_dir = "paper/data-exploration/")
+  my_render(drake::knitr_in("./paper/data-exploration/turnover.Rmd"), 
+            drake::file_out("./paper/data-exploration/turnover.md"))
 )
 
 full_plan <- rbind(

### 2018-10-26 paper/data-exploration/turnover.Rmd
Add thresholds to form focal species

@@
 
-species_list %>%
+sp_rank <- species_list %>%
   remove_unknown_species() %>% 
-  get_sp_freq_by_group(sp_name) %>% 
+  get_sp_freq_by_group(sp_name)
+
+sp_rank %>%
   plot_freq_step() +
+  geom_hline(yintercept = 4.5, size = 0.5, linetype = 2) +
   labs(title = "number of locations per species", 
-       subtitle = "species turnover in the Web of Life database")
+       subtitle = "species turnover in the Web of Life database", 
+       caption = "dashed line indicates the (arbitrary) threshold for selecting focal species")
 
-# species_list %>%
-#   remove_unknown_species() %>% 
-#   get_sp_freq_by_group(genus) %>%
-#   plot_freq_step()+
-#   ggtitle("number of locations per genus")
 ```
@@
 ```{r}
-species_list %>%
-  remove_unknown_species() %>% 
-  get_sp_freq_by_group(sp_name) %>%
+sp_rank %>% 
   dplyr::filter(n_loc_rank <= 10) %>%
@@
 
-interaction_list %>%
+int_rank <- interaction_list %>%
   remove_unknown_species() %>% 
-  get_int_freq_by_group(pla_name, pol_name) %>% 
+  get_int_freq_by_group(pla_name, pol_name)
+
+int_rank %>%
   plot_freq_step() +
+  geom_hline(yintercept = 2.9, size = 0.5, linetype = 2) +
   labs(title = "locations per interactions", 
-       subtitle = "interactions turnover in the Web of Life database")
-# 
-# interaction_list %>% 
-#   remove_unknown_species() %>% 
-#   get_int_freq_by_group(pla_genus, pol_genus) %>% 
-#   plot_freq_step() +
-#   ggtitle("locations per interactions (genus)")
+       subtitle = "interactions turnover in the Web of Life database", 
+       caption = "dashed line indicates the (arbitrary) threshold for selecting focal species")
 ```

### 2018-10-26 paper/data-exploration/turnover.Rmd
Add relationship between "widespreadness" and degree

@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE)
+knitr::opts_chunk$set(echo = FALSE, message = FALSE)
 ```
@@
 ```{r}
-interaction_list %>%
-  remove_unknown_species() %>% 
-  get_int_freq_by_group(pla_name, pol_name)  %>%
+int_rank %>%
   dplyr::filter(n_loc_rank <= 20) %>% 
@@
 ```
+
+### Degree vs. widespread
+
+```{r}
+degrees <- interaction_list %>%
+  dplyr::group_by(pla_name) %>%
+  dplyr::mutate(pla_deg = dplyr::n_distinct(pol_name)) %>%
+  dplyr::group_by(pol_name) %>%
+  dplyr::mutate(pol_deg = dplyr::n_distinct(pla_name))%>%
+  dplyr::group_by()
+
+guilds <- c("pla", "pol")
+
+sp_degree <- guilds %>%
+  purrr::map(~dplyr::select_at(degrees, dplyr::vars(dplyr::starts_with(.)))) %>%
+  purrr::map(~dplyr::distinct(.)) %>%
+  purrr::map_df(~`names<-`(., c("sp_name", "genus", "deg")), .id = "guild") %>%
+  dplyr::mutate(guild = factor(guild, labels = guilds), 
+                guild = as.character(guild)) %>%
+  remove_unknown_species()
+
+threshold <- 3
+# select species with interactions that occur in 3 locations or more
+sp_int_thres <- int_rank %>%
+  dplyr::filter(n_loc >= threshold) %>%
+  dplyr::select_at(dplyr::vars(dplyr::ends_with("name"))) %>%
+  tidyr::gather("guild", "sp_name", pla_name, pol_name) %>%
+  dplyr::mutate(guild = substr(guild, 1,3)) %>%
+  dplyr::distinct()
+
+# select species that occur in 3 locations or more
+sp_thres <- sp_rank %>%
+  dplyr::filter(n_loc >= 5) %>%
+  dplyr::select(guild, sp_name)
+
+selected_species <- dplyr::inner_join(sp_int_thres, sp_thres) %>%
+  dplyr::mutate(selected = TRUE)
+
+sp_deg_rank <- sp_rank %>%
+  dplyr::inner_join(sp_degree) %>% 
+  dplyr::left_join(selected_species) %>%
+  dplyr::mutate(selected = dplyr::if_else(is.na(selected), FALSE, selected)) 
+```
+
+```{r}
+require(ggplot2)
+require(ggrepel)
+
+sp_deg_rank %>%
+  ggplot(aes(x = deg, y = n_loc)) +
+  geom_point(aes(colour = selected, fill = selected, shape = guild)) +
+  geom_label_repel(data = dplyr::filter(sp_deg_rank, selected), 
+                  aes(label = sp_name), size = 3, fontface =  "italic",
+                  color = RColorBrewer::brewer.pal(3, "Paired")[2]) +
+  # scale_x_log10() +
+  scale_y_log10() +
+  scale_fill_manual(values = c(NA, RColorBrewer::brewer.pal(3, "Paired")[2])) +
+  scale_color_brewer(palette = "Paired") +
+  scale_shape_manual(values = c(21, 24)) +
+  guides(color = guide_legend("focal species"), 
+         fill = guide_legend("focal species")) +
+  theme_bw() +
+  theme(legend.position = c(0.02,0.98), 
+        legend.justification = c(0,1), 
+        legend.box = "horizontal") +
+  labs(title = "species degree vs. number of locations", 
+       subtitle = "there are 16 focal species, mostly generalist pollinators",
+       caption = "focal species are those that have the same interaction in >= 3 locations and are present >= 5 locations", 
+       y = "# locations", 
+       x = "species degree")
+
+sp_deg_rank %>%
+  dplyr::filter(selected) %>% 
+  dplyr::select(guild, sp_name, n_loc, deg) %>%
+  dplyr::arrange(guild, deg, n_loc) %>%
+  knitr::kable(col.names = c("guild", "species", "# locations", "degree"))
+```

### 2018-10-26 paper/data-exploration/turnover.Rmd
Log x axis

@@
                   color = RColorBrewer::brewer.pal(3, "Paired")[2]) +
-  # scale_x_log10() +
-  scale_y_log10() +
+  scale_x_log10() +
+  # scale_y_log10() +
   scale_fill_manual(values = c(NA, RColorBrewer::brewer.pal(3, "Paired")[2])) +

### 2018-10-29 paper/data-exploration/turnover.Rmd
higher dpi in figures
Remove tables, improve figures and add text explanation

@@
 
+# Interactions at the fringes, data exploration
+
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE, message = FALSE)
+knitr::opts_chunk$set(echo = FALSE, message = FALSE, dpi = 300)
 ```
@@
 
-We start by checking wether species (and interactions) occur in enough localities to be able to detect a change across the species ranges.
-
 ## Species & interaction turnover
 
-### Species turnover
+We start by checking wether species and interactions occur in enough localities. 
+Unknown and unindentified species are excluded from the final numbers.
+
+If species turnover is too high the data might not be adequate to answer the research question. 
+At first we set an arbitrary, but reasonable threshold of **five** locations. 
+We need species to be present in at least this number of locations to have a relatively OK coverage across their range.
+
+With this threshold of five we have 13 plants and 41 pollination species that could be candidates to be focal species.
 
@@
 
-plot_freq_step <- function(freq_df){
+th <- 5
+
+plot_freq_step <- function(freq_df, th = 5){
   if ("guild" %in% names(freq_df)){
@@
     scale_color_brewer(palette = "Paired", 
-                       labels = c("plants", "pollinators")) +
+                       aesthetics = c("colour", "fill")) +
+    scale_alpha_manual(values = c(0.5, 1)) +
+    scale_size_manual(values = c(0.5, 1)) +
     labs(x = "rank", 
          y = "# locations") +
-    theme(legend.position = c(0.99, 0.99), 
-          legend.justification = c(1,1))
+    theme(legend.position = c(0.98,0.98), 
+          legend.justification = c(1,1), 
+          legend.direction = "horizontal")
 }
@@
   remove_unknown_species() %>% 
-  get_sp_freq_by_group(sp_name)
+  get_sp_freq_by_group(sp_name)  %>%
+  dplyr::mutate(focal = n_loc >= th)
+
+n_sp <- sp_rank %>%
+  dplyr::group_by(guild, focal) %>%
+  dplyr::summarise(n_sp = dplyr::n_distinct(sp_name)) %>%
+  dplyr::mutate(label = paste(format(n_sp, big.mark = ","), guild)) %>%
+  dplyr::group_by() %>%
+  humanize()
 
 sp_rank %>%
+  dplyr::group_by() %>%
+  humanize() %>%
   plot_freq_step() +
-  geom_hline(yintercept = 4.5, size = 0.5, linetype = 2) +
+  geom_vline(data = n_sp, aes(xintercept = n_sp, 
+                              linetype = focal), 
+             size = 0.25, colour = "grey50") +
+  geom_text(data = n_sp, 
+            aes(label = label, x = n_sp, y = 15),
+            size = 3.5,
+            angle = 90, 
+            nudge_x = -0.05, show.legend = FALSE) +
+  geom_text(data = n_sp,
+            aes(label = focal, x = n_sp, y = 15), 
+            angle = 90, nudge_x = 0.05, colour = "grey30", 
+            size = 3) +
+  scale_linetype_manual(values = c(3,2)) +
+  guides(size = "none", linetype = "none") +
   labs(title = "number of locations per species", 
        subtitle = "species turnover in the Web of Life database", 
-       caption = "dashed line indicates the (arbitrary) threshold for selecting focal species")
+       caption = "we select as focal species those in 5 or more locations")
 
@@
 
-```{r}
-sp_rank %>% 
-  dplyr::filter(n_loc_rank <= 10) %>%
-  dplyr::select(n_loc_rank, guild, sp_name, n_loc) %>%
-  dplyr::arrange(guild, n_loc_rank) %>%
-  knitr::kable(col.names = c("", "guild", "species", "# locations"))
-```
+We then check the turnover of the interactions. 
+We expect a large degree of turnover here, but if we are to compare interactions at the fringes of a species distributions with those at the core, we need at some of the interactions to be sampled at several locations.
+These  would compose the "core" of the species interactions.
+At first we set an arbitrary, but reasonable threshold of **three** locations.
 
-### Interaction turnover
+With this threshold we have 44 interactions that repeat over at least three locations or more. 
+Specifically 22 plants and 31 pollinators are involved in these interactions.
 
@@
   remove_unknown_species() %>% 
-  get_int_freq_by_group(pla_name, pol_name)
+  get_int_freq_by_group(pla_name, pol_name) %>%
+  dplyr::mutate(focal = n_loc >= 3)
+
+n_int <- int_rank %>%
+  dplyr::group_by(focal) %>%
+  dplyr::summarise(n_int = dplyr::n_distinct(paste(pla_name, pol_name))) %>%
+  dplyr::mutate(label = paste(format(n_int, big.mark = ","), "int."))
+
+n_int_sp <- int_rank %>%
+  dplyr::filter(focal) %>%
+  dplyr::select_at(dplyr::vars(dplyr::contains("name"))) %>%
+  tidyr::gather("guild", "sp_name") %>%
+  dplyr::mutate(guild = substr(guild, 1,3)) %>%
+  dplyr::group_by(guild) %>%
+  dplyr::summarise(n_sp = dplyr::n_distinct(sp_name)) %>% {
+    l <- .
+    as.list(extract2(l, 2)) %>%
+      `names<-`(extract2(l, 1))
+  }
 
@@
   plot_freq_step() +
-  geom_hline(yintercept = 2.9, size = 0.5, linetype = 2) +
+  # geom_hline(yintercept = 2.9, size = 0.5, linetype = 2) +
+  geom_vline(data = n_int, aes(xintercept = n_int, 
+                                linetype = focal), 
+             size = 0.25, colour = "grey50", show.legend = F) +
+    scale_linetype_manual(values = c(3,2)) +
+  annotate(geom = "text", x = 46, y = 3.5, label = paste(n_int_sp[[1]], "plants and", n_int_sp[[2]], "pollinators with the\nsame int.
+in more than 3 locations"), size = 3, hjust = 0, colour = "grey30") +
   labs(title = "locations per interactions", 
        subtitle = "interactions turnover in the Web of Life database", 
-       caption = "dashed line indicates the (arbitrary) threshold for selecting focal species")
+       caption = "we select as focal species those with the same interaction in 3 or more locations")
 ```
 
-```{r}
-int_rank %>%
-  dplyr::filter(n_loc_rank <= 20) %>% 
-  dplyr::select(n_loc_rank, pla_name, pol_name, n_loc) %>%
-  dplyr::arrange(n_loc_rank) %>%
-  knitr::kable(col.names = c("", "plant", "pollinator", "# locations"), 
-               caption = 'Top 20 most "widespread" interactions')
+```{r, eval = F}
+selected <- int_rank %>%
+  dplyr::select(pla_name, pol_name, n_loc, focal) %>% 
+  tidyr::gather("guild", "sp_name", pla_name, pol_name) %>% 
+  dplyr::mutate(guild = substr(guild, 1,3),
+                focal_int = TRUE) %>% 
+  dplyr::group_by(guild, sp_name) %>%
+  dplyr::summarise(n_loc_int = mean(n_loc), 
+                   n_loc_max = max(n_loc),
+                   focal_int = any(focal), 
+                   n = n()) %>% 
+  dplyr::distinct() %>%
+  dplyr::left_join(sp_rank)
+
+selected %>% 
+  # dplyr::filter(focal, focal_int) %>%
+  ggplot(aes(x = n_loc, y = n_loc_int)) +
+  geom_point(aes(colour = log(n))) +
+  geom_label_repel(data = dplyr::filter(selected, focal, focal_int),
+                  aes(label = sp_name), size = 3, fontface =  "italic",
+                  color = RColorBrewer::brewer.pal(3, "Paired")[2]) 
 ```
@@
 
+median_deg <- sp_deg_rank %>%
+  dplyr::group_by(selected, guild) %>%
+  dplyr::summarise(deg = median(deg)) %>%
+  dplyr::mutate(focal = selected) %>%
+  dplyr::group_by() %>%
+  humanize()
+
 sp_deg_rank %>%
+  dplyr::group_by() %>%
+  humanize() %>%
   ggplot(aes(x = deg, y = n_loc)) +
+  geom_vline(data = median_deg, aes(xintercept = deg, colour = selected), 
+             size = 0.25, 
+             linetype = 2) +
+  geom_text(data = median_deg, 
+            aes(y = 20, 
+                label = paste("median", guild, "-", deg), 
+                color = selected),
+            nudge_x = -0.05,
+            angle = 90, 
+            size = 3) +
   geom_point(aes(colour = selected, fill = selected, shape = guild)) +
@@
        x = "species degree")
-
-sp_deg_rank %>%
-  dplyr::filter(selected) %>% 
-  dplyr::select(guild, sp_name, n_loc, deg) %>%
-  dplyr::arrange(guild, deg, n_loc) %>%
-  knitr::kable(col.names = c("guild", "species", "# locations", "degree"))
 ```

### 2018-10-29 paper/data-exploration/turnover.Rmd
Explore how number of focal species changes with the thershold

@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE, message = FALSE, dpi = 300)
+knitr::opts_chunk$set(echo = FALSE, message = FALSE, dpi = 300, fig.asp = 10/16)
 ```
@@
 
-```{r, eval = F}
-selected <- int_rank %>%
-  dplyr::select(pla_name, pol_name, n_loc, focal) %>% 
-  tidyr::gather("guild", "sp_name", pla_name, pol_name) %>% 
-  dplyr::mutate(guild = substr(guild, 1,3),
-                focal_int = TRUE) %>% 
-  dplyr::group_by(guild, sp_name) %>%
-  dplyr::summarise(n_loc_int = mean(n_loc), 
-                   n_loc_max = max(n_loc),
-                   focal_int = any(focal), 
-                   n = n()) %>% 
+Combining these two thresholds
+
+ * Only species with interactions that were sampled in three locations or more
+ * Only species sampled in 5 locations or more
+
+we have 16 focal species for which enough interaction data could be obtained from Bascompte's Web of Life. Four plants and 12 pollinators.
+
+Now let's have a little look at how these numbers depend on the chosen threshold.
+
+```{r}
+drake::loadd(focal_species_options)
+
+focal_species_options %>%
+  dplyr::group_by(int_threshold, sp_threshold, guild) %>%
+  dplyr::summarise(n = n()) %>% 
+  dplyr::group_by(int_threshold, sp_threshold) %>%
+  dplyr::mutate(n_total = sum(n), 
+                label = paste(format(n_total, big.mark = ","), "spp."),
+                label2 = paste(format(n, big.mark = ","), guild), 
+                label2 = paste(label2, collapse = "+")) %>%
+  dplyr::select(-guild) %>%
   dplyr::distinct() %>%
-  dplyr::left_join(sp_rank)
-
-selected %>% 
-  # dplyr::filter(focal, focal_int) %>%
-  ggplot(aes(x = n_loc, y = n_loc_int)) +
-  geom_point(aes(colour = log(n))) +
-  geom_label_repel(data = dplyr::filter(selected, focal, focal_int),
-                  aes(label = sp_name), size = 3, fontface =  "italic",
-                  color = RColorBrewer::brewer.pal(3, "Paired")[2]) 
+  humanize() %>%
+  ggplot(aes(x = int_threshold, y = sp_threshold)) +
+  geom_tile(aes(fill = n_total)) +
+  geom_text(aes(label = label), 
+            size = 3, 
+            fontface = "bold", 
+            nudge_y = 0.2, 
+            color = "white") +
+  geom_text(aes(label = label2), 
+            size = 3, 
+            nudge_y = -0.2, 
+            color = "white") +
+  geom_tile(aes(x = 3, y = 5), fill = NA, colour = "white", linetype = 2) +
+  scale_fill_continuous(trans = "log10") +
+  coord_cartesian(ylim = c(1,10)) +
+  scale_x_continuous(expand = c(0,0)) +
+  scale_y_continuous(breaks = 1:10) +
+  theme_bw() +
+  labs(title = "number of focal species", 
+       subtitle = "number of plants and pollinators using different thresholds", 
+       x = "repeated interaction threshold", 
+       y = "species location threshold", 
+       fill = "# spp.", 
+       caption = "dashed box indicate thresholds used here")
 ```
@@
 ### Degree vs. widespread
+
+Let's have a closer look at the chosen thresholds of 5 and 3. 
+I'm a bit worried that we're only selecting super generalist species and hence results might be biased. 
+We can see that indeed the overall species degree of the focal species is considerably larger than that of non-focal.
+We have still a decent range between 6 for *Fuchia regia* and like 400 for *Apis melifera*.
 
@@
         legend.justification = c(0,1), 
-        legend.box = "horizontal") +
+        legend.box = "horizontal", 
+        legend.direction = "horizontal") +
   labs(title = "species degree vs. number of locations", 

### 2018-10-29 code/exploration.R

@@ -67,3 +67,74 @@ get_int_freq_by_group <- function(interaction_list, pla_group, pol_group){
     dplyr::mutate(n_net_rank = dplyr::row_number(dplyr::desc(n_net)),
                   n_loc_rank = dplyr::row_number(dplyr::desc(n_loc)))
 }
+
+#x is a dataframe
+humanize <- function(x){
+  if ("guild" %in% names(x)) {
+    x %<>%
+      dplyr::mutate(guild = dplyr::case_when(
+        guild == "pla" ~ "plants", 
+        TRUE ~ "pollinators"
+      ))
+  }
+  if ("focal" %in% names(x)) {
+    x %<>%
+      dplyr::mutate(focal = dplyr::if_else(focal, 
+                                           "selected", 
+                                           "not-selected"))
+  }
+  x
+}
+
+get_focal_species_options <- function(species_list, interaction_list, categ = "loc") {
+  filter_var <- paste0("n_", categ)
+  
+  sp_rank <- species_list %>%
+    remove_unknown_species() %>% 
+    get_sp_freq_by_group(sp_name) 
+  
+  sp_values <- sp_rank %>%
+  {x <- .; unique(x[filter_var])} %>%
+    extract2(1)
+  
+  int_rank <- interaction_list %>%
+    remove_unknown_species() %>% 
+    get_int_freq_by_group(pla_name, pol_name)
+  
+  int_values <- int_rank %>%
+  {x <- .; unique(x[filter_var])} %>%
+    extract2(1)
+  
+  list(sp_threshold = sp_values, int_threshold = int_values) %>%
+    purrr::cross() %>%
+    purrr::map_df(purrr::lift(get_focal_species), 
+                  sp_rank = sp_rank, int_rank = int_rank, filter_var = filter_var)
+}
+
+# get focal
+get_focal_species <- function(sp_threshold, int_threshold, sp_rank, int_rank, filter_var){
+  
+  sp <- sp_rank %>%
+    dplyr::group_by() %>%
+    {d <- . ; d[d[filter_var] >= sp_threshold, ]} %>% 
+    dplyr::select(guild, sp_name)
+  
+  int <- int_rank %>%
+    dplyr::group_by() %>%
+    {d <- . ; d[d[filter_var] >= int_threshold, ]} %>% 
+    dplyr::select(pla_name, pol_name) %>%
+    gather_pla_pol() %>% 
+    dplyr::distinct()
+  
[…]

### 2018-10-29 main.R

@@ -17,6 +17,8 @@ read_data_plan <- drake::drake_plan(
 exploration_plan <- drake::drake_plan(
   species_list = get_species_list(networks, metadata), 
   interaction_list = get_interaction_list(networks, metadata),
+  # the thresholds are specificied on the number of locations a species is
+  focal_species_options = get_focal_species_options(species_list, interaction_list, categ = "loc"), 
   my_render(drake::knitr_in("./paper/data-exploration/turnover.Rmd"), 
             drake::file_out("./paper/data-exploration/turnover.md"))
 )

### 2018-10-29 paper/data-exploration/turnover.Rmd
Add number of GBIF georef records per species

@@
 
-### Degree vs. widespread
+## Degree vs. widespread
 
@@
 ```
+
+## Data completeness
+
+```{r}
+drake::loadd(n_occurrences)
+
+n_occurrences %>%
+  dplyr::group_by(sp_name, n, guild, n_occurrences) %>%
+  dplyr::do(canon_name = unlist(.$backbones[[1]]$canonicalName)) %>% 
+  dplyr::group_by() %>%
+  dplyr::mutate(sp_name = forcats::fct_reorder(sp_name, n), 
+                n_occurrences = dplyr::if_else(sp_name != canon_name, 
+                                               NA_integer_, 
+                                               as.integer(n_occurrences))) %>%
+  humanize() %>%
+  ggplot(aes(y = n_occurrences, x = sp_name, colour = guild)) +
+  geom_point() +
+  geom_segment(aes(xend = sp_name, yend = 0)) +
+  scale_y_log10() +
+  coord_flip() +
+  scale_color_brewer(palette = "Paired") +
+  theme_bw() +
+  theme(axis.text.y = element_text(face = "italic", size = 6)) +
+  labs(x = "", y = "# occurrences", 
+       title = "GBIF occurrences", 
+       subtitle = "number of GBIF georeferenced records per species", 
+       caption = "species ordered by how likely they are to be included as focal species")
+```

### 2018-10-29 code/exploration.R

@@ -138,3 +138,37 @@ gather_pla_pol <- function(x){
     tidyr::gather("guild", "sp_name", pla_name, pol_name) %>%
     dplyr::mutate(guild = substr(guild, 1,3))
 }
+
+# get a list of species for which extra GBIF information will be downloaded
+get_sp_extra_info <- function(focal_species_options, threshold){
+  focal_species_options %>%
+    dplyr::group_by(guild, sp_name) %>%
+    dplyr::summarise(n = n()) %>%
+    dplyr::filter(n > threshold) %>% 
+    dplyr::group_by() %>%
+    dplyr::arrange(desc(n))
+  }
+
+# get sp backbones
+get_sp_backbones <- function(sp_list_extra_info){
+  backbones <- sp_list_extra_info %>%
+    split(.$sp_name) %>%
+    purrr::map_df(~ tibble::data_frame(backbones = list(rgbif::name_backbone(.$sp_name))), .id = "sp_name") 
+  
+  dplyr::right_join(
+    sp_list_extra_info, 
+    backbones)
+}
+
+# get sp n_ocurrences
+get_n_ocurrences <- function(backbones){
+  n_occurences <- backbones %>% {
+    x <- . ; 
+    extract2(x, "backbones") %>%
+      purrr::map(~ .$speciesKey) %>%
+      `names<-`(x$sp_name)
+  } %>%
+    purrr::map_df(~ tibble::data_frame(n_occurrences = rgbif::occ_count(., georeferenced = TRUE)), .id = "sp_name")
+  
+  dplyr::right_join(backbones, n_occurences) 
+}

### 2018-10-29 main.R

@@ -19,6 +19,9 @@ exploration_plan <- drake::drake_plan(
   interaction_list = get_interaction_list(networks, metadata),
   # the thresholds are specificied on the number of locations a species is
   focal_species_options = get_focal_species_options(species_list, interaction_list, categ = "loc"), 
+  sp_list_extra_info = get_sp_extra_info(focal_species_options, 10),
+  backbones = get_sp_backbones(sp_list_extra_info),
+  n_occurrences = get_n_ocurrences(backbones),
   my_render(drake::knitr_in("./paper/data-exploration/turnover.Rmd"), 
             drake::file_out("./paper/data-exploration/turnover.md"))
 )

### 2019-05-08 paper/data-exploration/turnover.Rmd

--- 2018-10-29 paper/data-exploration/turnover.Rmd
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE, message = FALSE, dpi = 300, fig.asp = 10/16)
+knitr::opts_chunk$set(echo = FALSE, message = FALSE, dpi = 300, fig.asp = 10/16, warning = FALSE)
 ```
@@
 ```
+
+## Data completeness
+
+```{r}
+drake::loadd(n_occurrences)
+
+n_occurrences %>%
+  dplyr::group_by(sp_name, n, guild, n_occurrences) %>%
+  dplyr::do(canon_name = unlist(.$backbone[[1]]$canonicalName)) %>% 
+  dplyr::group_by() %>%
+  dplyr::mutate(sp_name = forcats::fct_reorder(sp_name, n), 
+                n_occurrences = dplyr::if_else(sp_name != canon_name, 
+                                               NA_integer_, 
+                                               as.integer(n_occurrences))) %>%
+  humanize() %>%
+  ggplot(aes(y = n_occurrences, x = sp_name, colour = guild)) +
+  geom_point() +
+  geom_segment(aes(xend = sp_name, yend = 0)) +
+  scale_y_log10() +
+  coord_flip() +
+  scale_color_brewer(palette = "Paired") +
+  theme_bw() +
+  theme(axis.text.y = element_text(face = "italic", size = 6)) +
+  labs(x = "", y = "# occurrences", 
+       title = "GBIF occurrences", 
+       subtitle = "number of GBIF georeferenced records per species", 
+       caption = "species ordered by how likely they are to be included as focal species")
+```
+
+```{r, fig.asp=3}
+drake::loadd(maps)
+
+selected_sp_map <- n_occurrences %>%
+  dplyr::slice(1:28) %>%
+  extract2("sp_name")
+maps %>% 
+  dplyr::filter(layer != 0, 
+                sp_name %in% selected_sp_map) %>%
+  ggplot(aes(x,y)) +
+  # mapWorld +
+  geom_tile(aes(fill = layer)) +
+  coord_quickmap() +
+  theme_bw() +
+  facet_wrap(~ sp_name, ncol = 2) +
+  theme(legend.position = "none")
+```

### 2019-05-09 paper/draft-info.Rmd
Add paper skeleton

---
title: "Draft information"
subtitle: "version: draft-0.0"
date: "20xx"
# bibliography: phd-bibliography/pollen-competition.bib
csl: ecology-letters.csl
output:
  bookdown::pdf_document2:
    # base_format: rticles::peerj_article
    keep_tex: yes
    number_sections: false
toc: false
geometry: 
  - textwidth=33em
  - textheight=48\baselineskip
# classoption: twocolumn
header-includes:
  - \usepackage{booktabs}
  - \usepackage{setspace}
  - \usepackage{lineno}
  - \usepackage{xr}
  - \usepackage[utf8]{inputenc}
  - \newcommand{\R}[1]{\label{#1}\linelabel{#1}}
  - \newcommand{\lr}[1]{page~\pageref{#1}, line~\lineref{#1}}
  - \externaldocument[M-]{manuscript}

---

\onehalfspacing

## Requests to coauthors

* Specify grant numbers in the Acknowledgements and make sure the ones stated there now are correct. 
* Suggestions to bring the abstract down to 150 words.
* Approve (or not) for submission.

### 2019-05-09 paper/manuscript.Rmd
Add paper skeleton

---
title: "XX"
author: 
  - "E. Fernando Cagua^1^ ([efc29@uclive.ac.nz](mailto:efc29@uclive.ac.nz))"
  - "Audrey Lustig^2^ ([audrey.lustig@canterbury.ac.nz](audrey.lustig@canterbury.ac.nz))"
  - "Jason M. Tylianakis^1^ ([jason.tylianakis@canterbury.ac.nz](jason.tylianakis@canterbury.ac.nz))"
  - "Daniel B. Stouffer^1^ ([daniel.stouffer@canterbury.ac.nz](daniel.stouffer@canterbury.ac.nz))"
# bibliography: phd-bibliography/pollen-competition.bib
csl: ecology-letters.csl
output: #word_document
  bookdown::pdf_document2:
    # base_format: rticles::peerj_article
    keep_tex: yes
    number_sections: false
toc: false
fontsize: 11pt
# classoption: a4paper
geometry: 
  - textwidth=33em
  - textheight=48\baselineskip
header-includes:
  - \usepackage{booktabs}
  - \usepackage{setspace}
  - \usepackage{lineno}
  - \usepackage{xr}
  - \usepackage[utf8]{inputenc}
  - \newcommand{\R}[1]{\label{#1}\linelabel{#1}}
  - \newcommand{\lr}[1]{page~\pageref{#1}, line~\lineref{#1}}
  - \externaldocument[S-]{supp-info}
  - \usepackage[export]{adjustbox}
---

\linenumbers
\doublespacing

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, 
                      warning = FALSE, dpi = 300)

loadd(abs_wordcount, msc_wordcount, n_displays, n_references, keywords)
```

^1^ Centre for Integrative Ecology, School of Biological Sciences, University of Canterbury, Private Bag 4800, Christchurch 8041, New Zealand

^2^ Geospatial Research Institute, University of Canterbury, Private Bag 4800, Christchurch 8041, New Zealand

**Running title:** XX

**Keywords:** `r keywords`

**Type of article:** XX

**Number of words:** `r abs_wordcount$n_words_stri` in abstract; `r format(round(msc_wordcount$n_words_stri), big.mark = ",")` in main text.

**Number of displays:** `r n_displays$figures` figures; `r n_displays$tables` tables; `r n_displays$text_boxes` text boxes.

**Number of references:** `r n_references`

**Author for correspondence:** E. Fernando Cagua (+64 20 4026 8153).

**Data accessibility:** Data supporting the results will be accessible in an appropriate data repository after publication. The DOI will be included here.

**Author contributions:** XX

\clearpage

# Abstract

`r paste(drake::readd(abstract), collapse = "")`

\clearpage

# Introduction

# Methods

# Results

# Discussion

# Acknowledgements

`r paste(drake::readd(acknowledgements), collapse = "")`

# References

### 2019-05-09 paper/supp-info.Rmd
Add paper skeleton

---
title: "The pollination trade-off"
# DBS: The title above needs editing to match the final version in the paper
subtitle: "Supplementary information"
author: "E. Fernando Cagua, Hugo J. Marrero, Jason M. Tylianakis, Daniel B. Stouffer"
# bibliography: references.bib
csl: ecology-letters.csl
documentclass: book
output: 
  bookdown::pdf_document2: 
    keep_tex: yes
    toc: false
header-includes:
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
  - \usepackage{xcolor}
editor_options: 
  chunk_output_type: console
---

<!-- To add an S before each figure and table -->
\renewcommand\thefigure{S\arabic{figure}}    
\setcounter{figure}{0}

\renewcommand\thetable{S\arabic{table}}    
\setcounter{table}{0}

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, 
                      warning = FALSE)
options(xtable.comment = FALSE, 
        xtable.caption.placement = 'bottom',
        xtable.size = 'small',
        booktabs = TRUE, 
        knitr.kable.NA = "-")
```

### 2019-05-09 code/paper_compilation.R

@@ -1,0 +1,142 @@
+# count words in a file
+count_words <- function(filename = "", lines_to_ignore = NULL, remove_md_headings = TRUE){
+  text_lines <- readLines(filename)
+  if (!is.null(lines_to_ignore)) {
+    text_lines <- text_lines[-lines_to_ignore]
+  }
+  if (remove_md_headings) {
+    heading_lines <- which(grepl("^#", text_lines))
+    if (length(heading_lines) > 0) {
+      text_lines <- text_lines[-heading_lines]
+    }
+  }
+  text_to_count <- paste(text_lines,
+                         collapse = " ")
+  get_text_stats(text_to_count)
+}
+
+# get stats of a text
+get_text_stats <- function(text){
+  text <- prep_text(text)
+  n_char_tot <- sum(stringi::stri_stats_latex(text)[c(1, 3)])
+  n_words_stri <- unname(stringi::stri_stats_latex(text)[4])
+  wpm <- 200
+  reading_time_stri <- ceiling(n_words_stri/wpm)
+  return(list(n_char_tot_stri = n_char_tot, n_words_stri = n_words_stri,
+              reading_time_stri = reading_time_stri))
+}
+
+prep_text <- function(text) {
+  text <- gsub("[\r\n]", " ", text)
+  text <- gsub("---.*--- ", "", text)
+  text <- gsub("```\\{.+?\\}.+?```", "", text)
+  text <- gsub("`r.+?`", "", text)
+  text <- gsub("<!--.+?-->", "", text)
+  text <- gsub("\\(http.+?\\)", "", text)
+  text <- gsub("!\\[.+?\\)", "", text)
+  text <- gsub("#*", "", text)
+  text <- gsub("<.+?>|</.+?>", "", text)
+  text <- gsub("%", "", text)
+  if (nchar(text) == 0) {
+    stop("You have not selected any text. Please select some text with the mouse and try again")
+  }
+  else {
+    return(text)
+  }
+}
+
+
+get_citations <- function(filename, lines_to_ignore = NULL, refs_to_exclude = NULL, refs_to_include = NULL){
+  text_lines <- readLines(filename)
+  if (!is.null(lines_to_ignore)) {
+    text_lines <- text_lines[-lines_to_ignore]
+  }
+  
+  citations <- text_lines %>%
+    stringr::str_extract("@\\w+") %>%
+    na.omit()
+  
+  if (!is.null(refs_to_exclude)) {
[…]

### 2019-05-09 code/plotting_and_formatting.R

@@ -1,0 +1,60 @@
+pub_theme <- function(){
+  theme_bw() +
+    theme(text = element_text(size = 8),
+          title = element_text(size = 8),
+          axis.title = element_text(size = 7),
+          plot.title = element_text(size = 7, face = "bold", margin = margin(b = 0)),
+          plot.subtitle = element_text(size = 7),
+          plot.tag = element_text(size = 7),
+          strip.background = element_blank(),
+          strip.text = element_text(hjust = 0),
+          legend.title = element_text(hjust = 0.5),
+          legend.key.size = unit(3, "mm"),
+          legend.margin = margin(),
+          axis.ticks.x = element_line(colour = "grey30", size = 0.05),
+          axis.ticks.y = element_line(colour = "grey30", size = 0.25),
+          # panel.border = element_blank(),
+          # axis.line.y = element_line(),
+          panel.grid = element_blank(),
+          panel.background = element_blank(),
+          plot.background = element_blank())
+}
+
+width <- function(type, unit=NULL){
+  # Ecology letters has a paper width of 200 mm
+  widths <- dplyr::case_when(
+    type == "single" ~ 3.57,
+    TRUE ~ 7.49
+  )
+  if(is.null(unit)) return(widths)
+  else if (unit=="in") {
+    widths %>%
+      as.character() %>%
+      paste0("in")
+  }
+}
+
+remove_legend <- function(x){
+  require(ggplot2)
+  x + theme(legend.position = 'none')
+}
+
+common_graphic_metrics <- function(){
+  list(
+    pal_rb3 = RColorBrewer::brewer.pal(4, "Greys")[c(3,1,2)],
+    pal_el_green = colorRampPalette(c("#d9e6cb", "#9fc17c", "#0d1108"), bias = 1, space = "rgb",
+                                    interpolate = "linear", alpha = FALSE)(9),
+    size_errorbars =  0.20,
+    color_errorbars = "grey30",
+    color_errorbars_light = "grey75",
+    log1p_axis_breaks_10 = c(0, 10, 100, 1000, 10000),
+    point_size = 1,
+    color_references = "grey50",
+    size_references = 0.25,
+    fill_rows = "grey95"
+  )
+}
+
+cgm <- function(){
+  common_graphic_metrics()
+}

### 2019-05-09 main.R

@@ -1,19 +1,20 @@
 # Prepare workspace -------------------------------------------------------
 
-pkgconfig::set_config("drake::strings_in_dots" = "literals")
+pkgconfig::set_config("strings_in_dots" = "literals")
 
 library(magrittr)
+library(drake)
 
 # load functions
 f <- lapply(list.files("code", full.names = T), source)
 
 
-read_data_plan <- drake::drake_plan(
+read_data_plan <- drake_plan(
   networks = read_networks(network_folder = "./data/raw/web-of-life_2018-10-23_042854"),
-  metadata = read_metadata(drake::file_in("./data/raw/web-of-life_2018-10-23_042854/references.csv"))
+  metadata = read_metadata(file_in("./data/raw/web-of-life_2018-10-23_042854/references.csv"))
 )
 
-exploration_plan <- drake::drake_plan(
+exploration_plan <- drake_plan(
   species_list = get_species_list(networks, metadata), 
   interaction_list = get_interaction_list(networks, metadata),
   # the thresholds are specificied on the number of locations a species is
@@ -22,14 +23,32 @@ exploration_plan <- drake::drake_plan(
   backbones = get_sp_backbones(sp_list_extra_info),
   n_occurrences = get_n_ocurrences(backbones),
   maps = fetch_maps(backbones),
-  my_render(drake::knitr_in("./paper/data-exploration/turnover.Rmd"), 
-            drake::file_out("./paper/data-exploration/turnover.md"))
+  turnover_exploration = my_render(knitr_in("./paper/data-exploration/turnover.Rmd"), 
+            file_out("./paper/data-exploration/turnover.md"))
+)
+
+
+reporting_plan <- drake_plan(
+  abstract = readLines(file_in("./paper/abstract.md")),
+  keywords = process_keywords(file_in("./paper/keywords.md")),
+  acknowledgements = readLines(file_in("./paper/acknowledgements.md")),
+  intro_line_number = get_line_number(file_in("paper/manuscript.Rmd"), "# Introduction"),
+  abs_wordcount = count_words(file_in("paper/abstract.md")),
+  msc_wordcount = count_words(file_in('paper/manuscript.Rmd'), lines_to_ignore = 1:intro_line_number),
[…]

### 2019-05-25 code/get-data-references.R
Get a doi for each reference in the data

@@ -1,0 +1,26 @@
+get_int_ref_dois <- function(int_metadata){
+  require(dplyr)
+  
+  refs <- int_metadata %>%
+    dplyr::mutate(published = is_reference_published(reference)) %>%
+    dplyr::filter(published) %$%
+    reference %>%
+    unique() 
+  
+  dois <- refs %>% 
+    purrr::map_df(~ rcrossref::cr_works(query = ., 
+                                     limit = 1, 
+                                     sort = "score", 
+                                     select = "DOI")$data)
+  
+  dois %>%
+    mutate(reference = refs) %>%
+    rename(likely_doi = doi)
+  
+}
+
+# determine if a reference (string) is likely published
+is_reference_published <- function(reference){
+  reference %>%
+    stringr::str_detect("unpubl", negate = TRUE)
+}

### 2019-05-25 main.R

@@ -57,6 +57,14 @@ download_ocurrence_data_plan <- drake_plan(
 )
 
 
+# Referencing -------------------------------------------------------------
+
+data_references_plan <- drake_plan(
+  interaction_references = get_int_ref_dois(int_metadata), 
+  dois_csv = readr::write_csv(interaction_references, 
+                              file_out("data/int_data_references.csv"))
+)
+
 # exploration------
 
 read_data_plan <- drake_plan(
@@ -109,7 +117,8 @@ paper_plan <- rbind(
   configuration_plan,
   get_data_plan,
   pre_process_int_plan,
-  download_ocurrence_data_plan
+  download_ocurrence_data_plan, 
+  data_references_plan
 )
 
 

### 2019-05-25 paper/manuscript.Rmd
Some basic methods

@@
 
+```{r}
+loadd(config)
+loadd(int_metadata)
+n_published_studies <- int_metadata$reference %>%
+  unique() %>%
+  stringr::str_detect(pattern = "unpubl", negate = TRUE) %>%
+  sum()
+```
+
+We downloaded plant pollinator networks from the Web of Life up to `r format(as.Date(config$raw_data_retrieved), "%b %d, %Y")`. 
+This included pollination networks from `r n_published_studies` studies which included plant-pollinator interactions in `r dplyr::n_distinct(int_metadata$loc_id)` independent locations (Figure X).
+
 # Results

### 2019-05-25 main.R
Formatting changes

@@ -22,8 +22,9 @@ get_web_of_life_pollination_networks_plan <- drake_plan(
   # the targed gets reevaluated if the date in the config file is changed
   wol_pol_networks = get_wol_networks(int_type = "plant-pollinator",
                                       download_date = data_download_date), 
-  wol_zip_file = download_wol_network_zip(wol_pol_networks, 
-                                          file_out("data/web-of-life_plant-pollinator.zip"))
+  wol_zip_file = download_wol_network_zip(
+    wol_pol_networks, 
+    file_out("data/web-of-life_plant-pollinator.zip"))
 )
 
 get_data_plan <- rbind(
@@ -33,7 +34,8 @@ get_data_plan <- rbind(
 # Pre-process interaction data --------------------------------------------
 
 pre_process_wol <- drake_plan(
-  wol_data_raw = read_wol_data(file_in("data/web-of-life_plant-pollinator.zip")),
+  wol_data_raw = read_wol_data(
+    file_in("data/web-of-life_plant-pollinator.zip")),
   wol_data = pre_process_wol_data(wol_data_raw), 
   wol_spp = get_wol_species_list(wol_data), 
   wol_int = get_wol_interaction_list(wol_data)

### 2019-05-26 paper/manuscript.Rmd
Add references for data sources of web of life

@@
   - "Daniel B. Stouffer^1^ ([daniel.stouffer@canterbury.ac.nz](daniel.stouffer@canterbury.ac.nz))"
-# bibliography: phd-bibliography/pollen-competition.bib
-csl: ecology-letters.csl
+bibliography: 
+  - bibliography.bib
+  - int-bibliography.bib
+# csl: ecology-letters.csl
 output: #word_document
@@
 loadd(int_metadata)
+loadd(interaction_citations)
+
 n_published_studies <- int_metadata$reference %>%
@@
   sum()
+
+all_int_cites <- paste0("@", interaction_citations$BIBTEXKEY) %>%
+  glue::glue_collapse(sep = "; ") %>%
+  paste0("[", ., "]")
 ```
@@
 This included pollination networks from `r n_published_studies` studies which included plant-pollinator interactions in `r dplyr::n_distinct(int_metadata$loc_id)` independent locations (Figure X).
+
+Studies are `r all_int_cites`
 

### 2019-05-26 main.R

@@ -93,6 +93,11 @@ reporting_plan <- drake_plan(
     command = get_bibliography("https://raw.githubusercontent.com/efcaguab/phd-bibliography/master/interactions%2Bsdm.bib",
                                file_out("paper/bibliography.bib"))
   ),
+  interaction_bibliography = target(
+    command = get_bibliography("https://raw.githubusercontent.com/efcaguab/phd-bibliography/master/interactions%2Bsdm_interaction-data-references.bib", 
+                               file_out("paper/int-bibliography.bib"))
+  ),
+  interaction_citations = bib2df::bib2df(file_in("paper/int-bibliography.bib")),
   abstract = readLines(file_in("./paper/abstract.md")),
   keywords = process_keywords(file_in("./paper/keywords.md")),
   acknowledgements = readLines(file_in("./paper/acknowledgements.md")),

### 2019-05-26 paper/manuscript.Rmd
Include data citations in the total citation count

@@
 loadd(abs_wordcount, msc_wordcount, n_displays, n_references, keywords)
+loadd(interaction_citations)
 ```
@@
 
-**Number of references:** `r n_references`
+**Number of references:** `r n_references + nrow(interaction_citations)`
 
@@
 loadd(int_metadata)
-loadd(interaction_citations)
 

### 2019-05-26 paper/manuscript.Rmd
Add worldmap of study sites

@@
 knitr::opts_chunk$set(echo = FALSE, message = FALSE, 
-                      warning = FALSE, dpi = 300)
+                      warning = FALSE, dpi = 300, 
+                      eval.after = "fig.cap")
 
@@
 
-all_int_cites <- paste0("@", interaction_citations$BIBTEXKEY) %>%
-  glue::glue_collapse(sep = "; ") %>%
-  paste0("[", ., "]")
 ```
@@
 
-Studies are `r all_int_cites`
+```{r, fig.cap=paste("Graph of", all_int_cites, "data points")}
+loadd(fig_worldmap)
+
+all_int_cites <- paste0("@", interaction_citations$BIBTEXKEY) %>%
+  glue::glue_collapse(sep = "; ") %>%
+  paste0("[", ., "]")
+
+fig_worldmap
+```
+
+Studies are
 

### 2019-05-26 code/figures.R

@@ -1,0 +1,20 @@
+plot_worldmap <- function(world_land, int_metadata){
+  require(ggplot2)
+  
+  p <- ggplot(world_land) +
+    geom_sf(size = 0.5, fill = "antiquewhite", colour = "antiquewhite4") +
+    geom_point(data = int_metadata,
+               aes(x = lon, y = lat),
+               shape = 21,
+               fill = "white") +
+    coord_sf(expand = FALSE) +
+    # pub_theme() +
+    theme(panel.grid = element_line(linetype = "dashed", colour = gray(0.5), size = 0.25), 
+          axis.title = element_blank(), 
+          panel.background = element_rect(fill = "aliceblue"), 
+          plot.title = element_text(size = 7, face = "bold", margin = margin(b = 0)),
+          plot.subtitle = element_text(size = 7)) +
+    labs(title = "Location of interaction networks")
+  
+  p
+}

### 2019-05-26 main.R

@@ -67,6 +67,14 @@ data_references_plan <- drake_plan(
                               file_out("data/int_data_references.csv"))
 )
 
+
+# Figures -----------------------------------------------------------------
+
+figures_plan <- drake_plan(
+  world_land = rnaturalearth::ne_download(type = "land", category = "physical", returnclass = "sf"),
+  fig_worldmap = plot_worldmap(world_land, int_metadata)
+)
+
 # exploration------
 
 read_data_plan <- drake_plan(
@@ -125,7 +133,8 @@ paper_plan <- rbind(
   get_data_plan,
   pre_process_int_plan,
   download_ocurrence_data_plan, 
-  data_references_plan
+  data_references_plan, 
+  figures_plan
 )
 
 

### 2019-05-27 code/figures.R
Make map look pretty(er)

@@ -2,19 +2,19 @@ plot_worldmap <- function(world_land, int_metadata){
   require(ggplot2)
   
   p <- ggplot(world_land) +
-    geom_sf(size = 0.5, fill = "antiquewhite", colour = "antiquewhite4") +
+    geom_sf(fill = cgm()$pal_rb3[2], colour = "antiquewhite4", 
+            lwd = 0.25) +
     geom_point(data = int_metadata,
                aes(x = lon, y = lat),
                shape = 21,
-               fill = "white") +
+               fill = "white", 
+               size = 1, 
+               color = cgm()$pal_el_green[9]) +
     coord_sf(expand = FALSE) +
-    # pub_theme() +
+    pub_theme() +
     theme(panel.grid = element_line(linetype = "dashed", colour = gray(0.5), size = 0.25), 
-          axis.title = element_blank(), 
-          panel.background = element_rect(fill = "aliceblue"), 
-          plot.title = element_text(size = 7, face = "bold", margin = margin(b = 0)),
-          plot.subtitle = element_text(size = 7)) +
-    labs(title = "Location of interaction networks")
+          axis.title = element_blank()) +
+    labs(title = "Geographic location of pollination communities")
   
   p
 }

### 2019-05-27 code/plotting_and_formatting.R

@@ -23,14 +23,15 @@ pub_theme <- function(){
 width <- function(type, unit=NULL){
   # Ecology letters has a paper width of 200 mm
   widths <- dplyr::case_when(
-    type == "single" ~ 3.57,
-    TRUE ~ 7.49
+    type == "single" ~ 3.23,
+    type == "double" ~ 6.81,
+    TRUE ~ 4.33
   )
   if(is.null(unit)) return(widths)
   else if (unit=="in") {
     widths %>%
       as.character() %>%
-      paste0("in")
+      paste0('in')
   }
 }
 

### 2019-05-27 paper/manuscript.Rmd
Use readd instead of loadd for figures
Use PNAS csl

@@
   - int-bibliography.bib
-# csl: ecology-letters.csl
+csl: pnas.csl
 output: #word_document
@@
 ```{r, fig.cap=paste("Graph of", all_int_cites, "data points")}
-loadd(fig_worldmap)
+readd(fig_worldmap)
 
@@
 
-fig_worldmap
 ```

### 2019-05-27 paper/manuscript.Rmd
Fix caption map figure

@@
 
-```{r, fig.cap=paste("Graph of", all_int_cites, "data points")}
+```{r fig-worldmap, fig.width = width('single'), fig.cap = paste("Worldwide distribution of pollination communities included in this study.
+We compile data from", length(interaction_citations$BIBTEXKEY), "published studies", all_int_cites, "which contain interaction information between plant and their pollinators at", dplyr::n_distinct(int_metadata$loc_id), "distinct locations.")}
 readd(fig_worldmap)

### 2019-05-27 paper/manuscript.Rmd
Edit methods to specify networks were put together when on the same place

@@
 ---
-title: "XX"
+title: "Flexibility of interactions depends on habitat suitability"
 author: 
@@
 
-We downloaded plant pollinator networks from the Web of Life up to `r format(as.Date(config$raw_data_retrieved), "%b %d, %Y")`. 
-This included pollination networks from `r n_published_studies` studies which included plant-pollinator interactions in `r dplyr::n_distinct(int_metadata$loc_id)` independent locations (Figure X).
+We retrieved plant-pollinator networks from the Web of Life database [@fortuna_web_2014] on`r format(as.Date(config$raw_data_retrieved), "%b %d, %Y")` (Figure \@ref(fig:fig-worldmap)). 
+Some studies included interaction data recorded at multiple points in time. 
+When this was the case, we combined them into one single interaction network per location. 
+All together, these networks included
 

### 2019-05-29 paper/manuscript.Rmd
Some citation info for climond

@@
 
-Studies are
+Climatic data: 
+These data are for use in research projects only.
+A 'research project' is any project carried out by an individual or organized by a university, a scientific institute, or similar organization (private or public) for non-commercial research purposes only.
+Results based on these data must be submitted for publication in the open literature without any delay linked to commercial objectives.
+An additional restriction is that the UK Met.
+Office/Hadley Centre requires strict adherence to the conditions set forth in their "License Statement", which applies to their model output: "These data are licensed for use in Research Projects only.
+A 'Research Project' is any project organised by a university, a scientific institute, or similar organisation (private or public), for non-commercial research purposes only.
+A necessary condition of the recognition of non-commercial purposes is that all the results obtained are openly available at delivery costs only, without any delay linked to commercial objectives, and that the research itself is submitted for open publication.
+
+Proper citation and acknowledgement
+In first making reference to the data obtained from the CliMond archive, please include the phrase "the CliMond dataset (Kriticos et al.
+2012)".
+Subsequent references within the same publication might refer to the data with terms such as " CliMond data", "the CliMond multi-model dataset", "the CliMond archive", or the " CliMond dataset".
+Please note the following critical references:
+
+CliMond:
+Kriticos DJ, Webber BL, Leriche A, Ota N, Bathols J, Macadam I, Scott JK (2012) CliMond: global high resolution historical and future scenario climate surfaces for bioclimatic modelling.
+Methods in Ecology and Evolution, 3, 53-64.
+WorldClim:
+Hijmans RJ, Cameron SE, Parra JL, Jones PG, Jarvis A (2005) Very high resolution interpolated climate surfaces for global land areas. International Journal of Climatology, 25, 1965-1978. 
+CRU:
+Mitchell TD, Carter TR, Jones PD, Hulme M, New M (2004) A comprehensive set of climate scenarios for Europe and the globe: the observed record (1900-2000) and 16 scenarios (2000-2100).University of East Anglia, Norwich,UK, pp.
+30.
+CMIP3:
+Meehl, G.
+A., C.
+Covey, T.
+Delworth, M.
+Latif, B.
+McAvaney, J.
+F.
+B.
+Mitchell, R.
+J.
+Stouffer, and K.
+E.
+Taylor (2007) The WCRP CMIP3 multi-model dataset: A new era in climate change research, Bulletin of the American Meteorological Society, 88, 1383-1394.
+CSIRO Mk 3.0:
+Collier MA, Dix MR, Hirst AC (2007) CSIRO Mk3 climate system model and meeting the strict IPCC AR4 data requirements.
+MODSIM07 International Congress on Modelling and Simulation : Land, water & environmental management : integrated systems for sustainability, 10-13 December [2007] : proceedings (eds Oxley L, Kulasiri D), Christchurch, pp.
+582-588.
+Modelling and Simulation Society of Australia and New Zealand.
+Miroc-H:
+Hasumi H, Emori S (2004) K-1 coupled model (MIROC) description, K-1 technical report, 1. Center for Climate System Research, University of Tokyo, Tokyo, 34 pp.
 

### 2019-06-12 main.R
Restore paper making plan

@@ -113,6 +113,34 @@ figures_plan <- drake_plan(
 )
 
 
+# Manuscript --------------------------------------------------------------
+
+reporting_plan <- drake_plan(	
+  bibliography = target(	
+    command = get_bibliography("https://raw.githubusercontent.com/efcaguab/phd-bibliography/master/interactions%2Bsdm_manuscript.bib",	
+                               file_out("paper/bibliography.bib"))	
+  ),	
+  interaction_bibliography = target(	
+    command = get_bibliography("https://raw.githubusercontent.com/efcaguab/phd-bibliography/master/interactions%2Bsdm_interaction-data-references.bib", 	
+                               file_out("paper/int-bibliography.bib"))	
+  ),	
+  interaction_citations = bib2df::bib2df(file_in("paper/int-bibliography.bib")),	
+  abstract = readLines(file_in("./paper/abstract.md")),	
+  keywords = process_keywords(file_in("./paper/keywords.md")),	
+  acknowledgements = readLines(file_in("./paper/acknowledgements.md")),	
+  intro_line_number = get_line_number(file_in("paper/manuscript.Rmd"), "# Introduction"),	
+  abs_wordcount = count_words(file_in("paper/abstract.md")),	
+  msc_wordcount = count_words(file_in('paper/manuscript.Rmd'), lines_to_ignore = 1:intro_line_number),	
+  n_references = count_references(file_in('paper/manuscript.Rmd'), lines_to_ignore = 1:intro_line_number, refs_to_exclude = "@ref"),	
+  n_displays = count_displays(file_in('paper/manuscript.Rmd'), lines_to_ignore = 1:intro_line_number),	
+  msc_title = get_yaml_title(file_in('paper/manuscript.Rmd')),	
+  supp_info = render_pdf(knitr_in('paper/supp-info.Rmd'), file_out('paper/supp-info.pdf'), clean_md = FALSE),	
+  draft_info = render_pdf(file_in('paper/draft-info.Rmd'), file_out('paper/draft-info.pdf'), clean_md = FALSE),	
+  manuscript = render_pdf(knitr_in('paper/manuscript.Rmd'), file_out('paper/manuscript.pdf'), clean_md = FALSE),	
+  cover_letter = knitr::knit2pdf(knitr_in("paper/cover-letter.Rnw"), output = file_out("paper/cover-letter.tex"))	
+)	
+
+
 paper_plan <- rbind(
   # full_plan,
   configuration_plan,

### 2019-06-12 paper/manuscript.Rmd
Add line to remind me to get topography data
First draft cleaning species methods

@@
 author: 
-  - "E. Fernando Cagua^1^ ([efc29@uclive.ac.nz](mailto:efc29@uclive.ac.nz))"
   - "Audrey Lustig^2^ ([audrey.lustig@canterbury.ac.nz](audrey.lustig@canterbury.ac.nz))"
@@
   - "Daniel B. Stouffer^1^ ([daniel.stouffer@canterbury.ac.nz](daniel.stouffer@canterbury.ac.nz))"
+  - "E. Fernando Cagua^1^ ([efc29@uclive.ac.nz](mailto:efc29@uclive.ac.nz))"
 bibliography: 
@@
   - \usepackage[export]{adjustbox}
+editor_options: 
+  chunk_output_type: console
 ---
@@
 We retrieved plant-pollinator networks from the Web of Life database [@fortuna_web_2014] on`r format(as.Date(config$raw_data_retrieved), "%b %d, %Y")` (Figure \@ref(fig:fig-worldmap)). 
+This database contains datasets originating from XX studies published in the primary literature between XX and XX. 
+Before assessing how habitat suitability affects interaction partners of plants and pollinators we need to link species across different datasets. 
+However, this task is complicated by the inacurracies often found in diverse data sources. 
+Most commonly, there are typos in the species names, species names have bee abbreviated or a single species might be recorded as different synonyms in different sources. 
+To alleviate this issue we restored to the following procedure.
+
+First, to
+
 Some studies included interaction data recorded at multiple points in time. 
@@
 
+See topography data from Species distribution model transferability and model grain size – finer may not always be better
+
 # Results

### 2019-06-12 code/plotting_and_formatting.R
Add function to convert numbers to words

@@ -59,3 +59,56 @@ common_graphic_metrics <- function(){
 cgm <- function(){
   common_graphic_metrics()
 }
+
+# numbers to words
+numbers2words <- function(x){
+  ## Function by John Fox found here:
+  ## http://tolstoy.newcastle.edu.au/R/help/05/04/2715.html
+  ## Tweaks by AJH to add commas and "and"
+  
+  helper <- function(x){
+    
+    digits <- rev(strsplit(as.character(x), "")[[1]])
+    nDigits <- length(digits)
+    if (nDigits == 1) as.vector(ones[digits])
+    else if (nDigits == 2)
+      if (x <= 19) as.vector(teens[digits[1]])
+    else trim(paste(tens[digits[2]],
+                    Recall(as.numeric(digits[1]))))
+    else if (nDigits == 3) trim(paste(ones[digits[3]], "hundred and",
+                                      Recall(makeNumber(digits[2:1]))))
+    else {
+      nSuffix <- ((nDigits + 2) %/% 3) - 1
+      if (nSuffix > length(suffixes)) stop(paste(x, "is too large!"))
+      trim(paste(Recall(makeNumber(digits[
+        nDigits:(3*nSuffix + 1)])),
+        suffixes[nSuffix],"," ,
+        Recall(makeNumber(digits[(3*nSuffix):1]))))
+    }
+  }
+  trim <- function(text){
+    #Tidy leading/trailing whitespace, space before comma
+    text=gsub("^\ ", "", gsub("\ *$", "", gsub("\ ,",",",text)))
+    #Clear any trailing " and"
+    text=gsub(" and$","",text)
+    #Clear any trailing comma
+    gsub("\ *,$","",text)
+  }
+  makeNumber <- function(...) as.numeric(paste(..., collapse=""))
+  #Disable scientific notation
+  opts <- options(scipen=100)
+  on.exit(options(opts))
+  ones <- c("", "one", "two", "three", "four", "five", "six", "seven",
+            "eight", "nine")
+  names(ones) <- 0:9
+  teens <- c("ten", "eleven", "twelve", "thirteen", "fourteen", "fifteen",
+             "sixteen", " seventeen", "eighteen", "nineteen")
+  names(teens) <- 0:9
+  tens <- c("twenty", "thirty", "forty", "fifty", "sixty", "seventy", "eighty",
+            "ninety")
+  names(tens) <- 2:9
+  x <- round(x)
[…]

### 2019-06-12 paper/manuscript.Rmd
Some more info about cleaning species methods

@@
 
-We retrieved plant-pollinator networks from the Web of Life database [@fortuna_web_2014] on`r format(as.Date(config$raw_data_retrieved), "%b %d, %Y")` (Figure \@ref(fig:fig-worldmap)). 
+We retrieved plant-pollinator networks from the Web of Life database [@fortuna_web_2014] on `r format(as.Date(config$raw_data_retrieved), "%B %Y")` (Figure \@ref(fig:fig-worldmap)). 
 This database contains datasets originating from XX studies published in the primary literature between XX and XX. 
@@
 
-First, to
+First, we used data from the Integrated Taxonomic Information System database (http://www.itis.gov) on `r format(as.Date(config$raw_data_retrieved), "%B %Y")` to find synonyms of species names recorded in the datasets.
+Subsequently, we checked the spelling of species names using the Global Names Resolver (https://resolver.globalnames.org) which includes taxonomic data from `r dplyr::n_distinct(taxize::gnr_datasources()$title)` taxonomic sources.
+Using the function `gnr_resolve` in the R package `taxize` [@chamberlain_taxize_2013; chamberlain_taxize_2019] and used fuzzy matching of the canonical names to obtain the most likely correct spelling of incorrect scientific names.
+As, ocassionally, homonimus species or genus names can be found in different taxa, we retrieved higher taxonomic hierarchy to confirm that the correct spelling obtained using the Global Names Resolver matches our expectations.
+This hierarchy was retrieved from the National Center for Biotechnology Information taxonomic database (https://www.ncbi.nlm.nih.gov/taxonomy).
+
+all together we found XX instances of species that were included with a datab
 

### 2019-06-12 main.R
Include reporting in the plan...

@@ -148,7 +148,8 @@ paper_plan <- rbind(
   pre_process_int_plan,
   download_ocurrence_data_plan, 
   data_references_plan, 
-  figures_plan
+  figures_plan, 
+  reporting_plan
 )
 
 # full_config <- drake_config(full_plan)

### 2019-06-12 code/paper_compilation.R
Add an easy way to re-download bibliography in the workflow

@@ -142,7 +142,7 @@ compile_pdf <- function(file_in, file_out, clean) {
 }
 
 
-get_bibliography <- function(filename_in, filename_out){
+get_bibliography <- function(filename_in, filename_out, ...){
   readLines(filename_in) %>%
     writeLines(filename_out)
   

### 2019-06-12 main.R

@@ -28,7 +28,8 @@ configuration_plan <- drake_plan(
   data_download_date = config$raw_data_retrieved,
   minimum_spp_locations = config$minimum_spp_locations, 
   itis_address = config$itis_address, 
-  ecoregions_address = config$ecoregions_address
+  ecoregions_address = config$ecoregions_address, 
+  biblio_download_date = config$bibliography_retrieved
 )
 
 # Download data ----------------------------------------------------------
@@ -118,11 +119,13 @@ figures_plan <- drake_plan(
 reporting_plan <- drake_plan(	
   bibliography = target(	
     command = get_bibliography("https://raw.githubusercontent.com/efcaguab/phd-bibliography/master/interactions%2Bsdm_manuscript.bib",	
-                               file_out("paper/bibliography.bib"))	
+                               file_out("paper/bibliography.bib"), 
+                               bibliography_retrieved)	
   ),	
   interaction_bibliography = target(	
     command = get_bibliography("https://raw.githubusercontent.com/efcaguab/phd-bibliography/master/interactions%2Bsdm_interaction-data-references.bib", 	
-                               file_out("paper/int-bibliography.bib"))	
+                               file_out("paper/int-bibliography.bib"), 
+                               bibliography_retrieved)	
   ),	
   interaction_citations = bib2df::bib2df(file_in("paper/int-bibliography.bib")),	
   abstract = readLines(file_in("./paper/abstract.md")),	

### 2019-06-12 paper/manuscript.Rmd
Add citations to taxize package

@@
 Subsequently, we checked the spelling of species names using the Global Names Resolver (https://resolver.globalnames.org) which includes taxonomic data from `r dplyr::n_distinct(taxize::gnr_datasources()$title)` taxonomic sources.
-Using the function `gnr_resolve` in the R package `taxize` [@chamberlain_taxize_2013; chamberlain_taxize_2019] and used fuzzy matching of the canonical names to obtain the most likely correct spelling of incorrect scientific names.
+Using the function `gnr_resolve` in the R package `taxize` [@chamberlain_taxize_2013; @chamberlain_taxize_2019] and used fuzzy matching of the canonical names to obtain the most likely correct spelling of incorrect scientific names.
 As, ocassionally, homonimus species or genus names can be found in different taxa, we retrieved higher taxonomic hierarchy to confirm that the correct spelling obtained using the Global Names Resolver matches our expectations.

### 2019-06-13 code/clean-species-names.R
Return right object to species names checking

@@ -190,6 +190,10 @@ check_spp_names <- function(spp, synonyms_db, prev_sp_name_assessments_path){
     sp_name %>%
     # extract(1:15) %>%
     purrr::map_df(assess_sp_name_memoised, prev_sp_name_assessments_path, synonyms_db)
+  
+  # Once is done just read the assessment file from disk and return it
+  readr::read_csv(prev_sp_name_assessments_path, col_types = "ccccidcc")
+  
 }
 
 # Memoised version of assess_sp_name that checks a data frame with species names

### 2019-06-13 code/clean-species-names.R
Catch up kingdom names for bacteria and stuff like that

@@ -69,7 +69,7 @@ definitely <- function(func, n_tries = 10, sleep = 1/10, ...){
   try_number = 1
   
   while(is.null(result) && try_number <= n_tries){
-    message("Try number: ", try_number)
+    # message("Try number: ", try_number)
     try_number = try_number + 1
     result = possibly_func(...)
     Sys.sleep(sleep)
@@ -83,7 +83,9 @@ get_possible_kingdoms <- function(this_sp_name){
   
   uids <- this_sp_name %>%
     taxize::get_uid_(db = "ncbi", messages = F) %>%
-    purrr::map_df(function(x){x})
+    purrr::map_df(function(x){x}) %>%
+    # because it could match random shit eg. Anthrax could max Bacilus anthracis anthrax
+    filter(scientificname == this_sp_name)
   
   # It it was not found in NCIB return NA
   if(nrow(uids) == 0){
@@ -98,10 +100,17 @@ get_possible_kingdoms <- function(this_sp_name){
 
 # Get the kingdom of a NCBI UID taxon
 get_kingdom_of_uid <- function(uid){
-  taxize::classification(uid, db = "ncbi")[[1]]  %>%
+  kingdom <- taxize::classification(uid, db = "ncbi")[[1]] %>%
     filter(rank == "kingdom") %$%
     name
+  
+  if(length(kingdom) == 0){
+    return("NoKingdomAvailable")
+  } else {
+    return(kingdom)
+  }
 }
+
 # Check wether a tentative species name (string is in the itis database) if it 
 # is check for synonyms, returns a data frame
 check_itis <- function(sp_name, synonyms_db){

### 2019-06-13 paper/manuscript.Rmd
COntinue description of species name cleaning process

@@
                       eval.after = "fig.cap")
+
+library(dplyr)
 
@@
 
+```{r scientific-names-cleaning-info}
+loadd(checked_sp_names, spp)
+
+checked_sp_names <- checked_sp_names %>%
+  mutate(sp_name_in_gnr = gnr_score >= 0.988, 
+         sp_name_itis_invalid = itis %in% c("invalid", "not accepted"), 
+         good_sp_name = sp_name_in_gnr & ! sp_name_itis_invalid, 
+         # good_sp_name = if_else(is.na(good_sp_name), FALSE, good_sp_name), 
+         good_queried_sp_name = good_sp_name & sp_name == queried_sp_name)
+
+n_sp_names <- n_distinct(spp$sp_name)
+
+n_sp_names_sp_level <- filter(spp, !sp_unidentified) %$% 
+  n_distinct(sp_name)
+
+n_sp_names_gen_level <- filter(spp, sp_unidentified, !gen_unidentified) %$% 
+  n_distinct(sp_name)
+
+n_no_tax_info <- filter(spp, gen_unidentified) %$% n_distinct(sp_name)
+
+n_sp_correct_in_data <- checked_sp_names %>%
+  filter(good_queried_sp_name) %$%
+  n_distinct(queried_sp_name)
+
+# n_sp_correct_in_data %>%
+#   group_by(queried_sp_name) %>%
+#   count(sort = TRUE)
+
+# sp_incorrect_in_data <- checked_sp_names %>%
+```
+
 First, we used data from the Integrated Taxonomic Information System database (http://www.itis.gov) on `r format(as.Date(config$raw_data_retrieved), "%B %Y")` to find synonyms of species names recorded in the datasets.
@@
 
-all together we found XX instances of species that were included with a datab
+All together, before correcting typos and synonyms, the data sources contained `r format(n_sp_names, big.mark = ",")` unique interacting species. 
+Out of those, `r format(n_sp_names_sp_level, big.mark = ",")` were originally identified to the species-level, `r format(n_sp_names_gen_level, big.mark = ",")` to the genus level, and no taxonomic information was avaliable for the restant `r format(n_no_tax_info, big.mark = ",")`.
+We were able to confirm the validity of `r format(n_sp_correct_in_data, big.mark = ",")` of the scientific names of organisms identified to the species level (roughly `r scales::percent(n_sp_correct_in_data/n_sp_names_sp_level, 1)`).
 

### 2019-06-14 paper/manuscript.Rmd
Continue methods of species cleaning

--- 2019-06-12 paper/manuscript.Rmd
@@
 author: 
+  - "E. Fernando Cagua^1^ ([efc29@uclive.ac.nz](mailto:efc29@uclive.ac.nz))"
   - "Audrey Lustig^2^ ([audrey.lustig@canterbury.ac.nz](audrey.lustig@canterbury.ac.nz))"
@@
   - "Daniel B. Stouffer^1^ ([daniel.stouffer@canterbury.ac.nz](daniel.stouffer@canterbury.ac.nz))"
-  - "E. Fernando Cagua^1^ ([efc29@uclive.ac.nz](mailto:efc29@uclive.ac.nz))"
 bibliography: 
@@
 
+```{r scientific-names-cleaning-info}
+loadd(checked_sp_names, spp)
+
+checked_sp_names <- checked_sp_names %>%
+  # remove variant and subspecies abbreviations from the retrieved species
+  # names, it is clear that they are one when there is 3 words or more in there
+  mutate(sp_name = stringr::str_replace_all(sp_name,"var. ", ""),
+         sp_name = stringr::str_replace_all(sp_name,"ssp. ", ""),
+         sp_name_in_gnr = !is.na(gnr_score), 
+         sp_name_itis_invalid = itis %in% c("invalid", "not accepted"), 
+         # good species name has been found and its not invalid
+         good_sp_name = sp_name_in_gnr & ! sp_name_itis_invalid, 
+         good_queried_sp_name = good_sp_name & sp_name == queried_sp_name, 
+         sp_name_rank = get_name_rank(sp_name), 
+         queried_sp_name_rank = get_name_rank(queried_sp_name)) %>%
+  group_by(queried_sp_name) %>%
+  mutate(corrected_typo = any(gnr_score == 0.750) & all(sp_name_rank == queried_sp_name_rank),
+         corrected_typo = tidyr::replace_na(corrected_typo, FALSE),
+         good_queried_sp_name = any(good_queried_sp_name), 
+         n_spellings = n_distinct(sp_name), 
+         any_sp_itis_invalid = any(sp_name_itis_invalid), 
+         alt_sp_name_found = n_spellings > 1 & any_sp_itis_invalid) %>%
+  ungroup()
+
+n_sp_names <- n_distinct(spp$sp_name)
+
+n_sp_names_sp_level <- filter(spp, !sp_unidentified) %$% 
+  n_distinct(sp_name)
+
+n_sp_names_gen_level <- filter(spp, sp_unidentified, !gen_unidentified) %$% 
+  n_distinct(sp_name)
+
+n_no_tax_info <- filter(spp, gen_unidentified) %$% n_distinct(sp_name)
+
+n_sp_correct_in_data <- checked_sp_names %>%
+  filter(good_queried_sp_name) %$%
+  n_distinct(queried_sp_name)
+
+n_sp_corrected_typos <- checked_sp_names %>%
+  filter(corrected_typo) %$% 
+  n_distinct(queried_sp_name)
+
+sp_with_synonyms <- checked_sp_names %>%
+  filter(alt_sp_name_found)
+
+n_sp_with_synonyms <- sp_with_synonyms %$%
+  n_distinct(queried_sp_name)
+
+n_sp_not_found <- checked_sp_names %>%
+  filter(!good_queried_sp_name) %>% 
+  filter(!alt_sp_name_found, !corrected_typo) %$%
+  n_distinct(queried_sp_name)
+
+checked_sp_names %>%
+  filter(!good_queried_sp_name, !alt_sp_name_found) %$% n_distinct(queried_sp_name)
+```
+
 First, we used data from the Integrated Taxonomic Information System database (http://www.itis.gov) on `r format(as.Date(config$raw_data_retrieved), "%B %Y")` to find synonyms of species names recorded in the datasets.
@@
 
-all together we found XX instances of species that were included with a datab
+All together, before correcting typos and synonyms, the data sources contained `r format(n_sp_names, big.mark = ",")` unique interacting species. 
+From that total, `r format(n_sp_names_sp_level, big.mark = ",")` were originally identified to the species-level, `r format(n_sp_names_gen_level, big.mark = ",")` to the genus level, and no taxonomic information was avaliable for the remaining `r format(n_no_tax_info, big.mark = ",")` organims.
+We were able to confirm the validity of `r format(n_sp_correct_in_data, big.mark = ",")` of the scientific names used to identify organisms to the species level (roughly `r scales::percent(n_sp_correct_in_data/n_sp_names_sp_level, 1)`).
+We assessed the validity of a scientific name by querying the Global Names Resolver database (https://resolver.globalnames.org) which includes taxonomic data from `r dplyr::n_distinct(taxize::gnr_datasources()$title)` taxonomic sources.
+Specifically, we used the function `gnr_resolve` from the R package `taxize `r as.character(packageVersion('taxize'))`` [@chamberlain_taxize_2013; @chamberlain_taxize_2019].
+
+From the remaining `r format(n_sp_names_sp_level - n_sp_correct_in_data, big.mark = ",")` names, we were able to identify and the correct missspelling of `r format(n_sp_corrected_typos, big.mark = ",")` organism names.
+Furthermore we found alternative names for `r format(n_sp_with_synonyms, big.mark = ",")` species. 
+Most commonly, due to the name being an invalid or not accepted synonym of a species, subspecies, or plant variety (\@ref(tab:tab-sp-synonym-reasons)). 
+We were unable to automatically correct `r format(n_sp_not_found, big.mark = ",")` names in the databases.
+
+```{r tab-sp-synonym-reasons}
+sp_with_synonyms %>%
+  filter(!is.na(itis_reason)) %>%
+  group_by(queried_sp_name) %>%
+  summarise(itis_reason = first(itis_reason)) %>%
+  group_by(itis_reason) %>%
+  count(sort = T) %>%
+  knitr::kable(col.names = c("reason of species alternative name", "n"), 
+               caption = "tablesita", 
+               booktabs = TRUE) %>%
+  kableExtra::kable_styling(font_size = 8) 
+```
 

### 2019-06-14 code/clean-species-names.R

@@ -234,3 +234,14 @@ assess_sp_name_memoised <- function(this_sp_name,
 # Phacelia secunda
 
 # assess_sp_name_memoised <- memoise::memoise(assess_sp_name, )
+
+
+
+get_name_rank <- function(x){
+  sp_name_n_spaces <- stringr::str_count(x, " ")
+  case_when(
+    sp_name_n_spaces == 0 ~ "genus", 
+    sp_name_n_spaces == 1 ~ "species", 
+    TRUE ~ "subspecies"
+  )
+}

### 2019-06-14 paper/manuscript.Rmd
Some informal checks for species that appear as both plants and pollinators

@@
 
+spp %>%
+  distinct(sp_name, guild, loc_id) %>%
+  group_by(sp_name) %>%
+  mutate(n_guilds = n_distinct(guild)) %>% 
+  inner_join(checked_sp_names, by = c("sp_name" = "queried_sp_name")) %>% 
+  filter(n_guilds > 1) %>% View
+  n_distinct(sp_name)
+
 n_sp_names <- n_distinct(spp$sp_name)
@@
 
-From the remaining `r format(n_sp_names_sp_level - n_sp_correct_in_data, big.mark = ",")` names, we were able to identify and the correct missspelling of `r format(n_sp_corrected_typos, big.mark = ",")` organism names.
+From the remaining `r format(n_sp_names_sp_level - n_sp_correct_in_data, big.mark = ",")` scientific names we were unable to validate, we were able to identify and the correct `r format(n_sp_corrected_typos, big.mark = ",")` spelling mistakes.
+These mistakes were corrected automatically used by fuzzy matching with the canonical names in the Global Names Resover database. 
 Furthermore we found alternative names for `r format(n_sp_with_synonyms, big.mark = ",")` species. 

### 2019-06-17 code/clean-species-names.R
Recode interactions to use species ids instead of names

@@ -323,3 +323,12 @@ get_final_name_list <-
     dplyr::mutate(sp_id = stringr::str_pad(sp_id, 5, pad = "0"), 
            sp_id = paste("sp", sp_id, sep = "_"))
 }
+
+recode_interactions <- function(species_ids, int){
+  int %>%
+    dplyr::left_join(species_ids, by = c("pla_name" = "sp_name")) %>%
+    dplyr::rename(pla_id = sp_id) %>%
+    dplyr::left_join(species_ids, by = c("pol_name" = "sp_name")) %>%
+    dplyr::rename(ani_id = sp_id) %>%
+    dplyr::select(-pla_name, -pol_name)
+}

### 2019-06-17 main.R

@@ -92,7 +92,8 @@ merge_interaction_data_plan <- drake_plan(
   species_ids = get_final_name_list(spp, checked_sp_names, 
                                     manual_name_corrections, 
                                     checked_manual_corrections),
-  int = merge_int(wol_int), 
+  int = merge_int(wol_int),
+  recoded_interactions = recode_interactions(species_ids, int),
   int_metadata = merge_metadata(wol_data)
 )
 

### 2019-06-17 code/clean-species-names.R
Remove problematic networks from interactions list

@@ -332,3 +332,9 @@ recode_interactions <- function(species_ids, int){
     dplyr::rename(ani_id = sp_id) %>%
     dplyr::select(-pla_name, -pol_name)
 }
+
+
+remove_problematic_networks <- function(recoded_interactions, problematic_networks){
+  recoded_interactions %>%
+    dplyr::filter(!loc_id %in% problematic_networks)
+}

### 2019-06-17 main.R

@@ -94,6 +94,7 @@ merge_interaction_data_plan <- drake_plan(
                                     checked_manual_corrections),
   int = merge_int(wol_int),
   recoded_interactions = recode_interactions(species_ids, int),
+  clean_interactions = remove_problematic_networks(recoded_interactions, problematic_networks), 
   int_metadata = merge_metadata(wol_data)
 )
 

### 2019-06-17 paper/supp-info.Rmd
Add list of manual corrections to supp. info

@@
         knitr.kable.NA = "-")
+library(dplyr)
 ```
+
+```{r tab-manual-name-corrections}
+loadd(spp, manual_name_corrections)
+manual_name_corrections %>%
+  inner_join(spp, by = c("queried_sp_name" = "sp_name")) %>%
+  distinct(queried_sp_name, sp_name, guild) %>%
+  filter(!is.na(sp_name)) %>%
+  arrange(guild, queried_sp_name, sp_name) %>%
+  mutate(sp_name = tidyr::replace_na(sp_name, "no replacement found"), 
+         sp_name = kableExtra::cell_spec(sp_name, italic = TRUE), 
+         guild = if_else(guild == "pla", "plant", "pollinator")) %>%
+  knitr::kable(caption = "Manually corrected canonnical names. More than one correct name have been included when an accepted/valid synonym the cannonical name exists.", 
+               col.names = c("incorrect name", "corrected name", "guild"),
+               booktabs = TRUE, 
+               escape = F) %>%
+  kableExtra::kable_styling(font_size = 8) %>%
+  kableExtra::collapse_rows(1, latex_hline = "none", valign = "top")
+```
+
+```{r eval = FALSE, tab-sp-synonym-reasons}
+sp_with_synonyms %>%
+  filter(!is.na(itis_reason)) %>%
+  group_by(queried_sp_name) %>%
+  summarise(itis_reason = first(itis_reason)) %>%
+  group_by(itis_reason) %>%
+  count(sort = T) %>%
+  knitr::kable("latex", 
+               col.names = c("reason of species alternative name", "n"), 
+               caption = "tablesita", 
+               booktabs = TRUE) %>%
+  kableExtra::kable_styling(font_size = 8) %>%
+  kableExtra::collapse_rows(columns = 1)
+```

### 2019-06-17 paper/manuscript.Rmd
Comment out climatic info from MSC for now

@@
 
-Climatic data: 
-These data are for use in research projects only.
+<!-- These data are for use in research projects only.
 A 'research project' is any project carried out by an individual or organized by a university, a scientific institute, or similar organization (private or public) for non-commercial research purposes only.
@@
 A necessary condition of the recognition of non-commercial purposes is that all the results obtained are openly available at delivery costs only, without any delay linked to commercial objectives, and that the research itself is submitted for open publication.
+-->
 
-Proper citation and acknowledgement
-In first making reference to the data obtained from the CliMond archive, please include the phrase "the CliMond dataset (Kriticos et al.
+<!-- Proper citation and acknowledgement -->
+<!-- In first making reference to the data obtained from the CliMond archive, please include the phrase "the CliMond dataset (Kriticos et al.
 2012)".
 Subsequent references within the same publication might refer to the data with terms such as " CliMond data", "the CliMond multi-model dataset", "the CliMond archive", or the " CliMond dataset".
-Please note the following critical references:
+Please note the following critical references: -->
 
-CliMond:
-Kriticos DJ, Webber BL, Leriche A, Ota N, Bathols J, Macadam I, Scott JK (2012) CliMond: global high resolution historical and future scenario climate surfaces for bioclimatic modelling.
+<!-- CliMond: -->
+<!-- Kriticos DJ, Webber BL, Leriche A, Ota N, Bathols J, Macadam I, Scott JK (2012) CliMond: global high resolution historical and future scenario climate surfaces for bioclimatic modelling.
 Methods in Ecology and Evolution, 3, 53-64.
-WorldClim:
-Hijmans RJ, Cameron SE, Parra JL, Jones PG, Jarvis A (2005) Very high resolution interpolated climate surfaces for global land areas. International Journal of Climatology, 25, 1965-1978. 
-CRU:
-Mitchell TD, Carter TR, Jones PD, Hulme M, New M (2004) A comprehensive set of climate scenarios for Europe and the globe: the observed record (1900-2000) and 16 scenarios (2000-2100).University of East Anglia, Norwich,UK, pp.
+-->
+<!-- WorldClim: -->
+<!-- Hijmans RJ, Cameron SE, Parra JL, Jones PG, Jarvis A (2005) Very high resolution interpolated climate surfaces for global land areas. International Journal of Climatology, 25, 1965-1978.  -->
+<!-- CRU: -->
+<!-- Mitchell TD, Carter TR, Jones PD, Hulme M, New M (2004) A comprehensive set of climate scenarios for Europe and the globe: the observed record (1900-2000) and 16 scenarios (2000-2100).University of East Anglia, Norwich,UK, pp.
 30.
-CMIP3:
-Meehl, G.
+-->
+<!-- CMIP3: -->
+<!-- Meehl, G.
 A., C.
@@
 Taylor (2007) The WCRP CMIP3 multi-model dataset: A new era in climate change research, Bulletin of the American Meteorological Society, 88, 1383-1394.
-CSIRO Mk 3.0:
-Collier MA, Dix MR, Hirst AC (2007) CSIRO Mk3 climate system model and meeting the strict IPCC AR4 data requirements.
+-->
+<!-- CSIRO Mk 3.0: -->
+<!-- Collier MA, Dix MR, Hirst AC (2007) CSIRO Mk3 climate system model and meeting the strict IPCC AR4 data requirements.
 MODSIM07 International Congress on Modelling and Simulation : Land, water & environmental management : integrated systems for sustainability, 10-13 December [2007] : proceedings (eds Oxley L, Kulasiri D), Christchurch, pp.
@@
 Modelling and Simulation Society of Australia and New Zealand.
-Miroc-H:
-Hasumi H, Emori S (2004) K-1 coupled model (MIROC) description, K-1 technical report, 1. Center for Climate System Research, University of Tokyo, Tokyo, 34 pp.
+-->
+<!-- Miroc-H: -->
+<!-- Hasumi H, Emori S (2004) K-1 coupled model (MIROC) description, K-1 technical report, 1. Center for Climate System Research, University of Tokyo, Tokyo, 34 pp. -->
 

### 2019-06-17 paper/manuscript.Rmd
Rework methods for species interactions data aquisition

@@
   - \newcommand{\lr}[1]{page~\pageref{#1}, line~\lineref{#1}}
-  - \externaldocument[S-]{supp-info}
+  - \externaldocument{supp-info}
   - \usepackage[export]{adjustbox}
@@
 
+## Data aquisition
+
+### Species interactions
+
 ```{r}
@@
 
+all_int_cites <- paste0("@", interaction_citations$BIBTEXKEY) %>%
+  glue::glue_collapse(sep = "; ") %>%
+  paste0("[", ., "]")
+
+int_citations_year_range <- range(interaction_citations$YEAR)
 ```
 
-We retrieved plant-pollinator networks from the Web of Life database [@fortuna_web_2014] on `r format(as.Date(config$raw_data_retrieved), "%B %Y")` (Figure \@ref(fig:fig-worldmap)). 
-This database contains datasets originating from XX studies published in the primary literature between XX and XX. 
-Before assessing how habitat suitability affects interaction partners of plants and pollinators we need to link species across different datasets. 
-However, this task is complicated by the inacurracies often found in diverse data sources. 
-Most commonly, there are typos in the species names, species names have bee abbreviated or a single species might be recorded as different synonyms in different sources. 
-To alleviate this issue we restored to the following procedure.
-
 ```{r scientific-names-cleaning-info}
-loadd(checked_sp_names, spp)
-
-checked_sp_names <- checked_sp_names %>%
-  # remove variant and subspecies abbreviations from the retrieved species
-  # names, it is clear that they are one when there is 3 words or more in there
-  mutate(sp_name = stringr::str_replace_all(sp_name,"var. ", ""),
-         sp_name = stringr::str_replace_all(sp_name,"ssp. ", ""),
-         sp_name_in_gnr = !is.na(gnr_score), 
-         sp_name_itis_invalid = itis %in% c("invalid", "not accepted"), 
-         # good species name has been found and its not invalid
-         good_sp_name = sp_name_in_gnr & ! sp_name_itis_invalid, 
-         good_queried_sp_name = good_sp_name & sp_name == queried_sp_name, 
-         sp_name_rank = get_name_rank(sp_name), 
-         queried_sp_name_rank = get_name_rank(queried_sp_name)) %>%
-  group_by(queried_sp_name) %>%
-  mutate(corrected_typo = any(gnr_score == 0.750) & all(sp_name_rank == queried_sp_name_rank),
-         corrected_typo = tidyr::replace_na(corrected_typo, FALSE),
-         good_queried_sp_name = any(good_queried_sp_name), 
-         n_spellings = n_distinct(sp_name), 
-         any_sp_itis_invalid = any(sp_name_itis_invalid), 
-         alt_sp_name_found = n_spellings > 1 & any_sp_itis_invalid) %>%
-  ungroup()
-
-spp %>%
-  distinct(sp_name, guild, loc_id) %>%
-  group_by(sp_name) %>%
-  mutate(n_guilds = n_distinct(guild)) %>% 
-  inner_join(checked_sp_names, by = c("sp_name" = "queried_sp_name")) %>% 
-  filter(n_guilds > 1) %>% View
-  n_distinct(sp_name)
+loadd(checked_sp_names, spp, manual_name_corrections, problematic_networks)
 
@@
 
-n_sp_not_found <- checked_sp_names %>%
+sp_not_found <- checked_sp_names %>%
   filter(!good_queried_sp_name) %>% 
-  filter(!alt_sp_name_found, !corrected_typo) %$%
+  filter(!alt_sp_name_found, !corrected_typo)
+
+n_sp_not_found <- sp_not_found %$%
   n_distinct(queried_sp_name)
 
-checked_sp_names %>%
-  filter(!good_queried_sp_name, !alt_sp_name_found) %$% n_distinct(queried_sp_name)
+n_sp_manual_corrections <- manual_name_corrections %>%
+  filter(!is.na(sp_name)) %$%
+  n_distinct(queried_sp_name)
+
+study_per_location <- int_metadata %>%
+  distinct(loc_id, reference)
+
+n_names_in_multiple_references_orig <- spp %>%
+  left_join(study_per_location, by = "loc_id") %>%
+  group_by(sp_name) %>%
+  summarise(n_net = n_distinct(loc_id), 
+            n_ref = n_distinct(reference)) %>%
+  filter(n_ref > 1) %$%
+  n_distinct(sp_name)
 ```
 
-First, we used data from the Integrated Taxonomic Information System database (http://www.itis.gov) on `r format(as.Date(config$raw_data_retrieved), "%B %Y")` to find synonyms of species names recorded in the datasets.
-Subsequently, we checked the spelling of species names using the Global Names Resolver (https://resolver.globalnames.org) which includes taxonomic data from `r dplyr::n_distinct(taxize::gnr_datasources()$title)` taxonomic sources.
-Using the function `gnr_resolve` in the R package `taxize` [@chamberlain_taxize_2013; @chamberlain_taxize_2019] and used fuzzy matching of the canonical names to obtain the most likely correct spelling of incorrect scientific names.
-As, ocassionally, homonimus species or genus names can be found in different taxa, we retrieved higher taxonomic hierarchy to confirm that the correct spelling obtained using the Global Names Resolver matches our expectations.
-This hierarchy was retrieved from the National Center for Biotechnology Information taxonomic database (https://www.ncbi.nlm.nih.gov/taxonomy).
+We retrieved plant-pollinator networks from the Web of Life database [@fortuna_web_2014]. 
+This database contains datasets originating from `r length(interaction_citations$BIBTEXKEY)` studies published in the primary literature between `r int_citations_year_range[1]` and `r int_citations_year_range[2]` `r all_int_cites`.
+All together, these data sources contained `r format(n_sp_names, big.mark = ",")` unique organism names; `r format(n_names_in_multiple_references_orig, big.mark = ",")` of them in more than one data source.
+Because assessing how habitat suitability affects interaction partners of plants and pollinators requires linking of species across different datasets, it was important to ensure that the cannnonical names used to identify species were as accurate as possible.
+From the total number of organisms, `r format(n_sp_names_sp_level, big.mark = ",")` were originally identified to the species-level, `r format(n_sp_names_gen_level, big.mark = ",")` to the genus level, and no taxonomic information was avaliable for the remaining `r format(n_no_tax_info, big.mark = ",")`.
 
-All together, before correcting typos and synonyms, the data sources contained `r format(n_sp_names, big.mark = ",")` unique interacting species. 
-From that total, `r format(n_sp_names_sp_level, big.mark = ",")` were originally identified to the species-level, `r format(n_sp_names_gen_level, big.mark = ",")` to the genus level, and no taxonomic information was avaliable for the remaining `r format(n_no_tax_info, big.mark = ",")` organims.
-We were able to confirm the validity of `r format(n_sp_correct_in_data, big.mark = ",")` of the scientific names used to identify organisms to the species level (roughly `r scales::percent(n_sp_correct_in_data/n_sp_names_sp_level, 1)`).
+We were able to confirm the validity of `r format(n_sp_correct_in_data, big.mark = ",")` of the cannonical names used to identify organisms to the species level (roughly `r scales::percent(n_sp_correct_in_data/n_sp_names_sp_level, 1)`).
 We assessed the validity of a scientific name by querying the Global Names Resolver database (https://resolver.globalnames.org) which includes taxonomic data from `r dplyr::n_distinct(taxize::gnr_datasources()$title)` taxonomic sources.
@@
 
-From the remaining `r format(n_sp_names_sp_level - n_sp_correct_in_data, big.mark = ",")` scientific names we were unable to validate, we were able to identify and the correct `r format(n_sp_corrected_typos, big.mark = ",")` spelling mistakes.
-These mistakes were corrected automatically used by fuzzy matching with the canonical names in the Global Names Resover database. 
-Furthermore we found alternative names for `r format(n_sp_with_synonyms, big.mark = ",")` species. 
-Most commonly, due to the name being an invalid or not accepted synonym of a species, subspecies, or plant variety (\@ref(tab:tab-sp-synonym-reasons)). 
-We were unable to automatically correct `r format(n_sp_not_found, big.mark = ",")` names in the databases.
+From the remaining `r format(n_sp_names_sp_level - n_sp_correct_in_data, big.mark = ",")` names we were unable to validate, we were able to identify and correct `r format(n_sp_corrected_typos, big.mark = ",")` spelling mistakes.
+These spelling mistakes were corrected automatically by fuzzy matching the canonical names in our data sources with tgose in the Global Names Resover database. 
+In rare occasions, the fuzzy matching algorithm can suggest a cannonical name that has similar spelling but that correspond to an organism in a completely different taxonomic group, often in a different kingdom.
+We, therefore, checked the taxonomic hierarchy of suggested names to confirm that it corresponded to our expectations. 
+We retrieved all taxonomic hierarchies from the National Center for Biotechnology Information taxonomic database (https://www.ncbi.nlm.nih.gov/taxonomy).
 
-```{r tab-sp-synonym-reasons}
-sp_with_synonyms %>%
-  filter(!is.na(itis_reason)) %>%
-  group_by(queried_sp_name) %>%
-  summarise(itis_reason = first(itis_reason)) %>%
-  group_by(itis_reason) %>%
-  count(sort = T) %>%
-  knitr::kable(col.names = c("reason of species alternative name", "n"), 
-               caption = "tablesita", 
-               booktabs = TRUE) %>%
-  kableExtra::kable_styling(font_size = 8) 
+Subsequently, we checked for possible synonyms of the canonnical names in our data sources. 
+Using data from the Integrated Taxonomic Information System database (http://www.itis.gov), we found synonyms and alternative names for `r format(n_sp_with_synonyms, big.mark = ",")` of those in our data sources.
+Finding these alternative names was important due to two reasons. 
+First, because we wanted to be able to identify the cases in which the same organism might have been recorded with different cannonical names in different data sources.
+This can ocurr not only with synonyms but also when the cannonical name has been changed or when there are widely used ortographic variants.
+Second, because retrieving occurrence data is often only possible using the latest accepted/valid name for a particular species.
+
+All together, from the `r format(n_sp_names_sp_level - n_sp_correct_in_data, big.mark = ",")` names we were unable to validate, it was not possible to automatically correct `r format(n_sp_not_found, big.mark = ",")` of them.
+We then manually consulted multiple online databases, chiefly Wikispecies (https://species.wikimedia.org/), and looked for cannonical names that resembled the unvalidated names and matched the geographic and taxonomic spectations.
+We were able to further correct `r n_sp_manual_corrections` names in this fashion.
+Most manual corrections were of species names that have been abbreviated or had more than two spelling mistakes. 
+A complete list of manual name corrections can bee seen in Table \@ref(tab:tab-manual-name-corrections).
+
+```{r}
+loadd(recoded_interactions, clean_interactions)
+
+n_sp_ids <- recoded_interactions %>%
+  select(-loc_id) %>%
+  purrr::map(n_distinct) %>%
+  unlist() %>% sum()
+
+n_names_in_multiple_references_after <- recoded_interactions %>%
+  tidyr::gather(key = "guild", "sp_id", pla_id, ani_id) %>%
+  left_join(study_per_location, by = "loc_id") %>%
+  group_by(sp_id) %>%
+  summarise(n_ref = n_distinct(reference)) %>%
+  filter(n_ref > 1) %$%
+  n_distinct(sp_id)
+
+stats_clean_int <- clean_interactions %>%
+  purrr::map(n_distinct)
 ```
 
-Some studies included interaction data recorded at multiple points in time. 
+This cleaning process allowed us to match further `r n_sp_names - n_sp_ids` names across data sources and, by doing so, identify another `r n_names_in_multiple_references_after - n_names_in_multiple_references_orig` species that were present in more than one study.
+It also allowed us to identify `r numbers2words(length(problematic_networks))` problematic networks in which some names were included as both plants and pollinators. 
+These networks were removed from further analysis. 
+Sometimes interaction data was recorded at multiple points in time within or across our data sources. 
 When this was the case, we combined them into one single interaction network per location. 
-All together, these networks included
+The cleaning process resulted on a total of `r format(stats_clean_int$pla_id, big.mark = ",")` plants and `r format(stats_clean_int$ani_id, big.mark = ",")` pollinator species distributed across `r format(stats_clean_int$loc_id)` locations arround the globe (Figure \@ref(fig:fig-worldmap)).
 
@@
 readd(fig_worldmap)
+```
 
-all_int_cites <- paste0("@", interaction_citations$BIBTEXKEY) %>%
-  glue::glue_collapse(sep = "; ") %>%
-  paste0("[", ., "]")
-
-```
+### Climatic and habitat
 

### 2019-06-17 paper/draft-info.Rmd
Update draft info

@@
 
-* Specify grant numbers in the Acknowledgements and make sure the ones stated there now are correct. 
-* Suggestions to bring the abstract down to 150 words.
-* Approve (or not) for submission.
+* Should I include more data?
+
+## Done
+
+* Downloaded network data from the Web of Life and cleaned it.
+I didn't anticipated data needed SO MUCH work!
+I estimated three days to do this but took roughly 3 weeks to do it propperly and there is still some work to do.
+Quite a mess...
+
+## To-do
+
+* Manually fix the remaining species names that are incorrect and were not picked up by the automatic procedure
+* Fix references. There are lots of mistakes re. author, years and publication venue.

### 2019-06-18 code/figures.R
Calculate figure data separately
So that it can be used somewhere else

@@ -25,7 +25,7 @@ plot_worldmap <- function(world_land, int_metadata, clean_interactions){
 }
 
 # plot distribution of number of species per number of locations
-plot_species_location_distribution <- function(clean_interactions, checked_sp_names, species_ids){
+plot_species_location_distribution <- function(dist_species_multiple_locations_data){
   
   suppressPackageStartupMessages({
     require(ggplot2)
@@ -33,33 +33,8 @@ plot_species_location_distribution <- function(clean_interactions, checked_sp_na
   })
   
   pal <- cgm()$pal_el_green[c(4,7)]
-
-  distribution_data <- clean_interactions %>%
-    tidyr::gather("guild", "sp_id", pla_id, ani_id) %>%
-    dplyr::group_by(guild, sp_id) %>%
-    dplyr::summarise(n_locations = dplyr::n_distinct(loc_id)) %>%
-    dplyr::group_by(guild, n_locations) %>%
-    dplyr::summarise(n_species = dplyr::n_distinct(sp_id), 
-                     sp_id = paste(sp_id, collapse = "."))
   
-  sp_id_to_highlight <- distribution_data %>%
-    dplyr::group_by(guild) %>%
-    dplyr::filter(n_species == 1, 
-                  n_locations == max(n_locations)
-                  ) %$%
-    sp_id
-  
-  species_to_highlight <- species_ids %>%
-    dplyr::filter(sp_id %in% sp_id_to_highlight)
-  
-  distribution_data_highlight <- distribution_data %>%
-    dplyr::inner_join(species_to_highlight, by = "sp_id") %>%
-    dplyr::inner_join(checked_sp_names, by = "sp_name") %>%
-    dplyr::filter(gnr_score >= 0.98)
-  
-   p <- distribution_data %>%
-    dplyr::left_join(distribution_data_highlight, 
-                     by = c("guild", "n_locations", "n_species", "sp_id")) %>%
+   p <- dist_species_multiple_locations_data %>%
     ggplot(aes(x = n_locations, y = n_species, fill = guild)) +
     geom_line(aes(colour = guild), linetype = 3, size = 0.5) +
     geom_point(shape = 21, size = 1) +
@@ -85,9 +60,42 @@ plot_species_location_distribution <- function(clean_interactions, checked_sp_na
           legend.justification = c(1,1), 
           legend.title = element_blank()) +
     labs(x = "number of locations", 
-         y = "numver of species",
[…]

### 2019-06-18 main.R

@@ -124,8 +124,11 @@ figures_plan <- drake_plan(
                                           category = "physical", 
                                           returnclass = "sf"),
   fig_worldmap = plot_worldmap(world_land, int_metadata, clean_interactions), 
-  fig_dist_species_multiple_locations = plot_species_location_distribution(
+  fig_dist_species_multiple_locations_data = get_dist_species_multiple_locations_data(
     clean_interactions, checked_sp_names, species_ids
+  ),
+  fig_dist_species_multiple_locations = plot_species_location_distribution(
+    fig_dist_species_multiple_locations_data
   )
 )
 

### 2019-06-18 paper/manuscript.Rmd
Add distribution figure to paper

@@
 When this was the case, we combined them into one single interaction network per location. 
-The cleaning process resulted on a total of `r format(stats_clean_int$pla_id, big.mark = ",")` plants and `r format(stats_clean_int$ani_id, big.mark = ",")` pollinator species distributed across `r format(stats_clean_int$loc_id)` locations arround the globe (Figure \@ref(fig:fig-worldmap)).
+The cleaning process resulted on a total of `r format(stats_clean_int$pla_id, big.mark = ",")` plants and `r format(stats_clean_int$ani_id, big.mark = ",")` pollinator species distributed across `r format(stats_clean_int$loc_id)` locations arround the globe (Figure \@ref(fig:fig-worldmap), \@ref(fig:fig-distribution-species-mult-locations)).
 
-```{r fig-worldmap, fig.width = width('single'), fig.cap = paste("Worldwide distribution of pollination communities included in this study.
-We compile data from", length(interaction_citations$BIBTEXKEY), "published studies", all_int_cites, "which contain interaction information between plant and their pollinators at", dplyr::n_distinct(int_metadata$loc_id), "distinct locations.")}
+```{r fig-worldmap, fig.width = width('single'), fig.cap ="Worldwide distribution of pollination communities included in this study"}
 readd(fig_worldmap)
+```
+
+```{r fig-distribution-species-mult-locations, fig.width = width('single'), fig.height = 2.2, fig.cap = fig_dist_species_multiple_locations_legend}
+
+most_popular_species <- readd(fig_dist_species_multiple_locations_data) %>%
+  filter(n_locations == max(n_locations)) %>%
+  arrange(guild)
+
+fig_dist_species_multiple_locations_legend <- 
+  paste0("Frequency distribution of the number of locations in which a species is present. The most common pollinator species was *", 
+       most_popular_species$sp_name[1], 
+       "*, which was sampled on ", 
+       most_popular_species$n_locations[1], 
+       " locations, while the most common plant species was *", 
+       most_popular_species$sp_name[2], 
+       "*, which was sampled on ", 
+       most_popular_species$n_locations[2], 
+       " locations.")
+
+readd(fig_dist_species_multiple_locations)
 ```

### 2019-06-19 main.R
Download climatic data

@@ -29,6 +29,9 @@ configuration_plan <- drake_plan(
   minimum_spp_locations = config$minimum_spp_locations, 
   itis_address = config$itis_address, 
   ecoregions_address = config$ecoregions_address, 
+  worldclim_address = config$worldclim_address,
+  envirem_address = config$envirem_address,
+  envirem_topo_address = config$envirem_topo_address,
   biblio_download_date = config$bibliography_retrieved
 )
 
@@ -56,14 +59,34 @@ get_itis_synonym_database <- drake_plan(
 get_ecoregions_database <- drake_plan(
   ecoregions_shapefile = get_file(
     ecoregions_address, 
-    file_out("data/downloads/terrestrial-ecoregions.zip")
+    file_out("data/downloads/terrestrial-ecoregions.zip"), 
+    data_download_date
+  )
+)
+
+get_climate_data <- drake_plan(
+  worldclim = get_file(
+    worldclim_address, 
+    file_out("data/downloads/wordclim_2-5m.zip"), 
+    data_download_date
+  ),
+  envirem = get_file(
+    envirem_address, 
+    file_out("data/downloads/envirem_2-5m.zip"), 
+    data_download_date
+  ),
+  envirem_topo = get_file(
+    envirem_topo_address, 
+    file_out("data/downloads/envirem_topo_2-5m.zip"), 
+    data_download_date
   )
 )
 
 get_data_plan <- rbind(
   get_web_of_life_pollination_networks_plan, 
   get_itis_synonym_database, 
-  get_ecoregions_database
+  get_ecoregions_database, 
+  get_climate_data
 )
 
 # Pre-process interaction data --------------------------------------------

### 2019-06-19 paper/manuscript.Rmd
Add preliminary description of climate data in methods

@@
 
-<!-- These data are for use in research projects only.
-A 'research project' is any project carried out by an individual or organized by a university, a scientific institute, or similar organization (private or public) for non-commercial research purposes only.
-Results based on these data must be submitted for publication in the open literature without any delay linked to commercial objectives.
-An additional restriction is that the UK Met.
-Office/Hadley Centre requires strict adherence to the conditions set forth in their "License Statement", which applies to their model output: "These data are licensed for use in Research Projects only.
-A 'Research Project' is any project organised by a university, a scientific institute, or similar organisation (private or public), for non-commercial research purposes only.
-A necessary condition of the recognition of non-commercial purposes is that all the results obtained are openly available at delivery costs only, without any delay linked to commercial objectives, and that the research itself is submitted for open publication.
--->
-
-<!-- Proper citation and acknowledgement -->
-<!-- In first making reference to the data obtained from the CliMond archive, please include the phrase "the CliMond dataset (Kriticos et al.
-2012)".
-Subsequent references within the same publication might refer to the data with terms such as " CliMond data", "the CliMond multi-model dataset", "the CliMond archive", or the " CliMond dataset".
-Please note the following critical references: -->
-
-<!-- CliMond: -->
-<!-- Kriticos DJ, Webber BL, Leriche A, Ota N, Bathols J, Macadam I, Scott JK (2012) CliMond: global high resolution historical and future scenario climate surfaces for bioclimatic modelling.
-Methods in Ecology and Evolution, 3, 53-64.
--->
-<!-- WorldClim: -->
-<!-- Hijmans RJ, Cameron SE, Parra JL, Jones PG, Jarvis A (2005) Very high resolution interpolated climate surfaces for global land areas. International Journal of Climatology, 25, 1965-1978.  -->
-<!-- CRU: -->
-<!-- Mitchell TD, Carter TR, Jones PD, Hulme M, New M (2004) A comprehensive set of climate scenarios for Europe and the globe: the observed record (1900-2000) and 16 scenarios (2000-2100).University of East Anglia, Norwich,UK, pp.
-30.
--->
-<!-- CMIP3: -->
-<!-- Meehl, G.
-A., C.
-Covey, T.
-Delworth, M.
-Latif, B.
-McAvaney, J.
-F.
-B.
-Mitchell, R.
-J.
-Stouffer, and K.
-E.
-Taylor (2007) The WCRP CMIP3 multi-model dataset: A new era in climate change research, Bulletin of the American Meteorological Society, 88, 1383-1394.
--->
-<!-- CSIRO Mk 3.0: -->
-<!-- Collier MA, Dix MR, Hirst AC (2007) CSIRO Mk3 climate system model and meeting the strict IPCC AR4 data requirements.
-MODSIM07 International Congress on Modelling and Simulation : Land, water & environmental management : integrated systems for sustainability, 10-13 December [2007] : proceedings (eds Oxley L, Kulasiri D), Christchurch, pp.
-582-588.
-Modelling and Simulation Society of Australia and New Zealand.
--->
-<!-- Miroc-H: -->
-<!-- Hasumi H, Emori S (2004) K-1 coupled model (MIROC) description, K-1 technical report, 1. Center for Climate System Research, University of Tokyo, Tokyo, 34 pp. -->
+First we downloaded climatic data from WorldClim V2.0 which includes 19 bioclimatic variables commonly used in species distribution modelling [@fick_worldclim_2017]. 
+These bioclimatic variables were complemented with 16 of bioclimatic and topographic variables available in ENVIREM [@title_envirem_2018]. 
+This additional set of variables have been shown to be relevant to ecological or physiological processes and as such have the potential to improve species distribition models.
+All climatic data was obtained with a 2.5 arc-minuteresolution which provides a reasonable match to the locational accuracy of the species occurrences found in GBIF, particularly those that come from museum collections.
+Furthermore, we obtained habitat data from the
 

### 2019-06-19 paper/draft-info.Rmd
Update draft info

@@
 
-* Should I include more data?
+* Should I include more networks?
+Easy to get some more from other published studies.
+Could improve the manuscript but every new data set has to be cleaned independently and might take one to half a day per network.
+* Should I increase the resolution of the bioclimatic variables?
+Currently working with 2.5' (~5km).
+Increasing to 30'' (~1km) might improve the analysis but we're talking about working with ~25GB+ of data instead of the 1GB used now.
 
@@
 Quite a mess...
+* Downloaded bioclimatic and habitat data
 
@@
 
-* Manually fix the remaining species names that are incorrect and were not picked up by the automatic procedure
+* Manually fix the remaining species names that are incorrect and were not picked up by the automatic procedure. Doing 5-10 per day, so should be done in a couple months
 * Fix references. There are lots of mistakes re. author, years and publication venue.

### 2019-06-19 code/download_ocurrence_data.R
Figuring out best way to use GBIF API
occ_data seems to be the best alternative

@@ -22,9 +22,25 @@ download_sp_ocurrences <- function(this_sp_names){
   data_fields <- c('key', 'scientificName', 'decimalLatitude', 'decimalLongitude', 'geodeticDatum', 'countryCode', 'country', 'individualCount', 'coordinateUncertaintyInMeters', 'year', 'basisOfRecord')
   
   system.time({
-    b <- rgbif::occ_search(scientificName = 'Stachys albi', limit = 1000000) 
+    c <- rgbif::occ_data(scientificName = c('Phacelia secunda'), 
+                           hasCoordinate = TRUE,
+                           limit = 1000000) 
+  })
+  
+  system.time({
+    c('Phacelia secunda', 'Phacelia secunda') %>%
+      purrr::map(~rgbif::occ_search(scientificName = ., 
+                                    hasCoordinate = TRUE,
+                                    limit = 1000000) )
   })
  
+  
+  system.time({
+    rgbif::occ_search(scientificName = 'Stachys albicaulis', 
+                                    hasCoordinate = TRUE,
+                                    limit = 1000000) 
+  })
+  
   a <- rgbif::occ_download('taxonKey=7316195', 'hasCoordinate = true') 
   rgbif::occ_download_meta(a)
   f <- rgbif::occ_download_get(a, overwrite = T)

### 2019-06-27 main.R
Use chunked cleaning instead of the whole thing so that it doesn't runs out of memory when converting occurrence locations into a spatial object

@@ -183,7 +183,8 @@ download_ocurrence_data_plan <- drake_plan(
                                          returnclass = "sp", 
                                          scale = 10),
   country_data_sf = rnaturalearth::ne_countries(returnclass = "sf", scale = 10), 
-  cleaned_occurrences = clean_occurrences(occurrences, land_data, country_data_sf)
+  cleaned_occurrences = clean_occurrences_chunked(occurrences, land_data, country_data_sf),
+  n_cleaned_occurrences = count_occurrences_per_taxon(cleaned_occurrences)
 )
 
 # Clean ocurrence data -----------------------------------------------------

### 2019-06-28 paper/manuscript.Rmd
Start drafting methods for occurrence download
Add more info about the occurrence cleaning process

@@
 We assessed the validity of a scientific name by querying the Global Names Resolver database (https://resolver.globalnames.org) which includes taxonomic data from `r dplyr::n_distinct(taxize::gnr_datasources()$title)` taxonomic sources.
-Specifically, we used the function `gnr_resolve` from the R package `taxize `r as.character(packageVersion('taxize'))`` [@chamberlain_taxize_2013; @chamberlain_taxize_2019].
+Specifically, we used the function `gnr_resolve` from the R package `taxize` `r as.character(packageVersion('taxize'))` [@chamberlain_taxize_2013; @chamberlain_taxize_2019].
 
@@
 
-### Climatic and habitat
+### Species suitability
 
+Our next step was to determine the habitat suitability of the `r format(nrow(readd(spp_to_download)), big.mark = ',')` species that were present in at least `r numbers2words(readd(minimum_spp_locations))` communities.
+To do that we first fit a climatic envelope for each  of them which requires information about the climate and their known occurrences. 
+We retrieved occurrences from the Global Biodiversity Information Facility (https://www.gbif.org) using the R package `rgbif` `r as.character(packageVersion('taxize'))` [@chamberlain_r_2017; @chamberlain_rgbif_2019].
+We only requested occurrences that had geolocation information and no known geospatial issue.
+This resulted into roughly `r round(sum(readd(n_occurrences)$N)/1000000, digits = 1)` million occurrences. 
+We then filtered these occurrence and kept only those with higher quality information. 
+Specifically, we removed occurrences with a coordinate uncertainity larger than 100km and those recorded prior to 1945 (Audrey: ref? or why?).
+We also removed occurrences in which the number of individuals recorded was zero or more than 100 as such large counts are often erroneous (Audrey: ref? or why?). 
+We only kept occurrence records describing a human observation and preserved specimens as they are more reliable (Audrey: ref?why?). 
+After these filtering, we used the R package `CoordinateCleaner` `r as.character(packageVersion('taxize'))` [@zizka_coordinatecleaner_2019] to further identify (*i*) coordinates outside the borders of the country in which they were recorde, (*ii*) those arround a the country capital or the centroid of the country and province centroids, (*iii*) those arond a biodiversity institution, and (*iv*) those located within oceans.
+We used land and country data from Natural Earth (https://www.naturalearthdata.com) with a 1:10,000,000 scale. 
+This resulted in
+
+We then tried to retrieve occurrences for  species that were present in at least  communities in our dataset. 
+To do that we 
 First we downloaded climatic data from WorldClim V2.0 which includes 19 bioclimatic variables commonly used in species distribution modelling [@fick_worldclim_2017]. 

### 2019-06-29 code/clean-occurrence-data.R
correct typo in function argument

@@ -138,7 +138,7 @@ get_occurrences_datasets <- function(occurrences){
   unique(occurrences, by = "datasetKey")[, datasetKey]
 }
 
-get_gbif_key_groups <- function(occurences){
+get_gbif_key_groups <- function(occurrences){
   suppressPackageStartupMessages({
     library(data.table)
   })

### 2019-06-29 paper/manuscript.Rmd
say how many clean and dirty occurrences there are in total and how many species were represented

@@
 
-Our next step was to determine the habitat suitability of the `r format(nrow(readd(spp_to_download)), big.mark = ',')` species that were present in at least `r numbers2words(readd(minimum_spp_locations))` communities.
+```{r}
+loadd(spp_to_download, gbif_keys, n_occurrences)
+n_species_with_occurrences <- dplyr::full_join(spp_to_download, gbif_keys, 
+		 by = c("sp_name" = "queried_sp_name")) %>%
+  dplyr::inner_join(n_occurrences, by = c("key" = "taxonKey")) %$% 
+  dplyr::n_distinct(sp_id)
+
+n_species_with_clean_occurrences <-  dplyr::full_join(spp_to_download, gbif_keys, 
+		 by = c("sp_name" = "queried_sp_name")) %>%
+  dplyr::inner_join(n_cleaned_occurrences, by = c("key" = "taxonKey")) %$% 
+  dplyr::n_distinct(sp_id)
+
+```
+
+Our next step was to determine the habitat suitability of the species that were present in at least `r numbers2words(readd(minimum_spp_locations))` communities.
 To do that we first fit a climatic envelope for each  of them which requires information about the climate and their known occurrences. 
@@
 We only requested occurrences that had geolocation information and no known geospatial issue.
-This resulted into roughly `r round(sum(readd(n_occurrences)$N)/1000000, digits = 1)` million occurrences. 
+This resulted into roughly `r round(sum(n_occurrences$N)/1000000, digits = 1)` million occurrences for `r format(n_species_with_occurrences, big.mark = ",")` species.
+We were unable to find occurrences for the remaining `r dplyr::n_distinct(spp_to_download$sp_id) - n_species_with_occurrences` species. 
 We then filtered these occurrence and kept only those with higher quality information. 
@@
 We used land and country data from Natural Earth (https://www.naturalearthdata.com) with a 1:10,000,000 scale. 
-This resulted in
+This resulted in `r round(sum(n_cleaned_occurrences$N)/1000000, digits = 1)` million occurrences for `r n_species_with_cleaned_occurences` species.
 

### 2019-07-01 paper/manuscript.Rmd
Info about subspecies in the manuscript

@@
 
-n_sp_names_sp_level <- filter(spp, !sp_unidentified) %$% 
+n_sp_names_subsp_level <- filter(spp, is_subspecies) %$%
+  n_distinct(sp_name)
+
+n_sp_names_sp_level <- filter(spp, !sp_unidentified, !subspecies) %$% 
   n_distinct(sp_name)
@@
 All together, these data sources contained `r format(n_sp_names, big.mark = ",")` unique organism names; `r format(n_names_in_multiple_references_orig, big.mark = ",")` of them in more than one data source.
-Because assessing how habitat suitability affects interaction partners of plants and pollinators requires linking of species across different datasets, it was important to ensure that the cannnonical names used to identify species were as accurate as possible.
-From the total number of organisms, `r format(n_sp_names_sp_level, big.mark = ",")` were originally identified to the species-level, `r format(n_sp_names_gen_level, big.mark = ",")` to the genus level, and no taxonomic information was avaliable for the remaining `r format(n_no_tax_info, big.mark = ",")`.
+Because assessing how habitat suitability affects interaction partners of plants and pollinators requires linking of species across different datasets, it was important to ensure that the names used to identify species were as accurate as possible.
+From the total number of organisms,`r format(n_sp_names_subsp_level, big.mark = ",")` were identified to the subspecies or variety level, `r format(n_sp_names_sp_level, big.mark = ",")`  to the species level, `r format(n_sp_names_gen_level, big.mark = ",")` to the genus level, and no taxonomic information was avaliable for the remaining `r format(n_no_tax_info, big.mark = ",")`.
+As the species level was the most common taxonomic level available in our interaction datasets, for all further analysis, we consider only the species of organisms that were identified to the subspecies or variety level.
 

### 2019-07-01 paper/manuscript.Rmd
Correct typo of variable for number of cleaned names in msc

@@
 ```{r}
-loadd(spp_to_download, gbif_keys, n_occurrences)
+loadd(spp_to_download, gbif_keys, n_occurrences, n_cleaned_occurrences)
 n_species_with_occurrences <- dplyr::full_join(spp_to_download, gbif_keys, 
@@
 
-n_species_with_clean_occurrences <-  dplyr::full_join(spp_to_download, gbif_keys, 
+n_species_with_cleaned_occurrences <-  dplyr::full_join(spp_to_download, gbif_keys, 
 		 by = c("sp_name" = "queried_sp_name")) %>%
@@
 Our next step was to determine the habitat suitability of the species that were present in at least `r numbers2words(readd(minimum_spp_locations))` communities.
+When organims were identified to the subspecies or varieties, we , 
 To do that we first fit a climatic envelope for each  of them which requires information about the climate and their known occurrences. 
@@
 We used land and country data from Natural Earth (https://www.naturalearthdata.com) with a 1:10,000,000 scale. 
-This resulted in `r round(sum(n_cleaned_occurrences$N)/1000000, digits = 1)` million occurrences for `r n_species_with_cleaned_occurences` species.
+This resulted in `r round(sum(n_cleaned_occurrences$N)/1000000, digits = 1)` million occurrences for `r n_species_with_cleaned_occurrences` species.
 

### 2019-07-01 code/web_of_life_data.R
Error in filtering of total rows as I was using wrong col names

@@ -160,9 +160,12 @@ get_wol_interaction_list <- function(wol_data){
     dplyr::mutate(pla_genus = get_first_word(pla_name), 
                   pol_genus = get_first_word(pol_name))  %>%
     # just in case 
-    dplyr::filter(sp_name %in% c('Frequency of occurrences"',
-                                 'Numbers of flowers',
-                                 'Number of flowers')) %>%
+    dplyr::filter(pla_name %in% c('Frequency of occurrences"',
+                                  'Numbers of flowers',
+                                  'Number of flowers'), 
+                  pol_name %in% c('Frequency of occurrences"',
+                                  'Numbers of flowers',
+                                  'Number of flowers')) %>%
     dplyr::inner_join(locality_info, by = "net_name") %>%
     tibble::as_tibble() %>%
     dplyr::distinct(pla_name, pol_name, loc_id)

### 2019-07-02 paper/manuscript.Rmd
Minor edits to the methods distinguising species from subspecies/varieties

@@
 
-n_sp_names_sp_level <- filter(spp, !sp_unidentified, !subspecies) %$% 
+n_sp_names_sp_level_no_subsp <- filter(spp, !sp_unidentified, !subspecies) %$% 
+  n_distinct(sp_name)
+
+n_sp_names_sp_level <- filter(spp, !sp_unidentified) %$% 
   n_distinct(sp_name)
@@
 Because assessing how habitat suitability affects interaction partners of plants and pollinators requires linking of species across different datasets, it was important to ensure that the names used to identify species were as accurate as possible.
-From the total number of organisms,`r format(n_sp_names_subsp_level, big.mark = ",")` were identified to the subspecies or variety level, `r format(n_sp_names_sp_level, big.mark = ",")`  to the species level, `r format(n_sp_names_gen_level, big.mark = ",")` to the genus level, and no taxonomic information was avaliable for the remaining `r format(n_no_tax_info, big.mark = ",")`.
-As the species level was the most common taxonomic level available in our interaction datasets, for all further analysis, we consider only the species of organisms that were identified to the subspecies or variety level.
+From the total number of organisms,`r format(n_sp_names_subsp_level, big.mark = ",")` were identified to the subspecies or variety level, `r format(n_sp_names_sp_level_no_subsp, big.mark = ",")` to the species level, `r format(n_sp_names_gen_level, big.mark = ",")` to the genus level, and no taxonomic information was avaliable for the remaining `r format(n_no_tax_info, big.mark = ",")`.
+As the species level was the most common taxonomic rank available in our interaction datasets, in all further analysis, we group together subspecies or varieties within a same species.
 
-We were able to confirm the validity of `r format(n_sp_correct_in_data, big.mark = ",")` of the cannonical names used to identify organisms to the species level (roughly `r scales::percent(n_sp_correct_in_data/n_sp_names_sp_level, 1)`).
-We assessed the validity of a scientific name by querying the Global Names Resolver database (https://resolver.globalnames.org) which includes taxonomic data from `r dplyr::n_distinct(taxize::gnr_datasources()$title)` taxonomic sources.
+We were able to confirm the validity of `r format(n_sp_correct_in_data, big.mark = ",")` of the cannonical names used to identify organisms (roughly `r scales::percent(n_sp_correct_in_data/n_sp_names_sp_level, 1)`).
+We assessed the validity of a cannonical name by querying the Global Names Resolver database (https://resolver.globalnames.org) which includes data from `r dplyr::n_distinct(taxize::gnr_datasources()$title)` taxonomic sources.
 Specifically, we used the function `gnr_resolve` from the R package `taxize` `r as.character(packageVersion('taxize'))` [@chamberlain_taxize_2013; @chamberlain_taxize_2019].

### 2019-07-06 code/niche-analyisis.R
Missing arguments to occurrence_thining function

@@ -1,4 +1,4 @@
-thin_occurrences_per_species <- function(cleaned_occurrences){
+thin_occurrences_per_species <- function(cleaned_occurrences, gbif_key_groups, org_ids, worldclim_stack){
   suppressPackageStartupMessages({
     library(data.table)
   })
@@ -8,7 +8,7 @@ thin_occurrences_per_species <- function(cleaned_occurrences){
     dplyr::inner_join(org_ids, by = c("key_id" = "sp_key_id")) %>%
     data.table::as.data.table() %>%
     split(by = "org_id") %>%
-    purrr::map(thin_occurrences) %>%
+    purrr::map(thin_occurrences, worldclim_stack) %>%
     rbindlist()
 }
 
@@ -28,7 +28,7 @@ get_organisms_ids <- function(gbif_key_groups, gbif_keys, species_ids){
                   org_id = paste("org", org_id, sep = "_"))
 }
 
-thin_occurrences <- function(this_sp_occurrences){
+thin_occurrences <- function(this_sp_occurrences, worldclim_stack){
   # get latitudes and longitudes
   lon_lats <- this_sp_occurrences %>%
     .[, list(decimalLongitude, decimalLatitude)]

### 2019-07-06 main.R

@@ -198,7 +198,10 @@ download_ocurrence_data_plan <- drake_plan(
 climatic_niche_plan <- drake_plan(
   worldclim_stack = get_worldclim_stack(file_in("data/downloads/wordclim_2-5m.zip")), 
   org_ids = get_organisms_ids(gbif_key_groups, gbif_keys, species_ids),
-  thinned_occurrences = thin_occurrences_per_species(cleaned_occurrences)
+  thinned_occurrences = thin_occurrences_per_species(cleaned_occurrences, 
+                                                     gbif_key_groups,
+                                                     org_ids, 
+                                                     worldclim_stack)
 )
 
 # Referencing -------------------------------------------------------------
@@ -259,6 +262,7 @@ paper_plan <- rbind(
   get_data_plan,
   pre_process_int_plan,
   download_ocurrence_data_plan,
+  climatic_niche_plan,
   data_references_plan, 
   figures_plan, 
   reporting_plan

### 2019-07-06 paper/manuscript.Rmd
Recompile paper when citations change
Better present summary of occurrence download and cleaning methods

@@
 
-loadd(abs_wordcount, msc_wordcount, n_displays, n_references, keywords)
+loadd(abs_wordcount, msc_wordcount, n_displays, n_references, keywords, bibliography)
 loadd(interaction_citations)
@@
 
-n_sp_names_sp_level_no_subsp <- filter(spp, !sp_unidentified, !subspecies) %$% 
+n_sp_names_sp_level_no_subsp <- filter(spp, !sp_unidentified, !is_subspecies) %$% 
   n_distinct(sp_name)
@@
 ```{r}
-loadd(spp_to_download, gbif_keys, n_occurrences, n_cleaned_occurrences)
-n_species_with_occurrences <- dplyr::full_join(spp_to_download, gbif_keys, 
-		 by = c("sp_name" = "queried_sp_name")) %>%
-  dplyr::inner_join(n_occurrences, by = c("key" = "taxonKey")) %$% 
-  dplyr::n_distinct(sp_id)
+loadd(n_occurrences, n_cleaned_occurrences, n_dirty_occurrences, gbif_key_groups, org_ids)
 
-n_species_with_cleaned_occurrences <-  dplyr::full_join(spp_to_download, gbif_keys, 
-		 by = c("sp_name" = "queried_sp_name")) %>%
-  dplyr::inner_join(n_cleaned_occurrences, by = c("key" = "taxonKey")) %$% 
-  dplyr::n_distinct(sp_id)
+get_n_species <- . %>%
+  dplyr::inner_join(gbif_key_groups, by = "taxonKey") %>%
+  dplyr::inner_join(org_ids, by = c("key_id" = "sp_key_id")) %$%
+  dplyr::n_distinct(org_id)
 
+n_species_with_occurrences <- get_n_species(n_occurrences)
+n_species_with_cleaned_occurrences <- get_n_species(n_cleaned_occurrences) 
+n_species_with_dirty_occurrences <- get_n_species(n_dirty_occurrences)
 ```
 
-Our next step was to determine the habitat suitability of the species that were present in at least `r numbers2words(readd(minimum_spp_locations))` communities.
+Our next step was to determine the suitability of the species that were present in at least `r numbers2words(readd(minimum_spp_locations))` communities.
 When organims were identified to the subspecies or varieties, we , 
@@
 We retrieved occurrences from the Global Biodiversity Information Facility (https://www.gbif.org) using the R package `rgbif` `r as.character(packageVersion('taxize'))` [@chamberlain_r_2017; @chamberlain_rgbif_2019].
-We only requested occurrences that had geolocation information and no known geospatial issue.
-This resulted into roughly `r round(sum(n_occurrences$N)/1000000, digits = 1)` million occurrences for `r format(n_species_with_occurrences, big.mark = ",")` species.
-We were unable to find occurrences for the remaining `r dplyr::n_distinct(spp_to_download$sp_id) - n_species_with_occurrences` species. 
-We then filtered these occurrence and kept only those with higher quality information. 
-Specifically, we removed occurrences with a coordinate uncertainity larger than 100km and those recorded prior to 1945 (Audrey: ref? or why?).
-We also removed occurrences in which the number of individuals recorded was zero or more than 100 as such large counts are often erroneous (Audrey: ref? or why?). 
-We only kept occurrence records describing a human observation and preserved specimens as they are more reliable (Audrey: ref?why?). 
-After these filtering, we used the R package `CoordinateCleaner` `r as.character(packageVersion('taxize'))` [@zizka_coordinatecleaner_2019] to further identify (*i*) coordinates outside the borders of the country in which they were recorde, (*ii*) those arround a the country capital or the centroid of the country and province centroids, (*iii*) those arond a biodiversity institution, and (*iv*) those located within oceans.
-We used land and country data from Natural Earth (https://www.naturalearthdata.com) with a 1:10,000,000 scale. 
-This resulted in `r round(sum(n_cleaned_occurrences$N)/1000000, digits = 1)` million occurrences for `r n_species_with_cleaned_occurrences` species.
+For each species, we downloaded occurrences for which the coordinates of the observation were available and that had no known geospatial issue in the GBIF database.
+Roughly, we downloaded `r round(sum(n_occurrences$N)/1000000, digits = 1)` million occurrences for `r format(n_species_with_occurrences, big.mark = ",")` of the species of interest. 
+The occurrences obtained contain observations of mixed quality, so we applied a series of simple filters to remove those of lower quality. 
+Specifically, we removed all occurrences with (*i*) a coordinate uncertainity larger than 100km; (*ii*) those recorded prior to 1945 (ref?
+or why?); (*iii*) those in which the number of individuals recorded was either zero or more than 100 as such large counts are often erroneous (ref?
+or why?); and (*iv*) those occurrences in which the "basis of record" was not a human observation or a preserved specimen (ref?
+why?).
+We then used the R package `CoordinateCleaner` `r as.character(packageVersion('taxize'))` [@zizka_coordinatecleaner_2019] and land mass and country data from Natural Earth (https://www.naturalearthdata.com) with a 1:10,000,000 scale to further identify and remove problematic occurrences.
+We removed occurrences in which their coordinates (*v*) fell outside the borders of the country in which they were recorded; (*vi*) those arround a the country capital or the centroid of the country and province centroids; (*vii*) those arond a biodiversity institution; and (*viii*) those located within oceans.
+Thorugh this cleaning process, we removed with `r round(sum(n_dirty_occurrences$N)/1000000, digits = 1)` million occurrences accross `r n_species_with_dirty_occurrences` species.
 
+Because some of the occurrences are clustered across 
 We then tried to retrieve occurrences for  species that were present in at least  communities in our dataset. 

### 2019-07-06 paper/manuscript.Rmd
Explain climatic variable download before occurrence download

@@
 Our next step was to determine the suitability of the species that were present in at least `r numbers2words(readd(minimum_spp_locations))` communities.
-When organims were identified to the subspecies or varieties, we , 
-To do that we first fit a climatic envelope for each  of them which requires information about the climate and their known occurrences. 
-We retrieved occurrences from the Global Biodiversity Information Facility (https://www.gbif.org) using the R package `rgbif` `r as.character(packageVersion('taxize'))` [@chamberlain_r_2017; @chamberlain_rgbif_2019].
+To do that we first fit a climatic envelope for each  of them which requires information about the climate and habitat at the locations where the species occurrs. 
+We retrieved climatic data from WorldClim V2.0 which includes 19 bioclimatic variables commonly used in species distribution modelling [@fick_worldclim_2017]. 
+These bioclimatic variables were complemented with 16 of bioclimatic and topographic variables available in Envirem [@title_envirem_2018]. 
+This additional set of variables have been shown to be relevant to ecological or physiological processes and as such have the potential to improve species distribition models.
+All climatic data was obtained with a 2.5 arc-minute resolution. 
+This resilution provides a reasonable match to the locational accuracy of the species occurrences found in GBIF, particularly those that come preserved specimens in museum collections. 
+Furthermore, we obtained habitat data from The Nature Conservation's terrestrial ecoregions of the world [@olson_global_2002].
+
+We retrieved occurrences from the Global Biodiversity Information Facility (GBIF; https://www.gbif.org) using the R package `rgbif` `r as.character(packageVersion('taxize'))` [@chamberlain_r_2017; @chamberlain_rgbif_2019].
 For each species, we downloaded occurrences for which the coordinates of the observation were available and that had no known geospatial issue in the GBIF database.
@@
 We removed occurrences in which their coordinates (*v*) fell outside the borders of the country in which they were recorded; (*vi*) those arround a the country capital or the centroid of the country and province centroids; (*vii*) those arond a biodiversity institution; and (*viii*) those located within oceans.
-Thorugh this cleaning process, we removed with `r round(sum(n_dirty_occurrences$N)/1000000, digits = 1)` million occurrences accross `r n_species_with_dirty_occurrences` species.
+Thorugh this cleaning process, we removed with `r round(sum(n_dirty_occurrences$N)/1000000, digits = 1)` million occurrences distributed accross `r n_species_with_dirty_occurrences` species.
 
-Because some of the occurrences are clustered across 
-We then tried to retrieve occurrences for  species that were present in at least  communities in our dataset. 
-To do that we 
-First we downloaded climatic data from WorldClim V2.0 which includes 19 bioclimatic variables commonly used in species distribution modelling [@fick_worldclim_2017]. 
-These bioclimatic variables were complemented with 16 of bioclimatic and topographic variables available in ENVIREM [@title_envirem_2018]. 
-This additional set of variables have been shown to be relevant to ecological or physiological processes and as such have the potential to improve species distribition models.
-All climatic data was obtained with a 2.5 arc-minuteresolution which provides a reasonable match to the locational accuracy of the species occurrences found in GBIF, particularly those that come from museum collections.
-Furthermore, we obtained habitat data from the
+Some species occurrences are heavily clustered close to each other a location We then removed the spatial autocorrelation bias 
+Because some of the occurrences are clustered close to each other,
 

### 2019-07-09 code/niche-analyisis.R
Remove species with few occurrences

@@ -41,9 +41,11 @@ thin_occurrences <- function(this_sp_occurrences, worldclim_stack){
     unique(by = c("wc_grid")) 
 }
 
-get_worldclim_stack <- function(worldclim_zip){
-  worldclim_zip <- "data/downloads/wordclim_2-5m.zip"
-  temp_dir <- file.path(tempdir(), "wordclim")
+remove_sp_few_occurrences <- function(thinned_occurrences, min_occurrences = 5){
+  thinned_occurrences[, n := .N, by = org_id][] %>%
+    .[n >= 5] %>%
+    .[, n := NULL]
+}
   unzip(worldclim_zip, exdir = temp_dir)
   file_names <- list.files(temp_dir, full.names = T)
   raster::stack(file_names)

### 2019-07-09 main.R

@@ -202,6 +202,7 @@ climatic_niche_plan <- drake_plan(
                                                      gbif_key_groups,
                                                      org_ids, 
                                                      worldclim_stack)
+  good_qual_occurrences = remove_sp_few_occurrences(thinned_occurrences, min_occurrences = 5), 
 )
 
 # Referencing -------------------------------------------------------------

### 2019-07-09 code/niche-analyisis.R
read ecoregions

@@ -46,6 +46,14 @@ remove_sp_few_occurrences <- function(thinned_occurrences, min_occurrences = 5){
     .[n >= 5] %>%
     .[, n := NULL]
 }
+
+read_ecoregions <- function(shapefile_path){
+  extract_dir <- file.path(tempdir(), "ecoregion")
+  unzip(shapefile_path, exdir = extract_dir)
+  sf::st_read(extract_dir) %>% 
+    dplyr::select(ECO_NAME, WWF_MHTNAM, WWF_REALM2) %>% 
+    dplyr::transmute('ecoregion' = ECO_NAME, 'major_habitat_type' = WWF_MHTNAM, 'biogeographic_realm'= WWF_REALM2)
+}
   unzip(worldclim_zip, exdir = temp_dir)
   file_names <- list.files(temp_dir, full.names = T)
   raster::stack(file_names)

### 2019-07-09 main.R

@@ -203,6 +203,7 @@ climatic_niche_plan <- drake_plan(
                                                      org_ids, 
                                                      worldclim_stack)
   good_qual_occurrences = remove_sp_few_occurrences(thinned_occurrences, min_occurrences = 5), 
+  ecoregions = read_ecoregions(file_in("data/downloads/terrestrial-ecoregions.zip"))
 )
 
 # Referencing -------------------------------------------------------------

### 2019-07-09 paper/draft-info.Rmd
Update draft info

@@
 Increasing to 30'' (~1km) might improve the analysis but we're talking about working with ~25GB+ of data instead of the 1GB used now.
+* Audrey: Could you please fill in the gaps in the rationale behind filtering out occurrences with potential low quality coordinates (\lr{rationale-occurrence-filtering})
 
@@
 * Downloaded bioclimatic and habitat data
+* Dowloaded species occurrences. Wasn't straightforward as there is a lot of species and lots of restrictions with the GBIF API. About a week getting this to work.
 

### 2019-07-09 paper/manuscript.Rmd
Update draft info

@@
 The occurrences obtained contain observations of mixed quality, so we applied a series of simple filters to remove those of lower quality. 
-Specifically, we removed all occurrences with (*i*) a coordinate uncertainity larger than 100km; (*ii*) those recorded prior to 1945 (ref?
+\R{rationale-occurrence-filtering}Specifically, we removed all occurrences with (*i*) a coordinate uncertainity larger than 100km; (*ii*) those recorded prior to 1945 (ref?
 or why?); (*iii*) those in which the number of individuals recorded was either zero or more than 100 as such large counts are often erroneous (ref?

### 2019-07-09 code/niche-analyisis.R
Temporary stuff to merge stacks

@@ -54,7 +54,64 @@ read_ecoregions <- function(shapefile_path){
     dplyr::select(ECO_NAME, WWF_MHTNAM, WWF_REALM2) %>% 
     dplyr::transmute('ecoregion' = ECO_NAME, 'major_habitat_type' = WWF_MHTNAM, 'biogeographic_realm'= WWF_REALM2)
 }
+
+get_raster_stack <- function(worldclim_zip){
+  # worldclim_zip <- "data/downloads/wordclim_2-5m.zip"
+  temp_dir <- tempfile()
   unzip(worldclim_zip, exdir = temp_dir)
   file_names <- list.files(temp_dir, full.names = T)
   raster::stack(file_names)
+}
+
+merge_stacks <- function(worldclim_stack, envirem_stack, topo_stack){
+  extents <- raster_stacks %>%
+    purrr::map(raster::extent) 
+  
+  smallest_extents_index <- extents %>% 
+    purrr::map(as.vector) %>%
+    purrr::map(abs) %>% 
+    purrr::pmap(cbind) %>%
+    purrr::map(as.vector) %>%
+    purrr::map(which.min)
+  
+  smallest_extent <- extents %>%
+    purrr::map(as.vector) %>%
+    purrr::pmap(cbind) %>%
+    purrr::map2_dbl(smallest_extents_index, function(x,y) x[y]) %>%
+    raster::extent()
+  
+  worldclim_stack %>%
+    purrr::map(~raster::crop(raster::raster(.)), smallest_extent)
+  
+  stack_names <-     purrr
+
+  1:raster::nlayers(worldclim_stack) %>%
+    purrr::map(~raster::subset(worldclim_stack, .)) %>%
+    # purrr::map(raster::raster) %>%
+    purrr::map(raster::crop, smallest_extent) %>%
+    # purrr::map2(names(worldclim_stack), `names<-`) %>%
+    # purrr::map(class)
+    raster::stack()
+    # raster::crop(raster::raster(raster::subset(worldclim_stack, 1)), smallest_extent)
+}
+
+crop_raster_stack <- function(stack, extent){
+  
+}
+
+get_climate_species <- function(this_occurrences, ecoregions){
+  this_occurrences <- good_qual_occurrences[org_id == "org_00001"]
+  this_occurrences_sf <- sf::st_as_sf(this_occurrences, coords = c("decimalLongitude" ,  "decimalLatitude"), crs = 4326)
[…]

### 2019-07-09 main.R

@@ -196,12 +196,17 @@ download_ocurrence_data_plan <- drake_plan(
 # Clean ocurrence data -----------------------------------------------------
 
 climatic_niche_plan <- drake_plan(
-  worldclim_stack = get_worldclim_stack(file_in("data/downloads/wordclim_2-5m.zip")), 
+  worldclim_stack = get_raster_stack(file_in("data/downloads/wordclim_2-5m.zip")), 
+  envirem_stack = get_raster_stack(file_in("data/downloads/envirem_2-5m.zip")),
+  topo_stack = get_raster_stack(file_in("data/downloads/envirem_topo_2-5m.zip")),
+  raster_stacks = list(worldclim = worldclim_stack, 
+                       envirem = envirem_stack, 
+                       topo = topo_stack),
   org_ids = get_organisms_ids(gbif_key_groups, gbif_keys, species_ids),
   thinned_occurrences = thin_occurrences_per_species(cleaned_occurrences, 
                                                      gbif_key_groups,
                                                      org_ids, 
-                                                     worldclim_stack)
+                                                     worldclim_stack), 
   good_qual_occurrences = remove_sp_few_occurrences(thinned_occurrences, min_occurrences = 5), 
   ecoregions = read_ecoregions(file_in("data/downloads/terrestrial-ecoregions.zip"))
 )

### 2019-07-15 code/niche-analyisis.R
Return NULL if no NA cells exist in the climatic-occurrence frame
Issue #16

@@ -136,6 +136,9 @@ average_climate_buffer <- function(climate_in_occurrences, pattern, stack, n_chu
     wc_grid # %>% 
     # extract(1:10)
   
+  # if there are no NA values just don't return anything
+  if (length(problematic_grids) == 0) return(NULL)
+  
   raster::xyFromCell(stack, problematic_grids) %>%
     raster::extract(stack, ., buffer = buffer,
                     cellnumbers = TRUE, 
@@ -145,6 +148,9 @@ average_climate_buffer <- function(climate_in_occurrences, pattern, stack, n_chu
 }
 
 fill_averages <- function(frame_with_na, averages){
+  
+  # If there are no averages return the same thing we got
+  if (is.null(averages)) return(frame_with_na)
   
   cols <- colnames(averages) %>% head(-1)
   

### 2019-07-15 code/niche-analyisis.R
Remove NAs from mean calculation when filling NA cells
Issue #16

@@ -142,7 +142,7 @@ average_climate_buffer <- function(climate_in_occurrences, pattern, stack, n_chu
   raster::xyFromCell(stack, problematic_grids) %>%
     raster::extract(stack, ., buffer = buffer,
                     cellnumbers = TRUE, 
-                    fun = mean) %>%
+                    fun = function(x) mean(x, na.rm = TRUE)) %>%
     tibble::as_tibble() %>%
     dplyr::mutate(wc_grid = problematic_grids)
 }

### 2019-07-15 paper/manuscript.Rmd
State that bioclimatic data are rasters composed by cells

@@
 This additional set of variables have been shown to be relevant to ecological or physiological processes and as such have the potential to improve species distribition models.
-All climatic data was obtained with a 2.5 arc-minute resolution. 
-This resilution provides a reasonable match to the locational accuracy of the species occurrences found in GBIF, particularly those that come preserved specimens in museum collections. 
+All climatic data was obtained as rasters composed by cells of 2.5 arc-minutes. 
+This resolution provides a reasonable match to the locational accuracy of the species occurrences found in GBIF, particularly those that come preserved specimens in museum collections. 
 Furthermore, we obtained habitat data from The Nature Conservation's terrestrial ecoregions of the world [@olson_global_2002].

### 2019-07-15 code/niche-analyisis.R
Fill cells by stages starting with a smaller buffer
Close #16

@@ -124,6 +124,7 @@ fill_missing_values <- function(climate_in_occurrences, raster_stacks, n_chunks,
 
   climate_in_occurrences %>%
     fill_averages(topo_averages) %>%
+    # dplyr::filter(wc_grid %in% problematic_grids) %>% View
     fill_averages(worldclim_averages) %>%
     fill_averages(envirem_averages)
 }  
@@ -164,7 +165,10 @@ fill_averages <- function(frame_with_na, averages){
   return(frame_with_na)
 }
 
-  
+
+count_occurrences_per_organism <- function(x){
+  x[, .N, by = org_id]
+}
 
 
 

### 2019-07-15 main.R

@@ -202,13 +202,19 @@ climatic_niche_plan <- drake_plan(
                                                      gbif_key_groups,
                                                      org_ids, 
                                                      get_climate()), 
-  climate_in_occurrences = get_climate_for_occurrences(thinned_occurrences, get_climate()),
+ n_thinned_occurrences = count_occurrences_per_organism(thinned_occurrences),
+ climate_in_occurrences = get_climate_for_occurrences(thinned_occurrences, get_climate()),
   filled_climate_in_occurrences = fill_missing_values(climate_in_occurrences, 
-                                                      get_climate(), 
-                                                      n_chunks,
-                                                      climate_buffer),
-  # good_qual_occurrences = remove_sp_few_occurrences(thinned_occurrences, min_occurrences = 5), 
-  ecoregions = read_ecoregions(file_in("data/downloads/terrestrial-ecoregions.zip"))
+ filled_climate_in_occurrences_1 = fill_missing_values(climate_in_occurrences, 
+                                                     get_climate(), 
+                                                     n_chunks,
+                                                     climate_buffer),
+ filled_climate_in_occurrences_2 = fill_missing_values(filled_climate_in_occurrences_1, 
+                                                     get_climate(), 
+                                                     n_chunks,
+                                                     climate_buffer*2),
+ # good_qual_occurrences = remove_sp_few_occurrences(thinned_occurrences, min_occurrences = 5), 
+ ecoregions = read_ecoregions(file_in("data/downloads/terrestrial-ecoregions.zip"))
 )
 
 # Referencing -------------------------------------------------------------

### 2019-07-15 main.R
Get stats of filling

@@ -204,15 +204,17 @@ climatic_niche_plan <- drake_plan(
                                                      get_climate()), 
  n_thinned_occurrences = count_occurrences_per_organism(thinned_occurrences),
  climate_in_occurrences = get_climate_for_occurrences(thinned_occurrences, get_climate()),
-  filled_climate_in_occurrences = fill_missing_values(climate_in_occurrences, 
+ complete_climate_cells = table(complete.cases(climate_in_occurrences)), 
  filled_climate_in_occurrences_1 = fill_missing_values(climate_in_occurrences, 
                                                      get_climate(), 
                                                      n_chunks,
                                                      climate_buffer),
+ complete_filled_cells_1 = table(complete.cases(filled_climate_in_occurrences_1)),
  filled_climate_in_occurrences_2 = fill_missing_values(filled_climate_in_occurrences_1, 
                                                      get_climate(), 
                                                      n_chunks,
                                                      climate_buffer*2),
+ complete_filled_cells_2 = table(complete.cases(filled_climate_in_occurrences_2)),
  # good_qual_occurrences = remove_sp_few_occurrences(thinned_occurrences, min_occurrences = 5), 
  ecoregions = read_ecoregions(file_in("data/downloads/terrestrial-ecoregions.zip"))
 )

### 2019-07-15 paper/manuscript.Rmd
Explain filling procedure in methods

@@
 ```{r}
-loadd(n_occurrences, n_cleaned_occurrences, n_dirty_occurrences, gbif_key_groups, org_ids)
+loadd(n_occurrences, n_cleaned_occurrences, n_dirty_occurrences, gbif_key_groups, org_ids, n_thinned_occurrences, complete_climate_cells, complete_filled_cells_1, complete_filled_cells_2)
 
@@
 n_species_with_dirty_occurrences <- get_n_species(n_dirty_occurrences)
+percent_thinned <- 1 - sum(n_thinned_occurrences$N) / sum(n_cleaned_occurrences$N)
+percent_filled_round_one <- 1-complete_filled_cells_1[1]/complete_climate_cells[1]
 ```
@@
 We retrieved climatic data from WorldClim V2.0 which includes 19 bioclimatic variables commonly used in species distribution modelling [@fick_worldclim_2017]. 
-These bioclimatic variables were complemented with 16 of bioclimatic and topographic variables available in Envirem [@title_envirem_2018]. 
+These bioclimatic variables were complemented with 18 of bioclimatic and topographic variables available in Envirem [@title_envirem_2018]. 
 This additional set of variables have been shown to be relevant to ecological or physiological processes and as such have the potential to improve species distribition models.
@@
 
-Some species occurrences are heavily clustered close to each other a location We then removed the spatial autocorrelation bias 
-Because some of the occurrences are clustered close to each other,
+Next, we overlapped the occurrence and our environmental rasters such that each occurrence location is characterized by a vector with information of our 37 bioclimatic and topographic variables . 
+If a species had more than one occurrence records within one of the cells of the bioclimatic raster we only included one of the occurrence records. 
+We did this to avoid giving more weight to areas with a high number of occurrences, a common scenario in occurrrence records collected opportunistically as the ones we use here. 
+Overall we removed `r scales::percent(percent_thinned)` of the occurrences which resulted in a total of `r round(sum(n_thinned_occurrences$N)/1000000, digits = 1)` million occurrences used in our niche analysis.
+A common issue of terrestrial bioclimatic datasets is that the boundaries of the cells with information do not exactly match the land mass boundaries. 
+The result of this missmatch is that at least one of the environmental variables was not available for `r format(complete_climate_cells[1], big.mark = ",")` of the raster cells with occurrences (`r scales::percent(complete_climate_cells[1]/sum(complete_climate_cells), accuracy = 0.1)` of the total).
+As expected a vast majority of these cells were close to the shore. 
+To address this issue, calculated average value of environmental variables within a `r config$climate_buffer/1000`km buffer of the center of the cell where the variable is missing, and used it to approximate the value of the variable in that cell.
+In this fashion we were able to fill environmental variables for `r scales::percent(percent_filled_round_one, accuracy = 0.1)` of the cells were they were missing. 
+To fill the remaining `r format(complete_filled_cells_1[1], big.mark= ",")` cells, we repeated the aforementioned procedure but using a `r config$climate_buffer*2/1000`km buffer. 
+We removed from further analyis occurrences located within the `r complete_filled_cells_2[1]` cells for which we were unable to fill environmental variables.
 

### 2019-07-20 paper/manuscript.Rmd
Say I added GBIF with network occurrences
Start drafting how niche suitability is calculated

@@
 Thorugh this cleaning process, we removed with `r round(sum(n_dirty_occurrences$N)/1000000, digits = 1)` million occurrences distributed accross `r n_species_with_dirty_occurrences` species. 
+We added the occurrences from our plant-pollinator networks to the cleaned occurrences retrieved from GBIF.
 
@@
 To fill the remaining `r format(complete_filled_cells_1[1], big.mark= ",")` cells, we repeated the aforementioned procedure but using a `r config$climate_buffer*2/1000`km buffer.
+
+Our main objective is to investigate wether the suitability of the environment was to obtain the suitability of the environment at the locations for which we have community data. 
+This involves two steps. 
+First, we determine the species' grinellian niche, the range of environmental conditions that are suitable for a positive growth rate. 
+We assume that the suitability of a particular set of environmental conditions (a point in the environmental space) can be inferred from the density of occurrences under these conditions. 
+This is, areas of the niche that have a higher density of occurrences have higher suitability and can be interpreted as the core of the species distribution in environental space. 
+Contrastingly, areas with a lower density are comparatively less suitable and represent the fringes of the species distribution. 
+The second step is to determine the location of our plant-pollinator communities (where the species is present) in the environmental space and calculate its corresponding environmental suitability.
+
+To determine the environmental niche of each species we use a principal component analysis of the 37 bioclimatic variables associated with the species occurrences. 
+Specifically we use the `dudi.pca` function from the R package `ade4` `r as.character(packageVersion('ade4'))` [@dray_ade4_2007] and center and scale all bioclimatic variables to have a mean of 0 and a unit standard deviation.
+We use the first two components to define the environmental space. 
+We then  The use of a kernel smoother makes the process of moving from geographical space to multivariate environmental space independent of both sam- pling effort and arbitrary choice of resolution in environmental space
+
 We removed from further analyis occurrences located within the `r complete_filled_cells_2[1]` cells for which we were unable to fill environmental variables.

### 2019-07-20 paper/manuscript.Rmd
Explain how kernel density was estimated

@@
 
-To determine the environmental niche of each species we use a principal component analysis of the 37 bioclimatic variables associated with the species occurrences. 
+To determine the environmental space of each species we use the first two components from a principal component analysis of the 37 bioclimatic variables associated with the species occurrences. 
 Specifically we use the `dudi.pca` function from the R package `ade4` `r as.character(packageVersion('ade4'))` [@dray_ade4_2007] and center and scale all bioclimatic variables to have a mean of 0 and a unit standard deviation.
-We use the first two components to define the environmental space. 
-We then  The use of a kernel smoother makes the process of moving from geographical space to multivariate environmental space independent of both sam- pling effort and arbitrary choice of resolution in environmental space
+We then estimate a kernel density function to determine a smooth density of occurrences in the environmenta space. 
+The main advantage of using a kernel smoother is that it reduces the sensitivity of the niche to sampling effort and the resolution chosen for the environmental space grid [@broennimann_measuring_2012].
+To calculate the kernel we use `ecospat.grid.clim.dyn` from the R package `ecospat` `r as.character(packageVersion('ecospat'))` [@ecospat_citation] with a grid resolution of 200.
+We normalise the occurrence density such that our suitability ranges beetween 1 for the grids with environmental conditions in which the species was most commonly observed and 0 for the grids in which it was never observed.
+We then determine the location in environmental space of the plant-pollinator communities where the species is present using the function `suprow` from `ade4` and calculate its corresponding suitability using the R package `raster` `r as.character(packageVersion('raster'))` [@raster_citation].
 

### 2019-07-21 code/niche-sensitivity.R
Move minimum suitability error to config file

@@ -91,7 +91,7 @@ mae <- function(x, y){
   sum(abs(x - y)) / length(x)
 }
 
-determine_min_occurrences <- function(error_subsamples){
+determine_min_occurrences <- function(error_subsamples, min_suitability_error){
   error_subsamples %>%
     dplyr::filter(niche_space == "single_species") %>%
     dplyr::mutate(prop_occ = n_occ/n_net_occurrences) %>%
@@ -102,7 +102,7 @@ determine_min_occurrences <- function(error_subsamples){
                                          max(error_subsamples$n_occ)/
                                            error_subsamples$n_net_occurrences[1],
                                          1000))) %$%
-    approx(x = .fitted, y = prop_occ, 0.1) %$%
+    approx(x = .fitted, y = prop_occ, min_suitability_error) %$%
     round_any(y, 5, ceiling)
 }
 

### 2019-07-21 main.R

@@ -38,7 +38,8 @@ configuration_plan <- drake_plan(
   n_chunks = config$n_chunks, 
   climate_buffer = config$climate_buffer, 
   env_space_resolution = config$env_space_resolution,
-  n_subsamples = config$n_subsamples
+  n_subsamples = config$n_subsamples, 
+  min_suitability_error = config$min_suitability_error
 )
 
 # Download data ----------------------------------------------------------
@@ -251,7 +252,7 @@ climatic_niche_plan <- drake_plan(
                                             sensitivity_species_ids[1], 
                                             n = n_subsamples),
  error_subsamples = calc_error_subsamples(suitability_subsamples),
- min_occurrences_factor = determine_min_occurrences(error_subsamples),
+ min_occurrences_factor = determine_min_occurrences(error_subsamples, min_suitability_error),
  enough_occurrences = remove_sp_few_occurrences(thinned_occurrences, min_occurrences_factor),
  independent_suitability = calc_suitability_independently_all(
    enough_occurrences, 

### 2019-07-21 paper/manuscript.Rmd
Explain sensitivity analysis in manuscript

@@
 To fill the remaining `r format(complete_filled_cells_1[1], big.mark= ",")` cells, we repeated the aforementioned procedure but using a `r config$climate_buffer*2/1000`km buffer. 
+We removed from further analyis occurrences located within the `r complete_filled_cells_2[1]` cells for which we were unable to fill environmental variables.
 
@@
 
-To determine the environmental space of each species we use the first two components from a principal component analysis of the 37 bioclimatic variables associated with the species occurrences. 
+To determine the environmental space we use the first two components from a principal component analysis of the 37 bioclimatic variables associated with the species occurrences. 
 Specifically we use the `dudi.pca` function from the R package `ade4` `r as.character(packageVersion('ade4'))` [@dray_ade4_2007] and center and scale all bioclimatic variables to have a mean of 0 and a unit standard deviation.
-We then estimate a kernel density function to determine a smooth density of occurrences in the environmenta space. 
-The main advantage of using a kernel smoother is that it reduces the sensitivity of the niche to sampling effort and the resolution chosen for the environmental space grid [@broennimann_measuring_2012].
+We then determine the position of species occurrences in the environmental space and estimate their bivariate density distribution using the kernel method. 
+The main advantage of using the kernel method is that it reduces the sensitivity of the niche to sampling effort and the resolution chosen for the environmental space grid [@broennimann_measuring_2012].
 To calculate the kernel we use `ecospat.grid.clim.dyn` from the R package `ecospat` `r as.character(packageVersion('ecospat'))` [@ecospat_citation] with a grid resolution of 200.
-We normalise the occurrence density such that our suitability ranges beetween 1 for the grids with environmental conditions in which the species was most commonly observed and 0 for the grids in which it was never observed.
+We then normalise the occurrence density distribution such that our suitability ranges beetween 1 for the grids with environmental conditions in which the species was most commonly observed and 0 for the grids in which it was never observed.
 We then determine the location in environmental space of the plant-pollinator communities where the species is present using the function `suprow` from `ade4` and calculate its corresponding suitability using the R package `raster` `r as.character(packageVersion('raster'))` [@raster_citation].
 
-We removed from further analyis occurrences located within the `r complete_filled_cells_2[1]` cells for which we were unable to fill environmental variables.
+```{r sensitivity-analysis-calculations}
+loadd(sensitivity_species_name, n_enough_occurrences)
+n_occ_sensitivity_species <- n_thinned_occurrences %>%
+  dplyr::filter(org_id == sensitivity_species_name$org_id[1]) %$% N
+
+n_spp_not_enough_occ <- nrow(n_thinned_occurrences) - nrow(n_enough_occurrences)
+```
+
+We used a sensitivity analysis to determine the minimum number of occurrences that are necessary to have robust environmental suitability values in our communities. 
+For that we used the species with most occurrences available, *`r sensitivity_species_name$canonicalName`*, and calculated the mean absolute error of the suitability values obtained with `r numbers2words(config$n_subsamples)` subsamples from the `r format(n_occ_sensitivity_species, big.mark  =","`  occurrences available from GBIF.
+We found that, when we calculate the environmental space independently for each sepecies, we need roughly `r readd(min_occurrences_factor)` independent occurrences for each community for which we calculated a suitability value in order to obtain a mean absolute error below `r config$min_suitability_error` (Fig.
+\@ref(fig:fig-sensitivity-analysis)).
+We therefore removed from further analyses `r n_spp_not_enough_occ` species for which we did not have enough occurrences to obtain robust estimates.
+
+```{r fig-sensitivity-analysis, fig.width = width('single'), fig.height = 2.2, fig.cap = "asd"}
+readd(fig_sensitivity_analysis)
+```
 

### 2019-07-21 main.R
Count number of species with enough occurrences

@@ -254,6 +254,7 @@ climatic_niche_plan <- drake_plan(
  error_subsamples = calc_error_subsamples(suitability_subsamples),
  min_occurrences_factor = determine_min_occurrences(error_subsamples, min_suitability_error),
  enough_occurrences = remove_sp_few_occurrences(thinned_occurrences, min_occurrences_factor),
+ n_enough_occurrences = count_occurrences_per_organism(enough_occurrences),
  independent_suitability = calc_suitability_independently_all(
    enough_occurrences, 
    interactions_org, 

### 2019-07-23 code/niche-analyisis.R
keep location ID when calculating suitability

@@ -399,7 +399,8 @@ calc_suitability <- function(
   # Put it all in a nice data frame format
   tibble::tibble(org_id = this_sp, 
                  suitability = suitabiliy, 
-                 w = w)
+                 w = w, 
+                 loc_id = this_net_locations)
 }
 
 # Gicen some locations (coded as a grid in the climate thingy) find their projection in niche space 

### 2019-07-23 code/suitability_vs_degree.R
draft of degree metrics for analysis

@@ -1,0 +1,66 @@
+ints_as_nets <- function(interactions_org){
+  interactions_org %>%
+    split(.$loc_id) %>%
+    purrr::map(dplyr::select, -loc_id) %>%
+    purrr::map(igraph::graph_from_data_frame, directed = FALSE) 
+
+}
+
+calc_org_degree <- function(nets){
+  degree_per_net <- nets %>%
+    purrr::map(igraph::degree) %>%
+    purrr::map_dfr(~tibble::tibble(org_id = names(.), k = .), .id = "loc_id")
+  
+  global_degree <- purrr::lift_dl(igraph::union)(nets) %>%
+    igraph::degree() %>%
+    tibble::tibble(org_id = names(.), k_global = .)
+  
+  net_size <- nets %>%
+    purrr::map(igraph::V) %>%
+    purrr::map(length) %>%
+    purrr::imap_dfr(~tibble(loc_id = .y, n = .x))
+  
+  degree_per_net %>%
+    dplyr::full_join(global_degree, by = "org_id") %>%
+    dplyr::full_join(net_size, by = "loc_id") %>% 
+    dplyr::mutate(normalised_k = k/n, 
+                  proportion_k = k/k_global)
+}
+
+get_possible_interactions <- function(interactions_org){
+  interactions_org %>%
+    dplyr::distinct() %>%
+    split(.$loc_id) %>%
+    purrr::map(tidyr::complete, pla_id, ani_id) %>%
+    purrr::map_dfr(dplyr::rename, int = loc_id, .id = "loc_id") %>%
+    dplyr::mutate(int = !is.na(int)) 
+}
+
+get_realised_to_possible <- function(possible_interactions){
+  
+  possible_interactions <-interactions_org %>%
+    dplyr::distinct() %>%
+    split(.$loc_id) %>%
+    purrr::map(tidyr::complete, pla_id, ani_id) %>%
+    purrr::map_dfr(dplyr::rename, int = loc_id, .id = "loc_id") %>%
+    dplyr::mutate(int = !is.na(int)) 
+  
+  possible_degree <- possible_interactions %>%
+    dplyr::group_by(pla_id, ani_id) %>%
+    dplyr::filter(any(int)) %>% 
+    tidyr::gather(key = "guild", 
+                  value = "org_id", 
+                  ani_id, pla_id) %>%
+    dplyr::group_by(org_id) %>%
+    dplyr::group_by(loc_id, org_id) %>%
[…]

### 2019-07-23 main.R

@@ -263,9 +263,13 @@ climatic_niche_plan <- drake_plan(
  ecoregions = read_ecoregions(file_in("data/downloads/terrestrial-ecoregions.zip"))
 )
 
-# Explore niche -----------------------------------------------------------
+# Suitability vs. generalism  ----------------------------------------------
 
-# niche_exploration_plan <-
+suitability_vs_generalism_plan <- drake::drake_plan(
+  nets = ints_as_nets(interactions_org), 
+  possible_interactions = get_possible_interactions(interactions_org), 
+  org_degree = calc_org_degree(nets)
+)
 
 # Referencing -------------------------------------------------------------
 
@@ -330,6 +334,7 @@ paper_plan <- rbind(
   pre_process_int_plan,
   download_ocurrence_data_plan,
   climatic_niche_plan,
+  suitability_vs_generalism_plan,
   data_references_plan, 
   figures_plan, 
   reporting_plan

### 2019-07-23 paper/manuscript.Rmd
Add a VERY rough idea for the intro

@@
 # Introduction
+
+Interactions are selected by species depending on the relative benefit they provide.
+The assumption goes that species with a large number of interactions are benefit relatively little from each of them, and species with a small number benefit largely with them, this is they focus in more optimal pollinators.
+
+AND
+
+We know that interactions are influenced by the environment.
+
+BUT
+
+We don't know how exactly wether the enviroment influences the patterns of generalisation/specialization.
+
+One option is that when species are in detrimental environmental conditions focus on most optimal partners and as such interact with a smaller number of species. 
+An alternative hypotheisis is that when species are in favourable environmental conditions they can afford to be more picky about their interactions and as such avoid those of less value, while individuals in unfavourable conditions must get rewards from whatever they can get.
+
+THEREFORE
+
+We used a global dataset on plant pollinator interactions, species occurrence, and bioclimatic data to test these hypotheses. 
+If the first option is true we should see a negative relationship between environmental sutability and the relative degree of a species. 
+If the second option is true we should see the opposite, a positive relationship between environmental suitability and the relative degree of a species.
 

### 2019-07-23 paper/manuscript.Rmd
Add caption for sensitivity analysis figure

@@
 ```{r sensitivity-analysis-calculations}
-loadd(sensitivity_species_name, n_enough_occurrences)
+loadd(sensitivity_species_name)
+loadd(n_enough_occurrences)
 n_occ_sensitivity_species <- n_thinned_occurrences %>%
@@
 We used a sensitivity analysis to determine the minimum number of occurrences that are necessary to have robust environmental suitability values in our communities. 
-For that we used the species with most occurrences available, *`r sensitivity_species_name$canonicalName`*, and calculated the mean absolute error of the suitability values obtained with `r numbers2words(config$n_subsamples)` subsamples from the `r format(n_occ_sensitivity_species, big.mark  =","`  occurrences available from GBIF.
+For that we used the species with most occurrences available, *`r sensitivity_species_name$canonicalName`*, and calculated the mean absolute error of the suitability values obtained with `r numbers2words(config$n_subsamples)` subsamples from the `r format(n_occ_sensitivity_species, big.mark  =",")`  occurrences available from GBIF.
 We found that, when we calculate the environmental space independently for each sepecies, we need roughly `r readd(min_occurrences_factor)` independent occurrences for each community for which we calculated a suitability value in order to obtain a mean absolute error below `r config$min_suitability_error` (Fig.
@@
 
-```{r fig-sensitivity-analysis, fig.width = width('single'), fig.height = 2.2, fig.cap = "asd"}
+```{r fig-sensitivity-analysis, fig.width = width('single'), fig.height = 2.2, fig.cap = fig_sensitivity_analysis_legend}
+
+fig_sensitivity_analysis_legend <- 
+  paste0("Sensitivity analysis of environmental suitability error. ",
+         "The number of independent occurrences retrieved from GBIF is inversely related to the error of environmental suitability for our plant-pollinator networks.", 
+         "The error was smaller when environmental space, where species ocurrences are projected, is calculated independently for each species. ", 
+         "The sensitivity analysis was performed by subsampling occurrences of", 
+         " *", sensitivity_species_name$canonicalName, "* ", 
+         "the species in our dataset with the largest number of occurrences in GBIF, which was recorded in two of our communities.")
+
 readd(fig_sensitivity_analysis)
 ```
+
+## Model
+
+We then investigated
 

### 2019-07-26 paper/manuscript.Rmd
Add some notes to Intro and discussion from bibliography checks

@@
 If the second option is true we should see the opposite, a positive relationship between environmental suitability and the relative degree of a species.
+
+Notes:
+
+**From donoso et al 2017: ** Intro: It is generally agreed that both neutral and niche-driven processes contribute to the occurrence of pairwise mutualistic interactions and network structure.
+That is, whether or not two species interact can be thought of as the result of two sequential processes.
+First, there is a stochastic (neutral) process driven by the local abundances of interacting species, such that abundant species are more likely to encounter each other than are rare ones.
+Secondly, there is a deterministic process driven by a matching of traits (e.g., phenology, morphology, behavior, etc.) that finally permits the interaction between co- occurring species.
+
+Intro: Mutualistic interactions are fundamentally dynamic, such that there is a turnover of species and individuals in space and time (Carnicer et al., 2009; Laliberté and Tylianakis, 2010; Hagen et al., 2012).
+
+I would then add a thrird one that is dictated by the rewards provided by an interaction. Maybe?
+
+Conclusion: Overall we found that the assemblage of pairwise interactions depended on the neutral effects of interacting species abundances (the more abundant the species of fruit and frugivore, the more frequent their pairwise interaction) and on the local context of ecological neighborhoods.
+
+**From Boulangeat et al 2012:** Intro: These drivers of species distributions may act at different spatial scales.
+For instance, frequent consideration is given to abiotic variables acting at large spatial scales.
+On the other hand, biotic interactions and consumer-resource dynamics are assumed to occur at smaller spatial scales.
+
+Conclusion: Biotic inetractions are def important at determining abundace.
+They observed positive effects of biotic interactions at colder climates (low suitability for plants) -- suggest facilitation.
+and negative effects of interactions at warmer climates (high suitability) suggesting competition.
+*Should I calculate the suitability of other species?*
 
@@
 
+We focus suitability in abiotic factors but can also be influenced by dispersal and species interactions themselves (e.g. competition and facilitation, Lortie et al. 2004). 
+We learnt that there is a trade-off pollination dynamics (Cagua in review?).
+This means that species with more environemntal favours are better prepared to deal with the trade-offs that pollination can convey. Cool!
+
+Suitability is not a meric of abbundances across sites (Pearce & Ferrier 2001; Sagarin et al. 2006) (Taken from Boulangeat)
+
+Add the suitability of possible competitors? I mean they are not really competitors so maybe not.
+
 # Acknowledgements

### 2019-07-28 paper/manuscript.Rmd
Some notes from Dormann et al. 2018

@@
 *Should I calculate the suitability of other species?*
+
+**From Dormann et al 2018:** Intro: Sometimes, an organism will be little affected by com- petitors, mutualists, pathogens or predators; a mature tree may appear to grow unfettered by its neighbours for decades.
+In other cases, an individual may struggle to survive the pressure of its community during every hour of its life; for example, a fish preying and escaping predators in a small river.
+Biotic interactions such as these can have major effects on local processes and population dynamics, and some, but not neces- sarily all, scale up to co-determining the range of a species (reviewed, e.g., by Wisz et al., 2013).
+
+Most BI-SDMs assume that biotic interactions are constant in space and time.
+It is more likely, however, that interaction strengths are modulated by the biotic and abiotic environment.
+Experimental studies showed that rates of biological interactions depend on environmental conditions: rates of herbivory are temperature dependent (Burnside, Erhardt, Hammond, & Brown, 2014); mycorrhizal symbioses change with resource availability (Cox, Barsoum, Lilleskov, & Bidartondo, 2010; Johnson, Wilson, Bowker, Wilson, & Miller, 2010); and plant–plant interactions can shift from competitive to facilitative along a stress gra- dient (Bertness & Callaway, 1994).
+Additionally, environmental change can modulate biotic interactions via phenological mismatches, such as for plant–pollinator interactions (Berg et al., 2010; Elzinga et al., 2007).
+In these conditions, the model must also allow for the interplay of envi- ronmental and biotic interactions (Clark et al., 2011), which has only recently started to be explored in BI-SDMs (Tikhonov, Abrego, Dunson, & Ovaskainen, 2017).
 

### 2019-07-28 paper/manuscript.Rmd
Some more notes and ideas

@@
 
+**Is my central topic turnover of interactions**?
+
+**Continuation: compare the suitability of the species that species do not interact with vs those that interact (when a possible interaction occurs but is not realised)?**
+
+**Continuation: average suitability of all species.
+If avg.
+competitors suitability is low, species, facilitation more common and resource sharing should increase.
+If avg.
+suitability is high, the opposite should happen?**
+
+**SHould I use relative suitability instead of absolute? Is not total suitability what matters but that relative to other species?**
+
 Notes:
@@
 and negative effects of interactions at warmer climates (high suitability) suggesting competition.
-*Should I calculate the suitability of other species?*
+*Should I calculate the suitability of other species and test this?*
 
@@
 Additionally, environmental change can modulate biotic interactions via phenological mismatches, such as for plant–pollinator interactions (Berg et al., 2010; Elzinga et al., 2007).
-In these conditions, the model must also allow for the interplay of envi- ronmental and biotic interactions (Clark et al., 2011), which has only recently started to be explored in BI-SDMs (Tikhonov, Abrego, Dunson, & Ovaskainen, 2017).
+In these conditions, the model must also allow for the interplay of environmental and biotic interactions (Clark et al., 2011), which has only recently started to be explored in BI-SDMs (Tikhonov, Abrego, Dunson, & Ovaskainen, 2017).
+
+**From Gravel et al.
+2018**: We apply this framework to host–parasite interactions across Europe and ind that two aspects of the environment (temperature and precipitation) exert a strong imprint on species co-occurrence, but not on species interactions.
+Even where species co-occur, interaction proves to be stochastic rather than deterministic, adding to variation in realized network structure.
+*Bingo: I show it's not completely stochastic and is likely to be determined by the suitability hehe*
+
+There is, however, ample evidence that interaction networks vary in space and time (Laliberté and Tylianakis 2010, Poisot et al.
+2012, 2016c, Schleuning et al.
+2012, Albouy et al.
+2014, Trøjelsgaard et al.
+2015), even though there is no common framework with which to generalize these results.
+
+he occurrence and intensity of interactions could vary because of the environment, species abundance, and higher- order ecological interactions (Poisot et al.
+2015).
+*Well do I show that could vary because of more stuff?*
+
+Variation in community composition can be independent of variation of ecological interactions, suggesting that species and inter- action distribution may well respond to diferent drivers (Poisot et al.
+2012).
 

### 2019-07-29 paper/manuscript.Rmd
Finishing Gravel 2018

@@
 
-**Is my central topic turnover of interactions**?
+**Is my central topic turnover of interactions**? If yes then I should quanitify turnover accross high and low suitability areas.
 
@@
 
-**SHould I use relative suitability instead of absolute? Is not total suitability what matters but that relative to other species?**
+**Continuation: Should I use relative suitability instead of absolute? Is not total suitability what matters but that relative to other species?**
+
+**Is smaller degree a smaller Eltonian niche?** Should I frame this as the relationship between Grinellian and Eltonian.
+A better position in the grinellian niche allows for a larger Realised Eltonian niche.
 
@@
 Even where species co-occur, interaction proves to be stochastic rather than deterministic, adding to variation in realized network structure.
-*Bingo: I show it's not completely stochastic and is likely to be determined by the suitability hehe*
+*Bingo: I show it's not completely stochastic and is likely to be determined by the suitability hehe* -- for real ( They test prob.
+of two co-occurring species to interact does not depend on environment.
+I test single species thingy).
+Should I do that?
+suit sp.1 and suit sp.
+2?
+It;s not about the environment, but about how the environment affect the species involved.
+Buya!
 
@@
 2012).
+
+Ecological interactions could also vary with the environment, P(Lijy | Ey ).
+Although it is rare to see a con- ditional representation of pairwise ecological interactions, experimental studies have frequently revealed interactions to be sensitive to the environment.
+For instance, McKinnon et al.
+(2010) showed that predation risks of shorebirds vary at the continental scale, decreasing from the south to the north.
+It is also common to see increasing top-down control with temperature (Shurin et al.
+2012, Gray et al.
+2016).
+Efects of the environment on interactions (Gibert and DeLong 2014) also propagate up the community and inluence net- work structure (Tylianakis et al.
+2007, Petchey et al.
+2010, Woodward et al.
+2010).
+
+In terms of species interacting with each other, our analysis suggests that the environment leaves a detectable imprint on species co-occurrence, but only a slight mark on the occurrence of realized links among species in a speciic place: the prob- ability of inding a given combination of species at a higher and a lower trophic level at the same site was clearly afected by the environment, whereas the probability of observing an interaction between the two was, given co-occurrence, not signiicantly so.
+
+This does not imply that species will always interact when they meet – **although this is a basic assumption in most documented metawebs to date** (Havens 1992, Wood et al. 2015).
+
+Evidence that the structure of ecological networks does vary across habitats (Tylianakis et al.
+2007), over environmental gradients (Lurgi et al.
+2012) and in time (Simanonok and Burkle 2014) is accumulating rapidly.
 
@@
 
+Remarkable that we found a consistent signal of suitability given our relatively small number of communities and the multitude of processes that shape n.
+interactions Eltonian niche.
+We didn;t even account for traits.
+Interactions can influence co-occurrence (indirect and third order too see refs in Gravel 2018)
+
 Add the suitability of possible competitors? I mean they are not really competitors so maybe not.

### 2019-07-29 paper/manuscript.Rmd
Devictor 2010
Godsoe 2017 + Mini comment

@@
 A better position in the grinellian niche allows for a larger Realised Eltonian niche.
+A problem of stating the hypothesis in terms of niches is that there are many definitions of niche and people is picky
+
+*Previous state of the world: We know interactions change with the environment but we don't know beyond co-occurrence patterns*
 
@@
 2012) and in time (Simanonok and Burkle 2014) is accumulating rapidly.
+
+**Devictor 2010:** I can use degree to quantify realised eltonian niche
+
+**Godsoe 2017**: Biogeographers and community ecologists have long debated the importance of biotic interactions (see Glossary) for species distributions and range limits [1–5].*But seldom the other way arround?*
 

### 2019-07-30 paper/manuscript.Rmd
Some goldies from Tylianakis 2017

@@
 **Godsoe 2017**: Biogeographers and community ecologists have long debated the importance of biotic interactions (see Glossary) for species distributions and range limits [1–5].*But seldom the other way arround?*
+
+**Tylianakis 2017**: Interactions can change because of environment because environment and habitat can change encounter rate.
+
+Specialist species (that lack flexibility in their choice of interaction partner) should theoretically be most vulnerable to phenological decoupling.
+However, one study of pollinator communities along an elevational gradient found that apparently specialized pollinators were facultatively more generalist than they appeared and could adapt their visitation patterns across sites as much as generalists to avoid phenological asynchrony (Benadi et al.
+2014).
+Similarly, duration of the fruiting season has been shown to predict the degree and strength of seed-dispersal interactions (Gonza ́ lez- Castro et al.
+2012), and a long-term study found no difference between specialist and generalist plant species in their interannual fluctuations in phenology and pollinator richness (Petanidou et al.
+2014).
+Although these findings suggest that the facultative generalism of pollination mutualisms may confer robustness to these networks in the face of altered phenology (see also discussion on rewiring above), this robustness may depend on the climate context and the diversity and specialization within the network (Hoiss et al.
+2015).
+Moreover, less-generalized interactions such as those between parasites and hosts may show less flexibility.
+
+many trophic and mutualistic interactions are relatively generalized and potentially opportunistic (Pimm et al.
+1991).
+Thus, we may expect that ecological networks will comprise a mixture of interactions that persist over the long-term owing to trait matching of partners through coevolution (Go ́ mez et al.
+2010, Guimaraes et al.
+2011) and those that occur opportunistically, perhaps with inferior long-term fitness benefits (Aizen et al.
+2016).
+Increases in the frequency of the former will strengthen any pattern of phylogenetic congruence, whereas increases in the latter will erode it.
+
+For example, environmental stressors could cause species to narrow their trophic breadth by increasing the search time to find alternative partners (Gauld 1987) or by imposing limits on the quality of interaction partners that can be used (i.e., using only resources to which a species is best adapted).
+Phylogenetic congruence becomes stronger in parasitoid–host networks with increasing temperature (Lavandero & Tylianakis 2013) and in plantation versus native forests (Peralta et al.
+2015), and such patterns appear consistent with a hy- pothesis of stress-induced reduction in trophic (phylogenetic) breadth (in the case of Lavandero & Tylianakis 2013, this occurred on genotype relatedness rather than between-species phylogenies).
+However, evidence for the hypothesized mechanism is still lacking, as experiments have revealed no change in the proportionate use of good or bad hosts when parasitoids are nutritionally stressed (Hopper et al.
+2013) or even decreased selectivity toward high-quality hosts under high levels of nutritional stress (Crespo et al.
+2015).
 
@@
 
+Discuss implications for network rewiring?
+
 # Acknowledgements

### 2019-07-30 paper/manuscript.Rmd
Some more Tylianakis and Peralta 2015

@@
 2015).
+
+In addition to seasonal patterns, interaction turnover can be driven by environmental fac- tors, such as community changes during drought years (Alarco ́n et al.
+2008) or along land use or landscape intensity gradients (Gagic et al.
+2012, Laliberte ́ & Tylianakis 2010).
+The impact of environmental conditions on interaction turnover can, in turn, be constrained by species traits such as feeding morphology (Carnicer et al.
+2009) or body size (Laliberte ́ & Tylianakis 2010).
+To understand this balance, species interactions can be thought of as having both a niche-based or trait-based component and a random or neutral component determined by encounter probability (Bartomeus et al.
+2016, Vazquez et al.
+2009).
+Any environmental driver that sufficiently increases encounter probability (see Section 2.2) for all species could reduce the neutral barrier to inter- actions and allow species to consistently select their interaction partner with optimally matched traits.
+This enhanced expression of species preferences would result in reduced spatial or temporal variability because the same interactions would consistently be realized (i.e., network homogeniza- tion; Laliberte ́ & Tylianakis 2010).
+Reduction of the neutral component of interactions could also lead to exaggeration of patterns of trait matching and phylogenetic congruence (Carnicer et al.
+2009) (see Section 2.3).
+Alternatively, a driver that increases the abundance of a subset of species could result in their overrepresentation in interactions by allowing the neutral component of inter- actions to be overexpressed relative to the trait-based component (Carnicer et al.
+2009).
+Because individual species may differ in the extent to which they engage in neutral interactions, changes to the relative abundance of species can alter network architecture.
+For example, exotic birds can be less selective in the fruit species on which they feed (i.e., feeding more neutrally on species in proportion to their abundance), and this low selectivity can allow them to fill the gap left by rare or extinct native birds and maintain high network nestedness and connectance (Garcıa et al.
+2014).
+
+**Peralta 2015:** Plantation forests (as opposed to native) habitat may impose stresses on parasitoids that constrain them to attack only host species for which they are best adapted.
+-> Consistent with more stress less generalism.
+
+Native herbivore–parasitoid combinations whose interac- tions contributed the most to the pattern of phylogenetic congruence were more abundant in plantations than in native forests.
+This stronger co-evolutionary signal in plantation forests suggests that parasitoids in disturbed habitats may only be able to utilize hosts that they have best evolved to attack.
+Analogously, climate warming has been shown to reduce the niche breadth plasticity of par- asitoids (Lavandero & Tylianakis 2013), suggesting that different environmental changes could reduce the ability of parasitoid communities to suppress a broad range of host species and genotypes in natural systems and biologi- cal control programmes.
 
@@
 
+Induced by latitude (more generalism in tropics) or diversity (more generalism with high diversity or the opposite), See Baiser 2019 for refsuse network as a random effect.
+
 # Results

### 2019-07-30 paper/manuscript.Rmd
Abstract attempt

@@
 
-Ecological interactions could also vary with the environment, P(Lijy | Ey ).
-Although it is rare to see a con- ditional representation of pairwise ecological interactions, experimental studies have frequently revealed interactions to be sensitive to the environment.
+Ecological interactions could also vary with the environment.
+Although it is rare to see a conditional representation of pairwise ecological interactions, experimental studies have frequently revealed interactions to be sensitive to the environment.
 For instance, McKinnon et al.

### 2019-08-08 code/suitability_vs_degree.R
For some reason is significant again...

@@ -15,7 +15,7 @@ get_possible_interactions <- function(interactions_org){
     dplyr::mutate(int = !is.na(int)) 
 }
 
-calc_org_degree <- function(possible_interactions, interactions_orgs){
+calc_org_degree <- function(possible_interactions, interactions_org){
   
   possible_interactions <-interactions_org %>%
     dplyr::distinct() %>%
@@ -68,21 +68,21 @@ tinker <- function(){
     dplyr::mutate(n_obs = dplyr::n()) %>% 
     # dplyr::group_by(org_id) %>%
     # dplyr::filter(any(n_partners != n_possible_partners)) %>%
-    dplyr::filter(n_obs > 5) %>%
-    glm(n_partners ~scale(suitability) + 
+    # dplyr::filter(n_obs > 5) %>%
+    # glm(n_partners ~scale(suitability)* guild + 
           # guild + 
-          scale(n_obs) ,
-          # scale(log(n_partners_global)) + 
+          # scale(n_obs) +
+          # scale(log(n_partners_global)) +
           # scale(n_possible_partners),
+                # family = "poisson",
+                # data = .)
+    lme4::glmer(n_partners ~ suitability*guild +
+                  scale(log(n_partners_global)) +
+                  # scale(n_possible_partners) +
+                  (suitability | org_id : guild),
                 family = "poisson",
                 data = .)
-    # lme4::glmer(n_partners ~ suitability + 
-    #               # scale(log(n_partners_global)) +
-    #               # scale(n_possible_partners) +
-    #               (suitability | guild),
-    #             family = "poisson", 
-    #             data = .) 
-  broom::glance(mod)
+  broom::glance(mod)$AIC
   summary(mod)
   
   mod %>%
@@ -94,8 +94,9 @@ tinker <- function(){
                        ymax = condval + 2 * condsd, 
                       colour = sign(condval - 2 * condsd) == sign(condval + 2 * condsd)), 
                    width = 0) +
-    facet_wrap(~term, ncol = 1, scales = "free") +
-    theme(legend.position = "none")
+    facet_wrap(~term, ncol = 2, scales = "free") +
+    theme(legend.position = "none") +
+    coord_flip()
     lm(n_partners ~ suitability + log(n_partners_global) + n_opposite_guild + n_possible_partners, data = .) %>% 
     summary()
 }

### 2019-08-08 paper/manuscript.Rmd
Comment out notes

@@
 
-Interactions are selected by species depending on the relative benefit they provide.
+<!-- Interactions are selected by species depending on the relative benefit they provide.
 The assumption goes that species with a large number of interactions are benefit relatively little from each of them, and species with a small number benefit largely with them, this is they focus in more optimal pollinators.
+-->
 
-AND
+<!-- AND  -->
 
-We know that interactions are influenced by the environment.
+<!-- We know that interactions are influenced by the environment.  -->
 
-BUT
+<!-- BUT -->
 
-We don't know how exactly wether the enviroment influences the patterns of generalisation/specialization.
+<!-- We don't know how exactly wether the enviroment influences the patterns of generalisation/specialization.  -->
 
-One option is that when species are in detrimental environmental conditions focus on most optimal partners and as such interact with a smaller number of species. 
-An alternative hypotheisis is that when species are in favourable environmental conditions they can afford to be more picky about their interactions and as such avoid those of less value, while individuals in unfavourable conditions must get rewards from whatever they can get.
+<!-- One option is that when species are in detrimental environmental conditions focus on most optimal partners and as such interact with a smaller number of species.  -->
+<!-- An alternative hypotheisis is that when species are in favourable environmental conditions they can afford to be more picky about their interactions and as such avoid those of less value, while individuals in unfavourable conditions must get rewards from whatever they can get.
+-->
 
-THEREFORE
+<!-- THEREFORE -->
 
-We used a global dataset on plant pollinator interactions, species occurrence, and bioclimatic data to test these hypotheses. 
-If the first option is true we should see a negative relationship between environmental sutability and the relative degree of a species. 
-If the second option is true we should see the opposite, a positive relationship between environmental suitability and the relative degree of a species.
+<!-- We used a global dataset on plant pollinator interactions, species occurrence, and bioclimatic data to test these hypotheses.  -->
+<!-- If the first option is true we should see a negative relationship between environmental sutability and the relative degree of a species.  -->
+<!-- If the second option is true we should see the opposite, a positive relationship between environmental suitability and the relative degree of a species.  -->
 
-**Is my central topic turnover of interactions**? If yes then I should quanitify turnover accross high and low suitability areas.
+<!-- **Is my central topic turnover of interactions**? If yes then I should quanitify turnover accross high and low suitability areas.  -->
 
-**Continuation: compare the suitability of the species that species do not interact with vs those that interact (when a possible interaction occurs but is not realised)?**
+<!-- **Continuation: compare the suitability of the species that species do not interact with vs those that interact (when a possible interaction occurs but is not realised)?** -->
 
-**Continuation: average suitability of all species.
+<!-- **Continuation: average suitability of all species.
 If avg.
@@
 If avg.
-suitability is high, the opposite should happen?**
+suitability is high, the opposite should happen?** -->
 
-**Continuation: Should I use relative suitability instead of absolute? Is not total suitability what matters but that relative to other species?**
+<!-- **Continuation: Should I use relative suitability instead of absolute? Is not total suitability what matters but that relative to other species?**  -->
 
-**Is smaller degree a smaller Eltonian niche?** Should I frame this as the relationship between Grinellian and Eltonian.
+<!-- **Is smaller degree a smaller Eltonian niche?** Should I frame this as the relationship between Grinellian and Eltonian.
 A better position in the grinellian niche allows for a larger Realised Eltonian niche.
-A problem of stating the hypothesis in terms of niches is that there are many definitions of niche and people is picky
+A problem of stating the hypothesis in terms of niches is that there are many definitions of niche and people is picky -->
 
-*Previous state of the world: We know interactions change with the environment but we don't know beyond co-occurrence patterns*
+<!-- *Previous state of the world: We know interactions change with the environment but we don't know beyond co-occurrence patterns* -->
 
-Notes:
+<!-- Notes: -->
 
-**From donoso et al 2017: ** Intro: It is generally agreed that both neutral and niche-driven processes contribute to the occurrence of pairwise mutualistic interactions and network structure.
+<!-- **From donoso et al 2017: ** Intro: It is generally agreed that both neutral and niche-driven processes contribute to the occurrence of pairwise mutualistic interactions and network structure.
 That is, whether or not two species interact can be thought of as the result of two sequential processes.
@@
 Secondly, there is a deterministic process driven by a matching of traits (e.g., phenology, morphology, behavior, etc.) that finally permits the interaction between co- occurring species.
+-->
 
-Intro: Mutualistic interactions are fundamentally dynamic, such that there is a turnover of species and individuals in space and time (Carnicer et al., 2009; Laliberté and Tylianakis, 2010; Hagen et al., 2012).
+<!-- Intro: Mutualistic interactions are fundamentally dynamic, such that there is a turnover of species and individuals in space and time (Carnicer et al., 2009; Laliberté and Tylianakis, 2010; Hagen et al., 2012).
+-->
 
-I would then add a thrird one that is dictated by the rewards provided by an interaction. Maybe?
+<!-- I would then add a thrird one that is dictated by the rewards provided by an interaction. Maybe? -->
 
-Conclusion: Overall we found that the assemblage of pairwise interactions depended on the neutral effects of interacting species abundances (the more abundant the species of fruit and frugivore, the more frequent their pairwise interaction) and on the local context of ecological neighborhoods.
+<!-- Conclusion: Overall we found that the assemblage of pairwise interactions depended on the neutral effects of interacting species abundances (the more abundant the species of fruit and frugivore, the more frequent their pairwise interaction) and on the local context of ecological neighborhoods.
+-->
 
-**From Boulangeat et al 2012:** Intro: These drivers of species distributions may act at different spatial scales.
+<!-- **From Boulangeat et al 2012:** Intro: These drivers of species distributions may act at different spatial scales.
 For instance, frequent consideration is given to abiotic variables acting at large spatial scales.
 On the other hand, biotic interactions and consumer-resource dynamics are assumed to occur at smaller spatial scales.
+-->
 
-Conclusion: Biotic inetractions are def important at determining abundace.
+<!-- Conclusion: Biotic inetractions are def important at determining abundace.
 They observed positive effects of biotic interactions at colder climates (low suitability for plants) -- suggest facilitation.
 and negative effects of interactions at warmer climates (high suitability) suggesting competition.
-*Should I calculate the suitability of other species and test this?*
+*Should I calculate the suitability of other species and test this?* -->
 
-**From Dormann et al 2018:** Intro: Sometimes, an organism will be little affected by com- petitors, mutualists, pathogens or predators; a mature tree may appear to grow unfettered by its neighbours for decades.
+<!-- **From Dormann et al 2018:** Intro: Sometimes, an organism will be little affected by com- petitors, mutualists, pathogens or predators; a mature tree may appear to grow unfettered by its neighbours for decades.
 In other cases, an individual may struggle to survive the pressure of its community during every hour of its life; for example, a fish preying and escaping predators in a small river.
 Biotic interactions such as these can have major effects on local processes and population dynamics, and some, but not neces- sarily all, scale up to co-determining the range of a species (reviewed, e.g., by Wisz et al., 2013).
+-->
 
-Most BI-SDMs assume that biotic interactions are constant in space and time.
+<!-- Most BI-SDMs assume that biotic interactions are constant in space and time.
 It is more likely, however, that interaction strengths are modulated by the biotic and abiotic environment.
@@
 In these conditions, the model must also allow for the interplay of environmental and biotic interactions (Clark et al., 2011), which has only recently started to be explored in BI-SDMs (Tikhonov, Abrego, Dunson, & Ovaskainen, 2017).
+-->
 
-**From Gravel et al.
+<!-- **From Gravel et al.
 2018**: We apply this framework to host–parasite interactions across Europe and ind that two aspects of the environment (temperature and precipitation) exert a strong imprint on species co-occurrence, but not on species interactions.
@@
 Buya!
+-->
 
-There is, however, ample evidence that interaction networks vary in space and time (Laliberté and Tylianakis 2010, Poisot et al.
+<!-- There is, however, ample evidence that interaction networks vary in space and time (Laliberté and Tylianakis 2010, Poisot et al.
 2012, 2016c, Schleuning et al.
@@
 2015), even though there is no common framework with which to generalize these results.
+-->
 
-he occurrence and intensity of interactions could vary because of the environment, species abundance, and higher- order ecological interactions (Poisot et al.
+<!-- he occurrence and intensity of interactions could vary because of the environment, species abundance, and higher- order ecological interactions (Poisot et al.
 2015).
-*Well do I show that could vary because of more stuff?*
+*Well do I show that could vary because of more stuff?* -->
 
-Variation in community composition can be independent of variation of ecological interactions, suggesting that species and inter- action distribution may well respond to diferent drivers (Poisot et al.
+<!-- Variation in community composition can be independent of variation of ecological interactions, suggesting that species and inter- action distribution may well respond to diferent drivers (Poisot et al.
 2012).
+-->
 
-Ecological interactions could also vary with the environment.
+<!-- Ecological interactions could also vary with the environment.
 Although it is rare to see a conditional representation of pairwise ecological interactions, experimental studies have frequently revealed interactions to be sensitive to the environment.
@@
 2010).
+-->
 
-In terms of species interacting with each other, our analysis suggests that the environment leaves a detectable imprint on species co-occurrence, but only a slight mark on the occurrence of realized links among species in a speciic place: the prob- ability of inding a given combination of species at a higher and a lower trophic level at the same site was clearly afected by the environment, whereas the probability of observing an interaction between the two was, given co-occurrence, not signiicantly so.
+<!-- In terms of species interacting with each other, our analysis suggests that the environment leaves a detectable imprint on species co-occurrence, but only a slight mark on the occurrence of realized links among species in a speciic place: the prob- ability of inding a given combination of species at a higher and a lower trophic level at the same site was clearly afected by the environment, whereas the probability of observing an interaction between the two was, given co-occurrence, not signiicantly so.
+-->
 
-This does not imply that species will always interact when they meet – **although this is a basic assumption in most documented metawebs to date** (Havens 1992, Wood et al. 2015).
+<!-- This does not imply that species will always interact when they meet – **although this is a basic assumption in most documented metawebs to date** (Havens 1992, Wood et al. 2015).  -->
 
-Evidence that the structure of ecological networks does vary across habitats (Tylianakis et al.
+<!-- Evidence that the structure of ecological networks does vary across habitats (Tylianakis et al.
 2007), over environmental gradients (Lurgi et al.
 2012) and in time (Simanonok and Burkle 2014) is accumulating rapidly.
+-->
 
-**Devictor 2010:** I can use degree to quantify realised eltonian niche
+<!-- **Devictor 2010:** I can use degree to quantify realised eltonian niche -->
 
-**Godsoe 2017**: Biogeographers and community ecologists have long debated the importance of biotic interactions (see Glossary) for species distributions and range limits [1–5].*But seldom the other way arround?*
+<!-- **Godsoe 2017**: Biogeographers and community ecologists have long debated the importance of biotic interactions (see Glossary) for species distributions and range limits [1–5].*But seldom the other way arround?* -->
 
-**Tylianakis 2017**: Interactions can change because of environment because environment and habitat can change encounter rate.
+<!-- **Tylianakis 2017**: Interactions can change because of environment because environment and habitat can change encounter rate.  -->
 
-Specialist species (that lack flexibility in their choice of interaction partner) should theoretically be most vulnerable to phenological decoupling.
+<!-- Specialist species (that lack flexibility in their choice of interaction partner) should theoretically be most vulnerable to phenological decoupling.
 However, one study of pollinator communities along an elevational gradient found that apparently specialized pollinators were facultatively more generalist than they appeared and could adapt their visitation patterns across sites as much as generalists to avoid phenological asynchrony (Benadi et al.
@@
 Moreover, less-generalized interactions such as those between parasites and hosts may show less flexibility.
+-->
 
-many trophic and mutualistic interactions are relatively generalized and potentially opportunistic (Pimm et al.
+<!-- many trophic and mutualistic interactions are relatively generalized and potentially opportunistic (Pimm et al.
 1991).
@@
 Increases in the frequency of the former will strengthen any pattern of phylogenetic congruence, whereas increases in the latter will erode it.
+-->
 
-For example, environmental stressors could cause species to narrow their trophic breadth by increasing the search time to find alternative partners (Gauld 1987) or by imposing limits on the quality of interaction partners that can be used (i.e., using only resources to which a species is best adapted).
+<!-- For example, environmental stressors could cause species to narrow their trophic breadth by increasing the search time to find alternative partners (Gauld 1987) or by imposing limits on the quality of interaction partners that can be used (i.e., using only resources to which a species is best adapted).
 Phylogenetic congruence becomes stronger in parasitoid–host networks with increasing temperature (Lavandero & Tylianakis 2013) and in plantation versus native forests (Peralta et al.
@@
 2015).
+-->
 
-In addition to seasonal patterns, interaction turnover can be driven by environmental fac- tors, such as community changes during drought years (Alarco ́n et al.
+<!-- In addition to seasonal patterns, interaction turnover can be driven by environmental fac- tors, such as community changes during drought years (Alarco ́n et al.
 2008) or along land use or landscape intensity gradients (Gagic et al.
@@
 2014).
+-->
 
-**Peralta 2015:** Plantation forests (as opposed to native) habitat may impose stresses on parasitoids that constrain them to attack only host species for which they are best adapted.
+<!-- **Peralta 2015:** Plantation forests (as opposed to native) habitat may impose stresses on parasitoids that constrain them to attack only host species for which they are best adapted.
 -> Consistent with more stress less generalism.
+-->
 
-Native herbivore–parasitoid combinations whose interac- tions contributed the most to the pattern of phylogenetic congruence were more abundant in plantations than in native forests.
+<!-- Native herbivore–parasitoid combinations whose interac- tions contributed the most to the pattern of phylogenetic congruence were more abundant in plantations than in native forests.
 This stronger co-evolutionary signal in plantation forests suggests that parasitoids in disturbed habitats may only be able to utilize hosts that they have best evolved to attack.
 Analogously, climate warming has been shown to reduce the niche breadth plasticity of par- asitoids (Lavandero & Tylianakis 2013), suggesting that different environmental changes could reduce the ability of parasitoid communities to suppress a broad range of host species and genotypes in natural systems and biologi- cal control programmes.
+-->
 
@@
 
-We then investigated
+<!-- We then investigated  -->
 
-See topography data from Species distribution model transferability and model grain size – finer may not always be better
+<!-- See topography data from Species distribution model transferability and model grain size – finer may not always be better -->
 
-Induced by latitude (more generalism in tropics) or diversity (more generalism with high diversity or the opposite), See Baiser 2019 for refsuse network as a random effect.
+<!-- Induced by latitude (more generalism in tropics) or diversity (more generalism with high diversity or the opposite), See Baiser 2019 for refsuse network as a random effect. -->
 
@@
 
-We focus suitability in abiotic factors but can also be influenced by dispersal and species interactions themselves (e.g. competition and facilitation, Lortie et al. 2004). 
-We learnt that there is a trade-off pollination dynamics (Cagua in review?).
-This means that species with more environemntal favours are better prepared to deal with the trade-offs that pollination can convey. Cool!
+<!-- We focus suitability in abiotic factors but can also be influenced by dispersal and species interactions themselves (e.g. competition and facilitation, Lortie et al. 2004).  -->
+<!-- We learnt that there is a trade-off pollination dynamics (Cagua in review?). -->
+<!-- This means that species with more environemntal favours are better prepared to deal with the trade-offs that pollination can convey. Cool! -->
 
-Suitability is not a meric of abbundances across sites (Pearce & Ferrier 2001; Sagarin et al. 2006) (Taken from Boulangeat)
+<!-- Suitability is not a meric of abbundances across sites (Pearce & Ferrier 2001; Sagarin et al. 2006) (Taken from Boulangeat) -->
 
-Remarkable that we found a consistent signal of suitability given our relatively small number of communities and the multitude of processes that shape n.
+<!-- Remarkable that we found a consistent signal of suitability given our relatively small number of communities and the multitude of processes that shape n.
 interactions Eltonian niche.
 We didn;t even account for traits.
-Interactions can influence co-occurrence (indirect and third order too see refs in Gravel 2018)
+Interactions can influence co-occurrence (indirect and third order too see refs in Gravel 2018) -->
 
-Add the suitability of possible competitors? I mean they are not really competitors so maybe not.
+<!-- Add the suitability of possible competitors? I mean they are not really competitors so maybe not.  -->
 
-Discuss implications for network rewiring?
+<!-- Discuss implications for network rewiring? -->
 

### 2019-08-08 paper/manuscript.Rmd
Add basic results

@@
 
+We found a positive association between environmental suitability and the niche breath. 
+This relationship was maintained when we account for the overall generality of a species and even in extremely conservative model parametrization when we include the number of possible interacting species as an independent variable.
+We define "possible" interacting species as one with which the species interacts in any of our ecological communities.
+
+No interaction significant between guild and relationship which highlights that differences are rooted in eco-evolutionary processes rather than behaviour.
+
+Relationship is even stronger when we only include species for which we have more info. i.e. in more that 5 communities.
+
+```
+Call:
+glm(formula = n_partners ~ scale(suitability) * guild, family = "poisson", 
+    data = .)
+
+Coefficients:
+                               Estimate Std. Error z value Pr(>|z|)    
+(Intercept)                     1.79092    0.02360  75.886  < 2e-16 ***
+scale(suitability)              0.07750    0.02454   3.158  0.00159 ** 
+guildpla_id                     0.64345    0.04361  14.756  < 2e-16 ***
+scale(suitability):guildpla_id  0.07645    0.03631   2.106  0.03524 *  
+---
+AIC: 3739.6
+```
+
+```
+Call:
+glm(formula = n_partners ~ scale(suitability) * guild + scale(log(n_partners_global)), 
+    family = "poisson", data = .)
+
+Coefficients:
+                               Estimate Std. Error z value Pr(>|z|)    
+(Intercept)                     1.70709    0.02541  67.172  < 2e-16 ***
+scale(suitability)              0.17021    0.02481   6.860 6.88e-12 ***
+guildpla_id                     0.61872    0.04378  14.132  < 2e-16 ***
+scale(log(n_partners_global))   0.42074    0.01970  21.362  < 2e-16 ***
+scale(suitability):guildpla_id -0.02134    0.03657  -0.584     0.56    
+---
+
+AIC: 3302.1
+```
+
+```
+Call:
+glm(formula = n_partners ~ scale(suitability) * guild + scale(log(n_partners_global)) + 
+    scale(n_possible_partners), family = "poisson", data = .)
+
+Coefficients:
+                               Estimate Std. Error z value Pr(>|z|)    
+(Intercept)                    1.667769   0.025701  64.892  < 2e-16 ***
+scale(suitability)             0.088729   0.024121   3.679 0.000235 ***
+guildpla_id                    0.423815   0.043904   9.653  < 2e-16 ***
+scale(log(n_partners_global))  0.138837   0.022829   6.082 1.19e-09 ***
+scale(n_possible_partners)     0.351851   0.008547  41.167  < 2e-16 ***
+scale(suitability):guildpla_id 0.010224   0.036728   0.278 0.780718    
+---
+
+AIC: 2141.5
+```
+
 # Discussion

### 2019-08-15 paper/manuscript.Rmd
Start explaining models in methods

@@
 
+We then used a series of bayesian multilevel models to evaluate the impact of environmental suitability on the number of interacting species. 
+These models differed on the predictors included and allowed us to evaluate the relative importance of suitability. 
+Our response variable was the number of species it interacts with in a community, the species degree. 
+We modelled degree using a logarithmic link function and a Poisson distribution. 
+Nevertheless results were qualitatively the same if instead we model the normalised degree (REF Martin Gonzalez 2010) using a binomial distribution in which degree is the number of successes and the number of species in the opposite guild is the number of trials (Supp info).
+
+Briefly, our baseline model included suitability and guild as population effects and two groups, species and the community. 
+Our main predictor, the environmental suitability of the species in that particular location, is an index defined betwen zero and one in which a value of zero indicates that the species has never been observed in this environment while a value of one indicates that the species is most commonly observed in that environment.
+As we are particularly intrested on understanding wether the effect of species suitability is conditional on the species guild (plant or pollinator), we also included guild and its interaction with suitability in the model.
+We allowed the intercept of degree and slope of the suitability-degree relationship to vary among species, this allowed us to investigate the extent to which suitability is a population or a group level effect.
+Finally, to account for unmeasured differences between communities, like sampling effort, sampling method, or richness, we calculated an intercept for each community in our study.
+
+We calculated three more alternative models. 
+The first alternative model accounted for the overall generalism of a species by including among the predictors the magnitude of the number of species it interacts with across networks. 
+The second alternative model, is highly prescriptive and accounts
+
 <!-- We then investigated  -->

### 2019-08-17 paper/manuscript.Rmd
Finish describing model methods

@@
 We calculated three more alternative models. 
-The first alternative model accounted for the overall generalism of a species by including among the predictors the magnitude of the number of species it interacts with across networks. 
-The second alternative model, is highly prescriptive and accounts
+The first alternative model accounted for the overall generalism of a species by also including among the predictors the magnitude of the total number of interacting species across networks. 
+In the second alternative model, we included as a predictor the number of known possible interacting species. 
+We calculated this predictor as the number of interacting species across networks that were present in the community. 
+Accounting for the number of possible interacting species is a particularly stringent way to test the effect of environmental suitability as for many species populations, the number of possible interacting species is the same or very similar to the number of species it actually interacts with.
+The third alternative model included both the overall species generalism and the possible number of interacting species. 
+Finally, the fourth model included both of the aforementioned predictors but excluded the effect of environmental suitability both at the population and the species level. 
+To facilitate model interpretation and convergence, we scaled all continuous variables to have a mean of zero and a unit standard deviation.
 
-<!-- We then investigated  -->
-
-<!-- See topography data from Species distribution model transferability and model grain size – finer may not always be better -->
-
-<!-- Induced by latitude (more generalism in tropics) or diversity (more generalism with high diversity or the opposite), See Baiser 2019 for refsuse network as a random effect. -->
+All models were fitted under a bayesian framework using the R package `brms` `r as.character(packageVersion('brms'))` [@burkner_brms_2017; @burkner_advanced_2018] as an interface for Stan [@carpenter_stan_2017].
+All models were fitted using four Markov chains of 4,000 iterations each; half of the iterations were used for warmup.
+We used weakly informative priors for all model parameters. 
+Specifically we used normal priors of mean zero and standard deviation ten for the population level effects and the intercepts, a half-Cauchy prior with a location of zero and a scale of two for the standard deviations, and, when applicable, an LKJ-correlation prior with parameter \(\zeta = 2\) for the correlation matrix between group-level parameters.
+We used the Wanatabe-Akaike information criterion (WAIC) to compare the out-of sample performance of the different models.
 

### 2019-08-17 paper/manuscript.Rmd
Some extra refs

@@
 We modelled degree using a logarithmic link function and a Poisson distribution. 
-Nevertheless results were qualitatively the same if instead we model the normalised degree (REF Martin Gonzalez 2010) using a binomial distribution in which degree is the number of successes and the number of species in the opposite guild is the number of trials (Supp info).
+Nevertheless results were qualitatively the same if instead we model the normalised degree [@martin_gonzalez_centrality_2010] using a binomial distribution in which degree is the number of successes and the number of species in the opposite guild is the number of trials (Supp info).
 

### 2019-08-19 paper/manuscript.Rmd
Improve methods models

--- 2019-08-15 paper/manuscript.Rmd
@@
 
-We then used a series of bayesian multilevel models to evaluate the impact of environmental suitability on the number of interacting species. 
-These models differed on the predictors included and allowed us to evaluate the relative importance of suitability. 
-Our response variable was the number of species it interacts with in a community, the species degree. 
-We modelled degree using a logarithmic link function and a Poisson distribution. 
-Nevertheless results were qualitatively the same if instead we model the normalised degree (REF Martin Gonzalez 2010) using a binomial distribution in which degree is the number of successes and the number of species in the opposite guild is the number of trials (Supp info).
+We then used a two sets of bayesian multilevel models to evaluate the impact of environmental suitability on the size of the realised Eltonian niche. 
+We measure the size of the Eltonian niche using the normalised degree of species, this is, the number of species it interacts with given the number of possible partners. 
+In the first set of models, we use a *naive* version of the normalised degree [@martin_gonzalez_centrality_2010] in which the number of possible partners is defined by the number of species in the opposite guild.
+This definition is the one commonly used in the ecological network literature. 
+In the second set of models, we use an *informed* version of the normalised degree in which the number of possible partners is defined by the number of species in the community with which the focal species is known to interact in any other location in our dataset.
+Measuring the size of the Eltonian niche using the informed version of normalised degree is a particularly stringent test of the effect of environmental suitability as for many species populations in our dataset, the number of possible interacting species is the same or very similar to the number of species it actually interacts with.
 
-Briefly, our baseline model included suitability and guild as population effects and two groups, species and the community. 
-Our main predictor, the environmental suitability of the species in that particular location, is an index defined betwen zero and one in which a value of zero indicates that the species has never been observed in this environment while a value of one indicates that the species is most commonly observed in that environment.
+In all models normalised degree was modelled using a logit link function and a binomial distribution in which the number of species interacts with is the number of successes and the number of possible partners is the number of trials.
+We are aware that wether species intreacts or not is not a bernoulli process as species interactions are not independent from each other, however a binomial distribution allow us to indirectly account for the differences in species richness across communities.
+Importantly, results are qualitatively the similar when we model species degree directly using a Poisson distribution and a logarithmic link function and include the number of possible partners as predictors (Supp info).
+
+Within each model set we evaluate several candidate models in order to evaluate the relative importance of suitability. 
+A first model included suitability and guild as population effects and two grouping levels, species and the community. 
+Our main predictor, the environmental suitability of the species in that particular community, is an index defined betwen zero and one in which a value of zero indicates that the species has never been observed in this environment while a value of one indicates that the species is most commonly observed in that environment.
 As we are particularly intrested on understanding wether the effect of species suitability is conditional on the species guild (plant or pollinator), we also included guild and its interaction with suitability in the model.
 We allowed the intercept of degree and slope of the suitability-degree relationship to vary among species, this allowed us to investigate the extent to which suitability is a population or a group level effect.
-Finally, to account for unmeasured differences between communities, like sampling effort, sampling method, or richness, we calculated an intercept for each community in our study.
+Finally, to account for unmeasured differences between communities, like sampling effort, sampling method, or diversity, we calculated an intercept for each community in our study.
+A second model accounted for the overall generalism of a species by also including among the predictors the magnitude of the total number of interacting species across networks. 
+Finally, a third alternative model included the overall species generalism but excluded the effect of environmental suitability both at the population and the species level. 
+To facilitate model interpretation and convergence, we scaled all continuous variables to have a mean of zero and a unit standard deviation.
 
-We calculated three more alternative models. 
-The first alternative model accounted for the overall generalism of a species by including among the predictors the magnitude of the number of species it interacts with across networks. 
-The second alternative model, is highly prescriptive and accounts
-
-<!-- We then investigated  -->
-
-<!-- See topography data from Species distribution model transferability and model grain size – finer may not always be better -->
-
-<!-- Induced by latitude (more generalism in tropics) or diversity (more generalism with high diversity or the opposite), See Baiser 2019 for refsuse network as a random effect. -->
+All models were fitted under a bayesian framework using the R package `brms` `r as.character(packageVersion('brms'))` [@burkner_brms_2017; @burkner_advanced_2018] as an interface for Stan [@carpenter_stan_2017].
+All models were fitted using four Markov chains of 4,000 iterations each; half of the iterations were used for warmup.
+We used weakly informative priors for all model parameters. 
+Specifically we used normal priors of mean zero and standard deviation ten for the population level effects and the intercepts, a half-Cauchy prior with a location of zero and a scale of two for the standard deviations, and, when applicable, an LKJ-correlation prior with parameter \(\zeta = 1\) for the correlation matrix between group-level parameters.
+We used the Wanatabe-Akaike information criterion (WAIC) to compare the out-of sample performance of the different models.
 
 # Results
+
+We found that environmental suitability is an important variable
 

### 2019-08-19 code/suitability_vs_degree.R
Add a binomial constrained model set

@@ -107,6 +107,22 @@ define_binomial_models <- function(){
   define_alternative_models(formula_base)
 }
 
+define_binomial_constrained_models <- function(){
+  suppressPackageStartupMessages({
+    require(brms)
+  })
+  
+  formula_base <- brmsformula(
+    n_partners | trials(n_possible_partners) ~ 
+      scaled_suitability * guild +
+      (1 + scaled_suitability | org_id) + (1 | loc_id), 
+    family = binomial, 
+    center = TRUE
+  )
+  
+  define_alternative_models(formula_base)
+}
+
 # Return a list of formulas for the poisson models
 define_poisson_models <- function(){
   suppressPackageStartupMessages({

### 2019-08-19 main.R

@@ -195,7 +195,7 @@ download_ocurrence_data_plan <- drake_plan(
                                          returnclass = "sp", 
                                          scale = 10),
   country_data_sf = rnaturalearth::ne_countries(returnclass = "sf", scale = 10), 
-  flagged_occurrences  = clean_occurrences_chunked(occurrences, land_data, country_data_sf, n_chunks),
+  flagged_occurrences = clean_occurrences_chunked(occurrences, land_data, country_data_sf, n_chunks),
   cleaned_occurrences =  flagged_occurrences[.sea_manual & .summary],
   gbif_key_groups = get_gbif_key_groups(cleaned_occurrences),
   n_cleaned_occurrences = count_occurrences_per_taxon(cleaned_occurrences), 
@@ -273,7 +273,9 @@ suitability_vs_generalism_plan <- drake::drake_plan(
   analysis_frame = build_analysis_frame(org_degree, independent_suitability), 
   poisson_formulas = define_poisson_models(), 
   binomial_formulas = define_binomial_models(), 
+  binomial_constrained_formulas = define_binomial_constrained_models(),
   binomial_models = fit_model(binomial_formulas, analysis_frame, brm_cores), 
+  binomial_constrained_models = fit_model(binomial_constrained_formulas, analysis_frame, brm_cores), 
   poisson_models = fit_model(poisson_formulas, analysis_frame, brm_cores)
 )
 

### 2019-08-19 code/suitability_vs_degree.R
Redefine alternative models

@@ -137,7 +137,22 @@ define_poisson_models <- function(){
     center = TRUE
   )
   
-  define_alternative_models(formula_base)
+  formula_global <-  update(
+    formula_base, 
+    ~ . + scaled_n_possible_partners + scaled_log_n_partners_global
+  )
+  
+  formula_no_suitability <- update(
+    formula_global, 
+    ~ . - scaled_suitability - scaled_suitability:guild -
+      (1 + scaled_suitability | org_id) +
+      (1 | org_id))
+    
+  list(
+    formula_base = formula_base, 
+    formula_global = formula_global, 
+    formula_no_suitability = formula_no_suitability
+  )
 }
 
 # Given a base formula with suitability return a list of alternative formulas
@@ -147,19 +162,9 @@ define_alternative_models <- function(formula_base){
     formula_base, 
     ~ . + scaled_log_n_partners_global
   )
-  
-  formula_possible <- update(
-    formula_base, 
-    ~ . + scaled_n_possible_partners
-  )
-  
-  formula_global_possible <- update(
-    formula_base, 
-    ~ . + scaled_log_n_partners_global + scaled_n_possible_partners
-  )
-  
+
   formula_no_suitability <- update(
-    formula_global_possible, 
+    formula_global, 
     ~ . - scaled_suitability - scaled_suitability:guild -
       (1 + scaled_suitability | org_id) +
       (1 | org_id)
@@ -168,8 +173,6 @@ define_alternative_models <- function(formula_base){
   list(
     formula_base = formula_base, 
     formula_global = formula_global, 
-    formula_possible = formula_possible, 
-    formula_global_possible = formula_global_possible, 
     formula_no_suitability = formula_no_suitability
   )
   

### 2019-08-19 code/suitability_vs_degree.R
Draft posterior fit checks

@@ -196,7 +196,7 @@ fit_model <- function(formulas, analysis_frame, cores = 1L){
                  set_prior("cauchy(0, 2)", class = "sd")
                  ),
                chains = 4, 
-               iter = 2000,
+               iter = 4000,
                # warmup = 2000, 
                cores = cores,
                # future = TRUE,
@@ -253,4 +253,44 @@ tinker <- function(){
     coord_flip()
     lm(n_partners ~ suitability + log(n_partners_global) + n_opposite_guild + n_possible_partners, data = .) %>% 
     summary()
+    
+    loo(poisson_models[[1]], poisson_models[[2]], poisson_models[[3]], poisson_models[[4]], poisson_models[[5]])
+    loo(binomial_models[[1]], binomial_models[[2]], binomial_models[[3]], binomial_models[[4]], binomial_models[[5]])
+    waic(binomial_constrained_models[[1]], binomial_constrained_models[[2]], binomial_constrained_models[[3]], binomial_constrained_models[[4]], binomial_models[[5]])
+    
+    ## extract fitted values
+    fit <- binomial_constrained_models[[4]]
+    fitted_values <- predict(fit) %>%
+      tibble::as.tibble() %>%
+      dplyr::mutate(trials = standata(fit)$trials)
+    # head(fitted_values)
+    
+    # inverse_logit_trans <- trans_new("inverse logit",
+    #                                  transform = plogis,
+    #                                  inverse = qlogis)
+    # 
+    # logit_trans <- trans_new("logit",
+    #                          transform = qlogis,
+    #                          inverse = plogis)
+    # 
+    
+    ## plot fitted means against actual response
+    dat <- as.data.frame(cbind(Y = standata(fit)$Y, fitted_values)) %>%
+      dplyr::mutate(trials = 1)
+    
+    ggplot(dat, aes(y = Estimate/trials, x = Y/trials, group = Y/trials)) + 
+      geom_point(alpha = 0.5, shape = 21) +
+      # scale_x_continuous(trans = logit_trans) +
+      # scale_y_continuous(trans = logit_trans) +
+      # coord_trans(x = inverse_logit_trans)
+      scale_y_log10() +
+      scale_x_log10() +
+        geom_ribbon(aes(ymin = Q2.5/trials, ymax = Q97.5/trials), 
+                     size = 0.25, alpha = 0.25) +
[…]

### 2019-08-20 code/figures.R
Thresholds for both niche spaces in the manuscript figure

@@ -107,6 +107,10 @@ plot_sensitivity_analysis <- function(error_subsamples, min_suitability_error,
     library(ggplot2)
   })
   
+  thresholds <- min_occurrences_factor %>% 
+    as.data.frame() %>% 
+    tidyr::gather(key = "niche_space")
+  
   pal <- cgm()$pal_el_green[c(4,7)]
   
   n_nets <- suitability_subsamples$n_net_occurrences[1]
@@ -114,17 +118,19 @@ plot_sensitivity_analysis <- function(error_subsamples, min_suitability_error,
   e <- error_subsamples %>%
     dplyr::group_by(niche_space) %>%
     dplyr::mutate(error = mae)
+  
   p <- e %>%
     ggplot(aes(x = n_occ, y = error, fill = niche_space)) +
     geom_point(data = dplyr::sample_n(e, 1000),
                shape = 21, alpha = 1, size = 1) +
     # geom_smooth(method = "glm", method.args = list(family = "binomial")) +
-    geom_smooth(aes(colour = niche_space), method = "gam" , 
-                method.args = list(family = "binomial"), 
-                formula = y ~ s(x), se = T, 
+    geom_smooth(aes(colour = niche_space), method = "gam" ,
+                method.args = list(family = "binomial"),
+                formula = y ~ s(x), se = T,
                 size = 0.5) +
     geom_hline(yintercept = min_suitability_error, size = 0.25, linetype = 2) +
-    geom_vline(xintercept = min_occurrences_factor*n_nets, size = 0.25, linetype = 3) +
+    geom_vline(data = thresholds, 
+               aes(xintercept = value*n_nets, colour = niche_space), size = 0.5, linetype = 2) +
     # scale_x_continuous(limits = c(2,35)) +
     scale_x_log10() +
     scale_fill_manual(values = pal, aesthetics = c("fill", "colour"), 

### 2019-08-20 paper/manuscript.Rmd
Make baseline model the full model and remove variables. Scale n networks and include as predictor

@@
 
-Within each model set we evaluate several candidate models in order to evaluate the relative importance of suitability. 
-A first model included suitability and guild as population effects and two grouping levels, species and the community. 
-Our main predictor, the environmental suitability of the species in that particular community, is an index defined betwen zero and one in which a value of zero indicates that the species has never been observed in this environment while a value of one indicates that the species is most commonly observed in that environment.
-As we are particularly intrested on understanding wether the effect of species suitability is conditional on the species guild (plant or pollinator), we also included guild and its interaction with suitability in the model.
+Within each model set we evaluate four candidate models in order to evaluate the relative importance of suitability. 
+A first model, our baseline model, included four population-level predictors and two grouping levels, species and the community. 
+The population-level predictors, commonly called fixed effects, were the environmental suitability, the species guild, the species generalism, and it's environmental niche breadth.
+The environmental suitability of the species in that particular community, is an index defined betwen zero and one in which a value of zero indicates that the species has never been observed in this environment while a value of one indicates that the species is most commonly observed in that environment.
+We were particularly intrested on understanding wether the effect of species suitability is conditional on the species guild (plant or pollinator), we therefore included guild and its interaction with suitability in the model.
+To estimate a species overal level of generalism we included among the predictors the magnitude of the total number of interacting species across communities in our dataset. 
+We included the number of communities where the species was present as a rough estimate of a species environmental niche breadth. 
 We allowed the intercept of degree and slope of the suitability-degree relationship to vary among species, this allowed us to investigate the extent to which suitability is a population or a group level effect.
 Finally, to account for unmeasured differences between communities, like sampling effort, sampling method, or diversity, we calculated an intercept for each community in our study.
-A second model accounted for the overall generalism of a species by also including among the predictors the magnitude of the total number of interacting species across networks. 
-Finally, a third alternative model included the overall species generalism but excluded the effect of environmental suitability both at the population and the species level. 
+
+The second, third, and fourth models within each model set were a reduction of the first. 
+In the second model we removed the species generalism as a predictor, in the third, we removed the environmental niche breadth, and in the fourth model we removed excluded the effect of environmental suitability (both at the population and the species level).
 To facilitate model interpretation and convergence, we scaled all continuous variables to have a mean of zero and a unit standard deviation.
@@
 
+We found that our models performe
 We found that environmental suitability is an important variable

### 2019-08-20 code/suitability_vs_degree.R

@@ -81,7 +81,8 @@ build_analysis_frame <- function(org_degree,
     dplyr::mutate(scaled_suitability = scale(suitability), 
                   log_n_partners_global = log(n_partners_global), 
                   scaled_log_n_partners_global = scale(log_n_partners_global), 
-                  scaled_n_possible_partners = scale(n_possible_partners))
+                  scaled_n_possible_partners = scale(n_possible_partners), 
+                  scaled_n_obs = scale(n_obs))
   
   # add scale attributes to main frame
   attr(af, "scale_attributes") <- lapply(af, attributes)
@@ -99,6 +100,8 @@ define_binomial_models <- function(){
   formula_base <- brmsformula(
     n_partners | trials(n_opposite_guild) ~ 
       scaled_suitability * guild +
+      scaled_n_possible_partners + scaled_log_n_partners_global +
+      scaled_n_obs +
       (1 + scaled_suitability | org_id) + (1 | loc_id), 
     family = binomial, 
     center = TRUE
@@ -115,12 +118,42 @@ define_binomial_constrained_models <- function(){
   formula_base <- brmsformula(
     n_partners | trials(n_possible_partners) ~ 
       scaled_suitability * guild +
+      scaled_log_n_partners_global + scaled_n_obs +
       (1 + scaled_suitability | org_id) + (1 | loc_id), 
     family = binomial, 
     center = TRUE
   )
   
   define_alternative_models(formula_base)
+}
+
+# Given a base formula with suitability return a list of alternative formulas
+define_alternative_models <- function(formula_base){
+  
+  formula_no_generalism <- update(
+    formula_base, 
+    ~ . - scaled_log_n_partners_global
+  )
+  
+  formula_no_grinell_niche_size <- update(
+    formula_base, 
+    ~ . - scaled_n_obs
+  )
+  
+  formula_no_suitability <- update(
+    formula_base, 
+    ~ . - scaled_suitability - scaled_suitability:guild -
+      (1 + scaled_suitability | org_id) +
+      (1 | org_id)
+  )
+  
+  list(
+    formula_base = formula_base, 
+    formula_no_generalism = formula_no_generalism, 
+    formula_no_grinell_niche_size = formula_no_grinell_niche_size, 
+    formula_no_suitability = formula_no_suitability
+  )
+  
 }
 
 # Return a list of formulas for the poisson models
[…]

### 2019-08-22 code/suitability_vs_degree.R
Add extra model removing number of possible partners

@@ -89,7 +89,8 @@ build_analysis_frame <- function(org_degree,
   attr(af, "scale_attributes") <- lapply(af, attributes)
   
   af %>%
-    dplyr::filter(!is.na(suitability))
+    dplyr::filter(!is.na(suitability)) %>%
+    dplyr::filter(n_obs > 1)
 }
 
 # Return a list of forumlas for the binomial models
@@ -119,7 +120,8 @@ define_binomial_constrained_models <- function(){
   formula_base <- brmsformula(
     n_partners | trials(n_possible_partners) ~ 
       scaled_suitability * guild +
-      scaled_log_n_partners_global + scaled_grinell_niche_size +
+      scaled_log_n_partners_global + scaled_grinell_niche_size + 
+      scaled_n_possible_partners +
       (1 + scaled_suitability | org_id) + (1 | loc_id), 
     family = binomial, 
     center = TRUE
@@ -141,6 +143,16 @@ define_alternative_models <- function(formula_base){
     ~ . - scaled_grinell_niche_size
   )
   
+  formula_no_possible_partners <- update(
+    formula_base, 
+    ~ . - scaled_n_possible_partners
+  )
+  
+  formula_no_possible_partners_generalism <- update(
+    formula_base, 
+    ~ . - scaled_n_possible_partners - scaled_log_n_partners_global
+  )
+  
   formula_no_suitability <- update(
     formula_base, 
     ~ . - scaled_suitability - scaled_suitability:guild -
@@ -151,7 +163,9 @@ define_alternative_models <- function(formula_base){
   list(
     formula_base = formula_base, 
     formula_no_generalism = formula_no_generalism, 
-    formula_no_grinell_niche_size = formula_no_grinell_niche_size, 
+    formula_no_grinell_niche_size = formula_no_grinell_niche_size,
+    formula_no_possible_partners = formula_no_possible_partners,
+    formula_no_possible_partners_generalism = formula_no_possible_partners_generalism,
     formula_no_suitability = formula_no_suitability
   )
   

### 2019-08-22 code/suitability_vs_degree.R
Functions to chose and rank models

@@ -217,6 +217,27 @@ fit_model <- function(formulas, analysis_frame, cores = 1L, iter = 4000){
                               max_treedepth =12))
 }
 
+get_chosen_model <- function(models, models_index, chosen_formula_type, chosen_dataset){
+  models_index %>%
+    dplyr::filter(formula_type == chosen_formula_type, 
+                  dataset_type == chosen_dataset) %$% 
+                  {
+                    extract2(models, i)  
+                  }
+}
+
+compare_models <- function(chosen_models){
+  model_loo <- chosen_models %>%
+    purrr::map(brms::loo)
+  
+  model_waic <- chosen_models %>%
+    purrr::map(brms::waic)
+  
+  list(loo = brms::loo_compare(model_loo), 
+       waic = brms::loo_compare(model_waic))
+}
+
+
 sample_baseline_population <- function(analysis_frame){
   analysis_frame %$%
     list(N = NROW(.), 

### 2019-08-22 main.R

@@ -291,7 +291,11 @@ suitability_vs_generalism_plan <- drake::drake_plan(
     purrr::imap_dfr(~tibble::tibble(i = .y, formula_type = .x[[1]], dataset_type = .x[[2]])),
   models = purrr::map(formulas_and_data,
                       ~fit_model(formulas = .[[1]], analysis_frame = .[[2]], 
-                                 cores = brm_cores, iter = 4000))
+                                 cores = brm_cores, iter = 4000)), 
+  chosen_models = get_chosen_model(models, models_index, 
+                                   chosen_formula_type = "binomial_formulas", 
+                                   chosen_dataset = "collective_suitability"), 
+  model_ranking = compare_models(chosen_models)
 )
 
 # Referencing -------------------------------------------------------------

### 2019-08-22 paper/manuscript.Rmd
Little attempt of some formal results in the manuscript

@@
 
-We found that our models performe
+We found that our models performed relativelly well. 
+Overall we found no relationship between 
 We found that environmental suitability is an important variable
+
+```{r}
+loadd(model_ranking)
+waic_scores <- as.data.frame(model_ranking$waic) %>%
+  tibble::rownames_to_column(var = "formula") %>%
+  dplyr::select(formula, waic, se_waic)
+
+loo_scores <- as.data.frame(model_ranking$loo) %>%
+  tibble::rownames_to_column(var = "formula") %>%
+  dplyr::select(formula, looic, se_looic)
+```
 

### 2019-08-22 code/model_predictions.R
Tinker with model predictions and plots
Need to read about tidybayes

@@ -1,0 +1,17 @@
+make_predictions <- function(this_model){
+  suppressPackageStartupMessages({
+    require(brms)
+    require(tidybayes)
+  })
+  
+  model_data <- standata(this_model)
+  median_trials <- this_model$data %>% 
+    dplyr::distinct(guild, n_opposite_guild) %>%
+    dplyr::group_by(guild) %>% 
+    dplyr::summarise(trials = median(n_opposite_guild))
+  
+  conditions <- data.frame(guild = c("pla_id", "ani_id"))
+  
+  me <- marginal_effects(this_model, "scaled_grinell_niche_size", conditions = median_trials)
+  
+}

### 2019-08-26 code/suitability_vs_degree.R
Save all parameters of models to calculate bayes factor if necessary

@@ -212,6 +212,7 @@ fit_model <- function(formulas, analysis_frame, cores = 1L, iter = 4000){
                iter = iter,
                # warmup = 2000, 
                cores = cores,
+               save_all_pars = TRUE,
                # future = TRUE,
                control = list(adapt_delta = 0.99, 
                               max_treedepth =12))

### 2019-08-26 paper/manuscript.Rmd
Add model comparison table to paper

--- 2019-08-20 paper/manuscript.Rmd
@@
 
-We found that our models performe
+We found that our models performed relativelly well. 
+Overall we found no relationship between 
 We found that environmental suitability is an important variable
+
+```{r fig-conditional-effects, fig.width = width('single'), fig.height = 2.2*4, fig.cap = "Conditional effects"}
+readd(fig_conditional_effects)
+```
+
+```{r model-comparison-table}
+loadd(model_ranking)
+waic_scores <- as.data.frame(model_ranking$waic) %>%
+  tibble::rownames_to_column(var = "formula") %>%
+  dplyr::select(formula, waic)
+
+loo_scores <- as.data.frame(model_ranking$loo) %>%
+  tibble::rownames_to_column(var = "formula") %>%
+  dplyr::select(formula, elpd_diff, se_diff,  looic)
+
+loo_scores %>%
+  dplyr::inner_join(waic_scores, by = "formula") %>%
+  dplyr::mutate(formula = translate_model_formula(formula, "long-abv"), 
+                formula = kableExtra::cell_spec(formula, format = "latex", 
+                                                bold =nchar(formula) == max(nchar(formula)))) %>%
+  knitr::kable("latex", 
+               booktabs = TRUE, 
+               digits = c(0,0,1,0,0), 
+               format.args = list(big.mark = ","), 
+               col.names = c("predictors", "$\\Delta$", "$SE_{\\Delta}$", "IC", "WAIC"),
+               escape = FALSE,
+               linesep = "",
+               caption = "Comparison in out of sample predictive power of the baseline model (bold) and their alternatives.
+We rank models by their expected log predictive density based on their leave-one-out cross-validation information criterion (LOO).
+The standard error of the LOO difference provides rough guidance to the uncertainty of the model ranking.
+We also show the widely applicable information criterion (WAIC) of each model for comparison.") %>%
+  kableExtra::kable_styling(font_size = 8) %>%
+  kableExtra::add_header_above(c(" " = 1, "LOO" = 3, " " = 1))
+```
 

### 2019-08-26 paper/manuscript.Rmd
Describe loo

@@
 Specifically we used normal priors of mean zero and standard deviation ten for the population level effects and the intercepts, a half-Cauchy prior with a location of zero and a scale of two for the standard deviations, and, when applicable, an LKJ-correlation prior with parameter \(\zeta = 1\) for the correlation matrix between group-level parameters.
-We used the Wanatabe-Akaike information criterion (WAIC) to compare the out-of sample performance of the different models.
+To minimise the potential effect of influential observations we used leave-one-out cross-valiadtion to estimate their expected log predictive density and compare the out-of sample performance of the different models.
+We also calculate the Wanatabe-Akaike information criterion (WAIC) for comparison.
 
@@
 
+```{r}
+loadd(bayesian_r2_baseline)
+```
+
 We found that our models performed relativelly well. 
-Overall we found no relationship between 
+The bayesian R-squared for our baseline model was `r round(bayesian_r2_baseline[1], digits = 2)`. 
+Overall we found only weak evidence of a relationship between the environmental niche size and the normalised degree. 
 We found that environmental suitability is an important variable

### 2019-08-26 paper/manuscript.Rmd
Ensure some space between tables and their caption

@@
   - \usepackage[export]{adjustbox}
+  - \usepackage{caption}
 editor_options: 
@@
 \doublespacing
+\captionsetup[table]{skip=10pt}
 

### 2019-08-27 code/figures.R
Improve looks of conditional effects plot

@@ -158,6 +158,7 @@ plot_all_conditional_effect <- function(this_model){
     require(ggplot2)
   })
   
+  pal <- cgm()$pal_el_green[c(8,7)]
   
   median_trials <- this_model$data %>%
     # dplyr::distinct(org_id, loc_id, .keep_all = F) %>% nrow
@@ -172,8 +173,8 @@ plot_all_conditional_effect <- function(this_model){
                     scaled_n_possible_partners = 0) %>%
     add_fitted_draws(this_model, re_formula = NA, n = 100) %>% 
     dplyr::mutate(var = scaled_grinell_niche_size) %>%
-    plot_conditional_effect_guild() +
-    labs(title = "(a) Effect of environmental niche size", 
+    plot_conditional_effect_guild(pal) +
+    labs(title = "(a) environmental niche size", 
          x = "environmental niche size (scaled)")
   
   suitability_scale_attr <- get_scale_attributes(this_model$data$scaled_suitability)
@@ -187,8 +188,8 @@ plot_all_conditional_effect <- function(this_model){
     add_fitted_draws(this_model, re_formula = NA, n = 100) %>%
     dplyr::mutate(suitability = scaled_to_unscaled(scaled_suitability, suitability_scale_attr), 
                   var = suitability) %>%
-    plot_conditional_effect_guild() +
-    labs(title = "(a) Environmental suitability", 
+    plot_conditional_effect_guild(pal) +
+    labs(title = "(b) environmental suitability", 
          x = "environmental suitability")
   
   generality_scale_attr <- get_scale_attributes(this_model$data$scaled_log_n_partners_global)
@@ -205,15 +206,16 @@ plot_all_conditional_effect <- function(this_model){
                   n_partners_global = exp(log_n_partners_global),
                   var = n_partners_global) %>%
     dplyr::filter(guild == "ani_id") %>%
-    plot_conditional_effect_guild() +
-    labs(title = "(c) Generality", 
-         x = "environmental suitability")
+    plot_conditional_effect_guild(pal) +
+    labs(title = "(c) generality", 
+         x = "# partners across communities")
   
   possible_scale_attr <- get_scale_attributes(this_model$data$scaled_n_possible_partners)
-  
-  possible_plot <- median_trials %>%
+
+    possible_plot <- median_trials %>%
     tidyr::crossing(scaled_grinell_niche_size = 0, 
-                    scaled_suitability = 0, 
+                    scaled_suitability = seq(unscaled_to_scaled(0, suitability_scale_attr),
[…]

### 2019-08-27 code/figures.R
Figure for sensitivity analysis only shows collective space now

@@ -109,7 +109,8 @@ plot_sensitivity_analysis <- function(error_subsamples, min_suitability_error,
   
   thresholds <- min_occurrences_factor %>% 
     as.data.frame() %>% 
-    tidyr::gather(key = "niche_space")
+    tidyr::gather(key = "niche_space") %>%
+    dplyr::filter(niche_space == "all_species")
   
   pal <- cgm()$pal_el_green[c(4,7)]
   
@@ -117,27 +118,35 @@ plot_sensitivity_analysis <- function(error_subsamples, min_suitability_error,
   
   e <- error_subsamples %>%
     dplyr::group_by(niche_space) %>%
-    dplyr::mutate(error = mae)
+    dplyr::mutate(error = mae) %>%
+    dplyr::filter(niche_space == "all_species")
   
   p <- e %>%
-    ggplot(aes(x = n_occ, y = error, fill = niche_space)) +
+    ggplot(aes(x = n_occ, y = error)) +
     geom_point(data = dplyr::sample_n(e, 1000),
-               shape = 21, alpha = 1, size = 1) +
+               shape = 21, alpha = 1, size = 1, colour = "grey30", stroke = 0.25) +
     # geom_smooth(method = "glm", method.args = list(family = "binomial")) +
-    geom_smooth(aes(colour = niche_space), method = "gam" ,
+    geom_smooth(method = "gam" ,
                 method.args = list(family = "binomial"),
-                formula = y ~ s(x), se = T,
-                size = 0.5) +
+                formula = y ~ s(x), se = F,
+                size = 0.5, colour = "black") +
     geom_hline(yintercept = min_suitability_error, size = 0.25, linetype = 2) +
     geom_vline(data = thresholds, 
-               aes(xintercept = value*n_nets, colour = niche_space), size = 0.5, linetype = 2) +
+               aes(xintercept = value*n_nets), size = 0.25, linetype = 2) +
+    geom_text(data = thresholds, 
+              aes(label = paste("~",  value, "occurrences\nper community"), 
+                  x = value*n_nets), 
+              y = max(e$error), angle = 90, hjust = 1, vjust = 1.2, 
+              size = 2.3, lineheight = 0.8) +
+    annotate("text", label = "10% error", x = max(e$n_occ), y = 0.1, hjust = 1, 
+             vjust = -1, size = 2.3) +
     # scale_x_continuous(limits = c(2,35)) +
     scale_x_log10() +
-    scale_fill_manual(values = pal, aesthetics = c("fill", "colour"), 
[…]

### 2019-08-27 paper/manuscript.Rmd
Wanatabe-Akaike instead of widely applicable information criteria

@@
 The standard error of the LOO difference provides rough guidance to the uncertainty of the model ranking.
-We also show the widely applicable information criterion (WAIC) of each model for comparison.") %>%
+We also show the Wanatabe-Akaike information criterion (WAIC) of each model for comparison.") %>%
   kableExtra::kable_styling(font_size = 8) %>%

### 2019-08-29 paper/manuscript.Rmd
Conditional effects plot a bit smaller in paper
Add figure in manuscript

@@
 
-```{r fig-conditional-effects, fig.width = width('single'), fig.height = 2.2*4, fig.cap = "Conditional effects"}
+```{r fig-conditional-effects, fig.width = width('single'), fig.height = 2.2*3, fig.cap = "Conditional effects"}
 readd(fig_conditional_effects)
@@
 
-```{r model-comparison-table}
+```{r tab-model-comparison-table}
 loadd(model_ranking)
@@
   kableExtra::add_header_above(c(" " = 1, "LOO" = 3, " " = 1))
+```
+
+```{r fig-random-effects, fig.width = width('single'), fig.height = 2.2*2.5, fig.cap = "Random effects"}
+readd(fig_random_effects)
 ```

### 2019-08-29 main.R

@@ -323,9 +323,9 @@ figures_plan <- drake_plan(
                                                        min_suitability_error, 
                                                        min_occurrences_factor, 
                                                        suitability_subsamples), 
-  fig_conditional_effects = plot_all_conditional_effect(chosen_models$formula_base)
+  fig_conditional_effects = plot_all_conditional_effect(chosen_models$formula_base), 
+  fig_random_effects = plot_ranf(chosen_models$formula_base)
 )
-
 
 # Manuscript --------------------------------------------------------------
 

### 2019-08-29 code/figures.R
Add mean line to density plot of random correlation

@@ -367,14 +367,19 @@ plot_ranf <- function(this_model){
     labs(y = "# interactions", 
          x = "environmental suitability",
          title = "(a) effect of suitability on individual species")
-  # a\[\w+,
+
+  correlation_posterior <- brms::posterior_samples(this_model, pars = c("cor_org_id__Intercept__scaled_suitability")) %>% 
+    dplyr::mutate(correlation = cor_org_id__Intercept__scaled_suitability)
   
-  b <- brms::posterior_samples(this_model, pars = c("cor_org_id__Intercept__scaled_suitability")) %>% 
-    dplyr::mutate(correlation = cor_org_id__Intercept__scaled_suitability) %>%
+  mean_correlation <- correlation_posterior %>%
+    dplyr::summarise_all(mean) %$% 
+    correlation
+  
+  correlation_plot <- correlation_posterior %>%
     ggplot(aes(x = correlation)) +
     geom_density(fill = cgm()$pal_el_green[1], colour = NA) +
     stat_density(geom = "line", colour = cgm()$pal_el_green[9], size = 0.25) +
-    # geom_vline(xintercept = 0, size = 0.25, linetype = 2) +
+    geom_vline(xintercept = mean_correlation, size = 0.25, linetype = 2) +
     coord_cartesian(expand = T) +
     pub_theme() +
     theme(panel.border = element_blank(), 
@@ -385,7 +390,7 @@ plot_ranf <- function(this_model){
     labs(title = "(b) correlation between random intercept and slope")
 
   
-  p <- cowplot::plot_grid(a, b, 
+  p <- cowplot::plot_grid(conditional_effects_plot, correlation_plot, 
                           ncol = 1 ,
                           rel_heights = c(2,0.5), 
                           align = "v")

### 2019-08-29 paper/manuscript.Rmd
Write first draft of results

@@
 loadd(bayesian_r2_baseline)
+loadd(parameter_posterior_summary)
+
+random_cor <- parameter_posterior_summary %>% 
+  as.data.frame() %>%
+  tibble::rownames_to_column(var = "parameter") %>%
+  dplyr::filter(parameter == "cor_org_id__Intercept__scaled_suitability")
 ```
@@
 We found that our models performed relativelly well.
-The bayesian R-squared for our baseline model was `r round(bayesian_r2_baseline[1], digits = 2)`. 
-Overall we found only weak evidence of a relationship between the environmental niche size and the normalised degree. 
-We found that environmental suitability is an important variable
+The bayesian R-squared for our baseline model was `r round(bayesian_r2_baseline[1], digits = 2)`, which indicates our models were able to capture a large proporton of the variability on the data. 
+Overall we found only weak evidence of a relationship between the environmental niche size and the normalised degree (Figure \@ref(fig:fig-conditional-effects)a). 
+This relationship was stronger for plants than for animals.
+Similarly environmental suitability does not show a consistent pattern accross species. 
+Indeed, when looking at the population level effects, suitability virtually no relationship with normalised degree, neither for plants or pollinators (Figure \@ref(fig:fig-conditional-effects)b). 
+However, suitability is still an important predictor as the difference between our baseline model and that that did not include suitability was XXX (±XX) (±SE). 
+Both among plants and pollinators for some species there is a strong negative relationship between suitability and normalised degree and some others with a strong positive relationship (Figure \@ref(fig:fig-random-effects)a).
+The slope of this relationship was negatively correlated with the species' intercept in the model (Figure \@ref(fig:fig-random-effects)b). 
+The correlation coefficient was `r round(random_cor$Estimate, 2)` with a `r round(random_cor$Q2.5, 2)` to `r round(random_cor$Q97.5, 2)` 95% credible interval.
+As expected, we found a positive relationship between a species generalism and normalised degree \@ref(fig:fig-conditional-effects)c). 
+However our model comparisons based on WAIC shows that including generalism in the model adds relatively little information once we have accounted for the other variables in the model.
+Finally, we found a strong and positive relationship between the number of possible interactions and the number of realised interactions in the community.
+
+Random effects SD. eviation
 
@@
 loadd(model_ranking)
+
 waic_scores <- as.data.frame(model_ranking$waic) %>%

### 2019-08-29 paper/manuscript.Rmd
Move sensitivity anaysis to results

@@
 For that we used the species with most occurrences available, *`r sensitivity_species_name$canonicalName`*, and calculated the mean absolute error of the suitability values obtained with `r numbers2words(config$n_subsamples)` subsamples from the `r format(n_occ_sensitivity_species, big.mark  =",")`  occurrences available from GBIF.
-We found that, when we calculate the environmental space independently for each sepecies, we need roughly `r readd(min_occurrences_factor)` independent occurrences for each community for which we calculated a suitability value in order to obtain a mean absolute error below `r config$min_suitability_error` (Fig.
-\@ref(fig:fig-sensitivity-analysis)).
-We therefore removed from further analyses `r n_spp_not_enough_occ` species for which we did not have enough occurrences to obtain robust estimates.
-
-```{r fig-sensitivity-analysis, fig.width = width('single'), fig.height = 2.2, fig.cap = fig_sensitivity_analysis_legend}
-
-fig_sensitivity_analysis_legend <- 
-  paste0("Sensitivity analysis of environmental suitability error. ",
-         "The number of independent occurrences retrieved from GBIF is inversely related to the error of environmental suitability for our plant-pollinator networks.", 
-         "The error was smaller when environmental space, where species ocurrences are projected, is calculated independently for each species. ", 
-         "The sensitivity analysis was performed by subsampling occurrences of", 
-         " *", sensitivity_species_name$canonicalName, "* ", 
-         "the species in our dataset with the largest number of occurrences in GBIF, which was recorded in two of our communities.")
-
-readd(fig_sensitivity_analysis)
-```
 
@@
 
-```{r}
+After performing our sensitivity analysis, we found that we need roughly `r readd(min_occurrences_factor)` independent occurrences for each community for which we calculated a suitability value in order to obtain a mean absolute error below `r config$min_suitability_error` (Fig.
+\@ref(fig:fig-sensitivity-analysis)).
+We therefore removed from further analyses `r n_spp_not_enough_occ` species for which we did not have enough occurrences to obtain robust estimates.
+
+```{r fig-sensitivity-analysis, fig.width = width('single'), fig.height = 2.2, fig.cap = fig_sensitivity_analysis_legend}
+
+fig_sensitivity_analysis_legend <- 
+  paste0("Sensitivity analysis of environmental suitability error. ",
+         "The number of independent occurrences retrieved from GBIF is inversely related to the error of environmental suitability for our plant-pollinator networks.", 
+         "The sensitivity analysis was performed by subsampling occurrences of", 
+         " *", sensitivity_species_name$canonicalName, "* ", 
+         "the species in our dataset with the largest number of occurrences in GBIF, which was recorded in two of our communities.")
+
+readd(fig_sensitivity_analysis)
+```
 loadd(bayesian_r2_baseline)

### 2019-08-29 paper/manuscript.Rmd
Remove old model outputs

@@
 
-```
-Call:
-glm(formula = n_partners ~ scale(suitability) * guild, family = "poisson", 
-    data = .)
-
-Coefficients:
-                               Estimate Std. Error z value Pr(>|z|)    
-(Intercept)                     1.79092    0.02360  75.886  < 2e-16 ***
-scale(suitability)              0.07750    0.02454   3.158  0.00159 ** 
-guildpla_id                     0.64345    0.04361  14.756  < 2e-16 ***
-scale(suitability):guildpla_id  0.07645    0.03631   2.106  0.03524 *  
----
-AIC: 3739.6
-```
-
-```
-Call:
-glm(formula = n_partners ~ scale(suitability) * guild + scale(log(n_partners_global)), 
-    family = "poisson", data = .)
-
-Coefficients:
-                               Estimate Std. Error z value Pr(>|z|)    
-(Intercept)                     1.70709    0.02541  67.172  < 2e-16 ***
-scale(suitability)              0.17021    0.02481   6.860 6.88e-12 ***
-guildpla_id                     0.61872    0.04378  14.132  < 2e-16 ***
-scale(log(n_partners_global))   0.42074    0.01970  21.362  < 2e-16 ***
-scale(suitability):guildpla_id -0.02134    0.03657  -0.584     0.56    
----
-
-AIC: 3302.1
-```
-
-```
-Call:
-glm(formula = n_partners ~ scale(suitability) * guild + scale(log(n_partners_global)) + 
-    scale(n_possible_partners), family = "poisson", data = .)
-
-Coefficients:
-                               Estimate Std. Error z value Pr(>|z|)    
-(Intercept)                    1.667769   0.025701  64.892  < 2e-16 ***
-scale(suitability)             0.088729   0.024121   3.679 0.000235 ***
-guildpla_id                    0.423815   0.043904   9.653  < 2e-16 ***
-scale(log(n_partners_global))  0.138837   0.022829   6.082 1.19e-09 ***
-scale(n_possible_partners)     0.351851   0.008547  41.167  < 2e-16 ***
-scale(suitability):guildpla_id 0.010224   0.036728   0.278 0.780718    
----
-
-AIC: 2141.5
-```
-
-# Discussion
-
 <!-- We focus suitability in abiotic factors but can also be influenced by dispersal and species interactions themselves (e.g. competition and facilitation, Lortie et al. 2004).  -->

### 2019-08-29 paper/manuscript.Rmd
Random effects results

@@
 ```
+
+```{r model-results-calculations}
 loadd(bayesian_r2_baseline)
@@
 random_cor <- parameter_posterior_summary %>%
-  as.data.frame() %>%
-  tibble::rownames_to_column(var = "parameter") %>%
   dplyr::filter(parameter == "cor_org_id__Intercept__scaled_suitability")
+
+sd_loc_id <- parameter_posterior_summary %>% 
+  dplyr::filter(stringr::str_detect(parameter, "sd_loc_id__Intercept"))
+
+sd_org_id <- parameter_posterior_summary %>% 
+  dplyr::filter(stringr::str_detect(parameter, "sd_org_id__Intercept"))
+
+sd_org_id_suitability <- parameter_posterior_summary %>% 
+  dplyr::filter(stringr::str_detect(parameter, "sd_org_id__scaled_suitability"))
 ```
@@
 
+The group level variation among communities was larger than that among species.
+The standard deviation (in the parameters scale) of the community intercepts was `r round(sd_loc_id$Estimate, 2)` [`r round(random_cor$Q2.5, 2)`, `r round(sd_loc_id$Q97.5, 2)`] while the standard deviation of the species intercept was `r round(sd_org_id$Estimate, 2)` [`r round(sd_org_id$Q2.5, 2)`, `r round(sd_org_id$Q97.5, 2)`], and that of the species' suitability slope was `r round(sd_org_id_suitability$Estimate, 2)` [`r round(sd_org_id_suitability$Q2.5, 2)`, `r round(sd_org_id_suitability$Q97.5, 2)`] (95% credible intervals shown within square brakets).
+Interestingly, the slope the relationship between suitability and normalised degree was negatively correlated with the species' intercept in the model (Figure \@ref(fig:fig-random-effects)b). 
+The mean correlation coefficient was `r round(random_cor$Estimate, 2)` [`r round(random_cor$Q2.5, 2)`, `r round(random_cor$Q97.5, 2)`].
+
 ```{r fig-random-effects, fig.width = width('single'), fig.height = 2.2*2.5, fig.cap = "Random effects"}
@@
 ```
+
+# Discussion
 

### 2019-08-29 paper/manuscript.Rmd
Draft conditional effects figure caption

@@
 Both among plants and pollinators for some species there is a strong negative relationship between suitability and normalised degree and some others with a strong positive relationship (Figure \@ref(fig:fig-random-effects)a).
-The slope of this relationship was negatively correlated with the species' intercept in the model (Figure \@ref(fig:fig-random-effects)b). 
-The correlation coefficient was `r round(random_cor$Estimate, 2)` with a `r round(random_cor$Q2.5, 2)` to `r round(random_cor$Q97.5, 2)` 95% credible interval.
 As expected, we found a positive relationship between a species generalism and normalised degree \@ref(fig:fig-conditional-effects)c). 
@@
 
-Random effects SD. eviation
+```{r fig-conditional-effects, fig.width = width('single'), fig.height = 2.2*3, fig.cap = fig_conditional_effects_legend}
 
-```{r fig-conditional-effects, fig.width = width('single'), fig.height = 2.2*3, fig.cap = "Conditional effects"}
+fig_conditional_effects_legend <- 
+  paste0("Conditional effects of predictors in our models. The predicted values of the number of interacting species are based on ",
+         "XX ", "plants and ", 
+         "XX ", "pollinators, ",
+         "which corresponds to the median number of species in each guild.
+In each panel we condition on the mean values of all other predictors in the model.
+This is a environmental suitability of To illustrate the uncertainity around the fitted estimates we plot the fits of 100 independent draws from the posterior distribution.
+The thick lines indicate the mean values of the response distribution.")
 readd(fig_conditional_effects)

### 2019-08-29 paper/draft-info.Rmd
Update draft info

@@
 Easy to get some more from other published studies.
-Could improve the manuscript but every new data set has to be cleaned independently and might take one to half a day per network.
+Could improve the manuscript but every new data set has to be cleaned independently.
+This could take around 2 days per network.
 * Should I increase the resolution of the bioclimatic variables?
@@
 * Audrey: Could you please fill in the gaps in the rationale behind filtering out occurrences with potential low quality coordinates (\lr{rationale-occurrence-filtering})
+* I chose, rather arbitrarily, a mean absolute error of 10% for the sensitivity analysis. Does this choice sound appropiate to you?
 
@@
 * Dowloaded species occurrences. Wasn't straightforward as there is a lot of species and lots of restrictions with the GBIF API. About a week getting this to work.
+* Calculated environmental niche size and the environmental suitability of species in their communities
+* Modelled the normalised degree of species as a proxy of eltonian niche size using a bayesian framework
 
@@
 * Manually fix the remaining species names that are incorrect and were not picked up by the automatic procedure. Doing 5-10 per day, so should be done in a couple months
-* Fix references. There are lots of mistakes re. author, years and publication venue.
+* Fix references. There are lots of mistakes re. author, years and publication venue particularly for those from which data was downloaded.

### 2019-08-30 code/figures.R
Annotate random effects plot with actual species name

@@ -219,7 +219,7 @@ plot_conditional_effect_guild <- function(data, pal, mean_val, log_transformed =
     labs(y = "# interactions")
 }
 
-plot_ranf <- function(random_species_draws, random_correlation_posterior){
+plot_ranf <- function(random_species_draws, random_correlation_posterior, random_sp_names){
   
   suppressPackageStartupMessages({
     require(ggplot2)
@@ -232,11 +232,12 @@ plot_ranf <- function(random_species_draws, random_correlation_posterior){
   conditional_effects_plot <- random_species_draws %>%
     dplyr::ungroup() %>%
     dplyr::mutate(guild = translate_guild(guild)) %>%
+    dplyr::left_join(random_sp_names, by = "org_id") %>%
     ggplot(aes(x = var, y = .value, colour = guild)) +
     geom_line(aes(group = org_id, alpha = highlight, size = highlight), stat = "summary",fun.y = "mean") +
     geom_mark_circle(aes(group = org_id, 
                          filter = highlight & mark, 
-                          label = org_id), 
+                          label = sp_name), 
                      expand = unit(0, "mm"), 
                      alpha = 0.1,
                       # concavity = 0, 

### 2019-08-30 code/model_predictions.R

@@ -141,6 +141,18 @@ get_posterior_random_correlation <- function(baseline_model){
     dplyr::mutate(correlation = cor_org_id__Intercept__scaled_suitability)
 }
 
+get_random_sp_names <- function(random_species_draws, org_ids, gbif_key_groups, gbif_keys,
+                                species_ids){
+  random_species_draws %>%
+    dplyr::filter(highlight) %$%
+    org_id %>% 
+    unique() %>%
+    purrr::map(get_sp_name, org_ids, gbif_key_groups, gbif_keys,
+               species_ids) %>%
+    purrr::map(dplyr::slice, 1) %>%
+    purrr::map_df(dplyr::select, org_id, sp_name)
+}
+
 tinker <- function(){
   # model_data <- standata(this_model)
   # conditions <- data.frame(guild = c("pla_id", "ani_id"))

### 2019-08-30 main.R

@@ -305,6 +305,8 @@ suitability_vs_generalism_plan <- drake::drake_plan(
   random_correlation_posterior = get_posterior_random_correlation(baseline_model), 
   parameter_scale_attributes = get_all_pars_scale_attributes(baseline_model), 
   mean_parameter_values = purrr::map(parameter_scale_attributes, ~scaled_to_unscaled(0, .)), 
+  random_sp_names = get_random_sp_names(random_species_draws, org_ids, gbif_key_groups, gbif_keys,
+                                        species_ids)
 )
 
 # Referencing -------------------------------------------------------------
@@ -331,7 +333,7 @@ figures_plan <- drake_plan(
                                                        min_occurrences_factor, 
                                                        suitability_subsamples), 
   fig_conditional_effects = plot_all_conditional_effect(cond_draws, mean_parameter_values), 
-  fig_random_effects = plot_ranf(random_species_draws, random_correlation_posterior)
+  fig_random_effects = plot_ranf(random_species_draws, random_correlation_posterior, random_sp_names)
 )
 
 # Manuscript --------------------------------------------------------------

### 2019-08-30 paper/manuscript.Rmd
Include median number of trials in conditional effects plot caption

--- 2019-08-29 paper/manuscript.Rmd
@@
 
-Random effects SD. eviation
+```{r fig-conditional-effects, fig.width = width('single'), fig.height = 2.2*3, fig.cap = fig_conditional_effects_legend}
+loadd(median_trials)
 
-```{r fig-conditional-effects, fig.width = width('single'), fig.height = 2.2*3, fig.cap = "Conditional effects"}
+median_n_pla <- median_trials %>%
+  dplyr::filter(guild == "pla_id") %$% 
+  n_opposite_guild
+
+median_n_ani <- median_trials %>%
+  dplyr::filter(guild == "ani_id") %$% 
+  n_opposite_guild
+
+fig_conditional_effects_legend <- 
+  paste0("Conditional effects of predictors in our baseline model. The predicted values of the number of interacting species are based on a hypothetical community with ",
+         median_n_pla, " plants and ", 
+         median_n_ani, " pollinators",
+         ".
+These values correspond to the median number of species in each guild respectively.
+In each panel we condition on the mean values of all other predictors in the model, mean values for each predictor are indicated with a vertical dashed line.
+For model fitting, we scaled all predictors to have mean of zero and unit variance.
+However, with the exception of environmental niche size, here we show the unscaled predictors to facilitate interpretation.
+To illustrate the uncertainity around the fitted estimates we plot the fits of 100 independent draws from the posterior distribution.
+The thick lines indicate the mean values of the response distribution.
+As there was no interaction between guild and generality or the number of possible interactions, for these two predictors we only show conditional the conditional effect of pollinators.")
 readd(fig_conditional_effects)

### 2019-08-30 code/suitability_vs_degree.R
Do not calculate model without generalism and # possible partners

@@ -167,10 +167,10 @@ define_alternative_models <- function(formula_base){
     ~ . - scaled_n_possible_partners
   )
   
-  formula_no_possible_partners_generalism <- update(
-    formula_base, 
-    ~ . - scaled_n_possible_partners - scaled_log_n_partners_global
-  )
+  # formula_no_possible_partners_generalism <- update(
+  #   formula_base, 
+  #   ~ . - scaled_n_possible_partners - scaled_log_n_partners_global
+  # )
   
   formula_no_suitability <- update(
     formula_base, 
@@ -184,7 +184,7 @@ define_alternative_models <- function(formula_base){
     formula_no_generalism = formula_no_generalism, 
     formula_no_grinell_niche_size = formula_no_grinell_niche_size,
     formula_no_possible_partners = formula_no_possible_partners,
-    formula_no_possible_partners_generalism = formula_no_possible_partners_generalism,
+    # formula_no_possible_partners_generalism = formula_no_possible_partners_generalism,
     formula_no_suitability = formula_no_suitability
   )
   

### 2019-08-30 paper/manuscript.Rmd
Calc WAIC model difference for suitability and baseline model and report it

@@
 loadd(parameter_posterior_summary)
+loadd(model_ranking)
 
@@
   dplyr::filter(stringr::str_detect(parameter, "sd_org_id__scaled_suitability"))
+
+waic_comp_suitability <- model_ranking$waic$formula_no_suitability$pointwise - model_ranking$waic$formula_base$pointwise
+
+waic_diff_suitability <- sum(waic_comp_suitability[, "waic"])
+
+waic_se_diff_suitability <- sqrt(nrow(waic_comp_suitability) * var(waic_comp_suitability[, "waic"]))
 ```
@@
 Indeed, when looking at the population level effects, suitability virtually no relationship with normalised degree, neither for plants or pollinators (Figure \@ref(fig:fig-conditional-effects)b). 
-However, suitability is still an important predictor as the difference between our baseline model and that that did not include suitability was XXX (±XX) (±SE). 
+However, suitability is still an important predictor as the WAIC difference between our baseline model and that that did not include suitability was `r round(waic_diff_suitability)` ± `r round(waic_se_diff_suitability)`.
 Both among plants and pollinators for some species there is a strong negative relationship between suitability and normalised degree and some others with a strong positive relationship (Figure \@ref(fig:fig-random-effects)a).

### 2019-08-30 code/suitability_vs_degree.R
Stop saving all pars in models. Won't use bayes factor beause whatever

@@ -212,7 +212,7 @@ fit_model <- function(formulas, analysis_frame, cores = 1L, iter = 4000){
                iter = iter,
                # warmup = 2000, 
                cores = cores,
-               save_all_pars = TRUE,
+               save_all_pars = FALSE,
                # future = TRUE,
                control = list(adapt_delta = 0.99, 
                               max_treedepth =12))

### 2019-08-30 paper/manuscript.Rmd
Model comparison table now based only on WAIC

@@
 As there was no interaction between guild and generality or the number of possible interactions, for these two predictors we only show conditional the conditional effect of pollinators.")
+
 readd(fig_conditional_effects)
@@
 ```{r tab-model-comparison-table}
-loadd(model_ranking)
-
-waic_scores <- as.data.frame(model_ranking$waic) %>%
-  tibble::rownames_to_column(var = "formula") %>%
-  dplyr::select(formula, waic)
-
-loo_scores <- as.data.frame(model_ranking$loo) %>%
-  tibble::rownames_to_column(var = "formula") %>%
-  dplyr::select(formula, elpd_diff, se_diff,  looic)
-
-loo_scores %>%
-  dplyr::inner_join(waic_scores, by = "formula") %>%
+model_ranking$waic %>%
+  purrr::map(~.$estimates["waic", ]) %>%
+  purrr::map_df(~tibble::tibble(estimate = .[1], se = .[2]), .id = "formula") %>%
   dplyr::mutate(formula = translate_model_formula(formula, "long-abv"), 
@@
                booktabs = TRUE, 
-               digits = c(0,0,1,0,0), 
+               digits = c(0,0,0), 
                format.args = list(big.mark = ","), 
-               col.names = c("predictors", "$\\Delta$", "$SE_{\\Delta}$", "IC", "WAIC"),
+               col.names = c("predictors", "WAIC", "SE"),
                escape = FALSE,
@@
 We also show the Wanatabe-Akaike information criterion (WAIC) of each model for comparison.") %>%
-  kableExtra::kable_styling(font_size = 8) %>%
-  kableExtra::add_header_above(c(" " = 1, "LOO" = 3, " " = 1))
+  kableExtra::kable_styling(font_size = 8) #%>%
+  # kableExtra::add_header_above(c(" " = 1, "LOO" = 3, " " = 1))
+# 
+# waic_scores <- as.data.frame(model_ranking$waic) %>%
+#   tibble::rownames_to_column(var = "formula") %>%
+#   dplyr::select(formula, waic)
+# 
+# loo_scores <- as.data.frame(model_ranking$loo) %>%
+#   tibble::rownames_to_column(var = "formula") %>%
+#   dplyr::select(formula, elpd_diff, se_diff,  looic) 
+# 
+# loo_scores %>%
+#   dplyr::inner_join(waic_scores, by = "formula") %>%
+#   dplyr::mutate(formula = translate_model_formula(formula, "long-abv"), 
+#                 formula = kableExtra::cell_spec(formula, format = "latex", 
+#                                                 bold =nchar(formula) == max(nchar(formula)))) %>%
+#   knitr::kable("latex", 
+#                booktabs = TRUE, 
+#                digits = c(0,0,1,0,0), 
+#                format.args = list(big.mark = ","), 
+#                col.names = c("predictors", "$\\Delta$", "$SE_{\\Delta}$", "IC", "WAIC"),
+#                escape = FALSE,
+#                linesep = "",
+#                caption = "Comparison in out of sample predictive power of the baseline model (bold) and their alternatives.
+We rank models by their expected log predictive density based on their leave-one-out cross-validation information criterion (LOO).
+The standard error of the LOO difference provides rough guidance to the uncertainty of the model ranking.
+We also show the Wanatabe-Akaike information criterion (WAIC) of each model for comparison.") %>%
+#   kableExtra::kable_styling(font_size = 8) %>%
+#   kableExtra::add_header_above(c(" " = 1, "LOO" = 3, " " = 1))
 ```

### 2019-08-30 paper/manuscript.Rmd
Add caption for random effects figure

@@
 
-```{r fig-random-effects, fig.width = width('single'), fig.height = 2.2*2.5, fig.cap = "Random effects"}
+```{r fig-random-effects, fig.width = width('single'), fig.height = 2.2*2.5, fig.cap = fig_random_effects_legend}
+loadd(random_species_draws)
+
+n_random_species <- random_species_draws %>%
+  dplyr::group_by(guild) %>%
+  dplyr::summarise(n_sp = dplyr::n_distinct(org_id))
+
+n_random_pla <- n_random_species %>%
+  dplyr::filter(guild == "pla_id")
+
+n_random_ani <- n_random_species %>%
+  dplyr::filter(guild == "ani_id")
+
+fig_random_effects_legend <- 
+  paste0("Species level effects of suitability.
+(a) Conditional effect of suitability for individual species.
+To facilitate visualization we show only species for which there is suitability information in at least six communities (",
+         n_random_pla, " plants and ", 
+         n_random_ani, " pollinators).
+As in the previous figure, fitted values assume a hypothetical community of median size.
+In each panel we highlight two species for which the relationship between environental suitability and normalised degree was particularly strong.
+",
+         "(b) The correlation between the species' intercept and the species' slope of suitability was negatively correlated.")
+
 readd(fig_random_effects)

### 2019-08-30 paper/manuscript.Rmd
Correct minor error reporting standard deviations

@@
 The group level variation among communities was larger than that among species.
-The standard deviation (in the parameters scale) of the community intercepts was `r round(sd_loc_id$Estimate, 2)` [`r round(random_cor$Q2.5, 2)`, `r round(sd_loc_id$Q97.5, 2)`] while the standard deviation of the species intercept was `r round(sd_org_id$Estimate, 2)` [`r round(sd_org_id$Q2.5, 2)`, `r round(sd_org_id$Q97.5, 2)`], and that of the species' suitability slope was `r round(sd_org_id_suitability$Estimate, 2)` [`r round(sd_org_id_suitability$Q2.5, 2)`, `r round(sd_org_id_suitability$Q97.5, 2)`] (95% credible intervals shown within square brakets).
+The standard deviation (in the parameters scale) of the community intercepts was `r round(sd_loc_id$Estimate, 2)` [`r round(sd_loc_id$Q2.5, 2)`, `r round(sd_loc_id$Q97.5, 2)`] while the standard deviation of the species intercept was `r round(sd_org_id$Estimate, 2)` [`r round(sd_org_id$Q2.5, 2)`, `r round(sd_org_id$Q97.5, 2)`], and that of the species' suitability slope was `r round(sd_org_id_suitability$Estimate, 2)` [`r round(sd_org_id_suitability$Q2.5, 2)`, `r round(sd_org_id_suitability$Q97.5, 2)`] (95% credible intervals shown within square brakets).
 Interestingly, the slope the relationship between suitability and normalised degree was negatively correlated with the species' intercept in the model (Figure \@ref(fig:fig-random-effects)b). 

### 2019-08-30 paper/manuscript.Rmd
Start writing intro

@@
 # Introduction
+
+From a mutualistic perspective, ecological interactions are thought to be selected based on the relative benefit they provide. 
+On one end of the spectrum, generalist are have traits that allow them to intract a large number of species.
+In average, the benefits they obtain from each of the species they interact with is relatively low compared to specialists.
+This is so because, on the other end of the spectrum, specialist species tend to have a have deeper co-evolutionary history with their partner species. 
+This in turn is reflected on a better trait-matching with the species it interacts with which leads to a higher benefit.
+
+The 
+At the same time, we know that ecological interactions are affected by the environment [@tylianakis_ecological_2017]. 
+Generally speaking,
+
+It is generally agreed that two species wether two species interact there is a neutral process
+
+ small number of partner species are thought to benefit largely from each  deeper co-evolutionary history that, through trait matching
+Species with a small number of partners, specialists, are often deemed to 
+Species with a large number of interactions, generalists, benefits relatively
+
+It is generally accepted that the species niche is the location in a multidimentional space defined by environmental conditions that allows a species to have a positive growth rate when rare (Godsoe).
+There are two dimensions of a species niche, the Grinellian niche which focuses on the
 
@@
 
-<!-- Variation in community composition can be independent of variation of ecological interactions, suggesting that species and inter- action distribution may well respond to diferent drivers (Poisot et al.
+<!-- Variation in community composition can be independent of variation of ecological interactions, suggesting that species and inter- ac tion distribution may well respond to diferent drivers (Poisot et al.
 2012).
@@
 
+Note that although abundances can inflence wether two species interact we cannot tease t appart because suitability is not necessarily related to abundance.
+ALthough abundance affects the frequency of the interaction, rather than wether they interacts or not (Donoso)
+
 # Acknowledgements

### 2019-08-30 paper/manuscript.Rmd
Nicer first paragraph

@@
 From a mutualistic perspective, ecological interactions are thought to be selected based on the relative benefit they provide. 
-On one end of the spectrum, generalist are have traits that allow them to intract a large number of species.
+On one end of the spectrum, generalist species have traits that allow them to interact with a large number of species.
 In average, the benefits they obtain from each of the species they interact with is relatively low compared to specialists.
-This is so because, on the other end of the spectrum, specialist species tend to have a have deeper co-evolutionary history with their partner species. 
-This in turn is reflected on a better trait-matching with the species it interacts with which leads to a higher benefit.
+On the other end of the spectrum, specialist species are thought to have a more deep-rooted co-evolutionary history with their partner species. 
+This tighter co-evolution, in turn, can be reflected on a better trait-matching with the species it interacts with which leads to a higher benefit.
+This niche-based rationale can also operate within a species. 
+We can expect that a species can obtain a higher benefit from interactions with species with traits that better match their requirements.
 

### 2019-08-30 paper/manuscript.Rmd
Second paragraph

@@
 
-The 
-At the same time, we know that ecological interactions are affected by the environment [@tylianakis_ecological_2017]. 
-Generally speaking,
+Although several other factors, chiefly neutral processes determined by abundance, can also influence the probability of whether two species interact or not, one that is commonly overlooked by community ecologists is the role of the abiotic environment [but see @gravel_bringing_2018].
+The most studied mechanism is through patterns of community composition. 
+The abiotic environment can strongly influence whether a species can have a positive growth-rate when rare in a particular location.
+For two species to interact, they first need to co-occur in the same community, which can only happen if the environmental conditions of the community fall within the Fundamental "Grinellian" niche of both species.
+However, community composition is only one part of the story as the abiotic environment is known to be able to influence the interactions directly [@tylianakis_ecological_2017].
 

### 2019-09-01 paper/manuscript.Rmd
Specify we're talking about the eltonian niche in first paragraph
Change first paragraph, make it even more broad

@@
 
+Species interactions are known to vary widely across space and time. 
+There are multiple examples of species that interact tightly in an ecological community or a particular season but not in another. 
+It is crucial to understand why and how this turnover of interactions occur because the network of interactions of an ecological community is known to underpin ecosystem function and stability. 
+Despite much progress in the last decades, we are still unable to predict species interactions, partially because we still have not accurately identified the factors that drive species to interact under certain conditions and not under another.
 From a mutualistic perspective, ecological interactions are thought to be selected based on the relative benefit they provide. 
@@
 This tighter co-evolution, in turn, can be reflected on a better trait-matching with the species it interacts with which leads to a higher benefit.
-This niche-based rationale can also operate within a species. 
+This "Eltionian" niche-based rationale can also operate within a species. 
 We can expect that a species can obtain a higher benefit from interactions with species with traits that better match their requirements.

### 2019-09-01 paper/manuscript.Rmd
Improve second and third paragraph

@@
 Despite much progress in the last decades, we are still unable to predict species interactions, partially because we still have not accurately identified the factors that drive species to interact under certain conditions and not under another.
-From a mutualistic perspective, ecological interactions are thought to be selected based on the relative benefit they provide. 
-On one end of the spectrum, generalist species have traits that allow them to interact with a large number of species.
-In average, the benefits they obtain from each of the species they interact with is relatively low compared to specialists.
-On the other end of the spectrum, specialist species are thought to have a more deep-rooted co-evolutionary history with their partner species. 
-This tighter co-evolution, in turn, can be reflected on a better trait-matching with the species it interacts with which leads to a higher benefit.
-This "Eltionian" niche-based rationale can also operate within a species. 
-We can expect that a species can obtain a higher benefit from interactions with species with traits that better match their requirements.
 
-Although several other factors, chiefly neutral processes determined by abundance, can also influence the probability of whether two species interact or not, one that is commonly overlooked by community ecologists is the role of the abiotic environment [but see @gravel_bringing_2018].
-The most studied mechanism is through patterns of community composition. 
-The abiotic environment can strongly influence whether a species can have a positive growth-rate when rare in a particular location.
+It is widely awknowledged that there are two main processes involved in whether two species in a community interact or not.
+The first is an "Eltonian" niche process that is underpinned by the traits of the interacting species.
+Under this rationale, when the traits of interacting species are optimally matched, due for example to a deep-rooted co-evolutionary history, species are able to obtain a high benefit from the interaction.
+Contrastingly, we can expect the per-capita benefit of interaction with a relatively low trait matching to be lower.
+The second is a neutral process underpinned by the abundance of the intereacting species. 
+All else being equal, when the abundance of a species is high their potential encounter rate is also high and therefore there is a higher probability to interact than if it were rare.
+
+Perhaps, because it operates at scales larger than those commonly considered by community ecologists, the abiotic environment is one of the factors that is commonly overlooked when explaining interaction turnover [but see @gravel_bringing_2018].
+The most evident, and best studied, way through which the environment can afect the structure of ecological networks is by way of patterns of community composition. 
+This is because the abiotic environment can strongly influence whether a species can have a positive growth-rate when rare in a particular location.
 For two species to interact, they first need to co-occur in the same community, which can only happen if the environmental conditions of the community fall within the Fundamental "Grinellian" niche of both species.
-However, community composition is only one part of the story as the abiotic environment is known to be able to influence the interactions directly [@tylianakis_ecological_2017].
+However, community composition is only one part of the story as the abiotic environment can also influence the interactions directly [@tylianakis_ecological_2017].
 

### 2019-09-01 paper/manuscript.Rmd
Improve clarity of paragraph 2 and 3 of intro

@@
 
-It is widely awknowledged that there are two main processes involved in whether two species in a community interact or not.
+There are two main processes involved in whether two species in a community interact or not.
 The first is an "Eltonian" niche process that is underpinned by the traits of the interacting species.
-Under this rationale, when the traits of interacting species are optimally matched, due for example to a deep-rooted co-evolutionary history, species are able to obtain a high benefit from the interaction.
-Contrastingly, we can expect the per-capita benefit of interaction with a relatively low trait matching to be lower.
-The second is a neutral process underpinned by the abundance of the intereacting species. 
-All else being equal, when the abundance of a species is high their potential encounter rate is also high and therefore there is a higher probability to interact than if it were rare.
+Under this rationale, when, for example,  a deep-rooted co-evolutionary history leads to optimally matched traits, the interacting species can obtain a substantial benefit from this interaction. 
+Contrastingly, we would expect a lower per-capita benefit from interactions with low trait matching.
+The second is a neutral process underpinned by the abundance of the interacting species. 
+All else being equal, when the abundance of a species is high, their potential encounter rate is also high, and therefore there is a higher probability to interact than if it were rare.
 
-Perhaps, because it operates at scales larger than those commonly considered by community ecologists, the abiotic environment is one of the factors that is commonly overlooked when explaining interaction turnover [but see @gravel_bringing_2018].
-The most evident, and best studied, way through which the environment can afect the structure of ecological networks is by way of patterns of community composition. 
-This is because the abiotic environment can strongly influence whether a species can have a positive growth-rate when rare in a particular location.
-For two species to interact, they first need to co-occur in the same community, which can only happen if the environmental conditions of the community fall within the Fundamental "Grinellian" niche of both species.
+Perhaps, because it operates at scales larger than those of the Eltonian niche concept, the abiotic environment is one of the factors that is commonly overlooked by community ecologists when explaining interaction turnover [but see @gravel_bringing_2018].
+The most evident—and best-studied—way through which the environment can affect the structure of ecological networks is by way of patterns of community composition. 
+At the heart of biogeography is the idea that the abiotic environment can determine whether a species can have a positive growth-rate when rare in a particular location.
+For two species to interact, they first need to co-occur in the same community, which can only happen if the environmental conditions of the community fall within the "Grinellian" niche of both species.
 However, community composition is only one part of the story as the abiotic environment can also influence the interactions directly [@tylianakis_ecological_2017].

### 2019-09-01 paper/manuscript.Rmd
A first attempt for the intro P4

@@
 Contrastingly, we would expect a lower per-capita benefit from interactions with low trait matching.
-The second is a neutral process underpinned by the abundance of the interacting species. 
-All else being equal, when the abundance of a species is high, their potential encounter rate is also high, and therefore there is a higher probability to interact than if it were rare.
+The second is a neutral process underpinned by the encounter rate of the interacting species. 
+All else being equal, when the encounter rate of interacting species is high there is a higher probability to interact than if the rate were smaller, for example due to species rarity.
 
@@
 
+When looked from an Eltonian-niche lens, one way the environment can influence wether two species interact or not is based on, what we call, stress-induced hypotheses of interaction turnover. 
+These hypotheses are rooted in the co-evolutionary processes that determine the quality of an interaction partner. 
+Environmental induced stress can
+
+Another way
+
+In a pollination context, it can for plant–pollinator interactions (Berg et al., 2010; Elzinga et al., 2007)
+.
+
+Second, and oare more subtle, mechanism through which enviroment can determine interactions is
+This is so because , species distributions are strongly determined 
+At the basis of species distrFormally, the fundamental "Grinellian" niche of a species is determined by the set of environments where a species has a positive groth rate when rare. 
+The environement, 
+From a "Grinellian" niche perspect
+Framed from a niche perspective,
+
 It is generally agreed that two species wether two species interact there is a neutral process
 
- small number of partner species are thought to benefit largely from each  deeper co-evolutionary history that, through trait matching
-Species with a small number of partners, specialists, are often deemed to 
-Species with a large number of interactions, generalists, benefits relatively
+HYPOTHESIS: many trophic and mutualistic interactions are relatively generalized and potentially opportunistic (Pimm et al.
+1991).
+Thus, we may expect that ecological networks will comprise a mixture of interactions that persist over the long-term owing to trait matching of partners through coevolution (Go ́ mez et al.
+2010, Guimaraes et al.
+2011) and those that occur opportunistically, perhaps with inferior long-term fitness benefits (Aizen et al.
+2016).
 

### 2019-09-01 paper/manuscript.Rmd
Some comments for the discussion

@@
 
-We found a positive association between environmental suitability and the niche breath. 
+<!-- We found a positive association between environmental suitability and the niche breath. 
 This relationship was maintained when we account for the overall generality of a species and even in extremely conservative model parametrization when we include the number of possible interacting species as an independent variable.
-We define "possible" interacting species as one with which the species interacts in any of our ecological communities.
+We define "possible" interacting species as one with which the species interacts in any of our ecological communities.  -->
 
-No interaction significant between guild and relationship which highlights that differences are rooted in eco-evolutionary processes rather than behaviour.
+<!-- No interaction significant between guild and relationship which highlights that differences are rooted in eco-evolutionary processes rather than behaviour.  -->
 
-Relationship is even stronger when we only include species for which we have more info. i.e. in more that 5 communities.
+<!-- Relationship is even stronger when we only include species for which we have more info. i.e. in more that 5 communities.  -->
 
+<!-- Environment can also affect neitral process because it affects encounter rates between species.
+This can happen either through changes in abundance driven by patterns of temporal or spatial overlap or through changes in the search efficiency.  -->
 <!-- We focus suitability in abiotic factors but can also be influenced by dispersal and species interactions themselves (e.g. competition and facilitation, Lortie et al. 2004).  -->

### 2019-09-01 paper/manuscript.Rmd
Add discourse of mutualistic interactions being generalised intro p2

@@
 The first is an "Eltonian" niche process that is underpinned by the traits of the interacting species. 
-Under this rationale, when, for example, a deep-rooted co-evolutionary history leads to optimally matched traits, the interacting species can obtain a substantial benefit from this interaction. 
-Contrastingly, we would expect a lower per-capita benefit from interactions with low trait matching.
+Compared to other kinds of trophic interactions, mutualistic interactions, and plant-pollination interactions in particular, are relatively generalised.
+While a large proportion of the interactions appear to be opportunistic, a fraction of interactions show a strong signature of deep co-evolutionary history [@hutchinson_cophylogenetic_2017]. 
+In contrast to opportunistic interactions with low trait-matching, the more co-evolved interactions with optimally matched traits are more persistent and presumably lead to a more substantial per-capita benefit for the interacting species.
 The second is a neutral process underpinned by the encounter rate of the interacting species. 
-All else being equal, when the encounter rate of interacting species is high there is a higher probability to interact than if the rate were smaller, for example due to species rarity.
+All else being equal, when the encounter rate of interacting species is high, there is a higher probability to interact than if the rate were lower, for example, due to species rarity.
 

### 2019-09-01 paper/manuscript.Rmd
Keep on drafting the first hypothesis

@@
 For two species to interact, they first need to co-occur in the same community, which can only happen if the environmental conditions of the community fall within the "Grinellian" niche of both species.
-However, community composition is only one part of the story as the abiotic environment can also influence the interactions directly [@tylianakis_ecological_2017].
 
-When looked from an Eltonian-niche lens, one way the environment can influence wether two species interact or not is based on, what we call, stress-induced hypotheses of interaction turnover. 
+After community composition has been determined, one way the environment can influence wether two species interact or not is by affecting their Eltonian-niche [@tylianakis_ecological_2017]. 
+This effect can happen through what we call stress/suitability-induced hypotheses of interaction turnover. 
+The first hypothesis is that when species are under environmental stress, they might be "pressured" to focus on the partners with which they are best adapted to interact. 
+For instance @peralta_phylogenetic_2015 found that parasitoids in plantation forest, where enviornmental stress were higher than in native forests, were constrained to attack only hosts they were best adapted to.
+Similarly, @lavandero_genotype_2013 found that environmental stress due to higer temperature reduced the breadth of the Eltonian niche of parasitoids. 
+The alternative hypotheis is that when species are under environmental stress they are forced
+
+One possible outcome of environmental stress, as reviewed by @tylianakis_ecological_2017, is that species are "pressured" to interact with species with which its best adapted
+
+.
 These hypotheses are rooted in the co-evolutionary processes that determine the quality of an interaction partner.
-Environmental induced stress can
 
-Another way
+Another possble outcome is that
+
+For example, environmental stressors could cause species to narrow their trophic breadth by increasing the search time to find alternative partners (Gauld 1987) or by imposing limits on the quality of interaction partners that can be used (i.e., using only resources to which a species is best adapted).
+Phylogenetic congruence becomes stronger in parasitoid–host networks with increasing temperature (Lavandero & Tylianakis 2013) and in plantation versus native forests (Peralta et al.
+2015), and such patterns appear consistent with a hy- pothesis of stress-induced reduction in trophic (phylogenetic) breadth (in the case of Lavandero & Tylianakis 2013, this occurred on genotype relatedness rather than between-species phylogenies).
 
@@
 . 
-
-Second, and oare more subtle, mechanism through which enviroment can determine interactions is
-This is so because , species distributions are strongly determined 
-At the basis of species distrFormally, the fundamental "Grinellian" niche of a species is determined by the set of environments where a species has a positive groth rate when rare. 
-The environement, 
-From a "Grinellian" niche perspect
-Framed from a niche perspective,
-
-It is generally agreed that two species wether two species interact there is a neutral process
-
-HYPOTHESIS: many trophic and mutualistic interactions are relatively generalized and potentially opportunistic (Pimm et al.
-1991).
-Thus, we may expect that ecological networks will comprise a mixture of interactions that persist over the long-term owing to trait matching of partners through coevolution (Go ́ mez et al.
-2010, Guimaraes et al.
-2011) and those that occur opportunistically, perhaps with inferior long-term fitness benefits (Aizen et al.
-2016).
+<!-- One option is that when species are in detrimental environmental conditions focus on most optimal partners and as such interact with a smaller number of species.  -->
+<!-- An alternative hypotheisis is that when species are in favourable environmental conditions they can afford to be more picky about their interactions and as such avoid those of less value, while individuals in unfavourable conditions must get rewards from whatever they can get.
+-->
 

### 2019-09-01 paper/manuscript.Rmd
"Finish off" intro P4

@@
 
-After community composition has been determined, one way the environment can influence wether two species interact or not is by affecting their Eltonian-niche [@tylianakis_ecological_2017]. 
+After community composition has been established, one way the environment can influence whether two species interact or not is by affecting their Eltonian-niche [@tylianakis_ecological_2017]. 
 This effect can happen through what we call stress/suitability-induced hypotheses of interaction turnover. 
 The first hypothesis is that when species are under environmental stress, they might be "pressured" to focus on the partners with which they are best adapted to interact. 
-For instance @peralta_phylogenetic_2015 found that parasitoids in plantation forest, where enviornmental stress were higher than in native forests, were constrained to attack only hosts they were best adapted to.
-Similarly, @lavandero_genotype_2013 found that environmental stress due to higer temperature reduced the breadth of the Eltonian niche of parasitoids. 
-The alternative hypotheis is that when species are under environmental stress they are forced
+For instance, @hoiss_altitude_2012 found increased phylogenetic clustering between plants and pollinators at higher altitudes; while @peralta_phylogenetic_2015 found that parasitoids in plantation forest, where environmental stress was higher than in native forests, were constrained to interact with hosts, they were best adapted to attack.
+Similarly, @lavandero_genotype_2013 found that environmental stress due to higher temperature reduced the breadth of the Eltonian niche of parasitoids. 
+An alternative hypothesis is that when species are under environmental stress, they are forced to be more flexible in their interactions as higher environmental stress is likely to be reflected in greater energetic or reproductive costs and therefore they might not be able to sustain encounter rates with their preferred partners at sufficient levels.
+For instance, @hoiss_interactive_2015 found that the specialization of plant-pollinator networks decreased both with elevation and after extreme drought events.
+Likewise, @pellissier_spatial_2010 found a positive relationship between niche breadth and environmental stress: disk- or bowl-shaped blossoms (which allow a large number of potential pollinator species to access pollen and nectar rewards) dominated at high altitude flower communities.
+
+Here, we expli
+Benadi found that
+
+Generalists vs specialists might show contrasting patterns.
+
+Here we
+
+Specialist species (that lack flexibility in their choice of interaction partner) should theoretically be most vulnerable to phenological decoupling.
+However, one study of pollinator communities along an elevational gradient found that apparently specialized pollinators were facultatively more generalist than they appeared and could adapt their visitation patterns across sites as much as generalists to avoid phenological asynchrony (Benadi et al.
+2014).
+Similarly, duration of the fruiting season has been shown to predict the degree and strength of seed-dispersal interactions (Gonza ́ lez- Castro et al.
+2012), and a long-term study found no difference between specialist and generalist plant species in their interannual fluctuations in phenology and pollinator richness (Petanidou et al.
+2014).
+Although these findings suggest that the facultative generalism of pollination mutualisms may confer robustness to these networks in the face of altered phenology (see also discussion on rewiring above), this robustness may depend on the climate context and the diversity and specialization within the network (Hoiss et al.
+2015).
+Moreover, less-generalized interactions such as those between parasites and hosts may show less flexibility.
 

### 2019-09-01 paper/manuscript.Rmd
Add a couple notes in the discussion

@@
 
-Note that although abundances can inflence wether two species interact we cannot tease t appart because suitability is not necessarily related to abundance.
-ALthough abundance affects the frequency of the interaction, rather than wether they interacts or not (Donoso)
+<!-- Note that although abundances can inflence wether two species interact we cannot tease t appart because suitability is not necessarily related to abundance.
+ALthough abundance affects the frequency of the interaction, rather than wether they interacts or not (Donoso) -->
+
+<!--Mention implications for community assembly? -->
 

### 2019-09-02 paper/manuscript.Rmd
Add more chachara to P3

@@
 For two species to interact, they first need to co-occur in the same community, which can only happen if the environmental conditions of the community fall within the "Grinellian" niche of both species.
+Although less understood, the environment can also affect the interactions, once community composition has been established [@tylianakis_ecological_2017]. 
+For instance some studies show that thropic interactions, like predation [@mckinnon_lower_2010; @vucic-pestic_warming_2011] and herbivory [@baskett_latitudinal_2018], can increase with temperature but might decreasse with precipitation [@pires_predicted_2016], and both plant-plant [@bertness_positive_1994] and plant-pollinator [@tur_evaluating_2016] interactions can switch from facilitative to competitive along a elevation/temperature gradient.
+Contrastingly, other studies have shown either no effect or non-linear effects of temperature or precipitation on plant pollinator interactions [@devoto_patterns_2005; @gravel_bringing_2018].
 

### 2019-09-02 paper/manuscript.Rmd
Fix some spelling in P3

--- 2019-09-01 paper/manuscript.Rmd
@@
 For two species to interact, they first need to co-occur in the same community, which can only happen if the environmental conditions of the community fall within the "Grinellian" niche of both species.
+Although less understood, the environment can also affect the interactions, once community composition has been established [@tylianakis_ecological_2017]. 
+For instance, some studies show that trophic interactions, like predation [@mckinnon_lower_2010; @vucic-pestic_warming_2011] and herbivory [@baskett_latitudinal_2018], can increase with temperature but might decrease with precipitation [@pires_predicted_2016], and both plant-plant [@bertness_positive_1994] and plant-pollinator [@tur_evaluating_2016] interactions can switch from facilitative to competitive along an elevation/temperature gradient.
+Contrastingly, other studies have shown either no effect or non-linear effects of temperature or precipitation on plant-pollinator interactions [@devoto_patterns_2005; @gravel_bringing_2018].
 

### 2019-09-02 paper/manuscript.Rmd
Readapt Intro P4

@@
 
-After community composition has been established, one way the environment can influence whether two species interact or not is by affecting their Eltonian-niche [@tylianakis_ecological_2017]. 
-This effect can happen through what we call stress/suitability-induced hypotheses of interaction turnover. 
-The first hypothesis is that when species are under environmental stress, they might be "pressured" to focus on the partners with which they are best adapted to interact. 
+One way to summarise the seemingly contradictory evidence of whether the environment can influence whether two species interact or not is by moving from gradients of temperature or precipitation to gradients of environmental stress/suitability.
+Previous research is so far equivocal and indicates that environmental stress can have two contrasting effects on species' Eltonian-niche [@tylianakis_ecological_2017].
+On the one hand, it is possible that when species are under environmental stress, they might be "pressured" to focus on partners with which they are best adapted to interact. 
 For instance, @hoiss_altitude_2012 found increased phylogenetic clustering between plants and pollinators at higher altitudes; while @peralta_phylogenetic_2015 found that parasitoids in plantation forest, where environmental stress was higher than in native forests, were constrained to interact with hosts, they were best adapted to attack.
 Similarly, @lavandero_genotype_2013 found that environmental stress due to higher temperature reduced the breadth of the Eltonian niche of parasitoids. 
-An alternative hypothesis is that when species are under environmental stress, they are forced to be more flexible in their interactions as higher environmental stress is likely to be reflected in greater energetic or reproductive costs and therefore they might not be able to sustain encounter rates with their preferred partners at sufficient levels.
+On the other, it is also possible that when species are under environmental stress, they are forced to be more flexible in their interactions as higher environmental stress is likely to be reflected in greater energetic or reproductive costs and therefore they might not be able to sustain encounter rates with their preferred partners at sufficient levels.
 For instance, @hoiss_interactive_2015 found that the specialization of plant-pollinator networks decreased both with elevation and after extreme drought events.

### 2019-09-02 paper/manuscript.Rmd
Continue attempt at intro P5

@@
 
-Here, we expli
+Here we use information on plant-pollinator interactions and their environmental suitability at a global scale to test the stress/suitability hypotheses of
+
+Here, we explicitly test 
 Benadi found that
@@
 
-Here we
-
 Specialist species (that lack flexibility in their choice of interaction partner) should theoretically be most vulnerable to phenological decoupling.
@@
 2014).
-Similarly, duration of the fruiting season has been shown to predict the degree and strength of seed-dispersal interactions (Gonza ́ lez- Castro et al.
+Similarly, duration of the fruiting season has been shown to predict the degree and strength of seed-dispersal interactions (Gonza lez- Castro et al.
 2012), and a long-term study found no difference between specialist and generalist plant species in their interannual fluctuations in phenology and pollinator richness (Petanidou et al.

### 2019-09-02 paper/manuscript.Rmd
FInish off last paragraph from intro!

--- 2019-09-02 paper/manuscript.Rmd
@@
 The first is an "Eltonian" niche process that is underpinned by the traits of the interacting species. 
-Compared to other kinds of trophic interactions, mutualistic interactions, and plant-pollination interactions in particular, are relatively generalised.
-While a large proportion of the interactions appear to be opportunistic, a fraction of interactions show a strong signature of deep co-evolutionary history [@hutchinson_cophylogenetic_2017]. 
+Compared to other kinds of trophic interactions, mutualistic interactions, and plant-pollination interactions, in particular, are relatively generalised.
+While a large proportion of the interactions appear to be opportunistic, a fraction of interactions shows a strong signature of deep co-evolutionary history [@hutchinson_cophylogenetic_2017]. 
 In contrast to opportunistic interactions with low trait-matching, the more co-evolved interactions with optimally matched traits are more persistent and presumably lead to a more substantial per-capita benefit for the interacting species.
@@
 On the other, it is also possible that when species are under environmental stress, they are forced to be more flexible in their interactions as higher environmental stress is likely to be reflected in greater energetic or reproductive costs and therefore they might not be able to sustain encounter rates with their preferred partners at sufficient levels.
-For instance, @hoiss_interactive_2015 found that the specialization of plant-pollinator networks decreased both with elevation and after extreme drought events.
+For instance, @hoiss_interactive_2015 found that the specialisation of plant-pollinator networks decreased both with elevation and after extreme drought events.
 Likewise, @pellissier_spatial_2010 found a positive relationship between niche breadth and environmental stress: disk- or bowl-shaped blossoms (which allow a large number of potential pollinator species to access pollen and nectar rewards) dominated at high altitude flower communities.
 
-Here, we expli
-Benadi found that
-
-Generalists vs specialists might show contrasting patterns.
-
-Here we
-
-Specialist species (that lack flexibility in their choice of interaction partner) should theoretically be most vulnerable to phenological decoupling.
-However, one study of pollinator communities along an elevational gradient found that apparently specialized pollinators were facultatively more generalist than they appeared and could adapt their visitation patterns across sites as much as generalists to avoid phenological asynchrony (Benadi et al.
-2014).
-Similarly, duration of the fruiting season has been shown to predict the degree and strength of seed-dispersal interactions (Gonza ́ lez- Castro et al.
-2012), and a long-term study found no difference between specialist and generalist plant species in their interannual fluctuations in phenology and pollinator richness (Petanidou et al.
-2014).
-Although these findings suggest that the facultative generalism of pollination mutualisms may confer robustness to these networks in the face of altered phenology (see also discussion on rewiring above), this robustness may depend on the climate context and the diversity and specialization within the network (Hoiss et al.
-2015).
-Moreover, less-generalized interactions such as those between parasites and hosts may show less flexibility.
-
-One possible outcome of environmental stress, as reviewed by @tylianakis_ecological_2017, is that species are "pressured" to interact with species with which its best adapted
-
-.
-These hypotheses are rooted in the co-evolutionary processes that determine the quality of an interaction partner.
-
-Another possble outcome is that
-
-For example, environmental stressors could cause species to narrow their trophic breadth by increasing the search time to find alternative partners (Gauld 1987) or by imposing limits on the quality of interaction partners that can be used (i.e., using only resources to which a species is best adapted).
-Phylogenetic congruence becomes stronger in parasitoid–host networks with increasing temperature (Lavandero & Tylianakis 2013) and in plantation versus native forests (Peralta et al.
-2015), and such patterns appear consistent with a hy- pothesis of stress-induced reduction in trophic (phylogenetic) breadth (in the case of Lavandero & Tylianakis 2013, this occurred on genotype relatedness rather than between-species phylogenies).
-
-In a pollination context, it can for plant–pollinator interactions (Berg et al., 2010; Elzinga et al., 2007)
-. 
-<!-- One option is that when species are in detrimental environmental conditions focus on most optimal partners and as such interact with a smaller number of species.  -->
-<!-- An alternative hypotheisis is that when species are in favourable environmental conditions they can afford to be more picky about their interactions and as such avoid those of less value, while individuals in unfavourable conditions must get rewards from whatever they can get.
--->
-
-It is generally accepted that the species niche is the location in a multidimentional space defined by environmental conditions that allows a species to have a positive growth rate when rare (Godsoe).
-There are two dimensions of a species niche, the Grinellian niche which focuses on the
+We collect available data on plant-pollinator interactions globally and calculate the environmental suitability of all species present at two or more communities to. 
+Our main aim is to leverage that information to test the two competing hypothesis that relate environmental stress and Eltionian niche breadth and whether there is a pattern within and across species.
+Specialist species have been found to be able to become "facultative" generalists to reduce their vulnerability to the absence of preferred partners [for example when phenologies are decoupled; @benadi_specialization_2014].
+We therefore also expect that as environmental stress increasses species with a relatively small number of partners are more likely to broaden their Eltonian niche. 
+Species with a large number of partners on the other hand should have a larger pool of available partners and might therefore be more likely to narrow their niche under environmental stress. 
+Importantly, when testing these hypotheses, we control for the potential effects of the environment in community composition and the size of the species fundamental niche, both from an Eltonian (interactions) and Grinellian (environment) perspective.
 

### 2019-09-02 paper/manuscript.Rmd
Re-check spelling intro

@@
 Contrastingly, other studies have shown either no effect or non-linear effects of temperature or precipitation on plant-pollinator interactions [@devoto_patterns_2005; @gravel_bringing_2018].
-
 One way to summarise the seemingly contradictory evidence of whether the environment can influence whether two species interact or not is by moving from gradients of temperature or precipitation to gradients of environmental stress/suitability.
@@
 We collect available data on plant-pollinator interactions globally and calculate the environmental suitability of all species present at two or more communities to. 
-Our main aim is to leverage that information to test the two competing hypothesis that relate environmental stress and Eltionian niche breadth and whether there is a pattern within and across species.
-Specialist species have been found to be able to become "facultative" generalists to reduce their vulnerability to the absence of preferred partners [for example when phenologies are decoupled; @benadi_specialization_2014].
-We therefore also expect that as environmental stress increasses species with a relatively small number of partners are more likely to broaden their Eltonian niche. 
-Species with a large number of partners on the other hand should have a larger pool of available partners and might therefore be more likely to narrow their niche under environmental stress. 
+Our main aim is to leverage that information to test the two competing hypotheses that relate environmental stress and Eltionian niche breadth and whether there is a pattern within and across species.
+Specialist species can become "facultative" generalists to reduce their vulnerability to the absence of preferred partners [for example, when variations in climate decouple phenologies; @benadi_specialization_2014].
+We therefore also expect that as environmental stress increases species with a relatively small number of partners are more likely to broaden their Eltonian niche. 
+Species with a large number of partners, on the other hand, should have a larger pool of available partners and might, therefore, be more likely to narrow their niche under environmental stress. 
 Importantly, when testing these hypotheses, we control for the potential effects of the environment in community composition and the size of the species fundamental niche, both from an Eltonian (interactions) and Grinellian (environment) perspective.

### 2019-09-06 paper/manuscript.Rmd
Minor edits to intro

@@
 The most evident—and best-studied—way through which the environment can affect the structure of ecological networks is by way of patterns of community composition. 
-At the heart of biogeography is the idea that the abiotic environment can determine whether a species can have a positive growth-rate when rare in a particular location.
-For two species to interact, they first need to co-occur in the same community, which can only happen if the environmental conditions of the community fall within the "Grinellian" niche of both species.
-Although less understood, the environment can also affect the interactions, once community composition has been established [@tylianakis_ecological_2017]. 
+At the heart of biogeography is the idea that the abiotic environment can determine the "Grinellian" niche of a species, this is whether the species can have a positive growth-rate when rare in a particular location.
+For two species to interact, they first need to co-occur in the same community, which can only happen if the environmental conditions of the community fall within the Grinellian niche of both species.
+Although less understood, the environment can also affect the interactions themselves, after community composition has been established [@tylianakis_ecological_2017]. 
 For instance, some studies show that trophic interactions, like predation [@mckinnon_lower_2010; @vucic-pestic_warming_2011] and herbivory [@baskett_latitudinal_2018], can increase with temperature but might decrease with precipitation [@pires_predicted_2016], and both plant-plant [@bertness_positive_1994] and plant-pollinator [@tur_evaluating_2016] interactions can switch from facilitative to competitive along an elevation/temperature gradient.
 Contrastingly, other studies have shown either no effect or non-linear effects of temperature or precipitation on plant-pollinator interactions [@devoto_patterns_2005; @gravel_bringing_2018].
-One way to summarise the seemingly contradictory evidence of whether the environment can influence whether two species interact or not is by moving from gradients of temperature or precipitation to gradients of environmental stress/suitability.
-Previous research is so far equivocal and indicates that environmental stress can have two contrasting effects on species' Eltonian-niche [@tylianakis_ecological_2017].
+One way to summarise the seemingly contradictory evidence of whether the environment can influence whether two species interact or not is by moving from gradients of temperature or precipitation to gradients of environmental stress.
+Previous research is so far equivocal and, taken together, suggest that environmental stress can have two contrasting effects on species' Eltonian-niche [@tylianakis_ecological_2017].
 On the one hand, it is possible that when species are under environmental stress, they might be "pressured" to focus on partners with which they are best adapted to interact. 
-For instance, @hoiss_altitude_2012 found increased phylogenetic clustering between plants and pollinators at higher altitudes; while @peralta_phylogenetic_2015 found that parasitoids in plantation forest, where environmental stress was higher than in native forests, were constrained to interact with hosts, they were best adapted to attack.
+For instance, @hoiss_altitude_2012 found increased phylogenetic clustering between plants and pollinators at higher altitudes; while @peralta_phylogenetic_2015 found that parasitoids in plantation forest, where environmental stress was higher than in native forests, were constrained to interact with hosts they were best adapted to attack.
 Similarly, @lavandero_genotype_2013 found that environmental stress due to higher temperature reduced the breadth of the Eltonian niche of parasitoids. 
 On the other, it is also possible that when species are under environmental stress, they are forced to be more flexible in their interactions as higher environmental stress is likely to be reflected in greater energetic or reproductive costs and therefore they might not be able to sustain encounter rates with their preferred partners at sufficient levels.
-For instance, @hoiss_interactive_2015 found that the specialisation of plant-pollinator networks decreased both with elevation and after extreme drought events.
+In line with this hypothesis, @hoiss_interactive_2015 found that the specialisation of plant-pollinator networks decreased both with elevation and after extreme drought events.
 Likewise, @pellissier_spatial_2010 found a positive relationship between niche breadth and environmental stress: disk- or bowl-shaped blossoms (which allow a large number of potential pollinator species to access pollen and nectar rewards) dominated at high altitude flower communities.
 
-We collect available data on plant-pollinator interactions globally and calculate the environmental suitability of all species present at two or more communities to. 
+We analyse data on plant-pollinator interactions globally and calculate the environmental suitability of all species present at two or more communities to. 
 Our main aim is to leverage that information to test the two competing hypotheses that relate environmental stress and Eltionian niche breadth and whether there is a pattern within and across species.

### 2019-09-06 paper/manuscript.Rmd
Move intro notes to draft info document

@@
 Importantly, when testing these hypotheses, we control for the potential effects of the environment in community composition and the size of the species fundamental niche, both from an Eltonian (interactions) and Grinellian (environment) perspective.
-
-<!-- Interactions are selected by species depending on the relative benefit they provide.
-The assumption goes that species with a large number of interactions are benefit relatively little from each of them, and species with a small number benefit largely with them, this is they focus in more optimal pollinators.
--->
-
-<!-- AND  -->
-
-<!-- We know that interactions are influenced by the environment.  -->
-
-<!-- BUT -->
-
-<!-- We don't know how exactly wether the enviroment influences the patterns of generalisation/specialization.  -->
-
-<!-- One option is that when species are in detrimental environmental conditions focus on most optimal partners and as such interact with a smaller number of species.  -->
-<!-- An alternative hypotheisis is that when species are in favourable environmental conditions they can afford to be more picky about their interactions and as such avoid those of less value, while individuals in unfavourable conditions must get rewards from whatever they can get.
--->
-
-<!-- THEREFORE -->
-
-<!-- We used a global dataset on plant pollinator interactions, species occurrence, and bioclimatic data to test these hypotheses.  -->
-<!-- If the first option is true we should see a negative relationship between environmental sutability and the relative degree of a species.  -->
-<!-- If the second option is true we should see the opposite, a positive relationship between environmental suitability and the relative degree of a species.  -->
-
-<!-- **Is my central topic turnover of interactions**? If yes then I should quanitify turnover accross high and low suitability areas.  -->
-
-<!-- **Continuation: compare the suitability of the species that species do not interact with vs those that interact (when a possible interaction occurs but is not realised)?** -->
-
-<!-- **Continuation: average suitability of all species.
-If avg.
-competitors suitability is low, species, facilitation more common and resource sharing should increase.
-If avg.
-suitability is high, the opposite should happen?** -->
-
-<!-- **Continuation: Should I use relative suitability instead of absolute? Is not total suitability what matters but that relative to other species?**  -->
-
-<!-- **Is smaller degree a smaller Eltonian niche?** Should I frame this as the relationship between Grinellian and Eltonian.
-A better position in the grinellian niche allows for a larger Realised Eltonian niche.
-A problem of stating the hypothesis in terms of niches is that there are many definitions of niche and people is picky -->
-
-<!-- *Previous state of the world: We know interactions change with the environment but we don't know beyond co-occurrence patterns* -->
-
-<!-- Notes: -->
-
-<!-- **From donoso et al 2017: ** Intro: It is generally agreed that both neutral and niche-driven processes contribute to the occurrence of pairwise mutualistic interactions and network structure.
-That is, whether or not two species interact can be thought of as the result of two sequential processes.
-First, there is a stochastic (neutral) process driven by the local abundances of interacting species, such that abundant species are more likely to encounter each other than are rare ones.
-Secondly, there is a deterministic process driven by a matching of traits (e.g., phenology, morphology, behavior, etc.) that finally permits the interaction between co- occurring species.
--->
-
-<!-- Intro: Mutualistic interactions are fundamentally dynamic, such that there is a turnover of species and individuals in space and time (Carnicer et al., 2009; Laliberté and Tylianakis, 2010; Hagen et al., 2012).
--->
-
-<!-- I would then add a thrird one that is dictated by the rewards provided by an interaction. Maybe? -->
-
-<!-- Conclusion: Overall we found that the assemblage of pairwise interactions depended on the neutral effects of interacting species abundances (the more abundant the species of fruit and frugivore, the more frequent their pairwise interaction) and on the local context of ecological neighborhoods.
--->
-
-<!-- **From Boulangeat et al 2012:** Intro: These drivers of species distributions may act at different spatial scales.
-For instance, frequent consideration is given to abiotic variables acting at large spatial scales.
-On the other hand, biotic interactions and consumer-resource dynamics are assumed to occur at smaller spatial scales.
--->
-
-<!-- Conclusion: Biotic inetractions are def important at determining abundace.
-They observed positive effects of biotic interactions at colder climates (low suitability for plants) -- suggest facilitation.
-and negative effects of interactions at warmer climates (high suitability) suggesting competition.
-*Should I calculate the suitability of other species and test this?* -->
-
-<!-- **From Dormann et al 2018:** Intro: Sometimes, an organism will be little affected by com- petitors, mutualists, pathogens or predators; a mature tree may appear to grow unfettered by its neighbours for decades.
-In other cases, an individual may struggle to survive the pressure of its community during every hour of its life; for example, a fish preying and escaping predators in a small river.
-Biotic interactions such as these can have major effects on local processes and population dynamics, and some, but not neces- sarily all, scale up to co-determining the range of a species (reviewed, e.g., by Wisz et al., 2013).
--->
-
-<!-- Most BI-SDMs assume that biotic interactions are constant in space and time.
-It is more likely, however, that interaction strengths are modulated by the biotic and abiotic environment.
-Experimental studies showed that rates of biological interactions depend on environmental conditions: rates of herbivory are temperature dependent (Burnside, Erhardt, Hammond, & Brown, 2014); mycorrhizal symbioses change with resource availability (Cox, Barsoum, Lilleskov, & Bidartondo, 2010; Johnson, Wilson, Bowker, Wilson, & Miller, 2010); and plant–plant interactions can shift from competitive to facilitative along a stress gra- dient (Bertness & Callaway, 1994).
-Additionally, environmental change can modulate biotic interactions via phenological mismatches, such as for plant–pollinator interactions (Berg et al., 2010; Elzinga et al., 2007).
-In these conditions, the model must also allow for the interplay of environmental and biotic interactions (Clark et al., 2011), which has only recently started to be explored in BI-SDMs (Tikhonov, Abrego, Dunson, & Ovaskainen, 2017).
--->
-
-<!-- **From Gravel et al.
-2018**: We apply this framework to host–parasite interactions across Europe and ind that two aspects of the environment (temperature and precipitation) exert a strong imprint on species co-occurrence, but not on species interactions.
-Even where species co-occur, interaction proves to be stochastic rather than deterministic, adding to variation in realized network structure.
-*Bingo: I show it's not completely stochastic and is likely to be determined by the suitability hehe* -- for real ( They test prob.
-of two co-occurring species to interact does not depend on environment.
-I test single species thingy).
-Should I do that?
-suit sp.1 and suit sp.
-2?
-It;s not about the environment, but about how the environment affect the species involved.
-Buya!
--->
-
-<!-- There is, however, ample evidence that interaction networks vary in space and time (Laliberté and Tylianakis 2010, Poisot et al.
-2012, 2016c, Schleuning et al.
-2012, Albouy et al.
-2014, Trøjelsgaard et al.
-2015), even though there is no common framework with which to generalize these results.
--->
-
-<!-- he occurrence and intensity of interactions could vary because of the environment, species abundance, and higher- order ecological interactions (Poisot et al.
-2015).
-*Well do I show that could vary because of more stuff?* -->
-
-<!-- Variation in community composition can be independent of variation of ecological interactions, suggesting that species and inter- ac tion distribution may well respond to diferent drivers (Poisot et al.
-2012).
--->
-
-<!-- Ecological interactions could also vary with the environment.
-Although it is rare to see a conditional representation of pairwise ecological interactions, experimental studies have frequently revealed interactions to be sensitive to the environment.
-For instance, McKinnon et al.
-(2010) showed that predation risks of shorebirds vary at the continental scale, decreasing from the south to the north.
-It is also common to see increasing top-down control with temperature (Shurin et al.
-2012, Gray et al.
-2016).
-Efects of the environment on interactions (Gibert and DeLong 2014) also propagate up the community and inluence net- work structure (Tylianakis et al.
-2007, Petchey et al.
-2010, Woodward et al.
-2010).
--->
-
-<!-- In terms of species interacting with each other, our analysis suggests that the environment leaves a detectable imprint on species co-occurrence, but only a slight mark on the occurrence of realized links among species in a speciic place: the prob- ability of inding a given combination of species at a higher and a lower trophic level at the same site was clearly afected by the environment, whereas the probability of observing an interaction between the two was, given co-occurrence, not signiicantly so.
--->
-
-<!-- This does not imply that species will always interact when they meet – **although this is a basic assumption in most documented metawebs to date** (Havens 1992, Wood et al. 2015).  -->
-
-<!-- Evidence that the structure of ecological networks does vary across habitats (Tylianakis et al.
-2007), over environmental gradients (Lurgi et al.
-2012) and in time (Simanonok and Burkle 2014) is accumulating rapidly.
--->
-
-<!-- **Devictor 2010:** I can use degree to quantify realised eltonian niche -->
-
-<!-- **Godsoe 2017**: Biogeographers and community ecologists have long debated the importance of biotic interactions (see Glossary) for species distributions and range limits [1–5].*But seldom the other way arround?* -->
-
-<!-- **Tylianakis 2017**: Interactions can change because of environment because environment and habitat can change encounter rate.  -->
-
-<!-- Specialist species (that lack flexibility in their choice of interaction partner) should theoretically be most vulnerable to phenological decoupling.
-However, one study of pollinator communities along an elevational gradient found that apparently specialized pollinators were facultatively more generalist than they appeared and could adapt their visitation patterns across sites as much as generalists to avoid phenological asynchrony (Benadi et al.
-2014).
-Similarly, duration of the fruiting season has been shown to predict the degree and strength of seed-dispersal interactions (Gonza ́ lez- Castro et al.
-2012), and a long-term study found no difference between specialist and generalist plant species in their interannual fluctuations in phenology and pollinator richness (Petanidou et al.
-2014).
-Although these findings suggest that the facultative generalism of pollination mutualisms may confer robustness to these networks in the face of altered phenology (see also discussion on rewiring above), this robustness may depend on the climate context and the diversity and specialization within the network (Hoiss et al.
-2015).
-Moreover, less-generalized interactions such as those between parasites and hosts may show less flexibility.
--->
-
-<!-- many trophic and mutualistic interactions are relatively generalized and potentially opportunistic (Pimm et al.
-1991).
-Thus, we may expect that ecological networks will comprise a mixture of interactions that persist over the long-term owing to trait matching of partners through coevolution (Go ́ mez et al.
-2010, Guimaraes et al.
-2011) and those that occur opportunistically, perhaps with inferior long-term fitness benefits (Aizen et al.
-2016).
-Increases in the frequency of the former will strengthen any pattern of phylogenetic congruence, whereas increases in the latter will erode it.
--->
-
-<!-- For example, environmental stressors could cause species to narrow their trophic breadth by increasing the search time to find alternative partners (Gauld 1987) or by imposing limits on the quality of interaction partners that can be used (i.e., using only resources to which a species is best adapted).
-Phylogenetic congruence becomes stronger in parasitoid–host networks with increasing temperature (Lavandero & Tylianakis 2013) and in plantation versus native forests (Peralta et al.
-2015), and such patterns appear consistent with a hy- pothesis of stress-induced reduction in trophic (phylogenetic) breadth (in the case of Lavandero & Tylianakis 2013, this occurred on genotype relatedness rather than between-species phylogenies).
-However, evidence for the hypothesized mechanism is still lacking, as experiments have revealed no change in the proportionate use of good or bad hosts when parasitoids are nutritionally stressed (Hopper et al.
-2013) or even decreased selectivity toward high-quality hosts under high levels of nutritional stress (Crespo et al.
-2015).
--->
-
-<!-- In addition to seasonal patterns, interaction turnover can be driven by environmental fac- tors, such as community changes during drought years (Alarco ́n et al.
-2008) or along land use or landscape intensity gradients (Gagic et al.
-2012, Laliberte ́ & Tylianakis 2010).
-The impact of environmental conditions on interaction turnover can, in turn, be constrained by species traits such as feeding morphology (Carnicer et al.
-2009) or body size (Laliberte ́ & Tylianakis 2010).
-To understand this balance, species interactions can be thought of as having both a niche-based or trait-based component and a random or neutral component determined by encounter probability (Bartomeus et al.
-2016, Vazquez et al.
-2009).
-Any environmental driver that sufficiently increases encounter probability (see Section 2.2) for all species could reduce the neutral barrier to inter- actions and allow species to consistently select their interaction partner with optimally matched traits.
-This enhanced expression of species preferences would result in reduced spatial or temporal variability because the same interactions would consistently be realized (i.e., network homogeniza- tion; Laliberte ́ & Tylianakis 2010).
-Reduction of the neutral component of interactions could also lead to exaggeration of patterns of trait matching and phylogenetic congruence (Carnicer et al.
-2009) (see Section 2.3).
-Alternatively, a driver that increases the abundance of a subset of species could result in their overrepresentation in interactions by allowing the neutral component of inter- actions to be overexpressed relative to the trait-based component (Carnicer et al.
-2009).
-Because individual species may differ in the extent to which they engage in neutral interactions, changes to the relative abundance of species can alter network architecture.
-For example, exotic birds can be less selective in the fruit species on which they feed (i.e., feeding more neutrally on species in proportion to their abundance), and this low selectivity can allow them to fill the gap left by rare or extinct native birds and maintain high network nestedness and connectance (Garcıa et al.
-2014).
--->
-
-<!-- **Peralta 2015:** Plantation forests (as opposed to native) habitat may impose stresses on parasitoids that constrain them to attack only host species for which they are best adapted.
--> Consistent with more stress less generalism.
--->
-
-<!-- Native herbivore–parasitoid combinations whose interac- tions contributed the most to the pattern of phylogenetic congruence were more abundant in plantations than in native forests.
-This stronger co-evolutionary signal in plantation forests suggests that parasitoids in disturbed habitats may only be able to utilize hosts that they have best evolved to attack.
-Analogously, climate warming has been shown to reduce the niche breadth plasticity of par- asitoids (Lavandero & Tylianakis 2013), suggesting that different environmental changes could reduce the ability of parasitoid communities to suppress a broad range of host species and genotypes in natural systems and biologi- cal control programmes.
--->
 

### 2019-09-06 paper/manuscript.Rmd
reorganise beginning of methods

@@
 
-## Data aquisition
-
-### Species interactions
-
 ```{r}
@@
 This database contains datasets originating from `r length(interaction_citations$BIBTEXKEY)` studies published in the primary literature between `r int_citations_year_range[1]` and `r int_citations_year_range[2]` `r all_int_cites`.
-All together, these data sources contained `r format(n_sp_names, big.mark = ",")` unique organism names; `r format(n_names_in_multiple_references_orig, big.mark = ",")` of them in more than one data source.
-Because assessing how habitat suitability affects interaction partners of plants and pollinators requires linking of species across different datasets, it was important to ensure that the names used to identify species were as accurate as possible.
-From the total number of organisms,`r format(n_sp_names_subsp_level, big.mark = ",")` were identified to the subspecies or variety level, `r format(n_sp_names_sp_level_no_subsp, big.mark = ",")` to the species level, `r format(n_sp_names_gen_level, big.mark = ",")` to the genus level, and no taxonomic information was avaliable for the remaining `r format(n_no_tax_info, big.mark = ",")`.
-As the species level was the most common taxonomic rank available in our interaction datasets, in all further analysis, we group together subspecies or varieties within a same species.
+Calculating the environmental stress of species in their community and their Eltonian niche breadth requires that the scientific names used to identify them are valid and unambiguous. 
+This is because valid scientific names are necessary to both accurately match species across studies and to obtain other information from biological databases. 
+However, a significant proportion of the data obtained contain spelling mistakes, taxonomic synonyms, or non-standard abbreviations. 
+Therefore, our first step was to validate and correct scientific names across studies to ensure that we matching of species across studies was as accurate as possible.
 
-We were able to confirm the validity of `r format(n_sp_correct_in_data, big.mark = ",")` of the cannonical names used to identify organisms (roughly `r scales::percent(n_sp_correct_in_data/n_sp_names_sp_level, 1)`).
-We assessed the validity of a cannonical name by querying the Global Names Resolver database (https://resolver.globalnames.org) which includes data from `r dplyr::n_distinct(taxize::gnr_datasources()$title)` taxonomic sources.
+Second, we calculated the suitability of the environment for a species in a particular community as a proxy of environmental stress. 
+We assume that the environmental stress a species experience in a particular location is inversely related to the suitability of the average environmental conditions in that place. 
+Our third and final step was to relate the environmental suitability to the relative number of partners a species has in a community, as a proxy for Eltionian niche breadth. 
+To explore this relationship within and across species, we used a multilevel Bayesian model in which we controlled for the potential effects of the environment on co-occurrence.
+
+## Plant-pollinator interactions
+
+All together, interaction data from the included studies included `r format(n_sp_names, big.mark = ",")` unique organism names. 
+From these `r format(n_names_in_multiple_references_orig, big.mark = ",")` were present in more than one study.
+From the total number of organisms, `r format(n_sp_names_subsp_level, big.mark = ",")` were identified to the subspecies or variety level, `r format(n_sp_names_sp_level_no_subsp, big.mark = ",")` to the species level, `r format(n_sp_names_gen_level, big.mark = ",")` to the genus level, whereas the remaining `r format(n_no_tax_info, big.mark = ",")` were unidentified.
+As the species level was the most common taxonomic rank available in our interaction datasets, in all further analysis, we grouped together subspecies or varieties within a same species.
+
+We were able to confirm the validity of `r format(n_sp_correct_in_data, big.mark = ",")` of the scientific names used to identify organisms (roughly `r scales::percent(n_sp_correct_in_data/n_sp_names_sp_level, 1)`).
+We assessed the validity of a name by querying the Global Names Resolver database (https://resolver.globalnames.org) which includes data from `r dplyr::n_distinct(taxize::gnr_datasources()$title)` taxonomic sources.
 Specifically, we used the function `gnr_resolve` from the R package `taxize` `r as.character(packageVersion('taxize'))` [@chamberlain_taxize_2013; @chamberlain_taxize_2019].
 
-From the remaining `r format(n_sp_names_sp_level - n_sp_correct_in_data, big.mark = ",")` names we were unable to validate, we were able to identify and correct `r format(n_sp_corrected_typos, big.mark = ",")` spelling mistakes.
+From the remaining `r format(n_sp_names_sp_level - n_sp_correct_in_data, big.mark = ",")` names we were unable to validate, we were able to identify and correct `r format(n_sp_corrected_typos, big.mark = ",")` that contained spelling mistakes.
 These spelling mistakes were corrected automatically by fuzzy matching the canonical names in our data sources with tgose in the Global Names Resover database. 

### 2019-09-08 paper/draft-info.Rmd

@@
 * Fix references. There are lots of mistakes re. author, years and publication venue particularly for those from which data was downloaded.
+
+<!-- Interactions are selected by species depending on the relative benefit they provide.
+The assumption goes that species with a large number of interactions are benefit relatively little from each of them, and species with a small number benefit largely with them, this is they focus in more optimal pollinators.
+-->
+
+<!-- AND  -->
+
+<!-- We know that interactions are influenced by the environment.  -->
+
+<!-- BUT -->
+
+<!-- We don't know how exactly wether the enviroment influences the patterns of generalisation/specialization.  -->
+
+<!-- One option is that when species are in detrimental environmental conditions focus on most optimal partners and as such interact with a smaller number of species.  -->
+<!-- An alternative hypotheisis is that when species are in favourable environmental conditions they can afford to be more picky about their interactions and as such avoid those of less value, while individuals in unfavourable conditions must get rewards from whatever they can get.
+-->
+
+<!-- THEREFORE -->
+
+<!-- We used a global dataset on plant pollinator interactions, species occurrence, and bioclimatic data to test these hypotheses.  -->
+<!-- If the first option is true we should see a negative relationship between environmental sutability and the relative degree of a species.  -->
+<!-- If the second option is true we should see the opposite, a positive relationship between environmental suitability and the relative degree of a species.  -->
+
+<!-- **Is my central topic turnover of interactions**? If yes then I should quanitify turnover accross high and low suitability areas.  -->
+
+<!-- **Continuation: compare the suitability of the species that species do not interact with vs those that interact (when a possible interaction occurs but is not realised)?** -->
+
+<!-- **Continuation: average suitability of all species.
+If avg.
+competitors suitability is low, species, facilitation more common and resource sharing should increase.
+If avg.
+suitability is high, the opposite should happen?** -->
+
+<!-- **Continuation: Should I use relative suitability instead of absolute? Is not total suitability what matters but that relative to other species?**  -->
+
+<!-- **Is smaller degree a smaller Eltonian niche?** Should I frame this as the relationship between Grinellian and Eltonian.
+A better position in the grinellian niche allows for a larger Realised Eltonian niche.
+A problem of stating the hypothesis in terms of niches is that there are many definitions of niche and people is picky -->
+
+<!-- *Previous state of the world: We know interactions change with the environment but we don't know beyond co-occurrence patterns* -->
+
+<!-- Notes: -->
+
+<!-- **From donoso et al 2017: ** Intro: It is generally agreed that both neutral and niche-driven processes contribute to the occurrence of pairwise mutualistic interactions and network structure.
+That is, whether or not two species interact can be thought of as the result of two sequential processes.
+First, there is a stochastic (neutral) process driven by the local abundances of interacting species, such that abundant species are more likely to encounter each other than are rare ones.
+Secondly, there is a deterministic process driven by a matching of traits (e.g., phenology, morphology, behavior, etc.) that finally permits the interaction between co- occurring species.
+-->
+
+<!-- Intro: Mutualistic interactions are fundamentally dynamic, such that there is a turnover of species and individuals in space and time (Carnicer et al., 2009; Laliberté and Tylianakis, 2010; Hagen et al., 2012).
+-->
+
+<!-- I would then add a thrird one that is dictated by the rewards provided by an interaction. Maybe? -->
+
+<!-- Conclusion: Overall we found that the assemblage of pairwise interactions depended on the neutral effects of interacting species abundances (the more abundant the species of fruit and frugivore, the more frequent their pairwise interaction) and on the local context of ecological neighborhoods.
+-->
+
+<!-- **From Boulangeat et al 2012:** Intro: These drivers of species distributions may act at different spatial scales.
+For instance, frequent consideration is given to abiotic variables acting at large spatial scales.
+On the other hand, biotic interactions and consumer-resource dynamics are assumed to occur at smaller spatial scales.
+-->
+
+<!-- Conclusion: Biotic inetractions are def important at determining abundace.
+They observed positive effects of biotic interactions at colder climates (low suitability for plants) -- suggest facilitation.
+and negative effects of interactions at warmer climates (high suitability) suggesting competition.
+*Should I calculate the suitability of other species and test this?* -->
+
+<!-- **From Dormann et al 2018:** Intro: Sometimes, an organism will be little affected by com- petitors, mutualists, pathogens or predators; a mature tree may appear to grow unfettered by its neighbours for decades.
+In other cases, an individual may struggle to survive the pressure of its community during every hour of its life; for example, a fish preying and escaping predators in a small river.
+Biotic interactions such as these can have major effects on local processes and population dynamics, and some, but not neces- sarily all, scale up to co-determining the range of a species (reviewed, e.g., by Wisz et al., 2013).
+-->
+
+<!-- Most BI-SDMs assume that biotic interactions are constant in space and time.
+It is more likely, however, that interaction strengths are modulated by the biotic and abiotic environment.
+Experimental studies showed that rates of biological interactions depend on environmental conditions: rates of herbivory are temperature dependent (Burnside, Erhardt, Hammond, & Brown, 2014); mycorrhizal symbioses change with resource availability (Cox, Barsoum, Lilleskov, & Bidartondo, 2010; Johnson, Wilson, Bowker, Wilson, & Miller, 2010); and plant–plant interactions can shift from competitive to facilitative along a stress gra- dient (Bertness & Callaway, 1994).
+Additionally, environmental change can modulate biotic interactions via phenological mismatches, such as for plant–pollinator interactions (Berg et al., 2010; Elzinga et al., 2007).
+In these conditions, the model must also allow for the interplay of environmental and biotic interactions (Clark et al., 2011), which has only recently started to be explored in BI-SDMs (Tikhonov, Abrego, Dunson, & Ovaskainen, 2017).
+-->
+
+<!-- **From Gravel et al.
+2018**: We apply this framework to host–parasite interactions across Europe and ind that two aspects of the environment (temperature and precipitation) exert a strong imprint on species co-occurrence, but not on species interactions.
+Even where species co-occur, interaction proves to be stochastic rather than deterministic, adding to variation in realized network structure.
+*Bingo: I show it's not completely stochastic and is likely to be determined by the suitability hehe* -- for real ( They test prob.
+of two co-occurring species to interact does not depend on environment.
+I test single species thingy).
+Should I do that?
+suit sp.1 and suit sp.
+2?
+It;s not about the environment, but about how the environment affect the species involved.
+Buya!
+-->
+
+<!-- There is, however, ample evidence that interaction networks vary in space and time (Laliberté and Tylianakis 2010, Poisot et al.
+2012, 2016c, Schleuning et al.
+2012, Albouy et al.
+2014, Trøjelsgaard et al.
+2015), even though there is no common framework with which to generalize these results.
+-->
+
+<!-- he occurrence and intensity of interactions could vary because of the environment, species abundance, and higher- order ecological interactions (Poisot et al.
+2015).
+*Well do I show that could vary because of more stuff?* -->
+
+<!-- Variation in community composition can be independent of variation of ecological interactions, suggesting that species and inter- ac tion distribution may well respond to diferent drivers (Poisot et al.
+2012).
+-->
+
+<!-- Ecological interactions could also vary with the environment.
+Although it is rare to see a conditional representation of pairwise ecological interactions, experimental studies have frequently revealed interactions to be sensitive to the environment.
+For instance, McKinnon et al.
+(2010) showed that predation risks of shorebirds vary at the continental scale, decreasing from the south to the north.
+It is also common to see increasing top-down control with temperature (Shurin et al.
+2012, Gray et al.
+2016).
+Efects of the environment on interactions (Gibert and DeLong 2014) also propagate up the community and inluence net- work structure (Tylianakis et al.
+2007, Petchey et al.
+2010, Woodward et al.
+2010).
+-->
+
+<!-- In terms of species interacting with each other, our analysis suggests that the environment leaves a detectable imprint on species co-occurrence, but only a slight mark on the occurrence of realized links among species in a speciic place: the prob- ability of inding a given combination of species at a higher and a lower trophic level at the same site was clearly afected by the environment, whereas the probability of observing an interaction between the two was, given co-occurrence, not signiicantly so.
+-->
+
+<!-- This does not imply that species will always interact when they meet – **although this is a basic assumption in most documented metawebs to date** (Havens 1992, Wood et al. 2015).  -->
+
+<!-- Evidence that the structure of ecological networks does vary across habitats (Tylianakis et al.
+2007), over environmental gradients (Lurgi et al.
+2012) and in time (Simanonok and Burkle 2014) is accumulating rapidly.
+-->
+
+<!-- **Devictor 2010:** I can use degree to quantify realised eltonian niche -->
+
+<!-- **Godsoe 2017**: Biogeographers and community ecologists have long debated the importance of biotic interactions (see Glossary) for species distributions and range limits [1–5].*But seldom the other way arround?* -->
+
+<!-- **Tylianakis 2017**: Interactions can change because of environment because environment and habitat can change encounter rate.  -->
+
+<!-- Specialist species (that lack flexibility in their choice of interaction partner) should theoretically be most vulnerable to phenological decoupling.
+However, one study of pollinator communities along an elevational gradient found that apparently specialized pollinators were facultatively more generalist than they appeared and could adapt their visitation patterns across sites as much as generalists to avoid phenological asynchrony (Benadi et al.
+2014).
+Similarly, duration of the fruiting season has been shown to predict the degree and strength of seed-dispersal interactions (Gonza ́ lez- Castro et al.
+2012), and a long-term study found no difference between specialist and generalist plant species in their interannual fluctuations in phenology and pollinator richness (Petanidou et al.
+2014).
+Although these findings suggest that the facultative generalism of pollination mutualisms may confer robustness to these networks in the face of altered phenology (see also discussion on rewiring above), this robustness may depend on the climate context and the diversity and specialization within the network (Hoiss et al.
+2015).
+Moreover, less-generalized interactions such as those between parasites and hosts may show less flexibility.
+-->
+
+<!-- many trophic and mutualistic interactions are relatively generalized and potentially opportunistic (Pimm et al.
+1991).
+Thus, we may expect that ecological networks will comprise a mixture of interactions that persist over the long-term owing to trait matching of partners through coevolution (Go ́ mez et al.
+2010, Guimaraes et al.
+2011) and those that occur opportunistically, perhaps with inferior long-term fitness benefits (Aizen et al.
+2016).
+Increases in the frequency of the former will strengthen any pattern of phylogenetic congruence, whereas increases in the latter will erode it.
+-->
+
+<!-- For example, environmental stressors could cause species to narrow their trophic breadth by increasing the search time to find alternative partners (Gauld 1987) or by imposing limits on the quality of interaction partners that can be used (i.e., using only resources to which a species is best adapted).
+Phylogenetic congruence becomes stronger in parasitoid–host networks with increasing temperature (Lavandero & Tylianakis 2013) and in plantation versus native forests (Peralta et al.
+2015), and such patterns appear consistent with a hy- pothesis of stress-induced reduction in trophic (phylogenetic) breadth (in the case of Lavandero & Tylianakis 2013, this occurred on genotype relatedness rather than between-species phylogenies).
+However, evidence for the hypothesized mechanism is still lacking, as experiments have revealed no change in the proportionate use of good or bad hosts when parasitoids are nutritionally stressed (Hopper et al.
+2013) or even decreased selectivity toward high-quality hosts under high levels of nutritional stress (Crespo et al.
+2015).
+-->
+
+<!-- In addition to seasonal patterns, interaction turnover can be driven by environmental fac- tors, such as community changes during drought years (Alarco ́n et al.
+2008) or along land use or landscape intensity gradients (Gagic et al.
+2012, Laliberte ́ & Tylianakis 2010).
+The impact of environmental conditions on interaction turnover can, in turn, be constrained by species traits such as feeding morphology (Carnicer et al.
+2009) or body size (Laliberte ́ & Tylianakis 2010).
+To understand this balance, species interactions can be thought of as having both a niche-based or trait-based component and a random or neutral component determined by encounter probability (Bartomeus et al.
+2016, Vazquez et al.
+2009).
+Any environmental driver that sufficiently increases encounter probability (see Section 2.2) for all species could reduce the neutral barrier to inter- actions and allow species to consistently select their interaction partner with optimally matched traits.
+This enhanced expression of species preferences would result in reduced spatial or temporal variability because the same interactions would consistently be realized (i.e., network homogeniza- tion; Laliberte ́ & Tylianakis 2010).
+Reduction of the neutral component of interactions could also lead to exaggeration of patterns of trait matching and phylogenetic congruence (Carnicer et al.
+2009) (see Section 2.3).
+Alternatively, a driver that increases the abundance of a subset of species could result in their overrepresentation in interactions by allowing the neutral component of inter- actions to be overexpressed relative to the trait-based component (Carnicer et al.
+2009).
+Because individual species may differ in the extent to which they engage in neutral interactions, changes to the relative abundance of species can alter network architecture.
+For example, exotic birds can be less selective in the fruit species on which they feed (i.e., feeding more neutrally on species in proportion to their abundance), and this low selectivity can allow them to fill the gap left by rare or extinct native birds and maintain high network nestedness and connectance (Garcıa et al.
+2014).
+-->
+
+<!-- **Peralta 2015:** Plantation forests (as opposed to native) habitat may impose stresses on parasitoids that constrain them to attack only host species for which they are best adapted.
+-> Consistent with more stress less generalism.
+-->
+
+<!-- Native herbivore–parasitoid combinations whose interac- tions contributed the most to the pattern of phylogenetic congruence were more abundant in plantations than in native forests.
+This stronger co-evolutionary signal in plantation forests suggests that parasitoids in disturbed habitats may only be able to utilize hosts that they have best evolved to attack.
+Analogously, climate warming has been shown to reduce the niche breadth plasticity of par- asitoids (Lavandero & Tylianakis 2013), suggesting that different environmental changes could reduce the ability of parasitoid communities to suppress a broad range of host species and genotypes in natural systems and biologi- cal control programmes.
+-->

### 2019-09-08 paper/manuscript.Rmd
edits to cleaning process

@@
 We assessed the validity of a name by querying the Global Names Resolver database (https://resolver.globalnames.org) which includes data from `r dplyr::n_distinct(taxize::gnr_datasources()$title)` taxonomic sources.
-Specifically, we used the function `gnr_resolve` from the R package `taxize` `r as.character(packageVersion('taxize'))` [@chamberlain_taxize_2013; @chamberlain_taxize_2019].
+We accessed this database using the function `gnr_resolve` from the R package `taxize` `r as.character(packageVersion('taxize'))` [@chamberlain_taxize_2013; @chamberlain_taxize_2019].
 
 From the remaining `r format(n_sp_names_sp_level - n_sp_correct_in_data, big.mark = ",")` names we were unable to validate, we were able to identify and correct `r format(n_sp_corrected_typos, big.mark = ",")` that contained spelling mistakes.
-These spelling mistakes were corrected automatically by fuzzy matching the canonical names in our data sources with tgose in the Global Names Resover database. 
-In rare occasions, the fuzzy matching algorithm can suggest a cannonical name that has similar spelling but that correspond to an organism in a completely different taxonomic group, often in a different kingdom.
-We, therefore, checked the taxonomic hierarchy of suggested names to confirm that it corresponded to our expectations. 
+These spelling mistakes were corrected automatically by fuzzy matching the canonical names in our data sources with those in the Global Names Resover database. 
+However, in rare occasions, the fuzzy matching algorithm can suggest a cannonical name that has similar spelling but that correspond to an organism in a different taxonomic group, often a different kingdom.
+To address this potential problem, we checked the taxonomic hierarchy of suggested names and confirmed that it matched to our expectated taxon.
 We retrieved all taxonomic hierarchies from the National Center for Biotechnology Information taxonomic database (https://www.ncbi.nlm.nih.gov/taxonomy).
 
-Subsequently, we checked for possible synonyms of the canonnical names in our data sources. 
-Using data from the Integrated Taxonomic Information System database (http://www.itis.gov), we found synonyms and alternative names for `r format(n_sp_with_synonyms, big.mark = ",")` of those in our data sources.
-Finding these alternative names was important due to two reasons. 
-First, because we wanted to be able to identify the cases in which the same organism might have been recorded with different cannonical names in different data sources.
-This can ocurr not only with synonyms but also when the cannonical name has been changed or when there are widely used ortographic variants.
+As species names are constantly changin, we subsequently checked for possible synonyms of the canonnical names in our data sources. 
+Using data from the Integrated Taxonomic Information System database (http://www.itis.gov), we found synonyms and alternative names for `r format(n_sp_with_synonyms, big.mark = ",")` species.  
+Finding these alternative names was important for two main reasons. 
+First, because we wanted to be able to identify the cases in which the same species might have been recorded with different names in various data sources. 
+This can ocurr not only when the cannonical name has been changed but also when there are widely used ortographic variants.
 Second, because retrieving occurrence data is often only possible using the latest accepted/valid name for a particular species.
 
-All together, from the `r format(n_sp_names_sp_level - n_sp_correct_in_data, big.mark = ",")` names we were unable to validate, it was not possible to automatically correct `r format(n_sp_not_found, big.mark = ",")` of them.
-We then manually consulted multiple online databases, chiefly Wikispecies (https://species.wikimedia.org/), and looked for cannonical names that resembled the unvalidated names and matched the geographic and taxonomic spectations.
-We were able to further correct `r n_sp_manual_corrections` names in this fashion.
-Most manual corrections were of species names that have been abbreviated or had more than two spelling mistakes. 
+All together, from the `r format(n_sp_names_sp_level - n_sp_correct_in_data, big.mark = ",")` names we were unable to validate, it was not possible to automatically correct or find synonyms `r format(n_sp_not_found, big.mark = ",")` of them.
+We then manually consulted multiple online databases, chiefly Wikispecies (https://species.wikimedia.org/), and looked for cannonical names that both, resembled the unvalidated names and matched the geographic and taxonomic spectations.
+In this fashion, we were able to further correct `r n_sp_manual_corrections` names. 
+Most manual corrections were made on names that have been abbreviated or had more than two spelling mistakes. 
 A complete list of manual name corrections can bee seen in Table \@ref(tab:tab-manual-name-corrections).
@@
 ```{r}
-loadd(recoded_interactions, clean_interactions)
+loadd(recoded_interactions, clean_interactions, int_metadata)
 
@@
   purrr::map(n_distinct)
+
+data_sources_mult_nets <- int_metadata %>%
+  group_by(loc_id) %>%
+  summarise(n_nets = n_distinct(net_name)) %>%
+  filter(n_nets > 1)
+
+n_data_sources_mult_nets <- nrow(data_sources_mult_nets)
 ```
@@
 This cleaning process allowed us to match further `r n_sp_names - n_sp_ids` names across data sources and, by doing so, identify another `r n_names_in_multiple_references_after - n_names_in_multiple_references_orig` species that were present in more than one study.
-It also allowed us to identify `r numbers2words(length(problematic_networks))` problematic networks in which some names were included as both plants and pollinators. 
-These networks were removed from further analysis. 
-Sometimes interaction data was recorded at multiple points in time within or across our data sources. 
-When this was the case, we combined them into one single interaction network per location. 
+The process also allowed us to identify `r numbers2words(length(problematic_networks))` problematic data sources in which some names were included as both plants and pollinators. 
+These data sources were removed from further analysis. 
+In `r numbers2words(n_data_sources_mult_nets)` of our data sources interaction data was recorded at multiple points in time. 
+When this was the case, we combined interaction data into one single interaction network.
+
 The cleaning process resulted on a total of `r format(stats_clean_int$pla_id, big.mark = ",")` plants and `r format(stats_clean_int$ani_id, big.mark = ",")` pollinator species distributed across `r format(stats_clean_int$loc_id)` locations arround the globe (Figure \@ref(fig:fig-worldmap), \@ref(fig:fig-distribution-species-mult-locations)).

### 2019-09-08 paper/manuscript.Rmd
check spelling checking method section

@@
 From the total number of organisms, `r format(n_sp_names_subsp_level, big.mark = ",")` were identified to the subspecies or variety level, `r format(n_sp_names_sp_level_no_subsp, big.mark = ",")` to the species level, `r format(n_sp_names_gen_level, big.mark = ",")` to the genus level, whereas the remaining `r format(n_no_tax_info, big.mark = ",")` were unidentified.
-As the species level was the most common taxonomic rank available in our interaction datasets, in all further analysis, we grouped together subspecies or varieties within a same species.
+As the species level was the most common taxonomic rank available in our interaction datasets, in all further analysis, we grouped together subspecies or varieties within the same species.
 
@@
 From the remaining `r format(n_sp_names_sp_level - n_sp_correct_in_data, big.mark = ",")` names we were unable to validate, we were able to identify and correct `r format(n_sp_corrected_typos, big.mark = ",")` that contained spelling mistakes.
-These spelling mistakes were corrected automatically by fuzzy matching the canonical names in our data sources with those in the Global Names Resover database. 
-However, in rare occasions, the fuzzy matching algorithm can suggest a cannonical name that has similar spelling but that correspond to an organism in a different taxonomic group, often a different kingdom.
-To address this potential problem, we checked the taxonomic hierarchy of suggested names and confirmed that it matched to our expectated taxon.
+These spelling mistakes were corrected automatically by fuzzy matching the canonical names in our data sources with those in the Global Names Resolver database. 
+However, on rare occasions, the fuzzy matching algorithm can suggest a scientific name that has a similar spelling, but that corresponds to an organism in a different taxonomic group, often a separate kingdom.
+To address this potential problem, we checked the taxonomic hierarchy of suggested names and confirmed that it matched our expected taxon.
 We retrieved all taxonomic hierarchies from the National Center for Biotechnology Information taxonomic database (https://www.ncbi.nlm.nih.gov/taxonomy).
 
-As species names are constantly changin, we subsequently checked for possible synonyms of the canonnical names in our data sources. 
+As species names are constantly changing, we subsequently checked for possible synonyms of the canonical names in our data sources. 
 Using data from the Integrated Taxonomic Information System database (http://www.itis.gov), we found synonyms and alternative names for `r format(n_sp_with_synonyms, big.mark = ",")` species.  
-Finding these alternative names was important for two main reasons. 
+Finding these alternative names was required for two main reasons. 
 First, because we wanted to be able to identify the cases in which the same species might have been recorded with different names in various data sources. 
-This can ocurr not only when the cannonical name has been changed but also when there are widely used ortographic variants.
+This can occur not only when the canonical name has been changed but also when there are widely used orthographic variants.
 Second, because retrieving occurrence data is often only possible using the latest accepted/valid name for a particular species.
@@
 All together, from the `r format(n_sp_names_sp_level - n_sp_correct_in_data, big.mark = ",")` names we were unable to validate, it was not possible to automatically correct or find synonyms `r format(n_sp_not_found, big.mark = ",")` of them.
-We then manually consulted multiple online databases, chiefly Wikispecies (https://species.wikimedia.org/), and looked for cannonical names that both, resembled the unvalidated names and matched the geographic and taxonomic spectations.
+We then manually consulted multiple online databases, chiefly Wikispecies (https://species.wikimedia.org/), and looked for canonical names that both, resembled the unvalidated names and matched the geographic and taxonomic expectations.
 In this fashion, we were able to further correct `r n_sp_manual_corrections` names. 

### 2019-09-09 paper/manuscript.Rmd
Add some stuff about how we calculated suitability

@@
 
-Our next step was to determine the suitability of the species that were present in at least `r numbers2words(readd(minimum_spp_locations))` communities.
-To do that we first fit a climatic envelope for each  of them which requires information about the climate and habitat at the locations where the species occurrs. 
+Our next step was to determine the habitat suitability of the species as a proxy of the environmental stress they experience in their community.
+As our aim is to compare the throphic niche for different suitability levels, we only do this for species that were present in at least `r numbers2words(readd(minimum_spp_locations))` communities.
+To calculate the suitability of a species in a particular location, using a (grinellian) niche-factor analysis [@hirzel_ecological-niche_2002; @broennimann_measuring_2012] which is based on the probabiliy density function of a species distribution in an environmental-bioclimatic variable space.
+Calculating this we To do that we first fit a climatic envelope for each  of them which requires information about the climate and habitat at the locations where the species occurrs. 
 We retrieved climatic data from WorldClim V2.0 which includes 19 bioclimatic variables commonly used in species distribution modelling [@fick_worldclim_2017]. 

### 2019-09-09 paper/manuscript.Rmd
Some more changes to the methods. Better explain download of occurrence and evironmental data

@@
 As our aim is to compare the throphic niche for different suitability levels, we only do this for species that were present in at least `r numbers2words(readd(minimum_spp_locations))` communities.
-To calculate the suitability of a species in a particular location, using a (grinellian) niche-factor analysis [@hirzel_ecological-niche_2002; @broennimann_measuring_2012] which is based on the probabiliy density function of a species distribution in an environmental-bioclimatic variable space.
-Calculating this we To do that we first fit a climatic envelope for each  of them which requires information about the climate and habitat at the locations where the species occurrs. 
-We retrieved climatic data from WorldClim V2.0 which includes 19 bioclimatic variables commonly used in species distribution modelling [@fick_worldclim_2017]. 
-These bioclimatic variables were complemented with 18 of bioclimatic and topographic variables available in Envirem [@title_envirem_2018]. 
-This additional set of variables have been shown to be relevant to ecological or physiological processes and as such have the potential to improve species distribition models.
-All climatic data was obtained as rasters composed by cells of 2.5 arc-minutes. 
-This resolution provides a reasonable match to the locational accuracy of the species occurrences found in GBIF, particularly those that come preserved specimens in museum collections. 
-Furthermore, we obtained habitat data from The Nature Conservation's terrestrial ecoregions of the world [@olson_global_2002].
+To calculate the suitability of a species in a particular location, we used a (grinellian) niche-factor analysis [@hirzel_ecological-niche_2002; @broennimann_measuring_2012]. 
+This approach is based on the probabiliy density function of a species distribution in an environmental variable space. 
+In a nutshell, habitats (characterised by a collection of environmental variables) in which the species ocurrs most often are deemed to be suitable for the species than habitats in which the species has never been observed.
+This approach to estimate the habitat suitability requires to key pieces of information. 
+First we require information about the occurrences of the species of interest.
+Second we require information about the environmental conditions for all the locations in which the species occurs.
 
 We retrieved occurrences from the Global Biodiversity Information Facility (GBIF; https://www.gbif.org) using the R package `rgbif` `r as.character(packageVersion('taxize'))` [@chamberlain_r_2017; @chamberlain_rgbif_2019].
-For each species, we downloaded occurrences for which the coordinates of the observation were available and that had no known geospatial issue in the GBIF database.
-Roughly, we downloaded `r round(sum(n_occurrences$N)/1000000, digits = 1)` million occurrences for `r format(n_species_with_occurrences, big.mark = ",")` of the species of interest. 
-The occurrences obtained contain observations of mixed quality, so we applied a series of simple filters to remove those of lower quality. 
+Specifically, for each species, we only requested occurrences for which the coordinates of the observation were available and that had no known geospatial issue in the GBIF database.
+Roughly, we downloaded `r round(sum(n_occurrences$N)/1000000, digits = 1)` million occurrences for the `r format(n_species_with_occurrences, big.mark = ",")` species we were interested on. 
+This occurrences however, contain observations of mixed quality. 
+Therefore, we followed (ref?) and applied a series of simple filters and geographic heuristics to remove those of lower quality. 
 \R{rationale-occurrence-filtering}Specifically, we removed all occurrences with (*i*) a coordinate uncertainity larger than 100km; (*ii*) those recorded prior to 1945 (ref?
@@
 Thorugh this cleaning process, we removed with `r round(sum(n_dirty_occurrences$N)/1000000, digits = 1)` million occurrences distributed accross `r n_species_with_dirty_occurrences` species. 
-We added the occurrences from our plant-pollinator networks to the cleaned occurrences retrieved from GBIF.
+Finally, we integrated the occurrences from our plant-pollinator communities to the cleaned occurrences retrieved from GBIF.
 
-Next, we overlapped the occurrence and our environmental rasters such that each occurrence location is characterized by a vector with information of our 37 bioclimatic and topographic variables . 
+We retrieved environmental data from WorldClim V2.0 which includes 19 bioclimatic variables commonly used in species distribution modelling [@fick_worldclim_2017]. 
+We then complemented data obtained from WorldClim with data from Envirem [@title_envirem_2018], which includes 16 extra bioclimatic and two topographic variables. 
+The additional set of variables from Envirem have been shown to be relevant to ecological or physiological processes and as such have the potential to improve our suitability estimation. 
+We obtained all environmental data as rasters composed by cells of 2.5 arc-minutes. 
+We chose this resolution because it provides a reasonable match to the locational accuracy of the species occurrences found in GBIF, particularly those that come preserved specimens in museum collections.
+
+After obtaining information about the species occurrence and the evironment, the next step was to merge these two datasets such that the location of each occurrence is characterized by a vector with information of our 37 bioclimatic and topographic variables.
 If a species had more than one occurrence records within one of the cells of the bioclimatic raster we only included one of the occurrence records. 
 We did this to avoid giving more weight to areas with a high number of occurrences, a common scenario in occurrrence records collected opportunistically as the ones we use here. 
-Overall we removed `r scales::percent(percent_thinned)` of the occurrences which resulted in a total of `r round(sum(n_thinned_occurrences$N)/1000000, digits = 1)` million occurrences used in our niche analysis.
+In this step we removed `r scales::percent(percent_thinned)` of the occurrences which resulted in a total of `r round(sum(n_thinned_occurrences$N)/1000000, digits = 1)` million occurrences used in our niche analysis.
+
 A common issue of terrestrial bioclimatic datasets is that the boundaries of the cells with information do not exactly match the land mass boundaries. 
-The result of this missmatch is that at least one of the environmental variables was not available for `r format(complete_climate_cells[1], big.mark = ",")` of the raster cells with occurrences (`r scales::percent(complete_climate_cells[1]/sum(complete_climate_cells), accuracy = 0.1)` of the total).
-As expected a vast majority of these cells were close to the shore. 
-To address this issue, calculated average value of environmental variables within a `r config$climate_buffer/1000`km buffer of the center of the cell where the variable is missing, and used it to approximate the value of the variable in that cell.
-In this fashion we were able to fill environmental variables for `r scales::percent(percent_filled_round_one, accuracy = 0.1)` of the cells were they were missing. 
-To fill the remaining `r format(complete_filled_cells_1[1], big.mark= ",")` cells, we repeated the aforementioned procedure but using a `r config$climate_buffer*2/1000`km buffer. 
+The result of this missmatch is that not all environmental variables was not available for `r format(complete_climate_cells[1], big.mark = ",")` of the raster cells with occurrences (`r scales::percent(complete_climate_cells[1]/sum(complete_climate_cells), accuracy = 0.1)` of the total).
+As expected, a vast majority of these problematic cells were close to the shore. 
+To address this issue, we calculated the average value of environmental variables within a `r config$climate_buffer/1000`km buffer of the center of the cell where the variable is missing, and used it to approximate the value of the variable in that cell.
+Using this procedure we were able to fill environmental variables for `r scales::percent(percent_filled_round_one, accuracy = 0.1)` of the cells were they were missing. 
+To fill the remaining `r format(complete_filled_cells_1[1], big.mark= ",")` cells, we repeated the aforementioned procedure but instead using a `r config$climate_buffer*2/1000`km buffer. 
 We removed from further analyis occurrences located within the `r complete_filled_cells_2[1]` cells for which we were unable to fill environmental variables.

### 2019-09-09 code/suitability_vs_degree.R
try out models with triple interactions

@@ -179,13 +179,25 @@ define_alternative_models <- function(formula_base){
       (1 | org_id)
   )
   
+  formula_triple_interaction <- update(
+    formula_base, 
+    ~ . + scaled_grinell_niche_size:scaled_suitability
+  )
+
+  formula_triple_interaction_no_niche <- update(
+    formula_base, 
+    ~ . + scaled_grinell_niche_size:scaled_suitability - scaled_grinell_niche_size - scaled_grinell_niche_size:guild
+  )
+  
   list(
     formula_base = formula_base, 
     formula_no_generalism = formula_no_generalism, 
     formula_no_grinell_niche_size = formula_no_grinell_niche_size,
     formula_no_possible_partners = formula_no_possible_partners,
+    formula_triple_interaction_no_niche = formula_triple_interaction_no_niche,
     # formula_no_possible_partners_generalism = formula_no_possible_partners_generalism,
-    formula_no_suitability = formula_no_suitability
+    formula_no_suitability = formula_no_suitability, 
+    formula_triple_interaction = formula_triple_interaction
   )
   
 }
@@ -204,9 +216,9 @@ fit_model <- function(formulas, analysis_frame, cores = 1L, iter = 4000){
                data = analysis_frame, 
                prior = c(
                  set_prior("normal(0,10)", class = "b"), 
-                 set_prior("normal(0,10)", class = "Intercept"), 
+                 set_prior("normal(0,10)", class = "Intercept")
                  # set_prior("lkj(2)", class = "cor"), 
-                 set_prior("cauchy(0, 2)", class = "sd")
+                 # set_prior("cauchy(0, 2)", class = "sd")
                  ),
                chains = 4, 
                iter = iter,
@@ -234,20 +246,21 @@ compare_models <- function(chosen_models){
   model_waic <- chosen_models %>%
     purrr::map(brms::waic)
   
-  model_kfold <- chosen_models %>%
-    purrr::map(brms::kfold)
-  
-  model_kfold_org <- chosen_models %>%
-    purrr::map(brms::kfold, group = "org_id", folds = "grouped")
-  
-  model_kfold_loc <- chosen_models %>%
-    purrr::map(brms::kfold, group = "loc_id", folds = "grouped")
+  # model_kfold <- chosen_models %>%
+  #   purrr::map(brms::kfold)
+  # 
+  # model_kfold_org <- chosen_models %>%
[…]

### 2019-09-09 paper/manuscript.Rmd
DOn't use PNAS bibliography notation for now

@@
   - int-bibliography.bib
-csl: pnas.csl
+# csl: pnas.csl
 output: #word_document

### 2019-09-09 paper/manuscript.Rmd
Edit methods for the model part

--- 2019-09-09 paper/manuscript.Rmd
@@
 
-Our main objective is to investigate wether the suitability of the environment was to obtain the suitability of the environment at the locations for which we have community data. 
-This involves two steps. 
-First, we determine the species' grinellian niche, the range of environmental conditions that are suitable for a positive growth rate. 
-We assume that the suitability of a particular set of environmental conditions (a point in the environmental space) can be inferred from the density of occurrences under these conditions. 
-This is, areas of the niche that have a higher density of occurrences have higher suitability and can be interpreted as the core of the species distribution in environental space. 
-Contrastingly, areas with a lower density are comparatively less suitable and represent the fringes of the species distribution. 
-The second step is to determine the location of our plant-pollinator communities (where the species is present) in the environmental space and calculate its corresponding environmental suitability.
-
+Next, we calculate the probability density function of the species distribution in environemntal space. 
 To determine the environmental space we use the first two components from a principal component analysis of the 37 bioclimatic variables associated with the species occurrences. 
 Specifically we use the `dudi.pca` function from the R package `ade4` `r as.character(packageVersion('ade4'))` [@dray_ade4_2007] and center and scale all bioclimatic variables to have a mean of 0 and a unit standard deviation.
-We then determine the position of species occurrences in the environmental space and estimate their bivariate density distribution using the kernel method. 
-The main advantage of using the kernel method is that it reduces the sensitivity of the niche to sampling effort and the resolution chosen for the environmental space grid [@broennimann_measuring_2012].
-To calculate the kernel we use `ecospat.grid.clim.dyn` from the R package `ecospat` `r as.character(packageVersion('ecospat'))` [@ecospat_citation] with a grid resolution of 200.
-We then normalise the occurrence density distribution such that our suitability ranges beetween 1 for the grids with environmental conditions in which the species was most commonly observed and 0 for the grids in which it was never observed.
-We then determine the location in environmental space of the plant-pollinator communities where the species is present using the function `suprow` from `ade4` and calculate its corresponding suitability using the R package `raster` `r as.character(packageVersion('raster'))` [@raster_citation].
+We then determine the position of species occurrences in the environmental space and estimate their bivariate probability density function. 
+We use a kernel method to estimate this density and normalise it such that it ranges beetween zero and one. 
+Specifically, to calculate the probability density function we use `ecospat.grid.clim.dyn` from the R package `ecospat` `r as.character(packageVersion('ecospat'))` [@ecospat_citation] with a grid resolution of 200.
+We then determine the location in environmental space of the plant-pollinator communities where the species is present using the function `suprow` from `ade4`.
+The normalised density at that particular location corresponds to our suitability metric, which we calculate using the R package `raster` `r as.character(packageVersion('raster'))` [@raster_citation].
+We use the kernel density method in the niche-factor analyisis [@broennimann_measuring_2012] rather than the distance from the mode [@hirzel_ecological-niche_2002], as it has been proposed earlier, as it has been shown to reduce the procedure's sensitivity to sampling effort and the resolution of the environmental space.
 
@@
 
-## Model
+## Data analysis
 
-We then used a two sets of bayesian multilevel models to evaluate the impact of environmental suitability on the size of the realised Eltonian niche. 
-We measure the size of the Eltonian niche using the normalised degree of species, this is, the number of species it interacts with given the number of possible partners. 
-In the first set of models, we use a *naive* version of the normalised degree [@martin_gonzalez_centrality_2010] in which the number of possible partners is defined by the number of species in the opposite guild.
-This definition is the one commonly used in the ecological network literature. 
-In the second set of models, we use an *informed* version of the normalised degree in which the number of possible partners is defined by the number of species in the community with which the focal species is known to interact in any other location in our dataset.
-Measuring the size of the Eltonian niche using the informed version of normalised degree is a particularly stringent test of the effect of environmental suitability as for many species populations in our dataset, the number of possible interacting species is the same or very similar to the number of species it actually interacts with.
+We then used a set of bayesian multilevel models to evaluate the impact of environmental suitability on the size of the realised Eltonian trophic niche. 
+We measure the size of the Eltonian niche using the normalised degree of species, this is, the number of species it interacts with given the number of species in the opposite guild [@martin_gonzalez_centrality_2010].
+Normalised degree was modelled using a logit link function and a binomial distribution in which the number of species interacts with is the number of successes and the number of species in the opposite guild is the number of trials.
+We are aware that wether species intreacts or not is not a bernoulli process as species interactions are not strictly independent from each other, however a binomial distribution allow us to indirectly account for the differences in species richness across communities.
+Importantly, however, results are qualitatively the similar when we model species degree directly using a Poisson distribution and a logarithmic link function (Supp info).
 
-In all models normalised degree was modelled using a logit link function and a binomial distribution in which the number of species interacts with is the number of successes and the number of possible partners is the number of trials.
-We are aware that wether species intreacts or not is not a bernoulli process as species interactions are not independent from each other, however a binomial distribution allow us to indirectly account for the differences in species richness across communities.
-Importantly, results are qualitatively the similar when we model species degree directly using a Poisson distribution and a logarithmic link function and include the number of possible partners as predictors (Supp info).
-
-Within each model set we evaluate four candidate models in order to evaluate the relative importance of suitability. 
+Within each model set we evaluate four models in order to evaluate the relative importance of suitability. 
 A first model, our baseline model, included four population-level predictors and two grouping levels, species and the community. 
-The population-level predictors, commonly called fixed effects, were the environmental suitability, the species guild, the species generalism, and it's environmental niche breadth.
-The environmental suitability of the species in that particular community, is an index defined betwen zero and one in which a value of zero indicates that the species has never been observed in this environment while a value of one indicates that the species is most commonly observed in that environment.
-We were particularly intrested on understanding wether the effect of species suitability is conditional on the species guild (plant or pollinator), we therefore included guild and its interaction with suitability in the model.
-To estimate a species overal level of generalism we included among the predictors the magnitude of the total number of interacting species across communities in our dataset. 
-We included the number of communities where the species was present as a rough estimate of a species environmental niche breadth. 
-We allowed the intercept of degree and slope of the suitability-degree relationship to vary among species, this allowed us to investigate the extent to which suitability is a population or a group level effect.
-Finally, to account for unmeasured differences between communities, like sampling effort, sampling method, or diversity, we calculated an intercept for each community in our study.
-
-The second, third, and fourth models within each model set were a reduction of the first. 
-In the second model we removed the species generalism as a predictor, in the third, we removed the environmental niche breadth, and in the fourth model we removed excluded the effect of environmental suitability (both at the population and the species level).
+The population-level predictors in the baseline model, commonly called fixed effects, were the habitat suitability, the species guild (whether it was a plant or a pollinator), a metric of the species generalism, and its number of known possible partners.
+We included the overall level of generalism as one would expect species with a large number of interactions globally to be more likely to interact with a large number of species locally. 
+Specifically, we estimated a species overal level of generalism as the total number of interacting species across communities in our dataset. 
+We also included the number of known possible partners as a predictor in our models as it allow us to control for the environmental effects on species co-occurrence. 
+We calculate the number of possible partners by determining the number of species in a community with which the species is known to interact in any other location in our dataset. 
+Controlling for the number of potential partners makes our model a particularly stringent test of our environemntal stress hypotheses as this number is often the same, or very close, to the number of actual partners, particularly for species in a small number of communities or with a small number of interactions.
+As we were particularly intrested on understanding wether the effect of habitat suitability is conditional on the species guild (plant or pollinator), we therefore included guild and its interaction with suitability in the model.
+We allowed the intercept of degree and slope of the suitability-degree relationship to vary among species, this allowed us to investigate two questions. 
+First, it allow us to inspect the extent to which suitability is a population or a group level effect. 
+Second, by investigating the correlation between the intercept and the slope as a model parameter it allowed us to inspect the extent by which species with a small or large number of interactions respond to increassing levels of environmental stress.
+To account for unmeasured differences between communities, like sampling effort, sampling method, or diversity, we calculated an intercept for each community in our study.
 To facilitate model interpretation and convergence, we scaled all continuous variables to have a mean of zero and a unit standard deviation.
 
+We compare this baseline model with three alternative models in which we remove one predictor at a time.
+To quantify the difference between models, in terms of their expected out-of-sample performance, we use the Wanatabe-Akaike information criterion (WAIC). 
 All models were fitted under a bayesian framework using the R package `brms` `r as.character(packageVersion('brms'))` [@burkner_brms_2017; @burkner_advanced_2018] as an interface for Stan [@carpenter_stan_2017].
-All models were fitted using four Markov chains of 4,000 iterations each; half of the iterations were used for warmup.
+For each model we used four Markov chains of 4,000 iterations each; half of the iterations were used for warmup.
 We used weakly informative priors for all model parameters. 
 Specifically we used normal priors of mean zero and standard deviation ten for the population level effects and the intercepts, a half-Cauchy prior with a location of zero and a scale of two for the standard deviations, and, when applicable, an LKJ-correlation prior with parameter \(\zeta = 1\) for the correlation matrix between group-level parameters.
-To minimise the potential effect of influential observations we used leave-one-out cross-valiadtion to estimate their expected log predictive density and compare the out-of sample performance of the different models.
-We also calculate the Wanatabe-Akaike information criterion (WAIC) for comparison.
 

### 2019-09-09 paper/manuscript.Rmd
Spellcheck methods

@@
 Our next step was to determine the habitat suitability of the species as a proxy of the environmental stress they experience in their community.
-As our aim is to compare the throphic niche for different suitability levels, we only do this for species that were present in at least `r numbers2words(readd(minimum_spp_locations))` communities.
-To calculate the suitability of a species in a particular location, we used a (grinellian) niche-factor analysis [@hirzel_ecological-niche_2002; @broennimann_measuring_2012]. 
-This approach is based on the probabiliy density function of a species distribution in an environmental variable space. 
-In a nutshell, habitats (characterised by a collection of environmental variables) in which the species ocurrs most often are deemed to be suitable for the species than habitats in which the species has never been observed.
-This approach to estimate the habitat suitability requires to key pieces of information. 
-First we require information about the occurrences of the species of interest.
-Second we require information about the environmental conditions for all the locations in which the species occurs.
+As we aim to compare the trophic niche for different suitability levels, we only do this for species that were present in at least `r numbers2words(readd(minimum_spp_locations))` communities.
+To calculate the suitability of a species in a particular location, we used a (Grinellian) niche-factor analysis [@hirzel_ecological-niche_2002; @broennimann_measuring_2012]. 
+This approach is based on the probability density function of species distribution in an environmental variable space. 
+In a nutshell, habitats (characterised by a collection of environmental variables) in which the species occurs most often are deemed to be suitable for the species than habitats in which the species has never been observed.
+This approach to estimating the habitat suitability requires two critical pieces of information. 
+First, we require information about the occurrences of the species of interest.
+Second, we require information about the environmental conditions for all the locations in which the species occurs.
 
@@
 Roughly, we downloaded `r round(sum(n_occurrences$N)/1000000, digits = 1)` million occurrences for the `r format(n_species_with_occurrences, big.mark = ",")` species we were interested on. 
-This occurrences however, contain observations of mixed quality. 
+This occurrences, however, contain observations of mixed quality. 
 Therefore, we followed (ref?) and applied a series of simple filters and geographic heuristics to remove those of lower quality. 
-\R{rationale-occurrence-filtering}Specifically, we removed all occurrences with (*i*) a coordinate uncertainity larger than 100km; (*ii*) those recorded prior to 1945 (ref?
-or why?); (*iii*) those in which the number of individuals recorded was either zero or more than 100 as such large counts are often erroneous (ref?
+\R{rationale-occurrence-filtering}Specifically, we removed all occurrences with (*i*) a coordinate uncertainty larger than 100km; (*ii*) those recorded prior to 1945 (ref?
+or why?); (*iii*) those in which the number of individuals registered was either zero or more than 100 as such large counts are often erroneous (ref?
 or why?); and (*iv*) those occurrences in which the "basis of record" was not a human observation or a preserved specimen (ref?
@@
 We then used the R package `CoordinateCleaner` `r as.character(packageVersion('taxize'))` [@zizka_coordinatecleaner_2019] and land mass and country data from Natural Earth (https://www.naturalearthdata.com) with a 1:10,000,000 scale to further identify and remove problematic occurrences.
-We removed occurrences in which their coordinates (*v*) fell outside the borders of the country in which they were recorded; (*vi*) those arround a the country capital or the centroid of the country and province centroids; (*vii*) those arond a biodiversity institution; and (*viii*) those located within oceans.
+We removed occurrences for which their coordinates (*v*) fell outside the borders of the country where they were recorded; (*vi*) those around a country capital or the centroid of the country and province centroids; (*vii*) those around a biodiversity institution; and (*viii*) those located within oceans.
 Thorugh this cleaning process, we removed with `r round(sum(n_dirty_occurrences$N)/1000000, digits = 1)` million occurrences distributed accross `r n_species_with_dirty_occurrences` species. 
@@
 
-We retrieved environmental data from WorldClim V2.0 which includes 19 bioclimatic variables commonly used in species distribution modelling [@fick_worldclim_2017]. 
-We then complemented data obtained from WorldClim with data from Envirem [@title_envirem_2018], which includes 16 extra bioclimatic and two topographic variables. 
-The additional set of variables from Envirem have been shown to be relevant to ecological or physiological processes and as such have the potential to improve our suitability estimation. 
+We retrieved environmental data from WorldClim V2.0, which includes 19 bioclimatic variables commonly used in species distribution modelling [@fick_worldclim_2017]. 
+We then complemented data obtained from WorldClim with data from Envirem [@title_envirem_2017], which includes 16 extra bioclimatic and two topographic variables. 
+The additional set of variables from Envirem are relevant to ecological or physiological processes and as such, have the potential to improve our suitability estimation [@title_envirem_2018]. 
 We obtained all environmental data as rasters composed by cells of 2.5 arc-minutes. 
@@
 
-After obtaining information about the species occurrence and the evironment, the next step was to merge these two datasets such that the location of each occurrence is characterized by a vector with information of our 37 bioclimatic and topographic variables.
-If a species had more than one occurrence records within one of the cells of the bioclimatic raster we only included one of the occurrence records. 
-We did this to avoid giving more weight to areas with a high number of occurrences, a common scenario in occurrrence records collected opportunistically as the ones we use here. 
+After obtaining information about species occurrence and the environment, we then merged these two datasets such that the location of each occurrence was characterised by a vector with details of our 37 bioclimatic and topographic variables.
+If a species had more than one occurrence records within one of the cells of the bioclimatic raster, we only included one of the occurrence records. 
+We did this to avoid giving more weight to areas with a high number of occurrences, a common scenario in occurrence records collected opportunistically as the ones we use here. 
 In this step we removed `r scales::percent(percent_thinned)` of the occurrences which resulted in a total of `r round(sum(n_thinned_occurrences$N)/1000000, digits = 1)` million occurrences used in our niche analysis.
 
-A common issue of terrestrial bioclimatic datasets is that the boundaries of the cells with information do not exactly match the land mass boundaries. 
+A common issue of terrestrial bioclimatic datasets is that the boundaries of the cells with information do not precisely match the landmass boundaries. 
 The result of this missmatch is that not all environmental variables was not available for `r format(complete_climate_cells[1], big.mark = ",")` of the raster cells with occurrences (`r scales::percent(complete_climate_cells[1]/sum(complete_climate_cells), accuracy = 0.1)` of the total).
-As expected, a vast majority of these problematic cells were close to the shore. 
-To address this issue, we calculated the average value of environmental variables within a `r config$climate_buffer/1000`km buffer of the center of the cell where the variable is missing, and used it to approximate the value of the variable in that cell.
-Using this procedure we were able to fill environmental variables for `r scales::percent(percent_filled_round_one, accuracy = 0.1)` of the cells were they were missing. 
+As expected, the vast majority of these problematic cells were close to the shore. 
+To address this issue, we calculated the average value of environmental variables within an `r config$climate_buffer/1000`km buffer of the centre of the cell where the variable was missing and used it to approximate the value of the variable in that cell.
+Using this procedure, we were able to fill environmental variables for `r scales::percent(percent_filled_round_one, accuracy = 0.1)` of the cells were they were missing. 
 To fill the remaining `r format(complete_filled_cells_1[1], big.mark= ",")` cells, we repeated the aforementioned procedure but instead using a `r config$climate_buffer*2/1000`km buffer. 
-We removed from further analyis occurrences located within the `r complete_filled_cells_2[1]` cells for which we were unable to fill environmental variables.
+We removed from further analysis occurrences located within the `r complete_filled_cells_2[1]` cells for which we were unable to fill environmental variables.
 
-Next, we calculate the probability density function of the species distribution in environemntal space. 
-To determine the environmental space we use the first two components from a principal component analysis of the 37 bioclimatic variables associated with the species occurrences. 
+Next, we calculate the probability density function of the species distribution in environmental space. 
+To determine the environmental space, we use the first two components from a principal component analysis of the 37 bioclimatic variables associated with the species occurrences. 
 Specifically we use the `dudi.pca` function from the R package `ade4` `r as.character(packageVersion('ade4'))` [@dray_ade4_2007] and center and scale all bioclimatic variables to have a mean of 0 and a unit standard deviation.
 We then determine the position of species occurrences in the environmental space and estimate their bivariate probability density function. 
-We use a kernel method to estimate this density and normalise it such that it ranges beetween zero and one. 
+We use a kernel method to estimate this density and normalise it such that it ranges between zero and one. 
 Specifically, to calculate the probability density function we use `ecospat.grid.clim.dyn` from the R package `ecospat` `r as.character(packageVersion('ecospat'))` [@ecospat_citation] with a grid resolution of 200.
-We then determine the location in environmental space of the plant-pollinator communities where the species is present using the function `suprow` from `ade4`.
+We then determine the location in the environmental space of the plant-pollinator communities using the function `suprow` from `ade4`.
 The normalised density at that particular location corresponds to our suitability metric, which we calculate using the R package `raster` `r as.character(packageVersion('raster'))` [@raster_citation].
-We use the kernel density method in the niche-factor analyisis [@broennimann_measuring_2012] rather than the distance from the mode [@hirzel_ecological-niche_2002], as it has been proposed earlier, as it has been shown to reduce the procedure's sensitivity to sampling effort and the resolution of the environmental space.
+We use the kernel density method in the niche-factor analysis [@broennimann_measuring_2012] rather than the distance from the mode [@hirzel_ecological-niche_2002], as it has been proposed earlier, as it has been shown to reduce the procedure's sensitivity to sampling effort and the resolution of the environmental space.
 
@@
 We measure the size of the Eltonian niche using the normalised degree of species, this is, the number of species it interacts with given the number of species in the opposite guild [@martin_gonzalez_centrality_2010].
-Normalised degree was modelled using a logit link function and a binomial distribution in which the number of species interacts with is the number of successes and the number of species in the opposite guild is the number of trials.
-We are aware that wether species intreacts or not is not a bernoulli process as species interactions are not strictly independent from each other, however a binomial distribution allow us to indirectly account for the differences in species richness across communities.
-Importantly, however, results are qualitatively the similar when we model species degree directly using a Poisson distribution and a logarithmic link function (Supp info).
+The normalised degree was modelled using a logit link function, and a binomial distribution in which the number of species interacts with is the number of successes, and the number of species in the opposite guild is the number of trials.
+We are aware that wether species interacts or not is not a Bernoulli process as species interactions are not strictly independent from each other. 
+However, a binomial distribution allows us to account for the differences in species richness across communities indirectly. 
+Importantly, however, results are qualitatively similar when we model species degree directly using a Poisson distribution and a logarithmic link function (Supp info).
 
-Within each model set we evaluate four models in order to evaluate the relative importance of suitability. 
+Within each model set, we evaluate four models to assess the relative importance of suitability. 
 A first model, our baseline model, included four population-level predictors and two grouping levels, species and the community. 
@@
 We included the overall level of generalism as one would expect species with a large number of interactions globally to be more likely to interact with a large number of species locally. 
-Specifically, we estimated a species overal level of generalism as the total number of interacting species across communities in our dataset. 
-We also included the number of known possible partners as a predictor in our models as it allow us to control for the environmental effects on species co-occurrence. 
-We calculate the number of possible partners by determining the number of species in a community with which the species is known to interact in any other location in our dataset. 
-Controlling for the number of potential partners makes our model a particularly stringent test of our environemntal stress hypotheses as this number is often the same, or very close, to the number of actual partners, particularly for species in a small number of communities or with a small number of interactions.
-As we were particularly intrested on understanding wether the effect of habitat suitability is conditional on the species guild (plant or pollinator), we therefore included guild and its interaction with suitability in the model.
+Concretely, we estimated an overall species level of generalism as the total number of interacting species across communities in our dataset. 
+We also included the number of known possible partners as a predictor in our models as it allows us to control for the environmental effects on species co-occurrence. 
+We calculate this metric by determining the number of partners with which the species is known to interact in any other community.
+Controlling for the number of potential partners makes our model a particularly stringent test of our environmental stress hypotheses. 
+Often the potential and the actual number of partners is the same or very close to each other, especially for rare species present only in a few communities.  
+As we were particularly interested in understanding whether the effect of habitat suitability is conditional on the species guild (plant or pollinator), we, therefore, included guild and its interaction with suitability in the model.
 We allowed the intercept of degree and slope of the suitability-degree relationship to vary among species, this allowed us to investigate two questions. 
-First, it allow us to inspect the extent to which suitability is a population or a group level effect. 
-Second, by investigating the correlation between the intercept and the slope as a model parameter it allowed us to inspect the extent by which species with a small or large number of interactions respond to increassing levels of environmental stress.
+First, it allows us to inspect the extent to which suitability is a population or a group level effect. 
+Second, by investigating the correlation between the intercept and the slope as a model parameter, it allowed us to inspect the extent by which species with a small or large number of interactions respond to increasing levels of environmental stress.
 To account for unmeasured differences between communities, like sampling effort, sampling method, or diversity, we calculated an intercept for each community in our study.
@@
 All models were fitted under a bayesian framework using the R package `brms` `r as.character(packageVersion('brms'))` [@burkner_brms_2017; @burkner_advanced_2018] as an interface for Stan [@carpenter_stan_2017].
-For each model we used four Markov chains of 4,000 iterations each; half of the iterations were used for warmup.
+For each model, we used four Markov chains of 4,000 iterations each; half of the iterations were used for warmup.
 We used weakly informative priors for all model parameters. 
-Specifically we used normal priors of mean zero and standard deviation ten for the population level effects and the intercepts, a half-Cauchy prior with a location of zero and a scale of two for the standard deviations, and, when applicable, an LKJ-correlation prior with parameter \(\zeta = 1\) for the correlation matrix between group-level parameters.
+Specifically we used normal priors of mean zero and standard deviation ten for the population-level effects and the intercepts, a half-Cauchy prior with a location of zero and a scale of two for the standard deviations, and, when applicable, an LKJ-correlation prior with parameter \(\zeta = 1\) for the correlation matrix between group-level parameters.
 

### 2019-09-09 paper/manuscript.Rmd
Missing paragraph break in intro
remove reference to multiple model sets

@@
 Contrastingly, other studies have shown either no effect or non-linear effects of temperature or precipitation on plant-pollinator interactions [@devoto_patterns_2005; @gravel_bringing_2018].
+
 One way to summarise the seemingly contradictory evidence of whether the environment can influence whether two species interact or not is by moving from gradients of temperature or precipitation to gradients of environmental stress.
@@
 
-Within each model set, we evaluate four models to assess the relative importance of suitability. 
-A first model, our baseline model, included four population-level predictors and two grouping levels, species and the community. 
-The population-level predictors in the baseline model, commonly called fixed effects, were the habitat suitability, the species guild (whether it was a plant or a pollinator), a metric of the species generalism, and its number of known possible partners.
+We evaluate four models to assess the relative importance of suitability. 
+A first model, our baseline model, included five population-level predictors and two grouping levels, species and the community. 
+The population-level predictors in the baseline model, commonly called fixed effects, were the habitat suitability, the species guild (plant or a pollinator), a metric of the species generalism, and its number of known possible partners.
 We included the overall level of generalism as one would expect species with a large number of interactions globally to be more likely to interact with a large number of species locally. 
@@
 
-We compare this baseline model with three alternative models in which we remove one predictor at a time.
+We compared this baseline model with three alternative models in which we remove one predictor at a time.
 To quantify the difference between models, in terms of their expected out-of-sample performance, we use the Wanatabe-Akaike information criterion (WAIC). 

### 2019-09-11 paper/manuscript.Rmd
Add some ideas to discussion

@@
 
+* Summarise results
+* We cannot completely distinguish between the effect on the environment on the niche itself or on neutral processes
+* The environment can certainly influence the number of interactions but its very variable among species
+* We don't know wether specialists are also constrained to interact with species they like because our dataset is biased for species that are there.
+This is we are only observing those specialist that survive the lack of interaction partners
+* It was clear that the compositional effect on communities is very strong and is really the determining factor at large.
+The environment only a fraction.
+However we differ that the way the rest happens is not stochastic but might be driven but driven of how environment mediates eco-evolutionary processes.
+* In the absence of abundance this is as much as we can say. 
+* It is remarkable we found a signal given the amount of data we had it is realy not that much for our question.
+It is not surprising that the slope of suitability was small for many species as we had little data.
+The results hold for when species had
+* The interaction between slope suitability was not related to guild.
+Emphasizes the relevance of eco-evolutionary processes for both guilds.
+If other factors like for example behaviour could explain that, we would expect markedly different outcomes for plants and pollinators.
+* Implications for community assembly and network rewiring.
+
 <!-- We found a positive association between environmental suitability and the niche breath. 

### 2019-09-11 paper/manuscript.Rmd
first paragraph of the discussion

@@
 
+We found that environemntal stress, which we meassured using habitat suitability, was a very importat predictor for the number of partners a species interacts with. 
+However, this relationship was highly variable among species. 
+So much so that, at the population level, there is no discernable pattern between stress and the number of interacting species.
+Interestingly, within species, there was a significant coorelaton between the number of partners a species has and the stress-partners relationship itself. 
+Specifically, species with a large number of partners in low-stress communities, were more likely to have a negative relatiosnship and hence reduce the number of partners as stress increasses. 
+Contrastingly, species in our datasets with a small number of parters in low-stress communities were more likely to have a larger number of partners in more stressful communities.
+
 * Summarise results

### 2019-09-12 paper/manuscript.Rmd
Add second paragraph of the discussion

@@
 
-* Summarise results
+Previous research supported the idea that the differences in network structure along an environmental gradient were due solely to changes to community composition. 
+In other words, it showed that the differences between two hypothetical communities with the same species were stochastic for the most part. 
+Here, by abstracting with multiple environmental gradients into a single gradient of environmental stress, we show that this might not be the case. 
+Instead, the environment can also have a direct impact on the number of partners a species interacts with and, therefore, influence network structure. 
+Our results still show that the primary channel through which environment affects interaction probabilities is determining which species are present or absent froma particular community. 
+However they also show that, for a large number of species, it can have an important effect on their realised Eltonian component of the niche.
+Indeed, as evidenced by the predictive power of competing models, habitat suitability had a substantial contribution to predicting the number of possible partners in the community.
+
+Previous We found that
+
+* Why is the relationship different across species?
+* Why is there no difference between plants and pollinators?
+* Why is there a correlation between the intercept and the slope?
+
 * We cannot completely distinguish between the effect on the environment on the niche itself or on neutral processes

### 2019-09-12 code/figures.R
trying to make new plot look ok, still have work to do

@@ -282,9 +282,13 @@ plot_ranf <- function(random_species_draws, random_correlation_posterior, random
           axis.line.x.bottom = element_line()) +
     labs(title = "(b) correlation between random intercept and slope")
 
-  slope_intercept_plot <- random_slope_intercepts %>%
-    ggplot(mapping = aes(x = Intercept_Estimate, y = scaled_suitability_Estimate)) +
-    geom_point() +
+  slope_intercept_plot <- random_species_draws %>%
+    dplyr::select(org_id, guild) %>%
+    dplyr::inner_join(random_slope_intercepts) %>%
+    ggplot(mapping = aes(colour = guild,
+                         x = Intercept_Estimate,
+                         y = scaled_suitability_Estimate)) +
+    geom_point(shape = 21, stroke = 0.25, size = 1) +
     geom_errorbar(mapping = aes(ymin = scaled_suitability_Q25,
                                 ymax = scaled_suitability_Q75),
                   size = 0.15, alpha = 0.25) +
@@ -294,14 +298,16 @@ plot_ranf <- function(random_species_draws, random_correlation_posterior, random
     geom_hline(yintercept = 0, linetype = 2, size = 0.25) +
     geom_vline(xintercept = 0, linetype = 2, size = 0.25) +
     pub_theme()
-
-  p <- cowplot::plot_grid(conditional_effects_plot,
-                          correlation_plot,
-                          slope_intercept_plot,
-                          ncol = 1 ,
-                          rel_heights = c(2,0.5, 1),
-                          align = "v")
-  # ggsave("plot.pdf", p, width = unit(width("single"), "in"), height = unit(2.2*2.5, "in"))
+  plot_left <- conditional_effects_plot
+  plot_right <- cowplot::plot_grid(slope_intercept_plot,
+                                   correlation_plot,
+                                   ncol = 1,
+                                   rel_heights = c(2, 1),
+                                   align = "v")
+  p <- cowplot::plot_grid(plot_left,
+                          plot_right,
+                          ncol = 2)
+  ggsave("plot.pdf", p, width = unit(width("double"), "in"), height = unit(2.2*2.5, "in"))
 
   p
 }

### 2019-09-12 code/plotting-and-formatting.R
Made facet titles a bit larger

@@ -7,7 +7,7 @@ pub_theme <- function(){
           plot.subtitle = element_text(size = 7),
           plot.tag = element_text(size = 7),
           strip.background = element_blank(),
-          strip.text = element_text(hjust = 0),
+          strip.text = element_text(hjust = 0, size = 7),
           legend.title = element_text(hjust = 0.5),
           legend.key.size = unit(3, "mm"),
           legend.margin = margin(),

### 2019-09-12 code/plotting-and-formatting.R
remove trailing whitespace from plotting and formatting script

@@ -66,9 +66,9 @@ numbers2words <- function(x){
   ## Function by John Fox found here:
   ## http://tolstoy.newcastle.edu.au/R/help/05/04/2715.html
   ## Tweaks by AJH to add commas and "and"
-  
+
   helper <- function(x){
-    
+
     digits <- rev(strsplit(as.character(x), "")[[1]])
     nDigits <- length(digits)
     if (nDigits == 1) as.vector(ones[digits])
@@ -115,24 +115,24 @@ numbers2words <- function(x){
 }
 
 translate_model_formula <- function(x, type = "short"){
-  
+
   if(type == "long-initial"){
     dplyr::case_when(
-      x == "formula_base" ~ "baseline: S + G + P + E", 
+      x == "formula_base" ~ "baseline: S + G + P + E",
       x == "formula_no_grinell_niche_size" ~ "S + G + P",
-      x == "formula_no_generalism" ~ "S + P + E", 
-      x == "formula_no_suitability" ~ "G + P + E", 
-      x == "formula_no_possible_partners_generalism" ~ "S + E", 
+      x == "formula_no_generalism" ~ "S + P + E",
+      x == "formula_no_suitability" ~ "G + P + E",
+      x == "formula_no_possible_partners_generalism" ~ "S + E",
       x == "formula_no_possible_partners" ~ "S + G + E",
       TRUE ~ "unknown"
-    ) 
+    )
   } else if(type == "long-abv"){
     dplyr::case_when(
-      x == "formula_base" ~ "Suit. + Gen. + Pot. + Env.", 
+      x == "formula_base" ~ "Suit. + Gen. + Pot. + Env.",
       x == "formula_no_grinell_niche_size" ~ "Suit. + Gen. + Pot.",
-      x == "formula_no_generalism" ~ "Suit. + Pot. + Env.", 
-      x == "formula_no_suitability" ~ "Gen. + Pot. + Env.", 
-      x == "formula_no_possible_partners_generalism" ~ "Suit. + Env.", 
+      x == "formula_no_generalism" ~ "Suit. + Pot. + Env.",
+      x == "formula_no_suitability" ~ "Gen. + Pot. + Env.",
+      x == "formula_no_possible_partners_generalism" ~ "Suit. + Env.",
       x == "formula_no_possible_partners" ~ "Suit. + Gen. + Env.",
       TRUE ~ "unknown"
     )
[…]

### 2019-09-12 paper/manuscript.Rmd
Some more sentences to discussion
Make random parameters figures two column wide

@@
 
-```{r fig-random-effects, fig.width = width('single'), fig.height = 2.2*2.5, fig.cap = fig_random_effects_legend}
+```{r fig-random-effects, fig.width = width('double'), fig.height = 2.2*2, fig.cap = fig_random_effects_legend}
 loadd(random_species_draws)
@@
 Indeed, as evidenced by the predictive power of competing models, habitat suitability had a substantial contribution to predicting the number of possible partners in the community.
+
+The significant relationship between the number of partners a species has in a hypothetical community with no environmental stress and the slope
+
+* Add in the intro that stress includes how traits mediate environment?
 

### 2019-09-13 code/figures.R
fix error, needed to load ggplot before making the plot

@@ -342,6 +342,11 @@ plot_ranf <- function(random_species_draws, random_correlation_posterior, random
 }
 
 plot_suitability <- function(suitability_distribution){
+
+  suppressPackageStartupMessages({
+    require(ggplot2)
+  })
+
   p <- suitability_distribution %>%
     ggplot(aes(x = median_suitability, y = loc_id)) +
     geom_point(size = 0.5, stroke = 0.25, colour = cgm()$pal_el_green[9]) +

### 2019-09-13 paper/manuscript.Rmd
Fix legend for random plot so that it shows number of species included in the plot a
add median suitability per community figure to manuscript

@@
 We therefore removed from further analyses `r n_spp_not_enough_occ` species for which we did not have enough occurrences to obtain robust estimates.
+When inspecting the suitability values of the analysed species we found that some communitues have larger overal suitability values. 
+However, most communities included species for which habitat suitability was low and species for which it was high (Fig. \@ref(fig:fig-median-suitability)).
 
@@
 readd(fig_sensitivity_analysis)
+```
+
+```{r fig-median-suitability, fig.width = width('single'), fig.height = 2.2*1.5, fig.cap = "Median habitat suitability of communities in our dataset.
+Each row represents a different community and horizontal lines represent span the 2.5 and 97.5 quantiles."}
+readd(fig_median_suitability)
 ```
@@
 n_random_pla <- n_random_species %>%
-  dplyr::filter(guild == "pla_id")
+  dplyr::filter(guild == "pla_id") %$%
+  n_sp
 
 n_random_ani <- n_random_species %>%
-  dplyr::filter(guild == "ani_id")
+  dplyr::filter(guild == "ani_id") %$%
+  n_sp
 

### 2019-09-13 paper/manuscript.Rmd
add third paragraph for the discussion

@@
 
+Although, we cannot tell with certainty how much of the effect of environmental stress is can be attributed to either niche or neutral processes it is likely that the patterns we observe are more related to the niche.
+In the one hand, it has been shown that environmental models, such as our niche factor analysis, do a poor job predicting species abundances across sites [@pearce_practical_2001; @sagarin_moving_2006].
+It would be, therefore, somewhat naive to assume that a high habitat suitability translates directly to high species abundances. 
+On the other hand, even if species abunances are correlated with suitability, we show that within a community there is a wide range of suitabilities, even for the limmited number of species we included in our analyses.
+Therefore, we might expect little or no overall effect of neutral processes on our response variable, as the abundance of some interaction partners might increasse and decreasse for others.
+
 The significant relationship between the number of partners a species has in a hypothetical community with no environmental stress and the slope
@@
 
-<!-- Suitability is not a meric of abbundances across sites (Pearce & Ferrier 2001; Sagarin et al. 2006) (Taken from Boulangeat) -->
-
 <!-- Remarkable that we found a consistent signal of suitability given our relatively small number of communities and the multitude of processes that shape n.

### 2019-09-13 paper/manuscript.Rmd
Fix size of double column figure

@@
 
-```{r fig-random-effects, fig.width = width('double'), fig.height = 2.2*2, fig.cap = fig_random_effects_legend}
+```{r fig-random-effects, fig.width = width('double'), fig.height = 2.2*2, fig.cap = fig_random_effects_legend, out.width = "6.81in", out.height = "4.4in", out.extra="center"}
 loadd(random_species_draws)

### 2019-09-13 paper/manuscript.Rmd
Fourth paragraph of the intro (which is now the third)

@@
 For two species to interact, they first need to co-occur in the same community, which can only happen if the environmental conditions of the community fall within the Grinellian niche of both species.
+
 Although less understood, the environment can also affect the interactions themselves, after community composition has been established [@tylianakis_ecological_2017]. 
@@
 Similarly, @lavandero_genotype_2013 found that environmental stress due to higher temperature reduced the breadth of the Eltonian niche of parasitoids.
-On the other, it is also possible that when species are under environmental stress, they are forced to be more flexible in their interactions as higher environmental stress is likely to be reflected in greater energetic or reproductive costs and therefore they might not be able to sustain encounter rates with their preferred partners at sufficient levels.
+
+On the other hand, it is also possible that when species are under environmental stress, they are forced to be more flexible in their interactions as higher environmental stress is likely to be reflected in greater energetic or reproductive costs and therefore they might not be able to sustain encounter rates with their preferred partners at sufficient levels.
 In line with this hypothesis, @hoiss_interactive_2015 found that the specialisation of plant-pollinator networks decreased both with elevation and after extreme drought events.
@@
 
+One of our most interesting results was the negative correlation between the species' intercept and the slope of the habitat suitability in our model.
+Specifically, species with a small intercept, this is, species that were likely to have an above-average number of partners in a community with little environemntal stress, were more likely to interact with a smaller number of partners as stress increassed.
+At least for these species, the hypothesis that species focus on partners with which they are best adapted to interact as environmental conditions deteriorates seems to hold weight.
+Contrastingly, species with a below-average number of partners in a low stress environment were more likely to interact with a large number of partners as stress increassed.
+At first glance, these species behave as facultative generalists when the environment worsens. 
+This is certainly true for this group of species in our dataset.
+However, there are some nuances to this observation once we take into account the biases inherent to community level interaction data. 
+Specifically, we have no information about species for which environmental conditions would, in principle, allow for a positive growth rate but are absent from our datasets.
+A ramification of this bias is that an undertermined number of species on this second group might also be more likely to focus on partners with higher trait matching as conditions deteriorate, but we are not able to detect that trend because these species are not recoded in community composition or interaction data.
+Presumably because their preferred partners are unavailable and as such they areabsent from the community or too rare to be observed.
+Note that the coorelation between species' intercept and slope is unlikely to be just a byproduct of our modelling framework, as, in principle, there is nothing preventing species with an above-average number of partners to interact with even more species as environmental stress increasses.
+
 Although, we cannot tell with certainty how much of the effect of environmental stress is can be attributed to either niche or neutral processes it is likely that the patterns we observe are more related to the niche.
@@
 Therefore, we might expect little or no overall effect of neutral processes on our response variable, as the abundance of some interaction partners might increasse and decreasse for others.  
-
-The significant relationship between the number of partners a species has in a hypothetical community with no environmental stress and the slope
+Furthermore, the fact that the effects of environemtal stress do not depend on wether the species is a plant or a pollinator (for which there can be niche differences based on individual behaviour) emphasises that niche processes driven by co-evolutionary history might be driving the patterns we observe.
 
 * Add in the intro that stress includes how traits mediate environment?
-
-Previous We found that
-
 * Why is the relationship different across species?
@@
 * Why is there a correlation between the intercept and the slope?
-
-* We cannot completely distinguish between the effect on the environment on the niche itself or on neutral processes
 * The environment can certainly influence the number of interactions but its very variable among species
-* We don't know wether specialists are also constrained to interact with species they like because our dataset is biased for species that are there.
-This is we are only observing those specialist that survive the lack of interaction partners
-* It was clear that the compositional effect on communities is very strong and is really the determining factor at large.
-The environment only a fraction.
-However we differ that the way the rest happens is not stochastic but might be driven but driven of how environment mediates eco-evolutionary processes.
 * In the absence of abundance this is as much as we can say. 
@@
 The results hold for when species had
-* The interaction between slope suitability was not related to guild.
-Emphasizes the relevance of eco-evolutionary processes for both guilds.
-If other factors like for example behaviour could explain that, we would expect markedly different outcomes for plants and pollinators.
 * Implications for community assembly and network rewiring.

### 2019-09-13 paper/draft-info.Rmd
add extra comments to request co-author feedback in draft info

@@
 Currently working with 2.5' (~5km).
-Increasing to 30'' (~1km) might improve the analysis but we're talking about working with ~25GB+ of data instead of the 1GB used now.
+Increasing to 30'' (~1km) might improve the analysis but we're talking about working with ~25GB+ of climatic data instead of the 1GB used now.
+Unsure the benefits would outweight the costs.
 * Audrey: Could you please fill in the gaps in the rationale behind filtering out occurrences with potential low quality coordinates (\lr{rationale-occurrence-filtering})
 * I chose, rather arbitrarily, a mean absolute error of 10% for the sensitivity analysis. Does this choice sound appropiate to you?
+* Should I remove the species overall generalism and the size of the grinellian niche from the model to simplify things.
+Both contribute little to the model and the story.
+For the former, seems to be redundant once the number of possible interacting species has been included in the model.
+For the later, there is little biological reasons (what I could gather from the lit.) to justify their inclussion in the model.
+What you think?
+If not, at the very least I think I would move panels a and c in Fig.
+5 to the supplementary info.
 

### 2019-09-13 paper/manuscript.Rmd
Remove fake line break from discussion
Add raster and envirem references

@@
 We use a kernel method to estimate this density and normalise it such that it ranges between zero and one. 
-Specifically, to calculate the probability density function we use `ecospat.grid.clim.dyn` from the R package `ecospat` `r as.character(packageVersion('ecospat'))` [@ecospat_citation] with a grid resolution of 200.
+Specifically, to calculate the probability density function we use `ecospat.grid.clim.dyn` from the R package `ecospat` `r as.character(packageVersion('ecospat'))` [@broennimann_ecospat_2018] with a grid resolution of 200.
 We then determine the location in the environmental space of the plant-pollinator communities using the function `suprow` from `ade4`.
-The normalised density at that particular location corresponds to our suitability metric, which we calculate using the R package `raster` `r as.character(packageVersion('raster'))` [@raster_citation].
+The normalised density at that particular location corresponds to our suitability metric, which we calculate using the R package `raster` `r as.character(packageVersion('raster'))` [@hijmans_raster_2019].
 We use the kernel density method in the niche-factor analysis [@broennimann_measuring_2012] rather than the distance from the mode [@hirzel_ecological-niche_2002], as it has been proposed earlier, as it has been shown to reduce the procedure's sensitivity to sampling effort and the resolution of the environmental space.

### 2019-09-14 paper/manuscript.Rmd
Another paragraph to the discussion

@@
 
+Although, we cannot tell with certainty how much of the effect of environmental stress is can be attributed to either niche or neutral processes it is likely that the patterns we observe are more related to the niche.
+In the one hand, it has been shown that environmental models, such as our niche factor analysis, do a poor job predicting species abundances across sites [@pearce_practical_2001; @sagarin_moving_2006].
+It would be, therefore, somewhat naive to assume that a high habitat suitability translates directly to high species abundances. 
+On the other hand, even if species abunances are correlated with suitability, we show that within a community there is a wide range of suitabilities, even for the limmited number of species we included in our analyses.
+Therefore, we might expect little or no overall effect of neutral processes on our response variable, as the abundance of some interaction partners might increasse and decreasse for others. 
+Furthermore, the fact that the effects of environemtal stress do not depend on wether the species is a plant or a pollinator (for which there can be niche differences based on individual behaviour) emphasises that niche processes driven by co-evolutionary history might be driving the patterns we observe.
+
 One of our most interesting results was the negative correlation between the species' intercept and the slope of the habitat suitability in our model.
@@
 
-Although, we cannot tell with certainty how much of the effect of environmental stress is can be attributed to either niche or neutral processes it is likely that the patterns we observe are more related to the niche.
-In the one hand, it has been shown that environmental models, such as our niche factor analysis, do a poor job predicting species abundances across sites [@pearce_practical_2001; @sagarin_moving_2006].
-It would be, therefore, somewhat naive to assume that a high habitat suitability translates directly to high species abundances. 
-On the other hand, even if species abunances are correlated with suitability, we show that within a community there is a wide range of suitabilities, even for the limmited number of species we included in our analyses.
-Therefore, we might expect little or no overall effect of neutral processes on our response variable, as the abundance of some interaction partners might increasse and decreasse for others. 
-Furthermore, the fact that the effects of environemtal stress do not depend on wether the species is a plant or a pollinator (for which there can be niche differences based on individual behaviour) emphasises that niche processes driven by co-evolutionary history might be driving the patterns we observe.
+These observations have implications for understanding the assembly of ecological networks and how it might be impacted by climate change, which currentlt threatens to increasse the environmental stress of species within its range.
+Previous research suggests that flexibility of interactions in ecological communities might be a rather ubiquitous phenomenon whenever environemntal conditions change in space or time [@caradonna_interaction_2017].
+This flexibility has been shown to confer robustness and stability to the loss of interaction partners [@kaiser-bunbury_robustness_2010]. 
+The current paradigm of interaction turnover suggest first that trait matching is a relatively unimportant driver of interaction turnover for generalist species [@caradonna_interaction_2017]. 
+The fact that species with a high number of interactions were more likely to interact with less species as environmental stress increassed indicates that trait matching might still play a role at determining the interactions of generalist species.
+Second, current research suggests that the rewiring of the interaction network is primarly driven by generalist species [@burkle_plant-pollinator_2013].
+We, however, demonstrate that at least a fraction of the species that appear to be specialist in their communities might be more flexible, if not more, than generalist species and, therefore, might a larger role in network persistence than previously expected.
+Contrastingly, specialists that are highly constrained to interact with partners of high trait-matching might be more vulnerable to increassed climate change induced environmental stress and habitat degradation.
+Taken together, the fact that most species appear to be flexible interaction partners, combined with the fact that those that are not flexible are less likely to persist, might expain why specialised communities that are highly constrained by trait matching [like some plant-humingbird networks; @vizentin-bugoni_processes_2014; @maruyama_morphological_2014] might be relatively rare.
+
+In conclusion, we show that
+
+It still remains to evaluate the role of abundance and neutral processes and
 
@@
 * Why is the relationship different across species?
-* Why is there no difference between plants and pollinators?
-* Why is there a correlation between the intercept and the slope?
 * The environment can certainly influence the number of interactions but its very variable among species

### 2019-09-14 paper/manuscript.Rmd
comment out extra text
add some more refs to the discussion
spellcheck discussion

--- 2019-09-13 paper/manuscript.Rmd
@@
 
-We found that environemntal stress, which we meassured using habitat suitability, was a very importat predictor for the number of partners a species interacts with. 
+We found that environmental stress, which we measured using habitat suitability, was an important predictor for the number of partners a species interacts with. 
 However, this relationship was highly variable among species. 
-So much so that, at the population level, there is no discernable pattern between stress and the number of interacting species.
-Interestingly, within species, there was a significant coorelaton between the number of partners a species has and the stress-partners relationship itself. 
-Specifically, species with a large number of partners in low-stress communities, were more likely to have a negative relatiosnship and hence reduce the number of partners as stress increasses. 
-Contrastingly, species in our datasets with a small number of parters in low-stress communities were more likely to have a larger number of partners in more stressful communities.
+So much so that, at the population level, there is no discernible pattern between stress and the number of partners.
+Interestingly, within species, there was a significant correlation between the number of partners a species has and the stress-partners relationship itself. 
+Specifically, species with a large number of partners in low-stress communities were more likely to have a negative relationship and hence reduce the number of partners as stress increases. 
+Contrastingly, species in our datasets with a small number of partners in low-stress communities were more likely to have a larger number of partners in more stressful communities.
 
@@
 Instead, the environment can also have a direct impact on the number of partners a species interacts with and, therefore, influence network structure. 
-Our results still show that the primary channel through which environment affects interaction probabilities is determining which species are present or absent froma particular community. 
-However they also show that, for a large number of species, it can have an important effect on their realised Eltonian component of the niche.
+Our results still show that the primary channel through which environment affects interaction probabilities is determining which species are present or absent from a particular community. 
+However, they also show that, for a large number of species, it can have a substantial effect on their realised Eltonian component of the niche.
 Indeed, as evidenced by the predictive power of competing models, habitat suitability had a substantial contribution to predicting the number of possible partners in the community.
 
+Although we cannot tell with certainty how much of the effect of environmental stress can be attributed to either niche or neutral processes, the patterns we observe are likely more related to the niche.
+On the one hand, it has been shown that environmental models, such as our niche factor analysis, do a poor job predicting species abundances across sites [@pearce_practical_2001; @sagarin_moving_2006].
+It would be, therefore, somewhat naive to assume that high habitat suitability translates directly to high species abundances. 
+On the other hand, even if species abundances are correlated with suitability, we show that within a community there is a wide range of suitabilities, even for the limited number of species we included in our analyses.
+Therefore, we might expect little or no overall effect of neutral processes on our response variable, as the abundance of some interaction partners might increase and decrease for others. 
+Furthermore, the fact that the effects of environmental stress do not depend on whether the species is a plant or a pollinator (for which there can be niche differences based on individual behaviour) emphasises that co-evolutionary history, which in turn shape niche processes driven by, might be driving the patterns we observe.
+
 One of our most interesting results was the negative correlation between the species' intercept and the slope of the habitat suitability in our model.
-Specifically, species with a small intercept, this is, species that were likely to have an above-average number of partners in a community with little environemntal stress, were more likely to interact with a smaller number of partners as stress increassed.
-At least for these species, the hypothesis that species focus on partners with which they are best adapted to interact as environmental conditions deteriorates seems to hold weight.
-Contrastingly, species with a below-average number of partners in a low stress environment were more likely to interact with a large number of partners as stress increassed.
+Specifically, species with a small intercept, this is, species that were likely to have an above-average number of partners in a community with little environmental stress, were more likely to interact with a smaller number of partners as stress increased.
+At least for these species, the hypothesis that species focus on partners with which they are best adapted to interact as environmental conditions deteriorate seems to hold weight.
+Contrastingly, species with a below-average number of partners in a low-stress environment were more likely to interact with a large number of partners as stress increased.
 At first glance, these species behave as facultative generalists when the environment worsens. 
 This is certainly true for this group of species in our dataset.
-However, there are some nuances to this observation once we take into account the biases inherent to community level interaction data. 
+However, there are some nuances to this observation once we take into account the biases inherent to community-level interaction data. 
 Specifically, we have no information about species for which environmental conditions would, in principle, allow for a positive growth rate but are absent from our datasets.
-A ramification of this bias is that an undertermined number of species on this second group might also be more likely to focus on partners with higher trait matching as conditions deteriorate, but we are not able to detect that trend because these species are not recoded in community composition or interaction data.
-Presumably because their preferred partners are unavailable and as such they areabsent from the community or too rare to be observed.
-Note that the coorelation between species' intercept and slope is unlikely to be just a byproduct of our modelling framework, as, in principle, there is nothing preventing species with an above-average number of partners to interact with even more species as environmental stress increasses.
+A ramification of this bias is that an undetermined number of species on this second group might also be more likely to focus on partners with higher trait matching as conditions deteriorate. 
+However, we are not able to detect that trend because these species are not recorded in community composition or interaction data. 
+Presumably, because their preferred partners are unavailable and as such, they are absent from the community or too rare to be observed.
+Note that the correlation between species' intercept and the slope is unlikely to be just a byproduct of our modelling framework, as, in principle, there is nothing preventing species with an above-average number of partners to interact with even more species as environmental stress increases.
 
-Although, we cannot tell with certainty how much of the effect of environmental stress is can be attributed to either niche or neutral processes it is likely that the patterns we observe are more related to the niche.
-In the one hand, it has been shown that environmental models, such as our niche factor analysis, do a poor job predicting species abundances across sites [@pearce_practical_2001; @sagarin_moving_2006].
-It would be, therefore, somewhat naive to assume that a high habitat suitability translates directly to high species abundances. 
-On the other hand, even if species abunances are correlated with suitability, we show that within a community there is a wide range of suitabilities, even for the limmited number of species we included in our analyses.
-Therefore, we might expect little or no overall effect of neutral processes on our response variable, as the abundance of some interaction partners might increasse and decreasse for others. 
-Furthermore, the fact that the effects of environemtal stress do not depend on wether the species is a plant or a pollinator (for which there can be niche differences based on individual behaviour) emphasises that niche processes driven by co-evolutionary history might be driving the patterns we observe.
+These observations have implications for understanding the assembly of ecological networks and how it might be impacted by climate change, which currently threatens to increase the environmental stress of species within its range.
+Previous research suggests that flexibility of interactions in ecological communities might be a rather ubiquitous phenomenon whenever environmental conditions change in space or time [@caradonna_interaction_2017].
+This flexibility has been shown to confer robustness and stability to the loss of interaction partners [@kaiser-bunbury_robustness_2010]. 
+The current paradigm of interaction turnover suggests first that trait matching is a relatively unimportant driver of interaction turnover for generalist species [@caradonna_interaction_2017]. 
+The fact that species with a high number of interactions were more likely to interact with fewer species as environmental stress increased indicates that trait matching might still play a role in determining the interactions of generalist species.
+Second, current research suggests that the rewiring of the interaction network is primarily driven by generalist species [@burkle_plant-pollinator_2013].
+We, however, demonstrate that at least a fraction of the species that appear to be specialist in their communities might be more flexible, if not more, than generalist species and, therefore, might have a more significant role in network persistence than previously expected.
+Contrastingly, specialists that are highly constrained to interact with partners of high trait-matching might be more vulnerable to increased climate change-induced environmental stress and habitat degradation.
+Taken together, the fact that most species appear to be flexible interaction partners, combined with the fact that those that are not flexible are less likely to persist, might explain why specialised communities that are highly constrained by trait matching [like some plant-hummingbird networks; @vizentin-bugoni_processes_2014; @maruyama_morphological_2014] might be relatively rare.
+
+In conclusion, we show that...
+
+<!-- It still remains to evaluate the role of abundance and neutral processes and
 
@@
 The results hold for when species had
-* Implications for community assembly and network rewiring.
+* Implications for community assembly and network rewiring. -->
 

### 2019-09-14 paper/supp-info.Rmd
update paper's title

@@
 ---
-title: "The pollination trade-off"
-# DBS: The title above needs editing to match the final version in the paper
+title: "Environmental stress affects niche breadth in plant-pollinator communities"
 subtitle: "Supplementary information"

### 2019-09-14 paper/draft-info.Rmd
update draft info with TODOs

@@
 5 to the supplementary info.
+* What you think would be the best way to end the paper? Thinking about what could be highlighted in the conclusion.
 
@@
 * Fix references. There are lots of mistakes re. author, years and publication venue particularly for those from which data was downloaded.
-
+* Finish off discussion with a punchy conclusion. 
+* Fix the WAIC table. Currently shows the model without guild as unknown.
+* Add Lupe's feedback to the intro. Need to better define stress and Eltonian/Grinellian niche and don't need to say realised Eltonian niche when I really just mean number of partners
 <!-- Interactions are selected by species depending on the relative benefit they provide.

### 2019-11-05 paper/manuscript.Rmd
update paper's title
Edit first couple paragraphs in introduction

@@
 ---
-title: "Flexibility of interactions depends on habitat suitability"
+title: "Environmental stress affects niche breadth in plant-pollinator communities"
 author: 
@@
 Species interactions are known to vary widely across space and time. 
-There are multiple examples of species that interact tightly in an ecological community or a particular season but not in another. 
-It is crucial to understand why and how this turnover of interactions occur because the network of interactions of an ecological community is known to underpin ecosystem function and stability. 
+There are multiple examples of species that interact with a large number of partners in an ecological community or a particular season but with fewer in another. 
+It has been proposed that some of variation can be attributed to environmental drivers. 
+However, how exactly the environment, and the stress it imposes, affects the turnover of interactions is still unknown. 
+It is crucial to understand why and how this turnover occur because the network of interactions of an ecological community is known to underpin ecosystem function and stability. 
 Despite much progress in the last decades, we are still unable to predict species interactions, partially because we still have not accurately identified the factors that drive species to interact under certain conditions and not under another.
+
+Species interactions are determined in part by niche processes (the matching of traits) and partly by neutral processes (more abundant species are more likely to encounter each other and, thus, interact).
+Both of these processes can be influenced by the environment. 
+Therefore, it is not surprising that multiple studies have shown how changes to interactions, both pairwise and at the community level, can be driven by environmental change [@tylianakis_ecological_2017].
+For instance, some studies show that the rate of some trophic interactions, like predation [@mckinnon_lower_2010; @vucic-pestic_warming_2011] and herbivory [@baskett_latitudinal_2018], can increase with temperature but might decrease with precipitation [@pires_predicted_2016].
+Contrastingly, other studies have shown either no effect or non-linear effects of temperature or precipitation on plant-pollinator interactions [@devoto_patterns_2005; @gravel_bringing_2018].
+Overall,
 
@@
 Perhaps, because it operates at scales larger than those of the Eltonian niche concept, the abiotic environment is one of the factors that is commonly overlooked by community ecologists when explaining interaction turnover [but see @gravel_bringing_2018].
+
 The most evident—and best-studied—way through which the environment can affect the structure of ecological networks is by way of patterns of community composition. 

### 2019-11-05 paper/manuscript.Rmd
more changes to intro:

@@
 There are multiple examples of species that interact with a large number of partners in an ecological community or a particular season but with fewer in another. 
-It has been proposed that some of variation can be attributed to environmental drivers. 
-However, how exactly the environment, and the stress it imposes, affects the turnover of interactions is still unknown. 
-It is crucial to understand why and how this turnover occur because the network of interactions of an ecological community is known to underpin ecosystem function and stability. 
+It has been proposed that at least some of this variation can be attributed to environmental drivers. 
 Despite much progress in the last decades, we are still unable to predict species interactions, partially because we still have not accurately identified the factors that drive species to interact under certain conditions and not under another.
 
+However, how exactly the environment, and the stress it imposes on species, affects wether two species interact or not, and ultimately species degree the number of partners a species has---its degree---is still unknown.
+It is crucial to understand why and how species degree might change because it underpins species importance and, collectively is the foundation of network structure that underpins ecosystem function and stability.
+
 Species interactions are determined in part by niche processes (the matching of traits) and partly by neutral processes (more abundant species are more likely to encounter each other and, thus, interact).
+These two processes in turn 
 Both of these processes can be influenced by the environment. 
-Therefore, it is not surprising that multiple studies have shown how changes to interactions, both pairwise and at the community level, can be driven by environmental change [@tylianakis_ecological_2017].
+Therefore, it is not surprising that multiple studies have shown how changes to interactions can be driven by environmental change [@tylianakis_ecological_2017].
 For instance, some studies show that the rate of some trophic interactions, like predation [@mckinnon_lower_2010; @vucic-pestic_warming_2011] and herbivory [@baskett_latitudinal_2018], can increase with temperature but might decrease with precipitation [@pires_predicted_2016].
-Contrastingly, other studies have shown either no effect or non-linear effects of temperature or precipitation on plant-pollinator interactions [@devoto_patterns_2005; @gravel_bringing_2018].
-Overall,
+Contrastingly, other studies have shown either no overall effect or non-linear effects of temperature or precipitation on plant-pollinator interactions at the community level [@devoto_patterns_2005; @gravel_bringing_2018].
 
-There are two main processes involved in whether two species in a community interact or not.
-The first is an "Eltonian" niche process that is underpinned by the traits of the interacting species. 
-Compared to other kinds of trophic interactions, mutualistic interactions, and plant-pollination interactions, in particular, are relatively generalised.
-While a large proportion of the interactions appear to be opportunistic, a fraction of interactions shows a strong signature of deep co-evolutionary history [@hutchinson_cophylogenetic_2017]. 
-In contrast to opportunistic interactions with low trait-matching, the more co-evolved interactions with optimally matched traits are more persistent and presumably lead to a more substantial per-capita benefit for the interacting species.
-The second is a neutral process underpinned by the encounter rate of the interacting species. 
-All else being equal, when the encounter rate of interacting species is high, there is a higher probability to interact than if the rate were lower, for example, due to species rarity.
-
-Perhaps, because it operates at scales larger than those of the Eltonian niche concept, the abiotic environment is one of the factors that is commonly overlooked by community ecologists when explaining interaction turnover [but see @gravel_bringing_2018].
-
-The most evident—and best-studied—way through which the environment can affect the structure of ecological networks is by way of patterns of community composition. 
-At the heart of biogeography is the idea that the abiotic environment can determine the "Grinellian" niche of a species, this is whether the species can have a positive growth-rate when rare in a particular location.
-For two species to interact, they first need to co-occur in the same community, which can only happen if the environmental conditions of the community fall within the Grinellian niche of both species.
-
-Although less understood, the environment can also affect the interactions themselves, after community composition has been established [@tylianakis_ecological_2017]. 
-For instance, some studies show that trophic interactions, like predation [@mckinnon_lower_2010; @vucic-pestic_warming_2011] and herbivory [@baskett_latitudinal_2018], can increase with temperature but might decrease with precipitation [@pires_predicted_2016], and both plant-plant [@bertness_positive_1994] and plant-pollinator [@tur_evaluating_2016] interactions can switch from facilitative to competitive along an elevation/temperature gradient.
-Contrastingly, other studies have shown either no effect or non-linear effects of temperature or precipitation on plant-pollinator interactions [@devoto_patterns_2005; @gravel_bringing_2018].
-
-One way to summarise the seemingly contradictory evidence of whether the environment can influence whether two species interact or not is by moving from gradients of temperature or precipitation to gradients of environmental stress.
-Previous research is so far equivocal and, taken together, suggest that environmental stress can have two contrasting effects on species' Eltonian-niche [@tylianakis_ecological_2017].
+Each species can have multiple partners. 
+Each of these partners, as well as the interactions with them, can be simultaneoulsy affected by the environmental conditions. 
+Given all these sources of variation, it is not clear whether the environment can systematically affect species degree. 
+Previous research suggests that there might be two alternative hypothesis of how the environment, in particular the environmental stress, affects the number of partners of a species [@tylianakis_ecological_2017].
 On the one hand, it is possible that when species are under environmental stress, they might be "pressured" to focus on partners with which they are best adapted to interact. 
@@
 Likewise, @pellissier_spatial_2010 found a positive relationship between niche breadth and environmental stress: disk- or bowl-shaped blossoms (which allow a large number of potential pollinator species to access pollen and nectar rewards) dominated at high altitude flower communities.
+
+<!-- There are two main processes involved in whether two species in a community interact or not. -->
+<!-- The first is an "Eltonian" niche process that is underpinned by the traits of the interacting species.  -->
+<!-- Compared to other kinds of trophic interactions, mutualistic interactions, and plant-pollination interactions, in particular, are relatively generalised. -->
+<!-- While a large proportion of the interactions appear to be opportunistic, a fraction of interactions shows a strong signature of deep co-evolutionary history [@hutchinson_cophylogenetic_2017].
+-->
+<!-- In contrast to opportunistic interactions with low trait-matching, the more co-evolved interactions with optimally matched traits are more persistent and presumably lead to a more substantial per-capita benefit for the interacting species.
+-->
+<!-- The second is a neutral process underpinned by the encounter rate of the interacting species.  -->
+<!-- All else being equal, when the encounter rate of interacting species is high, there is a higher probability to interact than if the rate were lower, for example, due to species rarity.  -->
+
+<!-- Perhaps, because it operates at scales larger than those of the Eltonian niche concept, the abiotic environment is one of the factors that is commonly overlooked by community ecologists when explaining interaction turnover [but see @gravel_bringing_2018].
+-->
+
+<!-- The most evident—and best-studied—way through which the environment can affect the structure of ecological networks is by way of patterns of community composition.  -->
+<!-- At the heart of biogeography is the idea that the abiotic environment can determine the "Grinellian" niche of a species, this is whether the species can have a positive growth-rate when rare in a particular location.
+-->
+<!-- For two species to interact, they first need to co-occur in the same community, which can only happen if the environmental conditions of the community fall within the Grinellian niche of both species.
+-->
+
+<!-- Although less understood, the environment can also affect the interactions themselves, after community composition has been established [@tylianakis_ecological_2017].  -->
+<!-- For instance, some studies show that trophic interactions, like predation [@mckinnon_lower_2010; @vucic-pestic_warming_2011] and herbivory [@baskett_latitudinal_2018], can increase with temperature but might decrease with precipitation [@pires_predicted_2016], and both plant-plant [@bertness_positive_1994] and plant-pollinator [@tur_evaluating_2016] interactions can switch from facilitative to competitive along an elevation/temperature gradient.
+-->
+<!-- Contrastingly, other studies have shown either no effect or non-linear effects of temperature or precipitation on plant-pollinator interactions [@devoto_patterns_2005; @gravel_bringing_2018]. -->
+
+<!-- One way to summarise the seemingly contradictory evidence of whether the environment can influence whether two species interact or not is by moving from gradients of temperature or precipitation to gradients of environmental stress.
+-->
 

### 2019-11-06 paper/manuscript.Rmd
intro structure revised, still need to address minor comments

@@
 There are multiple examples of species that interact with a large number of partners in an ecological community or a particular season but with fewer in another. 
-It has been proposed that at least some of this variation can be attributed to environmental drivers. 
-Despite much progress in the last decades, we are still unable to predict species interactions, partially because we still have not accurately identified the factors that drive species to interact under certain conditions and not under another.
-
-However, how exactly the environment, and the stress it imposes on species, affects wether two species interact or not, and ultimately species degree the number of partners a species has---its degree---is still unknown.
-It is crucial to understand why and how species degree might change because it underpins species importance and, collectively is the foundation of network structure that underpins ecosystem function and stability.
+Some of this variation can be attributed to environmental drivers. 
+However, how exactly the environment, specifically the stress it imposes on species, affects wether two species interact or not, and ultimately the number of partners a species has is still unknown. 
+Understanding how the number of partners—the species degree—is driven by the environment is crucial, because it underpins the species role in its community and shapes the structure of the network of interactions.
+A determinant of ecosystem function and stability.
 
 Species interactions are determined in part by niche processes (the matching of traits) and partly by neutral processes (more abundant species are more likely to encounter each other and, thus, interact).
-These two processes in turn 
 Both of these processes can be influenced by the environment. 
-Therefore, it is not surprising that multiple studies have shown how changes to interactions can be driven by environmental change [@tylianakis_ecological_2017].
-For instance, some studies show that the rate of some trophic interactions, like predation [@mckinnon_lower_2010; @vucic-pestic_warming_2011] and herbivory [@baskett_latitudinal_2018], can increase with temperature but might decrease with precipitation [@pires_predicted_2016].
-Contrastingly, other studies have shown either no overall effect or non-linear effects of temperature or precipitation on plant-pollinator interactions at the community level [@devoto_patterns_2005; @gravel_bringing_2018].
+It is, therefore, not surprising that multiple studies have been able to show how changes to interactions can be related to environmental change [@tylianakis_ecological_2017].
+For instance, some studies suggest that the rate of some trophic interactions, like predation [@mckinnon_lower_2010; @vucic-pestic_warming_2011] and herbivory [@baskett_latitudinal_2018], can increase with temperature but might decrease with precipitation [@pires_predicted_2016].
+Some other sudies, however, have shown either no effect (on average) or non-linear effects of temperature or precipitation on plant-pollinator interactions [@devoto_patterns_2005; @gravel_bringing_2018].
 
-Each species can have multiple partners. 
+One possible explanation for the seemingly contradictory evidence is that each species can have multiple partners. 
 Each of these partners, as well as the interactions with them, can be simultaneoulsy affected by the environmental conditions. 
-Given all these sources of variation, it is not clear whether the environment can systematically affect species degree. 
-Previous research suggests that there might be two alternative hypothesis of how the environment, in particular the environmental stress, affects the number of partners of a species [@tylianakis_ecological_2017].
+And therefore is possible that the environmental stress affects the number of partners in different ways depending on its role in the community (for example its thropic guild) or even the species itself.
+Previous research suggests that there might be two alternative hypothesis of how in particular the environmental stress may affect species degree [@tylianakis_ecological_2017]. 
 On the one hand, it is possible that when species are under environmental stress, they might be "pressured" to focus on partners with which they are best adapted to interact. 
@@
 Likewise, @pellissier_spatial_2010 found a positive relationship between niche breadth and environmental stress: disk- or bowl-shaped blossoms (which allow a large number of potential pollinator species to access pollen and nectar rewards) dominated at high altitude flower communities.
+
+Here, we investigate whether, and how, environmental stress can systematically affect species degree. 
+Our main aim is to test the two competing hypotheses that relate environmental stress and species degree and investigate whether there is a pattern within and across species and species guilds. 
+We propose that specialist species can become "facultative" generalists to reduce their vulnerability to the absence of preferred partners [for example, when variations in climate decouple phenologies; @benadi_specialization_2014].
+We therefore also expect that as environmental stress increases species with a relatively small number of partners are more likely to engage with more partners and broaden their thropic niche. 
+Species with a large number of partners, on the other hand, should have a larger pool of available partners and might, therefore, be more likely to narrow their niche under environmental stress. 
+Importantly, when testing these hypotheses, we control for the potential effects of the environment in community composition and the size of the species fundamental niche, both from an Eltonian (interactions) and Grinellian (environment) perspective.
+We test these hypothesis using data on plant-pollinator interactions globally and use their global patterns of occurrence to calculate the environmental suitability of all species present at two or more communities.
 
@@
 -->
-
-We analyse data on plant-pollinator interactions globally and calculate the environmental suitability of all species present at two or more communities to. 
-Our main aim is to leverage that information to test the two competing hypotheses that relate environmental stress and Eltionian niche breadth and whether there is a pattern within and across species.
-Specialist species can become "facultative" generalists to reduce their vulnerability to the absence of preferred partners [for example, when variations in climate decouple phenologies; @benadi_specialization_2014].
-We therefore also expect that as environmental stress increases species with a relatively small number of partners are more likely to broaden their Eltonian niche. 
-Species with a large number of partners, on the other hand, should have a larger pool of available partners and might, therefore, be more likely to narrow their niche under environmental stress. 
-Importantly, when testing these hypotheses, we control for the potential effects of the environment in community composition and the size of the species fundamental niche, both from an Eltonian (interactions) and Grinellian (environment) perspective.
 

### 2019-11-07 paper/manuscript.Rmd
Incorporate more feedback to intro. Still missing some references

@@
 Species interactions are known to vary widely across space and time. 
-There are multiple examples of species that interact with a large number of partners in an ecological community or a particular season but with fewer in another. 
+There are multiple examples of species that interact with a large number of partners in a particular community or season, but with fewer in another. 
 Some of this variation can be attributed to environmental drivers. 
-However, how exactly the environment, specifically the stress it imposes on species, affects wether two species interact or not, and ultimately the number of partners a species has is still unknown. 
-Understanding how the number of partners—the species degree—is driven by the environment is crucial, because it underpins the species role in its community and shapes the structure of the network of interactions.
-A determinant of ecosystem function and stability.
+However, how exactly the environment, specifically the stress it imposes on species, affects whether two species interact or not, and ultimately the number of partners a species has is still unknown. 
+Understanding how the number of partners—the species degree—is driven by the environment is crucial because it underpins the species role in its community and shapes the structure of the network of interactions.
+This structure, in turn, determines ecosystem function and stability.
 
 Species interactions are determined in part by niche processes (the matching of traits) and partly by neutral processes (more abundant species are more likely to encounter each other and, thus, interact).
-Both of these processes can be influenced by the environment. 
-It is, therefore, not surprising that multiple studies have been able to show how changes to interactions can be related to environmental change [@tylianakis_ecological_2017].
-For instance, some studies suggest that the rate of some trophic interactions, like predation [@mckinnon_lower_2010; @vucic-pestic_warming_2011] and herbivory [@baskett_latitudinal_2018], can increase with temperature but might decrease with precipitation [@pires_predicted_2016].
-Some other sudies, however, have shown either no effect (on average) or non-linear effects of temperature or precipitation on plant-pollinator interactions [@devoto_patterns_2005; @gravel_bringing_2018].
+The environment can influence both of these processes. 
+It is, therefore, not surprising that, despite limitations on the spatial extent or the number of environmental gradients considered, multiple studies have been able to show how changes to interactions can be related to environmental change [@tylianakis_ecological_2017].
+For instance, some studies suggest that the strenghth of some trophic interactions, like predation [@mckinnon_lower_2010; @vucic-pestic_warming_2011] and herbivory [@baskett_latitudinal_2018], can increase with temperature but might decrease with precipitation [@pires_predicted_2016].
+Some other studies, however, have shown either no effect (on average) or non-linear effects of temperature or precipitation on plant-pollinator interactions [@devoto_patterns_2005; @gravel_bringing_2018].
+Overall, while it looks clear that pairwise interactions respond to environmental drivers, there is high variability in the response [@tylianakis_global_2008].
 
 One possible explanation for the seemingly contradictory evidence is that each species can have multiple partners. 
-Each of these partners, as well as the interactions with them, can be simultaneoulsy affected by the environmental conditions. 
-And therefore is possible that the environmental stress affects the number of partners in different ways depending on its role in the community (for example its thropic guild) or even the species itself.
-Previous research suggests that there might be two alternative hypothesis of how in particular the environmental stress may affect species degree [@tylianakis_ecological_2017]. 
+Each of these partners, as well as the interactions with them, can be simultaneously affected by the environmental conditions. 
+Therefore environmental stress may affect the number of partners in different ways depending on its role in the community (for example its trophic guild) or even the species itself. 
+Previous research suggests that there might be two alternative hypotheses of how environmental stress may affect species degree [@tylianakis_ecological_2017]. 
 On the one hand, it is possible that when species are under environmental stress, they might be "pressured" to focus on partners with which they are best adapted to interact. 
-For instance, @hoiss_altitude_2012 found increased phylogenetic clustering between plants and pollinators at higher altitudes; while @peralta_phylogenetic_2015 found that parasitoids in plantation forest, where environmental stress was higher than in native forests, were constrained to interact with hosts they were best adapted to attack.
+For instance, @hoiss_altitude_2012 found increased phylogenetic clustering between plants and pollinators at higher altitudes; while @peralta_phylogenetic_2015 found that parasitoids in plantation forest, where environmental stress was higher than in native forests, were constrained to interact with hosts, they were best adapted to attack.
 Similarly, @lavandero_genotype_2013 found that environmental stress due to higher temperature reduced the breadth of the Eltonian niche of parasitoids.
 
-On the other hand, it is also possible that when species are under environmental stress, they are forced to be more flexible in their interactions as higher environmental stress is likely to be reflected in greater energetic or reproductive costs and therefore they might not be able to sustain encounter rates with their preferred partners at sufficient levels.
+On the other hand, it is also possible that when species are under environmental stress, they are forced to be more flexible in their interactions as higher environmental stress is likely to be reflected in greater energetic or reproductive costs.
+Therefore they might not be able to sustain encounter rates with their preferred partners at sufficient levels. 
 In line with this hypothesis, @hoiss_interactive_2015 found that the specialisation of plant-pollinator networks decreased both with elevation and after extreme drought events.
@@
 Here, we investigate whether, and how, environmental stress can systematically affect species degree. 
-Our main aim is to test the two competing hypotheses that relate environmental stress and species degree and investigate whether there is a pattern within and across species and species guilds. 
+Our main aim is to test the two competing hypotheses that relate environmental stress and species degree and investigate whether this changes across species or between trophic guilds. 
 We propose that specialist species can become "facultative" generalists to reduce their vulnerability to the absence of preferred partners [for example, when variations in climate decouple phenologies; @benadi_specialization_2014].
-We therefore also expect that as environmental stress increases species with a relatively small number of partners are more likely to engage with more partners and broaden their thropic niche. 
-Species with a large number of partners, on the other hand, should have a larger pool of available partners and might, therefore, be more likely to narrow their niche under environmental stress. 
+We therefore also expect that as environmental stress increases species with a relatively small number of partners are more likely to engage with more partners and broaden their trophic niche. 
+Species with a large number of partners, on the other hand, should have a larger pool of available partners and might, therefore, be more likely to narrow their niche under environmental stress by focusing on the most benefitial partners.
 Importantly, when testing these hypotheses, we control for the potential effects of the environment in community composition and the size of the species fundamental niche, both from an Eltonian (interactions) and Grinellian (environment) perspective.
-We test these hypothesis using data on plant-pollinator interactions globally and use their global patterns of occurrence to calculate the environmental suitability of all species present at two or more communities.
+
+We test these hypotheses using data on plant-pollinator interactions. 
+We use the species' patterns of occurrence to estimate the environmental suitability in their communities as an indirect measure of the environmental stress they might experience. 
+Condensing the environmental variation over multiple factors (like temperature and precipitation) into a single metric is crucial to generalise our findings at a global scale.
 

### 2019-11-10 paper/supp-info.Rmd
Use paper formatting for supp-info

@@
 author: "E. Fernando Cagua, Hugo J. Marrero, Jason M. Tylianakis, Daniel B. Stouffer"
-# bibliography: references.bib
-csl: ecology-letters.csl
-documentclass: book
+bibliography: 
+  - bibliography.bib
+  - int-bibliography.bib
+# csl: pnas.csl
 output: 
   bookdown::pdf_document2:
+    # base_format: rticles::peerj_article
     keep_tex: yes
+    number_sections: false
 toc: false
+fontsize: 11pt
+# classoption: a4paper
+geometry: 
+  - textwidth=33em
+  - textheight=48\baselineskip
 header-includes:
@@
   - \usepackage{xcolor}
+  - \usepackage{setspace}
+  - \usepackage{caption}
 editor_options: 
@@
 ---
+
+\onehalfspacing
+\captionsetup[table]{skip=10pt}
 

### 2019-11-10 paper/manuscript.Rmd
Move data cleaning to supp-info

@@
 loadd(abs_wordcount, msc_wordcount, n_displays, n_references, keywords, bibliography)
-loadd(interaction_citations)
 ```
@@
 
-<!-- There are two main processes involved in whether two species in a community interact or not. -->
-<!-- The first is an "Eltonian" niche process that is underpinned by the traits of the interacting species.  -->
-<!-- Compared to other kinds of trophic interactions, mutualistic interactions, and plant-pollination interactions, in particular, are relatively generalised. -->
-<!-- While a large proportion of the interactions appear to be opportunistic, a fraction of interactions shows a strong signature of deep co-evolutionary history [@hutchinson_cophylogenetic_2017].
--->
-<!-- In contrast to opportunistic interactions with low trait-matching, the more co-evolved interactions with optimally matched traits are more persistent and presumably lead to a more substantial per-capita benefit for the interacting species.
--->
-<!-- The second is a neutral process underpinned by the encounter rate of the interacting species.  -->
-<!-- All else being equal, when the encounter rate of interacting species is high, there is a higher probability to interact than if the rate were lower, for example, due to species rarity.  -->
-
-<!-- Perhaps, because it operates at scales larger than those of the Eltonian niche concept, the abiotic environment is one of the factors that is commonly overlooked by community ecologists when explaining interaction turnover [but see @gravel_bringing_2018].
--->
-
-<!-- The most evident—and best-studied—way through which the environment can affect the structure of ecological networks is by way of patterns of community composition.  -->
-<!-- At the heart of biogeography is the idea that the abiotic environment can determine the "Grinellian" niche of a species, this is whether the species can have a positive growth-rate when rare in a particular location.
--->
-<!-- For two species to interact, they first need to co-occur in the same community, which can only happen if the environmental conditions of the community fall within the Grinellian niche of both species.
--->
-
-<!-- Although less understood, the environment can also affect the interactions themselves, after community composition has been established [@tylianakis_ecological_2017].  -->
-<!-- For instance, some studies show that trophic interactions, like predation [@mckinnon_lower_2010; @vucic-pestic_warming_2011] and herbivory [@baskett_latitudinal_2018], can increase with temperature but might decrease with precipitation [@pires_predicted_2016], and both plant-plant [@bertness_positive_1994] and plant-pollinator [@tur_evaluating_2016] interactions can switch from facilitative to competitive along an elevation/temperature gradient.
--->
-<!-- Contrastingly, other studies have shown either no effect or non-linear effects of temperature or precipitation on plant-pollinator interactions [@devoto_patterns_2005; @gravel_bringing_2018]. -->
-
-<!-- One way to summarise the seemingly contradictory evidence of whether the environment can influence whether two species interact or not is by moving from gradients of temperature or precipitation to gradients of environmental stress.
--->
-
 # Methods
@@
 ```{r}
-loadd(config)
-loadd(int_metadata)
+loadd(interaction_citations)
+int_citations_year_range <- range(interaction_citations$YEAR)
 
-n_published_studies <- int_metadata$reference %>%
-  unique() %>%
-  stringr::str_detect(pattern = "unpubl", negate = TRUE) %>%
-  sum()
-
-all_int_cites <- paste0("@", interaction_citations$BIBTEXKEY) %>%
-  glue::glue_collapse(sep = "; ") %>%
-  paste0("[", ., "]")
-
-int_citations_year_range <- range(interaction_citations$YEAR)
-```
-
-```{r scientific-names-cleaning-info}
-loadd(checked_sp_names, spp, manual_name_corrections, problematic_networks)
-
-n_sp_names <- n_distinct(spp$sp_name)
-
-n_sp_names_subsp_level <- filter(spp, is_subspecies) %$%
-  n_distinct(sp_name)
-
-n_sp_names_sp_level_no_subsp <- filter(spp, !sp_unidentified, !is_subspecies) %$% 
-  n_distinct(sp_name)
-
-n_sp_names_sp_level <- filter(spp, !sp_unidentified) %$% 
-  n_distinct(sp_name)
-
-n_sp_names_gen_level <- filter(spp, sp_unidentified, !gen_unidentified) %$% 
-  n_distinct(sp_name)
-
-n_no_tax_info <- filter(spp, gen_unidentified) %$% n_distinct(sp_name)
-
-n_sp_correct_in_data <- checked_sp_names %>%
-  filter(good_queried_sp_name) %$%
-  n_distinct(queried_sp_name)
-
-n_sp_corrected_typos <- checked_sp_names %>%
-  filter(corrected_typo) %$% 
-  n_distinct(queried_sp_name)
-
-sp_with_synonyms <- checked_sp_names %>%
-  filter(alt_sp_name_found)
-
-n_sp_with_synonyms <- sp_with_synonyms %$%
-  n_distinct(queried_sp_name)
-
-sp_not_found <- checked_sp_names %>%
-  filter(!good_queried_sp_name) %>% 
-  filter(!alt_sp_name_found, !corrected_typo)
-
-n_sp_not_found <- sp_not_found %$%
-  n_distinct(queried_sp_name)
-
-n_sp_manual_corrections <- manual_name_corrections %>%
-  filter(!is.na(sp_name)) %$%
-  n_distinct(queried_sp_name)
-
-study_per_location <- int_metadata %>%
-  distinct(loc_id, reference)
-
-n_names_in_multiple_references_orig <- spp %>%
-  left_join(study_per_location, by = "loc_id") %>%
-  group_by(sp_name) %>%
-  summarise(n_net = n_distinct(loc_id), 
-            n_ref = n_distinct(reference)) %>%
-  filter(n_ref > 1) %$%
-  n_distinct(sp_name)
+loadd(clean_interactions)
+stats_clean_int <- clean_interactions %>%
+  purrr::map(n_distinct)
 ```
@@
 We retrieved plant-pollinator networks from the Web of Life database [@fortuna_web_2014]. 
-This database contains datasets originating from `r length(interaction_citations$BIBTEXKEY)` studies published in the primary literature between `r int_citations_year_range[1]` and `r int_citations_year_range[2]` `r all_int_cites`.
-Calculating the environmental stress of species in their community and their Eltonian niche breadth requires that the scientific names used to identify them are valid and unambiguous. 
-This is because valid scientific names are necessary to both accurately match species across studies and to obtain other information from biological databases. 
-However, a significant proportion of the data obtained contain spelling mistakes, taxonomic synonyms, or non-standard abbreviations. 
-Therefore, our first step was to validate and correct scientific names across studies to ensure that we matching of species across studies was as accurate as possible.
-
-Second, we calculated the suitability of the environment for a species in a particular community as a proxy of environmental stress. 
-We assume that the environmental stress a species experience in a particular location is inversely related to the suitability of the average environmental conditions in that place. 
-Our third and final step was to relate the environmental suitability to the relative number of partners a species has in a community, as a proxy for Eltionian niche breadth. 
-To explore this relationship within and across species, we used a multilevel Bayesian model in which we controlled for the potential effects of the environment on co-occurrence.
-
-## Plant-pollinator interactions
-
-All together, interaction data from the included studies included `r format(n_sp_names, big.mark = ",")` unique organism names. 
-From these `r format(n_names_in_multiple_references_orig, big.mark = ",")` were present in more than one study.
-From the total number of organisms, `r format(n_sp_names_subsp_level, big.mark = ",")` were identified to the subspecies or variety level, `r format(n_sp_names_sp_level_no_subsp, big.mark = ",")` to the species level, `r format(n_sp_names_gen_level, big.mark = ",")` to the genus level, whereas the remaining `r format(n_no_tax_info, big.mark = ",")` were unidentified.
-As the species level was the most common taxonomic rank available in our interaction datasets, in all further analysis, we grouped together subspecies or varieties within the same species.
-
-We were able to confirm the validity of `r format(n_sp_correct_in_data, big.mark = ",")` of the scientific names used to identify organisms (roughly `r scales::percent(n_sp_correct_in_data/n_sp_names_sp_level, 1)`).
-We assessed the validity of a name by querying the Global Names Resolver database (https://resolver.globalnames.org) which includes data from `r dplyr::n_distinct(taxize::gnr_datasources()$title)` taxonomic sources.
-We accessed this database using the function `gnr_resolve` from the R package `taxize` `r as.character(packageVersion('taxize'))` [@chamberlain_taxize_2013; @chamberlain_taxize_2019].
-
-From the remaining `r format(n_sp_names_sp_level - n_sp_correct_in_data, big.mark = ",")` names we were unable to validate, we were able to identify and correct `r format(n_sp_corrected_typos, big.mark = ",")` that contained spelling mistakes.
-These spelling mistakes were corrected automatically by fuzzy matching the canonical names in our data sources with those in the Global Names Resolver database. 
-However, on rare occasions, the fuzzy matching algorithm can suggest a scientific name that has a similar spelling, but that corresponds to an organism in a different taxonomic group, often a separate kingdom.
-To address this potential problem, we checked the taxonomic hierarchy of suggested names and confirmed that it matched our expected taxon.
-We retrieved all taxonomic hierarchies from the National Center for Biotechnology Information taxonomic database (https://www.ncbi.nlm.nih.gov/taxonomy).
-
-As species names are constantly changing, we subsequently checked for possible synonyms of the canonical names in our data sources. 
-Using data from the Integrated Taxonomic Information System database (http://www.itis.gov), we found synonyms and alternative names for `r format(n_sp_with_synonyms, big.mark = ",")` species.  
-Finding these alternative names was required for two main reasons. 
-First, because we wanted to be able to identify the cases in which the same species might have been recorded with different names in various data sources. 
-This can occur not only when the canonical name has been changed but also when there are widely used orthographic variants.
-Second, because retrieving occurrence data is often only possible using the latest accepted/valid name for a particular species.
-
-All together, from the `r format(n_sp_names_sp_level - n_sp_correct_in_data, big.mark = ",")` names we were unable to validate, it was not possible to automatically correct or find synonyms `r format(n_sp_not_found, big.mark = ",")` of them.
-We then manually consulted multiple online databases, chiefly Wikispecies (https://species.wikimedia.org/), and looked for canonical names that both, resembled the unvalidated names and matched the geographic and taxonomic expectations.
-In this fashion, we were able to further correct `r n_sp_manual_corrections` names. 
-Most manual corrections were made on names that have been abbreviated or had more than two spelling mistakes. 
-A complete list of manual name corrections can bee seen in Table \@ref(tab:tab-manual-name-corrections).
-
-```{r}
-loadd(recoded_interactions, clean_interactions, int_metadata)
-
-n_sp_ids <- recoded_interactions %>%
-  select(-loc_id) %>%
-  purrr::map(n_distinct) %>%
-  unlist() %>% sum()
-
-n_names_in_multiple_references_after <- recoded_interactions %>%
-  tidyr::gather(key = "guild", "sp_id", pla_id, ani_id) %>%
-  left_join(study_per_location, by = "loc_id") %>%
-  group_by(sp_id) %>%
-  summarise(n_ref = n_distinct(reference)) %>%
-  filter(n_ref > 1) %$%
-  n_distinct(sp_id)
-
-stats_clean_int <- clean_interactions %>%
-  purrr::map(n_distinct)
-
-data_sources_mult_nets <- int_metadata %>%
-  group_by(loc_id) %>%
-  summarise(n_nets = n_distinct(net_name)) %>%
-  filter(n_nets > 1)
-
-n_data_sources_mult_nets <- nrow(data_sources_mult_nets)
-```
-
-This cleaning process allowed us to match further `r n_sp_names - n_sp_ids` names across data sources and, by doing so, identify another `r n_names_in_multiple_references_after - n_names_in_multiple_references_orig` species that were present in more than one study.
-The process also allowed us to identify `r numbers2words(length(problematic_networks))` problematic data sources in which some names were included as both plants and pollinators. 
-These data sources were removed from further analysis. 
-In `r numbers2words(n_data_sources_mult_nets)` of our data sources interaction data was recorded at multiple points in time. 
-When this was the case, we combined interaction data into one single interaction network.
-
+This database contains datasets originating from `r length(interaction_citations$BIBTEXKEY)` studies published in the primary literature between `r int_citations_year_range[1]` and `r int_citations_year_range[2]`.
+Calculating the environmental stress of species in their community and their Eltonian niche breadth required us to reduce both the taxonomic and distributional/locational uncertainty.
+A critical step towards reducing this uncertainty is to ensure that the names used to identify species are valid and unambiguous, which in turn allow us to obtain further information from biological databases and accurately match species across studies.
+Therefore, our first step was to ensure consistent spelling and standarisation of species names synonyms (See Supplementary Information - \@ref[supp-methods]).
+This ensured that the matching of species across studies was as accurate as possible. 
 The cleaning process resulted on a total of `r format(stats_clean_int$pla_id, big.mark = ",")` plants and `r format(stats_clean_int$ani_id, big.mark = ",")` pollinator species distributed across `r format(stats_clean_int$loc_id)` locations arround the globe (Figure \@ref(fig:fig-worldmap), \@ref(fig:fig-distribution-species-mult-locations)).
@@
 ```
+
+Second, we calculated the suitability of the environment for a species in a particular community as a proxy of environmental stress. 
+We assume that the environmental stress a species experience in a particular location is inversely related to the suitability of the average environmental conditions in that place. 
+Our third and final step was to relate the environmental suitability to the relative number of partners a species has in a community, as a proxy for Eltionian niche breadth. 
+To explore this relationship within and across species, we used a multilevel Bayesian model in which we controlled for the potential effects of the environment on co-occurrence.
 

### 2019-11-10 paper/supp-info.Rmd
Move data cleaning to supp-info

@@
                       warning = FALSE)
-options(xtable.comment = FALSE, 
-        xtable.caption.placement = 'bottom',
-        xtable.size = 'small',
-        booktabs = TRUE, 
+options(booktabs = TRUE, 
         knitr.kable.NA = "-")
@@
 ```
+
+# Supplementary methods
+
+```{r scientific-names-cleaning-info}
+loadd(checked_sp_names, spp, manual_name_corrections, problematic_networks)
+loadd(int_metadata)
+
+n_sp_names <- n_distinct(spp$sp_name)
+
+n_sp_names_subsp_level <- filter(spp, is_subspecies) %$%
+  n_distinct(sp_name)
+
+n_sp_names_sp_level_no_subsp <- filter(spp, !sp_unidentified, !is_subspecies) %$% 
+  n_distinct(sp_name)
+
+n_sp_names_sp_level <- filter(spp, !sp_unidentified) %$% 
+  n_distinct(sp_name)
+
+n_sp_names_gen_level <- filter(spp, sp_unidentified, !gen_unidentified) %$% 
+  n_distinct(sp_name)
+
+n_no_tax_info <- filter(spp, gen_unidentified) %$% n_distinct(sp_name)
+
+n_sp_correct_in_data <- checked_sp_names %>%
+  filter(good_queried_sp_name) %$%
+  n_distinct(queried_sp_name)
+
+n_sp_corrected_typos <- checked_sp_names %>%
+  filter(corrected_typo) %$% 
+  n_distinct(queried_sp_name)
+
+sp_with_synonyms <- checked_sp_names %>%
+  filter(alt_sp_name_found)
+
+n_sp_with_synonyms <- sp_with_synonyms %$%
+  n_distinct(queried_sp_name)
+
+sp_not_found <- checked_sp_names %>%
+  filter(!good_queried_sp_name) %>% 
+  filter(!alt_sp_name_found, !corrected_typo)
+
+n_sp_not_found <- sp_not_found %$%
+  n_distinct(queried_sp_name)
+
+n_sp_manual_corrections <- manual_name_corrections %>%
+  filter(!is.na(sp_name)) %$%
+  n_distinct(queried_sp_name)
+
+study_per_location <- int_metadata %>%
+  distinct(loc_id, reference)
+
+n_names_in_multiple_references_orig <- spp %>%
+  left_join(study_per_location, by = "loc_id") %>%
+  group_by(sp_name) %>%
+  summarise(n_net = n_distinct(loc_id), 
+            n_ref = n_distinct(reference)) %>%
+  filter(n_ref > 1) %$%
+  n_distinct(sp_name)
+
+all_int_cites <- paste0("@", interaction_citations$BIBTEXKEY) %>%
+  glue::glue_collapse(sep = "; ") %>%
+  paste0("[", ., "]")
+```
+
+Data was obtained from the Web of Life database [@fortuna_web_2014] which includes data from `r length(interaction_citations$BIBTEXKEY)` published studies `r all_int_cites`.
+
+All together, interaction data from the included studies included `r format(n_sp_names, big.mark = ",")` unique organism names. 
+From these `r format(n_names_in_multiple_references_orig, big.mark = ",")` were present in more than one study.
+From the total number of organisms, `r format(n_sp_names_subsp_level, big.mark = ",")` were identified to the subspecies or variety level, `r format(n_sp_names_sp_level_no_subsp, big.mark = ",")` to the species level, `r format(n_sp_names_gen_level, big.mark = ",")` to the genus level, whereas the remaining `r format(n_no_tax_info, big.mark = ",")` were unidentified.
+As the species level was the most common taxonomic rank available in our interaction datasets, in all further analysis, we grouped together subspecies or varieties within the same species.
+
+We were able to confirm the validity of `r format(n_sp_correct_in_data, big.mark = ",")` of the scientific names used to identify organisms (roughly `r scales::percent(n_sp_correct_in_data/n_sp_names_sp_level, 1)`).
+We assessed the validity of a name by querying the Global Names Resolver database (https://resolver.globalnames.org) which includes data from `r dplyr::n_distinct(taxize::gnr_datasources()$title)` taxonomic sources.
+We accessed this database using the function `gnr_resolve` from the R package `taxize` `r as.character(packageVersion('taxize'))` [@chamberlain_taxize_2013; @chamberlain_taxize_2019].
+
+From the remaining `r format(n_sp_names_sp_level - n_sp_correct_in_data, big.mark = ",")` names we were unable to validate, we were able to identify and correct `r format(n_sp_corrected_typos, big.mark = ",")` that contained spelling mistakes.
+These spelling mistakes were corrected automatically by fuzzy matching the canonical names in our data sources with those in the Global Names Resolver database. 
+However, on rare occasions, the fuzzy matching algorithm can suggest a scientific name that has a similar spelling, but that corresponds to an organism in a different taxonomic group, often a separate kingdom.
+To address this potential problem, we checked the taxonomic hierarchy of suggested names and confirmed that it matched our expected taxon.
+We retrieved all taxonomic hierarchies from the National Center for Biotechnology Information taxonomic database (https://www.ncbi.nlm.nih.gov/taxonomy).
+
+As species names are constantly changing, we subsequently checked for possible synonyms of the canonical names in our data sources. 
+Using data from the Integrated Taxonomic Information System database (http://www.itis.gov), we found synonyms and alternative names for `r format(n_sp_with_synonyms, big.mark = ",")` species.  
+Finding these alternative names was required for two main reasons. 
+First, because we wanted to be able to identify the cases in which the same species might have been recorded with different names in various data sources. 
+This can occur not only when the canonical name has been changed but also when there are widely used orthographic variants.
+Second, because retrieving occurrence data is often only possible using the latest accepted/valid name for a particular species.
+
+All together, from the `r format(n_sp_names_sp_level - n_sp_correct_in_data, big.mark = ",")` names we were unable to validate, it was not possible to automatically correct or find synonyms `r format(n_sp_not_found, big.mark = ",")` of them.
+We then manually consulted multiple online databases, chiefly Wikispecies (https://species.wikimedia.org/), and looked for canonical names that both, resembled the unvalidated names and matched the geographic and taxonomic expectations.
+In this fashion, we were able to further correct `r n_sp_manual_corrections` names. 
+Most manual corrections were made on names that have been abbreviated or had more than two spelling mistakes. 
+A complete list of manual name corrections can bee seen in Table \@ref(tab:tab-manual-name-corrections).
 

### 2019-11-10 paper/supp-info.Rmd
Draft reference table

@@
   mutate(sp_name = tidyr::replace_na(sp_name, "no replacement found"), 
-         sp_name = kableExtra::cell_spec(sp_name, italic = TRUE), 
+         sp_name = kableExtra::cell_spec(sp_name, 
+                                         format = "latex", 
+                                         italic = TRUE), 
          guild = if_else(guild == "pla", "plant", "pollinator")) %>%
-  knitr::kable(caption = "Manually corrected canonnical names. More than one correct name have been included when an accepted/valid synonym the cannonical name exists.", 
+  knitr::kable(format = "latex", 
+               caption = "Manually corrected canonnical names. More than one correct name have been included when an accepted/valid synonym the cannonical name exists.", 
                col.names = c("incorrect name", "corrected name", "guild"),
@@
   kableExtra::collapse_rows(1, latex_hline = "none", valign = "top")
+```
+
+```{r}
+loadd(recoded_interactions, int_metadata)
+
+n_sp_ids <- recoded_interactions %>%
+  select(-loc_id) %>%
+  purrr::map(n_distinct) %>%
+  unlist() %>% sum()
+
+n_names_in_multiple_references_after <- recoded_interactions %>%
+  tidyr::gather(key = "guild", "sp_id", pla_id, ani_id) %>%
+  left_join(study_per_location, by = "loc_id") %>%
+  group_by(sp_id) %>%
+  summarise(n_ref = n_distinct(reference)) %>%
+  filter(n_ref > 1) %$%
+  n_distinct(sp_id)
+
+data_sources_mult_nets <- int_metadata %>%
+  group_by(loc_id) %>%
+  summarise(n_nets = n_distinct(net_name)) %>%
+  filter(n_nets > 1)
+
+n_data_sources_mult_nets <- nrow(data_sources_mult_nets)
+```
+
+This cleaning process allowed us to match further `r n_sp_names - n_sp_ids` names across data sources and, by doing so, identify another `r n_names_in_multiple_references_after - n_names_in_multiple_references_orig` species that were present in more than one study.
+The process also allowed us to identify `r numbers2words(length(problematic_networks))` problematic data sources in which some names were included as both plants and pollinators. 
+These data sources were removed from further analysis. 
+In `r numbers2words(n_data_sources_mult_nets)` of our data sources interaction data was recorded at multiple points in time. 
+When this was the case, we combined interaction data into one single interaction network.
+
+```{r tab-studies, eval = F}
+loadd(int_metadata)
+loadd(interaction_citations)
+
+simple_metadata <- int_metadata %>%
+  filter(stringr::str_detect(reference, pattern = "unpubl", negate = TRUE)) %>%
+  group_by(loc_id) %>%
+  summarise(location = paste0(round(mean(lon), 2), ", ", 
+                              round(mean(lat), 2)), 
+            name = first(loc_name), 
+            ref = first(reference)) %>%
+  # first word in the references is the main author (usually)
+  mutate(first_author = stringr::str_extract(ref, "^\\w+"), 
+         # the first number of four digits is the year
+         year = stringr::str_extract(ref, "[0-9]{4}"), 
+         key = paste(tolower(first_author), year, sep = "_")) %>%
+  select(-first_author, -year)
+
+interaction_citations %>%
+  mutate(first_author = stringr::str_extract(BIBTEXKEY, "[^_-]+"), 
+         year = stringr::str_extract(BIBTEXKEY, "[0-9]{4}"), 
+         key = paste(tolower(first_author), year, sep = "_"), 
+         bibtex_key = BIBTEXKEY) %>%
+  select(bibtex_key, key) %>%
+  fuzzyjoin::stringdist_full_join(simple_metadata, 
+                                  by = c(key = "key"), 
+                                  max_dist = 6, 
+                                  distance_col = "dist") %>% 
+  group_by(key.y) %>%
+  filter(dist == min(dist)) %>%
+  ungroup() %>%
+  select(location, name, bibtex_key) %>%
+  mutate(bibtex_key = paste0("@", bibtex_key, "")) %>%
+  knitr::kable(format = "markdown", 
+               escape = F, 
+               booktabs = T, 
+               col.names = c("coordinates", "site", "reference"),
+               caption = "Sites included in this study")
+  kableExtra::kable_styling(font_size = 8)
 ```
@@
 ```
+
+# Supplementary references

### 2019-11-15 paper/manuscript.Rmd
Add location cleaning to supp info

@@
 
-n_species_with_occurrences <- get_n_species(n_occurrences)
-n_species_with_cleaned_occurrences <- get_n_species(n_cleaned_occurrences) 
-n_species_with_dirty_occurrences <- get_n_species(n_dirty_occurrences)
 percent_thinned <- 1 - sum(n_thinned_occurrences$N) / sum(n_cleaned_occurrences$N)
-percent_filled_round_one <- 1-complete_filled_cells_1[1]/complete_climate_cells[1]
+percent_filled_round_one <- 1 - complete_filled_cells_1[1]/complete_climate_cells[1]
 ```
@@
 As we aim to compare the trophic niche for different suitability levels, we only do this for species that were present in at least `r numbers2words(readd(minimum_spp_locations))` communities.
-To calculate the suitability of a species in a particular location, we used a (Grinellian) niche-factor analysis [@hirzel_ecological-niche_2002; @broennimann_measuring_2012]. 
+To calculate the suitability of a species in a particular location, we used a niche-factor analysis [@hirzel_ecological-niche_2002; @broennimann_measuring_2012]. 
 This approach is based on the probability density function of species distribution in an environmental variable space. 
@@
 
-We retrieved occurrences from the Global Biodiversity Information Facility (GBIF; https://www.gbif.org) using the R package `rgbif` `r as.character(packageVersion('taxize'))` [@chamberlain_r_2017; @chamberlain_rgbif_2019].
-Specifically, for each species, we only requested occurrences for which the coordinates of the observation were available and that had no known geospatial issue in the GBIF database.
-Roughly, we downloaded `r round(sum(n_occurrences$N)/1000000, digits = 1)` million occurrences for the `r format(n_species_with_occurrences, big.mark = ",")` species we were interested on. 
-This occurrences, however, contain observations of mixed quality. 
-Therefore, we followed (ref?) and applied a series of simple filters and geographic heuristics to remove those of lower quality. 
-\R{rationale-occurrence-filtering}Specifically, we removed all occurrences with (*i*) a coordinate uncertainty larger than 100km; (*ii*) those recorded prior to 1945 (ref?
-or why?); (*iii*) those in which the number of individuals registered was either zero or more than 100 as such large counts are often erroneous (ref?
-or why?); and (*iv*) those occurrences in which the "basis of record" was not a human observation or a preserved specimen (ref?
-why?).
-We then used the R package `CoordinateCleaner` `r as.character(packageVersion('taxize'))` [@zizka_coordinatecleaner_2019] and land mass and country data from Natural Earth (https://www.naturalearthdata.com) with a 1:10,000,000 scale to further identify and remove problematic occurrences.
-We removed occurrences for which their coordinates (*v*) fell outside the borders of the country where they were recorded; (*vi*) those around a country capital or the centroid of the country and province centroids; (*vii*) those around a biodiversity institution; and (*viii*) those located within oceans.
-Thorugh this cleaning process, we removed with `r round(sum(n_dirty_occurrences$N)/1000000, digits = 1)` million occurrences distributed accross `r n_species_with_dirty_occurrences` species. 
-Finally, we integrated the occurrences from our plant-pollinator communities to the cleaned occurrences retrieved from GBIF.
+We retrieved `r round(sum(n_occurrences$N)/1000000, digits = 1)` million occurrences from the Global Biodiversity Information Facility (GBIF; https://www.gbif.org). 
+Issues with data quality are a central issue hampering the use of publicly available species occurrence GBIF data in ecology and biogeography (Jetz et al 2019). 
+We, therefore we followed a series of filters and geographic heuristics to correct or remove erroneous and imprecise referencing records [See supplementary methods; @zizka_coordinatecleaner_2019] which allowed us to identify and remove `r round(sum(n_dirty_occurrences$N)/1000000, digits = 1)` million problematic occurrences from further analysis.
+We integrated the occurrences from our plant-pollinator communities to the cleaned occurrences retrieved from GBIF.
 

### 2019-11-15 paper/supp-info.Rmd
Add location cleaning to supp info

@@
 
-```{r tab-studies, eval = F}
-loadd(int_metadata)
-loadd(interaction_citations)
+## Reducing location uncertainty
 
-simple_metadata <- int_metadata %>%
-  filter(stringr::str_detect(reference, pattern = "unpubl", negate = TRUE)) %>%
-  group_by(loc_id) %>%
-  summarise(location = paste0(round(mean(lon), 2), ", ", 
-                              round(mean(lat), 2)), 
-            name = first(loc_name), 
-            ref = first(reference)) %>%
-  # first word in the references is the main author (usually)
-  mutate(first_author = stringr::str_extract(ref, "^\\w+"), 
-         # the first number of four digits is the year
-         year = stringr::str_extract(ref, "[0-9]{4}"), 
-         key = paste(tolower(first_author), year, sep = "_")) %>%
-  select(-first_author, -year)
+```{r}
+loadd(n_occurrences, n_cleaned_occurrences, n_dirty_occurrences, gbif_key_groups, org_ids)
 
-interaction_citations %>%
-  mutate(first_author = stringr::str_extract(BIBTEXKEY, "[^_-]+"), 
-         year = stringr::str_extract(BIBTEXKEY, "[0-9]{4}"), 
-         key = paste(tolower(first_author), year, sep = "_"), 
-         bibtex_key = BIBTEXKEY) %>%
-  select(bibtex_key, key) %>%
-  fuzzyjoin::stringdist_full_join(simple_metadata, 
-                                  by = c(key = "key"), 
-                                  max_dist = 6, 
-                                  distance_col = "dist") %>% 
-  group_by(key.y) %>%
-  filter(dist == min(dist)) %>%
-  ungroup() %>%
-  select(location, name, bibtex_key) %>%
-  mutate(bibtex_key = paste0("@", bibtex_key, "")) %>%
-  knitr::kable(format = "markdown", 
-               escape = F, 
-               booktabs = T, 
-               col.names = c("coordinates", "site", "reference"),
-               caption = "Sites included in this study")
-  kableExtra::kable_styling(font_size = 8)
+get_n_species <- . %>%
+  dplyr::inner_join(gbif_key_groups, by = "taxonKey") %>%
+  dplyr::inner_join(org_ids, by = c("key_id" = "sp_key_id")) %$%
+  dplyr::n_distinct(org_id)
+
+n_species_with_occurrences <- get_n_species(n_occurrences)
+n_species_with_cleaned_occurrences <- get_n_species(n_cleaned_occurrences) 
+n_species_with_dirty_occurrences <- get_n_species(n_dirty_occurrences)
 ```
 
-```{r eval = FALSE, tab-sp-synonym-reasons}
-sp_with_synonyms %>%
-  filter(!is.na(itis_reason)) %>%
-  group_by(queried_sp_name) %>%
-  summarise(itis_reason = first(itis_reason)) %>%
-  group_by(itis_reason) %>%
-  count(sort = T) %>%
-  knitr::kable("latex", 
-               col.names = c("reason of species alternative name", "n"), 
-               caption = "tablesita", 
-               booktabs = TRUE) %>%
-  kableExtra::kable_styling(font_size = 8) %>%
-  kableExtra::collapse_rows(columns = 1)
-```
+We retrieved occurrences from the Global Biodiversity Information Facility (GBIF; https://www.gbif.org) using the R package `rgbif` `r as.character(packageVersion('taxize'))` [@chamberlain_r_2017; @chamberlain_rgbif_2019].
+Specifically, for each species, we only requested occurrences for which the coordinates of the observation were available and that had no known geospatial issue in the GBIF database.
+Roughly, we downloaded `r round(sum(n_occurrences$N)/1000000, digits = 1)` million occurrences for the `r format(n_species_with_occurrences, big.mark = ",")` species we were interested on. 
+This occurrences, however, contain observations of mixed quality. 
+Therefore, we followed @zizka_coordinatecleaner_2019 and applied a series of simple filters and geographic heuristics to remove those of lower quality. 
+Specifically, we removed all occurrences with (*i*) a coordinate uncertainty larger than 100km; (*ii*) those recorded prior to 1945 (as records prior to this date have been shown to be often impreciseref); (*iii*) those in which the number of counts in the occurrence were registered was either zero (as that indicates that the species has not been recorded); and (*iv*) those occurrences in which the "basis of record" was not a human observation or a preserved specimen (as occirrences from unknown and fossil records are known to be highly unreliable).
+We then used the R package `CoordinateCleaner` `r as.character(packageVersion('taxize'))` [@zizka_coordinatecleaner_2019] and land mass and country data from Natural Earth (https://www.naturalearthdata.com) with a 1:10,000,000 scale to further identify and remove problematic occurrences.
+We removed occurrences for which their coordinates (*v*) fell outside the borders of the country where they were recorded; (*vi*) those around a country capital or the centroid of the country and province centroids; (*vii*) those around a biodiversity institution; and (*viii*) those located within oceans.
+Thorugh this cleaning process, we removed with `r round(sum(n_dirty_occurrences$N)/1000000, digits = 1)` million occurrences distributed accross `r n_species_with_dirty_occurrences` species.
+
+# Supplementary results
 

### 2019-11-15 paper/manuscript.Rmd
Explain autocorrelation in data

@@
 After obtaining information about species occurrence and the environment, we then merged these two datasets such that the location of each occurrence was characterised by a vector with details of our 37 bioclimatic and topographic variables.
-If a species had more than one occurrence records within one of the cells of the bioclimatic raster, we only included one of the occurrence records. 
+
+Sets of occurrence data tend to be spatially aggregated due to sample bias (tendency to collect close to cities, certain countries). 
+Spatial autocorrelation arises in ecological data because geographically clumped records tend to be more similar, in physical characteristics and/or species abundances, than are pairs locations that are farther apart.
+To account for such spatial dependency in occurrence data, if a species had more than one occurrence records within one of the cells of the bioclimatic raster, we only included one of the occurrence records.
 We did this to avoid giving more weight to areas with a high number of occurrences, a common scenario in occurrence records collected opportunistically as the ones we use here. 

### 2019-11-15 paper/manuscript.Rmd
Remove eltonian niche size from menthods analysis section

@@
 
-We then used a set of bayesian multilevel models to evaluate the impact of environmental suitability on the size of the realised Eltonian trophic niche. 
-We measure the size of the Eltonian niche using the normalised degree of species, this is, the number of species it interacts with given the number of species in the opposite guild [@martin_gonzalez_centrality_2010].
+We then used a set of bayesian multilevel models to evaluate the impact of environmental suitability on the number of partners a species has. 
+Specifically, we use the normalised degree of species as our response variable, this is, the number of species it interacts with given the number of species in the opposite guild [@martin_gonzalez_centrality_2010].
 The normalised degree was modelled using a logit link function, and a binomial distribution in which the number of species interacts with is the number of successes, and the number of species in the opposite guild is the number of trials.

### 2019-11-15 paper/manuscript.Rmd
Use only three main variables in base formula

@@
 The normalised degree was modelled using a logit link function, and a binomial distribution in which the number of species interacts with is the number of successes, and the number of species in the opposite guild is the number of trials.
-We are aware that wether species interacts or not is not a Bernoulli process as species interactions are not strictly independent from each other. 
+We are aware that whether species interact or not is not a Bernoulli process as species interactions are not strictly independent from each other. 
 However, a binomial distribution allows us to account for the differences in species richness across communities indirectly. 
@@
 We evaluate four models to assess the relative importance of suitability. 
-A first model, our baseline model, included five population-level predictors and two grouping levels, species and the community. 
-The population-level predictors in the baseline model, commonly called fixed effects, were the habitat suitability, the species guild (plant or a pollinator), a metric of the species generalism, and its number of known possible partners.
-We included the overall level of generalism as one would expect species with a large number of interactions globally to be more likely to interact with a large number of species locally. 
-Concretely, we estimated an overall species level of generalism as the total number of interacting species across communities in our dataset. 
-We also included the number of known possible partners as a predictor in our models as it allows us to control for the environmental effects on species co-occurrence. 
+A first model, our baseline model, included three population-level predictors and two grouping levels, species and the community. 
+The population-level predictors in the baseline model, commonly called fixed effects, were the habitat suitability, the species guild (plant or a pollinator), and its number of known possible partners.
+We included the number of known possible partners as a predictor in our models as it allows us to control for the environmental effects on species co-occurrence. 
 We calculate this metric by determining the number of partners with which the species is known to interact in any other community.
@@
 Often the potential and the actual number of partners is the same or very close to each other, especially for rare species present only in a few communities.  
-As we were particularly interested in understanding whether the effect of habitat suitability is conditional on the species guild (plant or pollinator), we, therefore, included guild and its interaction with suitability in the model.
+As we were interested in understanding whether the effect of habitat suitability is conditional on the species guild (plant or pollinator), we, therefore, included guild and its interaction with suitability in the model.
 We allowed the intercept of degree and slope of the suitability-degree relationship to vary among species, this allowed us to investigate two questions. 
@@
 Second, by investigating the correlation between the intercept and the slope as a model parameter, it allowed us to inspect the extent by which species with a small or large number of interactions respond to increasing levels of environmental stress.
-To account for unmeasured differences between communities, like sampling effort, sampling method, or diversity, we calculated an intercept for each community in our study.
+To account for unmeasured differences between communities, like sampling effort, sampling method, or diversity, we also calculated an intercept for each community in our study.
 To facilitate model interpretation and convergence, we scaled all continuous variables to have a mean of zero and a unit standard deviation.
 
-We compared this baseline model with three alternative models in which we remove one predictor at a time.
+We compared this baseline model with two alternative models in which we remove one predictor at a time.
 To quantify the difference between models, in terms of their expected out-of-sample performance, we use the Wanatabe-Akaike information criterion (WAIC). 

### 2019-11-15 code/clean-occurrence-data.R
Do not ignore occurrences with more than 100 observations

@@ -36,7 +36,7 @@ clean_occurrences <- function(dirty_occurrences, land_data, country_data_sf, ver
       (basisOfRecord == "HUMAN_OBSERVATION" |
          basisOfRecord == "OBSERVATION" |
          basisOfRecord == "PRESERVED_SPECIMEN") &
-      (individualCount > 0 | individualCount < 99 | is.na(individualCount)) &
+      (individualCount > 0 & !is.na(individualCount)) &
       (year > 1945)]
   
   cleaned_occurrences <- dirty_occurrences %>%

### 2019-11-16 paper/manuscript.Rmd
Add ref to supplementary methods in msc
Move least interesting results figures to supplementary info

@@
 There are multiple examples of species that interact with a large number of partners in a particular community or season, but with fewer in another.
+
 Some of this variation can be attributed to environmental drivers. 
@@
 A critical step towards reducing this uncertainty is to ensure that the names used to identify species are valid and unambiguous, which in turn allow us to obtain further information from biological databases and accurately match species across studies.
-Therefore, our first step was to ensure consistent spelling and standarisation of species names synonyms (See Supplementary Information - \@ref[supp-methods]).
+Therefore, our first step was to ensure consistent spelling and standarisation of species names synonyms (See Supplementary Methods).
 This ensured that the matching of species across studies was as accurate as possible. 
@@
 However, most communities included species for which habitat suitability was low and species for which it was high (Fig. \@ref(fig:fig-median-suitability)).
-
-```{r fig-sensitivity-analysis, fig.width = width('single'), fig.height = 2.2, fig.cap = fig_sensitivity_analysis_legend}
-
-fig_sensitivity_analysis_legend <- 
-  paste0("Sensitivity analysis of environmental suitability error. ",
-         "The number of independent occurrences retrieved from GBIF is inversely related to the error of environmental suitability for our plant-pollinator networks.", 
-         "The sensitivity analysis was performed by subsampling occurrences of", 
-         " *", sensitivity_species_name$canonicalName, "* ", 
-         "the species in our dataset with the largest number of occurrences in GBIF, which was recorded in two of our communities.")
-
-readd(fig_sensitivity_analysis)
-```
-
-```{r fig-median-suitability, fig.width = width('single'), fig.height = 2.2*1.5, fig.cap = "Median habitat suitability of communities in our dataset.
-Each row represents a different community and horizontal lines represent span the 2.5 and 97.5 quantiles."}
-readd(fig_median_suitability)
-```
 

### 2019-11-16 paper/supp-info.Rmd
Add subheding to supplementary materials analysis
Move least interesting results figures to supplementary info

@@
 # Supplementary methods
+
+## Reducing taxononic uncertainty
 
@@
 
-All together, interaction data from the included studies included `r format(n_sp_names, big.mark = ",")` unique organism names. 
+Interaction data from the included studies included `r format(n_sp_names, big.mark = ",")` unique organism names. 
 From these `r format(n_names_in_multiple_references_orig, big.mark = ",")` were present in more than one study.
@@
 
+```{r fig-sensitivity-analysis, fig.width = width('single'), fig.height = 2.2, fig.cap = fig_sensitivity_analysis_legend}
+
+fig_sensitivity_analysis_legend <- 
+  paste0("Sensitivity analysis of environmental suitability error. ",
+         "The number of independent occurrences retrieved from GBIF is inversely related to the error of environmental suitability for our plant-pollinator networks.", 
+         "The sensitivity analysis was performed by subsampling occurrences of", 
+         " *", sensitivity_species_name$canonicalName, "* ", 
+         "the species in our dataset with the largest number of occurrences in GBIF, which was recorded in two of our communities.")
+
+readd(fig_sensitivity_analysis)
+```
+
+```{r fig-median-suitability, fig.width = width('single'), fig.height = 2.2*1.5, fig.cap = "Median habitat suitability of communities in our dataset.
+Each row represents a different community and horizontal lines represent span the 2.5 and 97.5 quantiles."}
+readd(fig_median_suitability)
+```
+
 # Supplementary references

### 2019-11-16 paper/manuscript.Rmd
Explain why models with potential number of partners are stringent

@@
 We calculate this metric by determining the number of partners with which the species is known to interact in any other community.
-Controlling for the number of potential partners makes our model a particularly stringent test of our environmental stress hypotheses. 
+Controlling for the number of potential partners makes our model a particularly stringent test of our environmental stress hypotheses because this variable could explain a large proportion of variance.
 Often the potential and the actual number of partners is the same or very close to each other, especially for rare species present only in a few communities.

### 2019-11-16 paper/manuscript.Rmd
Minor changes to methods

@@
 However, a binomial distribution allows us to account for the differences in species richness across communities indirectly. 
-Importantly, however, results are qualitatively similar when we model species degree directly using a Poisson distribution and a logarithmic link function (Supp info).
+Importantly, however, results are qualitatively similar when we model species degree directly using a Poisson distribution and a logarithmic link function.
 
@@
 
-We compared this baseline model with two alternative models in which we remove one predictor at a time.
+We compared this baseline model with three alternative models in which we remove one predictor at a time.
 To quantify the difference between models, in terms of their expected out-of-sample performance, we use the Wanatabe-Akaike information criterion (WAIC).

### 2019-11-16 paper/manuscript.Rmd
Improve results

@@
 We therefore removed from further analyses `r n_spp_not_enough_occ` species for which we did not have enough occurrences to obtain robust estimates.
-When inspecting the suitability values of the analysed species we found that some communitues have larger overal suitability values. 
-However, most communities included species for which habitat suitability was low and species for which it was high (Fig. \@ref(fig:fig-median-suitability)).
+When inspecting the suitability values of the analysed species we found that most communities included species for which habitat suitability was low and species for which it was high (Fig.
+\@ref(fig:fig-median-suitability)).
 
@@
 
-We found that our models performed relativelly well.
+Our models performed relativelly well.
 The bayesian R-squared for our baseline model was `r round(bayesian_r2_baseline[1], digits = 2)`, which indicates our models were able to capture a large proporton of the variability on the data. 
-Overall we found only weak evidence of a relationship between the environmental niche size and the normalised degree (Figure \@ref(fig:fig-conditional-effects)a). 
-This relationship was stronger for plants than for animals.
-Similarly environmental suitability does not show a consistent pattern accross species. 
-Indeed, when looking at the population level effects, suitability virtually no relationship with normalised degree, neither for plants or pollinators (Figure \@ref(fig:fig-conditional-effects)b). 
-However, suitability is still an important predictor as the WAIC difference between our baseline model and that that did not include suitability was `r round(waic_diff_suitability)` ± `r round(waic_se_diff_suitability)`.
-Both among plants and pollinators for some species there is a strong negative relationship between suitability and normalised degree and some others with a strong positive relationship (Figure \@ref(fig:fig-random-effects)a).
-As expected, we found a positive relationship between a species generalism and normalised degree \@ref(fig:fig-conditional-effects)c). 
-However our model comparisons based on WAIC shows that including generalism in the model adds relatively little information once we have accounted for the other variables in the model.
-Finally, we found a strong and positive relationship between the number of possible interactions and the number of realised interactions in the community.
+Overall we found that environmental suitability does not show a consistent pattern accross species. 
+Indeed, when looking at the population level effects, suitability has virtually no relationship with normalised degree, neither for plants or pollinators (Figure \@ref(fig:fig-conditional-effects)b). 
+However, suitability is an important predictor as the WAIC difference between our baseline model and that that did not include suitability was `r round(waic_diff_suitability)` ± `r round(waic_se_diff_suitability)` (Table \@ref(tab:tab-model-comparison)).
+This apparent discrepancy can be explained by the variability of the suitability-degree relationship across species.
 
@@
 
-```{r tab-model-comparison-table}
+```{r tab-model-comparison}
 model_ranking$waic %>%
@@
 
-The group level variation among communities was larger than that among species.
-The standard deviation (in the parameters scale) of the community intercepts was `r round(sd_loc_id$Estimate, 2)` [`r round(sd_loc_id$Q2.5, 2)`, `r round(sd_loc_id$Q97.5, 2)`] while the standard deviation of the species intercept was `r round(sd_org_id$Estimate, 2)` [`r round(sd_org_id$Q2.5, 2)`, `r round(sd_org_id$Q97.5, 2)`], and that of the species' suitability slope was `r round(sd_org_id_suitability$Estimate, 2)` [`r round(sd_org_id_suitability$Q2.5, 2)`, `r round(sd_org_id_suitability$Q97.5, 2)`] (95% credible intervals shown within square brakets).
-Interestingly, the slope the relationship between suitability and normalised degree was negatively correlated with the species' intercept in the model (Figure \@ref(fig:fig-random-effects)b). 
+While for some species there is a strong negative relationship between suitability and normalised degree, for some others with a strong positive relationship (Figure \@ref(fig:fig-random-effects)a). 
+Interestingly, the slope this relationship was negatively correlated with the species' intercept in the model (Figure \@ref(fig:fig-random-effects)b). 
 The mean correlation coefficient was `r round(random_cor$Estimate, 2)` [`r round(random_cor$Q2.5, 2)`, `r round(random_cor$Q97.5, 2)`].
+In other words, the slope of the suitability-degree relationship was more likelt to be positive for species with a smaller number of partners in lower-suitability and negative for species with a larger number of partners in lower-suitability conditions.
 
@@
 ```
+
+As expected, we found a strong and positive relationship between the number of possible interactions and the number of realised interactions in the community. 
+There was a large difference on WAIC between the model that included this predictor and that that excluded it. 
+This result indicates that the availability of potential partners accounts for a large proportion of the variabiity on species degree.  
+Importantly, our findings about the suitability-degree relationship were qualitatively unchanged whether this variable was included or not.
+
+The group level variation among communities was larger than that among species which further indicates the importance of the local context when determining species degree.
+Specifically, the standard deviation (in the parameters scale) of the community intercepts was `r round(sd_loc_id$Estimate, 2)` [`r round(sd_loc_id$Q2.5, 2)`, `r round(sd_loc_id$Q97.5, 2)`] while the standard deviation of the species intercept was `r round(sd_org_id$Estimate, 2)` [`r round(sd_org_id$Q2.5, 2)`, `r round(sd_org_id$Q97.5, 2)`], and that of the species' suitability slope was `r round(sd_org_id_suitability$Estimate, 2)` [`r round(sd_org_id_suitability$Q2.5, 2)`, `r round(sd_org_id_suitability$Q97.5, 2)`] (95% credible intervals shown within square brakets).
 

### 2019-11-16 paper/manuscript.Rmd
Remove unnecessary code

@@
   kableExtra::kable_styling(font_size = 8) #%>%
-  # kableExtra::add_header_above(c(" " = 1, "LOO" = 3, " " = 1))
-# 
-# waic_scores <- as.data.frame(model_ranking$waic) %>%
-#   tibble::rownames_to_column(var = "formula") %>%
-#   dplyr::select(formula, waic)
-# 
-# loo_scores <- as.data.frame(model_ranking$loo) %>%
-#   tibble::rownames_to_column(var = "formula") %>%
-#   dplyr::select(formula, elpd_diff, se_diff,  looic) 
-# 
-# loo_scores %>%
-#   dplyr::inner_join(waic_scores, by = "formula") %>%
-#   dplyr::mutate(formula = translate_model_formula(formula, "long-abv"), 
-#                 formula = kableExtra::cell_spec(formula, format = "latex", 
-#                                                 bold =nchar(formula) == max(nchar(formula)))) %>%
-#   knitr::kable("latex", 
-#                booktabs = TRUE, 
-#                digits = c(0,0,1,0,0), 
-#                format.args = list(big.mark = ","), 
-#                col.names = c("predictors", "$\\Delta$", "$SE_{\\Delta}$", "IC", "WAIC"),
-#                escape = FALSE,
-#                linesep = "",
-#                caption = "Comparison in out of sample predictive power of the baseline model (bold) and their alternatives.
-We rank models by their expected log predictive density based on their leave-one-out cross-validation information criterion (LOO).
-The standard error of the LOO difference provides rough guidance to the uncertainty of the model ranking.
-We also show the Wanatabe-Akaike information criterion (WAIC) of each model for comparison.") %>%
-#   kableExtra::kable_styling(font_size = 8) %>%
-#   kableExtra::add_header_above(c(" " = 1, "LOO" = 3, " " = 1))
 ```

### 2019-11-16 paper/manuscript.Rmd
Fix first paragraph of discussion

@@
 
-We found that environmental stress, which we measured using habitat suitability, was an important predictor for the number of partners a species interacts with. 
-However, this relationship was highly variable among species. 
-So much so that, at the population level, there is no discernible pattern between stress and the number of partners.
-Interestingly, within species, there was a significant correlation between the number of partners a species has and the stress-partners relationship itself. 
-Specifically, species with a large number of partners in low-stress communities were more likely to have a negative relationship and hence reduce the number of partners as stress increases. 
+We set out to explore wether and how environmental stress can systematically affect species degree. 
+After accounting for the pool of potential partners, we found that indeed environmental conditions contribute to determining wether a species is a generalist or a specialist in their community. 
+However, we also found that the particular effect of environment is strongly dependent on the species.
+We proposed two altenative hypotheses of how environmental stress may affect degree and we found evidence for both of them.
+Species with a large number of partners in low-stress communities were more likely to have a negative relationship and hence reduce the number of partners as stress increases. 
 Contrastingly, species in our datasets with a small number of partners in low-stress communities were more likely to have a larger number of partners in more stressful communities.

### 2019-11-16 paper/manuscript.Rmd
Fix second paragraph discussion

@@
 
-Previous research supported the idea that the differences in network structure along an environmental gradient were due solely to changes to community composition. 
-In other words, it showed that the differences between two hypothetical communities with the same species were stochastic for the most part. 
-Here, by abstracting with multiple environmental gradients into a single gradient of environmental stress, we show that this might not be the case. 
-Instead, the environment can also have a direct impact on the number of partners a species interacts with and, therefore, influence network structure. 
-Our results still show that the primary channel through which environment affects interaction probabilities is determining which species are present or absent from a particular community. 
-However, they also show that, for a large number of species, it can have a substantial effect on their realised Eltonian component of the niche.
-Indeed, as evidenced by the predictive power of competing models, habitat suitability had a substantial contribution to predicting the number of possible partners in the community.
+Our results suggest that changes in community composition are indeed the primmary channel through which environment determines changes interaction probability. 
+However, they also show that, for a large number of species, the environment may also play a substantial role on determining their realised (Eltonian) niche. 
+While previous research has recognised that environmental factors may help explain the changes in network structure along environmental gradients that cannot be explained by community composition [@tylianakis_habitat_2007], how these two factors were linked had been elusive so far [@gravel_bringing_2018].
+We believe that part of this difficulty could have arisen because species, and ultimately network structre, can respond multiple, and contrasting, ways depending on the particular bioclimatic variable being examined (e.g.
+temperature or precipitation).
+Using stress to summarise the effect on species of multiple environmental gradients allowed us to detect a clear signal of the environment in species' interaction patterns.
 

### 2019-11-16 code/figures.R
Add argument to plot of sensitivity analysis to chose type of niche

@@ -102,7 +102,8 @@ get_dist_species_multiple_locations_data <- function(clean_interactions, checked
 
 plot_sensitivity_analysis <- function(error_subsamples, min_suitability_error,
                                       min_occurrences_factor,
-                                      suitability_subsamples){
+                                      suitability_subsamples, 
+                                      chosen_niche_space = "all_species"){
   suppressPackageStartupMessages({
     library(ggplot2)
   })
@@ -110,7 +111,7 @@ plot_sensitivity_analysis <- function(error_subsamples, min_suitability_error,
   thresholds <- min_occurrences_factor %>%
     as.data.frame() %>%
     tidyr::gather(key = "niche_space") %>%
-    dplyr::filter(niche_space == "all_species")
+    dplyr::filter(niche_space == chosen_niche_space)
 
   pal <- cgm()$pal_el_green[c(4,7)]
 

### 2019-11-17 paper/manuscript.Rmd
Third paragraph of discussion

@@
 
-Although we cannot tell with certainty how much of the effect of environmental stress can be attributed to either niche or neutral processes, the patterns we observe are likely more related to the niche.
-On the one hand, it has been shown that environmental models, such as our niche factor analysis, do a poor job predicting species abundances across sites [@pearce_practical_2001; @sagarin_moving_2006].
-It would be, therefore, somewhat naive to assume that high habitat suitability translates directly to high species abundances. 
-On the other hand, even if species abundances are correlated with suitability, we show that within a community there is a wide range of suitabilities, even for the limited number of species we included in our analyses.
-Therefore, we might expect little or no overall effect of neutral processes on our response variable, as the abundance of some interaction partners might increase and decrease for others. 
-Furthermore, the fact that the effects of environmental stress do not depend on whether the species is a plant or a pollinator (for which there can be niche differences based on individual behaviour) emphasises that co-evolutionary history, which in turn shape niche processes driven by, might be driving the patterns we observe.
+Although both niche and neutral processes are relevant at determining species interactions, our model suggests that niche processes may be the predominant mechanism through which the environment *systematically* affect species degree.
+First, it is unlikely that environmental suitability is correlated to local species abundances [@pearce_practical_2001; @sagarin_moving_2006]. 
+Second, even if there is a relationship between suitability and abundances, a particular environmental gradient could have a positive effect in the abundance some species and a negative effect in others.
+Indeed, we show that within a community there is a wide range of suitability values, even for the relatively limited number of species we were able to include in our analyis.
 

### 2019-11-17 paper/manuscript.Rmd
Fourth paragraph of discussion

@@
 
-One of our most interesting results was the negative correlation between the species' intercept and the slope of the habitat suitability in our model.
-Specifically, species with a small intercept, this is, species that were likely to have an above-average number of partners in a community with little environmental stress, were more likely to interact with a smaller number of partners as stress increased.
-At least for these species, the hypothesis that species focus on partners with which they are best adapted to interact as environmental conditions deteriorate seems to hold weight.
-Contrastingly, species with a below-average number of partners in a low-stress environment were more likely to interact with a large number of partners as stress increased.
-At first glance, these species behave as facultative generalists when the environment worsens. 
-This is certainly true for this group of species in our dataset.
-However, there are some nuances to this observation once we take into account the biases inherent to community-level interaction data. 
+Recent research suggest that species are continuoisly chaning there interaction partners wherever environmental conditions change in space of time [@raimundo_adaptive_2018].
+So far it appears that this rewiring is primarly driven by generalist species [@ponisio_opportunistic_2017; @burkle_plant-pollinator_2013], presumably because generalist species are less sensitive to trait matching of their interaction partners [@caradonna_interaction_2017].
+Our results add two important nuances to these findings. 
+First, because generalists seem to focus on a smaller number of partners as environmental conditions deteriorate, we show that trait matching might still play a role in determining the interactions of generalist species.
+Second, we demonstrate that rewiring is not exclusive to generalists.
+At least a fraction of the species that appear to be specialist in their communities might be as flexible, if not more, than generalist species, effectively behaving as facultative generalists in the face of environmental change.
+These flexible specialists might, therefore, have a more significant role in network persistence than previously expected.
 Specifically, we have no information about species for which environmental conditions would, in principle, allow for a positive growth rate but are absent from our datasets.

### 2019-11-17 paper/manuscript.Rmd
Evolutionary and structural implications

@@
 These flexible specialists might, therefore, have a more significant role in network persistence than previously expected.
-Specifically, we have no information about species for which environmental conditions would, in principle, allow for a positive growth rate but are absent from our datasets.
-A ramification of this bias is that an undetermined number of species on this second group might also be more likely to focus on partners with higher trait matching as conditions deteriorate. 
-However, we are not able to detect that trend because these species are not recorded in community composition or interaction data. 
-Presumably, because their preferred partners are unavailable and as such, they are absent from the community or too rare to be observed.
-Note that the correlation between species' intercept and the slope is unlikely to be just a byproduct of our modelling framework, as, in principle, there is nothing preventing species with an above-average number of partners to interact with even more species as environmental stress increases.
 
-These observations have implications for understanding the assembly of ecological networks and how it might be impacted by climate change, which currently threatens to increase the environmental stress of species within its range.
-Previous research suggests that flexibility of interactions in ecological communities might be a rather ubiquitous phenomenon whenever environmental conditions change in space or time [@caradonna_interaction_2017].
-This flexibility has been shown to confer robustness and stability to the loss of interaction partners [@kaiser-bunbury_robustness_2010]. 
-The current paradigm of interaction turnover suggests first that trait matching is a relatively unimportant driver of interaction turnover for generalist species [@caradonna_interaction_2017]. 
-The fact that species with a high number of interactions were more likely to interact with fewer species as environmental stress increased indicates that trait matching might still play a role in determining the interactions of generalist species.
-Second, current research suggests that the rewiring of the interaction network is primarily driven by generalist species [@burkle_plant-pollinator_2013].
-We, however, demonstrate that at least a fraction of the species that appear to be specialist in their communities might be more flexible, if not more, than generalist species and, therefore, might have a more significant role in network persistence than previously expected.
-Contrastingly, specialists that are highly constrained to interact with partners of high trait-matching might be more vulnerable to increased climate change-induced environmental stress and habitat degradation.
-Taken together, the fact that most species appear to be flexible interaction partners, combined with the fact that those that are not flexible are less likely to persist, might explain why specialised communities that are highly constrained by trait matching [like some plant-hummingbird networks; @vizentin-bugoni_processes_2014; @maruyama_morphological_2014] might be relatively rare.
+While our model detected how the environment affects interaction of two types of species, generalists and flexible specialists, there is a third group that remained invisible for our model but has important implications for network persistence and stability.
+It has been shown that species that are able to flexibly vary their interaction partners and their role in the network are more likely to persist in their community as environmental conditions vary [@gaiarsa_interaction_2019].
+We propose this third group of is composed by specialists that are constrained to interact with parterns of high trait-matching and therefore were not likely to be found in more than one community. 
+If species that are not flexible are unlikely to persist over temporal or spatial environmental gradients we can expect specialised communities that are highly constrained by trait-matching [like some plant-hummingbird networks; @vizentin-bugoni_processes_2014; @maruyama_morphological_2014] to be far more vulnerable to increased climate change-induced environmental stress and habitat degradation than communities where role and interaction flexibility are more prevalent.
 
-In conclusion, we show that...
+Similarly, if the patterns we see in our models have also played a role during the evolutionary history of pollination communities, our results also help explain why only a small fraction of plant-pollinator interactions show a strong signature of deep co-evolutionary history.
+The increasses on stress that species are predicted to experience due to rapid environmental change might further erode the co-evolutionary history of specialist species.
+Communities as a whole might be set in a trayectory of even more diffuse co-evolution.
+For specialist species, at least, the longer term benefits of being able to interact with multiple partners might be more important than the shorter term benefits of interacting with partners of high trait matching.
 
-<!-- It still remains to evaluate the role of abundance and neutral processes and
+The structural implications of the "regression towards the mean" that environmental stress promotes are less clear. 
+However, it is plausible to expect that nestedness, and therefore network stability, might be reduced in the face of rapid environmental change.
+Determining exactly how the changes in degree caused by environmental stress is also reflected in systematic changes in network structure would be an interesting avenue of research. 
+This would require expanding our suitability analysis to all species in the community and compare the degree distribution of networks along a gradient of stress for the community as a whole.
 

### 2019-11-17 paper/manuscript.Rmd
Add conclusion

@@
 
-* Add in the intro that stress includes how traits mediate environment?
-* Why is the relationship different across species?
-* The environment can certainly influence the number of interactions but its very variable among species
+In conclusion, we show that the environment is able to affect the realised niche of plants and pollinators in systematic ways beyond community composition. 
+On the one hand, species that are inflexible with their interaction partners are unlikely to persist under more stressful environmental conditions. 
+On the other, species that are flexible with their interactions partners experience a regression towards intermediate levels of degree, where generalist species tend to interact with fewer, presumably more effective, partners and specialist tend to interact with more partners.
 * In the absence of abundance this is as much as we can say. 

### 2019-11-17 paper/manuscript.Rmd
Remove extra old comments

@@
 On the other, species that are flexible with their interactions partners experience a regression towards intermediate levels of degree, where generalist species tend to interact with fewer, presumably more effective, partners and specialist tend to interact with more partners.
-* In the absence of abundance this is as much as we can say. 
-* It is remarkable we found a signal given the amount of data we had it is realy not that much for our question.
-It is not surprising that the slope of suitability was small for many species as we had little data.
-The results hold for when species had
-* Implications for community assembly and network rewiring. -->
-
-<!-- We found a positive association between environmental suitability and the niche breath. 
-This relationship was maintained when we account for the overall generality of a species and even in extremely conservative model parametrization when we include the number of possible interacting species as an independent variable.
-We define "possible" interacting species as one with which the species interacts in any of our ecological communities.  -->
-
-<!-- No interaction significant between guild and relationship which highlights that differences are rooted in eco-evolutionary processes rather than behaviour.  -->
-
-<!-- Relationship is even stronger when we only include species for which we have more info. i.e. in more that 5 communities.  -->
-
-<!-- Environment can also affect neitral process because it affects encounter rates between species.
-This can happen either through changes in abundance driven by patterns of temporal or spatial overlap or through changes in the search efficiency.  -->
-<!-- We focus suitability in abiotic factors but can also be influenced by dispersal and species interactions themselves (e.g. competition and facilitation, Lortie et al. 2004).  -->
-<!-- We learnt that there is a trade-off pollination dynamics (Cagua in review?). -->
-<!-- This means that species with more environemntal favours are better prepared to deal with the trade-offs that pollination can convey. Cool! -->
-
-<!-- Remarkable that we found a consistent signal of suitability given our relatively small number of communities and the multitude of processes that shape n.
-interactions Eltonian niche.
-We didn;t even account for traits.
-Interactions can influence co-occurrence (indirect and third order too see refs in Gravel 2018) -->
-
-<!-- Add the suitability of possible competitors? I mean they are not really competitors so maybe not.  -->
-
-<!-- Discuss implications for network rewiring? -->
-
-<!-- Note that although abundances can inflence wether two species interact we cannot tease t appart because suitability is not necessarily related to abundance.
-ALthough abundance affects the frequency of the interaction, rather than wether they interacts or not (Donoso) -->
-
-<!--Mention implications for community assembly? -->
 

### 2019-11-17 paper/manuscript.Rmd
Regression to the mean idea
Check spelling manuscript

@@
 It is, therefore, not surprising that, despite limitations on the spatial extent or the number of environmental gradients considered, multiple studies have been able to show how changes to interactions can be related to environmental change [@tylianakis_ecological_2017].
-For instance, some studies suggest that the strenghth of some trophic interactions, like predation [@mckinnon_lower_2010; @vucic-pestic_warming_2011] and herbivory [@baskett_latitudinal_2018], can increase with temperature but might decrease with precipitation [@pires_predicted_2016].
+For instance, some studies suggest that the strength of some trophic interactions, like predation [@mckinnon_lower_2010; @vucic-pestic_warming_2011] and herbivory [@baskett_latitudinal_2018], can increase with temperature but might decrease with precipitation [@pires_predicted_2016].
 Some other studies, however, have shown either no effect (on average) or non-linear effects of temperature or precipitation on plant-pollinator interactions [@devoto_patterns_2005; @gravel_bringing_2018].
@@
 We therefore also expect that as environmental stress increases species with a relatively small number of partners are more likely to engage with more partners and broaden their trophic niche. 
-Species with a large number of partners, on the other hand, should have a larger pool of available partners and might, therefore, be more likely to narrow their niche under environmental stress by focusing on the most benefitial partners.
+Species with a large number of partners, on the other hand, should have a larger pool of available partners and might, therefore, be more likely to narrow their niche under environmental stress by focusing on the most beneficial partners.
 Importantly, when testing these hypotheses, we control for the potential effects of the environment in community composition and the size of the species fundamental niche, both from an Eltonian (interactions) and Grinellian (environment) perspective.
@@
 A critical step towards reducing this uncertainty is to ensure that the names used to identify species are valid and unambiguous, which in turn allow us to obtain further information from biological databases and accurately match species across studies.
-Therefore, our first step was to ensure consistent spelling and standarisation of species names synonyms (See Supplementary Methods).
+Therefore, our first step was to ensure consistent spelling and standardisation of species names synonyms (See Supplementary Methods).
 This ensured that the matching of species across studies was as accurate as possible. 
@@
 We retrieved `r round(sum(n_occurrences$N)/1000000, digits = 1)` million occurrences from the Global Biodiversity Information Facility (GBIF; https://www.gbif.org). 
-Issues with data quality are a central issue hampering the use of publicly available species occurrence GBIF data in ecology and biogeography (Jetz et al 2019). 
+Issues with data quality are a central issue hampering the use of publicly available species occurrence GBIF data in ecology and biogeography [@jetz_essential_2019]. 
 We, therefore we followed a series of filters and geographic heuristics to correct or remove erroneous and imprecise referencing records [See supplementary methods; @zizka_coordinatecleaner_2019] which allowed us to identify and remove `r round(sum(n_dirty_occurrences$N)/1000000, digits = 1)` million problematic occurrences from further analysis.
@@
 Sets of occurrence data tend to be spatially aggregated due to sample bias (tendency to collect close to cities, certain countries). 
-Spatial autocorrelation arises in ecological data because geographically clumped records tend to be more similar, in physical characteristics and/or species abundances, than are pairs locations that are farther apart.
+Spatial autocorrelation arises in ecological data because geographically clumped records tend to be more similar, in physical characteristics and/or species abundances, than are pairs of locations that are farther apart.
 To account for such spatial dependency in occurrence data, if a species had more than one occurrence records within one of the cells of the bioclimatic raster, we only included one of the occurrence records.
@@
 We then used a set of bayesian multilevel models to evaluate the impact of environmental suitability on the number of partners a species has. 
-Specifically, we use the normalised degree of species as our response variable, this is, the number of species it interacts with given the number of species in the opposite guild [@martin_gonzalez_centrality_2010].
+Specifically, we use the normalised degree of species as our response variable; this is, the number of species it interacts with given the number of species in the opposite guild [@martin_gonzalez_centrality_2010].
 The normalised degree was modelled using a logit link function, and a binomial distribution in which the number of species interacts with is the number of successes, and the number of species in the opposite guild is the number of trials.
@@
 As we were interested in understanding whether the effect of habitat suitability is conditional on the species guild (plant or pollinator), we, therefore, included guild and its interaction with suitability in the model.
-We allowed the intercept of degree and slope of the suitability-degree relationship to vary among species, this allowed us to investigate two questions. 
+We allowed the intercept of degree and slope of the suitability-degree relationship to vary among species. 
+This allowed us to investigate two questions. 
 First, it allows us to inspect the extent to which suitability is a population or a group level effect. 
@@
 \@ref(fig:fig-sensitivity-analysis)).
-We therefore removed from further analyses `r n_spp_not_enough_occ` species for which we did not have enough occurrences to obtain robust estimates.
-When inspecting the suitability values of the analysed species we found that most communities included species for which habitat suitability was low and species for which it was high (Fig.
+We, therefore, removed from further analyses `r n_spp_not_enough_occ` species for which we did not have enough occurrences to obtain robust estimates.
+When inspecting the suitability values of the analysed species, we found that most communities included species for which habitat suitability was low and species for which it was high (Fig.
 \@ref(fig:fig-median-suitability)).
@@
 
-Our models performed relativelly well.
-The bayesian R-squared for our baseline model was `r round(bayesian_r2_baseline[1], digits = 2)`, which indicates our models were able to capture a large proporton of the variability on the data. 
-Overall we found that environmental suitability does not show a consistent pattern accross species. 
-Indeed, when looking at the population level effects, suitability has virtually no relationship with normalised degree, neither for plants or pollinators (Figure \@ref(fig:fig-conditional-effects)b). 
+Our models performed relatively well.
+The bayesian R-squared for our baseline model was `r round(bayesian_r2_baseline[1], digits = 2)`, which indicates our models were able to capture a large proportion of the variability on the data. 
+Overall we found that environmental suitability does not show a consistent pattern across species. 
+Indeed, when looking at the population level effects, suitability has virtually no relationship with the normalised degree, neither for plants or pollinators (Figure \@ref(fig:fig-conditional-effects)b).
 However, suitability is an important predictor as the WAIC difference between our baseline model and that that did not include suitability was `r round(waic_diff_suitability)` ± `r round(waic_se_diff_suitability)` (Table \@ref(tab:tab-model-comparison)).
@@
          ".
-These values correspond to the median number of species in each guild respectively.
-In each panel we condition on the mean values of all other predictors in the model, mean values for each predictor are indicated with a vertical dashed line.
-For model fitting, we scaled all predictors to have mean of zero and unit variance.
+These values correspond to the median number of species in each guild, respectively.
+In each panel, we condition on the mean values of all other predictors in the model, mean values for each predictor are indicated with a vertical dashed line.
+For model fitting, we scaled all predictors to have a mean of zero and unit variance.
 However, with the exception of environmental niche size, here we show the unscaled predictors to facilitate interpretation.
-To illustrate the uncertainity around the fitted estimates we plot the fits of 100 independent draws from the posterior distribution.
+To illustrate the uncertainty around the fitted estimates, we plot the fits of 100 independent draws from the posterior distribution.
 The thick lines indicate the mean values of the response distribution.
-As there was no interaction between guild and generality or the number of possible interactions, for these two predictors we only show conditional the conditional effect of pollinators.")
+As there was no interaction between guild and generality or the number of possible interactions, for these two predictors, we only show conditional the conditional effect of pollinators.")
 
@@
 While for some species there is a strong negative relationship between suitability and normalised degree, for some others with a strong positive relationship (Figure \@ref(fig:fig-random-effects)a). 
-Interestingly, the slope this relationship was negatively correlated with the species' intercept in the model (Figure \@ref(fig:fig-random-effects)b). 
+Interestingly, the slope of this relationship was negatively correlated with the species' intercept in the model (Figure \@ref(fig:fig-random-effects)b). 
 The mean correlation coefficient was `r round(random_cor$Estimate, 2)` [`r round(random_cor$Q2.5, 2)`, `r round(random_cor$Q97.5, 2)`].
-In other words, the slope of the suitability-degree relationship was more likelt to be positive for species with a smaller number of partners in lower-suitability and negative for species with a larger number of partners in lower-suitability conditions.
+In other words, the slope of the suitability-degree relationship was more likely to be positive for species with a smaller number of partners in lower-suitability and negative for species with a larger number of partners in lower-suitability conditions.
 
@@
 fig_random_effects_legend <- 
-  paste0("Species level effects of suitability.
+  paste0("Species-level effects of suitability.
 (a) Conditional effect of suitability for individual species.
@@
 As in the previous figure, fitted values assume a hypothetical community of median size.
-In each panel we highlight two species for which the relationship between environental suitability and normalised degree was particularly strong.
+In each panel, we highlight two species for which the relationship between environmental suitability and the normalised degree was particularly strong.
 ",
@@
 There was a large difference on WAIC between the model that included this predictor and that that excluded it. 
-This result indicates that the availability of potential partners accounts for a large proportion of the variabiity on species degree.  
-Importantly, our findings about the suitability-degree relationship were qualitatively unchanged whether this variable was included or not.
+This result indicates that the availability of potential partners accounts for a large proportion of the variability on species degree.  
+Importantly, our findings of the suitability-degree relationship were qualitatively unchanged whether this variable was included or not.
 
-The group level variation among communities was larger than that among species which further indicates the importance of the local context when determining species degree.
+The group-level variation among communities was larger than that among species which further indicates the importance of the local context when determining species degree.
 Specifically, the standard deviation (in the parameters scale) of the community intercepts was `r round(sd_loc_id$Estimate, 2)` [`r round(sd_loc_id$Q2.5, 2)`, `r round(sd_loc_id$Q97.5, 2)`] while the standard deviation of the species intercept was `r round(sd_org_id$Estimate, 2)` [`r round(sd_org_id$Q2.5, 2)`, `r round(sd_org_id$Q97.5, 2)`], and that of the species' suitability slope was `r round(sd_org_id_suitability$Estimate, 2)` [`r round(sd_org_id_suitability$Q2.5, 2)`, `r round(sd_org_id_suitability$Q97.5, 2)`] (95% credible intervals shown within square brakets).
@@
 
-We set out to explore wether and how environmental stress can systematically affect species degree. 
-After accounting for the pool of potential partners, we found that indeed environmental conditions contribute to determining wether a species is a generalist or a specialist in their community. 
-However, we also found that the particular effect of environment is strongly dependent on the species.
-We proposed two altenative hypotheses of how environmental stress may affect degree and we found evidence for both of them.
+We set out to explore whether and how environmental stress can systematically affect species degree. 
+After accounting for the pool of potential partners, we found that indeed environmental conditions contribute to determining whether a species is a generalist or a specialist in their community. 
+However, we also found that the particular effect of the environment is strongly dependent on the species.
+We proposed two alternative hypotheses of how environmental stress may affect the degree, and we found evidence for both of them.
 Species with a large number of partners in low-stress communities were more likely to have a negative relationship and hence reduce the number of partners as stress increases. 
 Contrastingly, species in our datasets with a small number of partners in low-stress communities were more likely to have a larger number of partners in more stressful communities.
+In summary, environmental stress pushes species that are flexible enough to change their interaction partners towards intermediate levels of degree, a so-called "regression towards the mean".
 
-Our results suggest that changes in community composition are indeed the primmary channel through which environment determines changes interaction probability. 
-However, they also show that, for a large number of species, the environment may also play a substantial role on determining their realised (Eltonian) niche. 
+Our results suggest that changes in community composition are indeed the primary channel through which the environment determines changes interaction probability. 
+However, they also show that, for a large number of species, the environment may also play a substantial role in determining their realised (Eltonian) niche. 
 While previous research has recognised that environmental factors may help explain the changes in network structure along environmental gradients that cannot be explained by community composition [@tylianakis_habitat_2007], how these two factors were linked had been elusive so far [@gravel_bringing_2018].
-We believe that part of this difficulty could have arisen because species, and ultimately network structre, can respond multiple, and contrasting, ways depending on the particular bioclimatic variable being examined (e.g.
+We believe that part of this difficulty could have arisen because species, and ultimately network structure, can respond in multiple and contrasting, ways depending on the particular bioclimatic variable being examined (e.g.
 temperature or precipitation).
@@
 First, it is unlikely that environmental suitability is correlated to local species abundances [@pearce_practical_2001; @sagarin_moving_2006]. 
-Second, even if there is a relationship between suitability and abundances, a particular environmental gradient could have a positive effect in the abundance some species and a negative effect in others.
-Indeed, we show that within a community there is a wide range of suitability values, even for the relatively limited number of species we were able to include in our analyis.
+Second, even if there is a relationship between suitability and abundances, a particular environmental gradient could have a positive effect on the abundance of some species and a negative effect on others.
+Indeed, we show that within a community there is a wide range of suitability values, even for the relatively limited number of species we were able to include in our analysis.
 
-Recent research suggest that species are continuoisly chaning there interaction partners wherever environmental conditions change in space of time [@raimundo_adaptive_2018].
-So far it appears that this rewiring is primarly driven by generalist species [@ponisio_opportunistic_2017; @burkle_plant-pollinator_2013], presumably because generalist species are less sensitive to trait matching of their interaction partners [@caradonna_interaction_2017].
+Recent research suggests that species are continuously changing their interaction partners wherever environmental conditions change in space or time [@raimundo_adaptive_2018].
+So far it appears that this rewiring is primarily driven by generalist species [@ponisio_opportunistic_2017; @burkle_plant-pollinator_2013], presumably because generalist species are less sensitive to trait matching of their interaction partners [@caradonna_interaction_2017].
 Our results add two important nuances to these findings. 
@@
 
-While our model detected how the environment affects interaction of two types of species, generalists and flexible specialists, there is a third group that remained invisible for our model but has important implications for network persistence and stability.
-It has been shown that species that are able to flexibly vary their interaction partners and their role in the network are more likely to persist in their community as environmental conditions vary [@gaiarsa_interaction_2019].
-We propose this third group of is composed by specialists that are constrained to interact with parterns of high trait-matching and therefore were not likely to be found in more than one community. 
+While our model detected how the environment affects the interactions of two types of species, generalists and flexible specialists, there is a third group that remained invisible for our model but has important implications for network persistence and stability.
+It has been shown that species that are able to vary their interaction partners flexibly and their role in the network are more likely to persist in their community as environmental conditions vary [@gaiarsa_interaction_2019].
+We propose this third group of is composed of specialists that are constrained to interact with partners of high trait-matching and therefore were not likely to be found in more than one community. 
 If species that are not flexible are unlikely to persist over temporal or spatial environmental gradients we can expect specialised communities that are highly constrained by trait-matching [like some plant-hummingbird networks; @vizentin-bugoni_processes_2014; @maruyama_morphological_2014] to be far more vulnerable to increased climate change-induced environmental stress and habitat degradation than communities where role and interaction flexibility are more prevalent.
 
-Similarly, if the patterns we see in our models have also played a role during the evolutionary history of pollination communities, our results also help explain why only a small fraction of plant-pollinator interactions show a strong signature of deep co-evolutionary history.
-The increasses on stress that species are predicted to experience due to rapid environmental change might further erode the co-evolutionary history of specialist species.
-Communities as a whole might be set in a trayectory of even more diffuse co-evolution.
-For specialist species, at least, the longer term benefits of being able to interact with multiple partners might be more important than the shorter term benefits of interacting with partners of high trait matching.
+Similarly, if the patterns we see in our models have also played a role during the evolutionary history of pollination communities, our results also help explain why only a small fraction of plant-pollinator interactions show a strong signature of deep co-evolutionary history [@hutchinson_cophylogenetic_2017].
+The increases on the stress that species are predicted to experience due to rapid environmental change might further erode the co-evolutionary history of specialist species.
+Communities as a whole might be set in a trajectory of even more diffuse co-evolution.
+For specialist species, at least, the longer-term benefits of being able to interact with multiple partners might be more important than the shorter-term benefits of interacting with partners of high trait matching.
 

### 2019-11-17 paper/manuscript.Rmd
A bit more clarity

@@
 
-**Data accessibility:** Data supporting the results will be accessible in an appropriate data repository after publication. The DOI will be included here.
+**Data accessibility:** Data supporting the results will be accessible in an appropriate data repository after publication. We will include the DOI here.
 
@@
 Therefore, our first step was to ensure consistent spelling and standardisation of species names synonyms (See Supplementary Methods).
-This ensured that the matching of species across studies was as accurate as possible. 
+This step ensured that the matching of species across studies was as accurate as possible. 
 The cleaning process resulted on a total of `r format(stats_clean_int$pla_id, big.mark = ",")` plants and `r format(stats_clean_int$ani_id, big.mark = ",")` pollinator species distributed across `r format(stats_clean_int$loc_id)` locations arround the globe (Figure \@ref(fig:fig-worldmap), \@ref(fig:fig-distribution-species-mult-locations)).
@@
 
-After obtaining information about species occurrence and the environment, we then merged these two datasets such that the location of each occurrence was characterised by a vector with details of our 37 bioclimatic and topographic variables.
+After obtaining information about species occurrence and the environment, we then merged these two datasets such that a vector with details of our 37 bioclimatic and topographic variables characterised the location of each occurrence.
 
@@
 We allowed the intercept of degree and slope of the suitability-degree relationship to vary among species. 
-This allowed us to investigate two questions. 
+This approach allowed us to investigate two questions. 
 First, it allows us to inspect the extent to which suitability is a population or a group level effect. 
@@
 All models were fitted under a bayesian framework using the R package `brms` `r as.character(packageVersion('brms'))` [@burkner_brms_2017; @burkner_advanced_2018] as an interface for Stan [@carpenter_stan_2017].
-For each model, we used four Markov chains of 4,000 iterations each; half of the iterations were used for warmup.
+For each model, we used four Markov chains of 4,000 iterations each; we used half of the iterations for warmup.
 We used weakly informative priors for all model parameters. 
@@
 These values correspond to the median number of species in each guild, respectively.
-In each panel, we condition on the mean values of all other predictors in the model, mean values for each predictor are indicated with a vertical dashed line.
+In each panel, we condition on the mean values of all other predictors in the model.
+We indicate mean values for each predictor with a vertical dashed line.
 For model fitting, we scaled all predictors to have a mean of zero and unit variance.
-However, with the exception of environmental niche size, here we show the unscaled predictors to facilitate interpretation.
+However, except for environmental niche size, here we show the unscaled predictors to facilitate interpretation.
 To illustrate the uncertainty around the fitted estimates, we plot the fits of 100 independent draws from the posterior distribution.
@@
 While for some species there is a strong negative relationship between suitability and normalised degree, for some others with a strong positive relationship (Figure \@ref(fig:fig-random-effects)a). 
-Interestingly, the slope of this relationship was negatively correlated with the species' intercept in the model (Figure \@ref(fig:fig-random-effects)b). 
+Interestingly, the slope of this relationship correlates negatively with the species' intercept in the model (Figure \@ref(fig:fig-random-effects)b). 
 The mean correlation coefficient was `r round(random_cor$Estimate, 2)` [`r round(random_cor$Q2.5, 2)`, `r round(random_cor$Q97.5, 2)`].
@@
 This result indicates that the availability of potential partners accounts for a large proportion of the variability on species degree.  
-Importantly, our findings of the suitability-degree relationship were qualitatively unchanged whether this variable was included or not.
+Importantly, our findings of the suitability-degree relationship were qualitatively unchanged whether we included this variable or not.
 
@@
 While previous research has recognised that environmental factors may help explain the changes in network structure along environmental gradients that cannot be explained by community composition [@tylianakis_habitat_2007], how these two factors were linked had been elusive so far [@gravel_bringing_2018].
-We believe that part of this difficulty could have arisen because species, and ultimately network structure, can respond in multiple and contrasting, ways depending on the particular bioclimatic variable being examined (e.g.
+We believe that part of this difficulty could have arisen because species, and ultimately network structure, can respond in multiple and contrasting, ways depending on the particular bioclimatic variable examined (e.g.
 temperature or precipitation).
@@
 Although both niche and neutral processes are relevant at determining species interactions, our model suggests that niche processes may be the predominant mechanism through which the environment *systematically* affect species degree.
-First, it is unlikely that environmental suitability is correlated to local species abundances [@pearce_practical_2001; @sagarin_moving_2006]. 
+First, it is unlikely that environmental suitability correlates to local species abundances [@pearce_practical_2001; @sagarin_moving_2006]. 
 Second, even if there is a relationship between suitability and abundances, a particular environmental gradient could have a positive effect on the abundance of some species and a negative effect on others.
@@
 While our model detected how the environment affects the interactions of two types of species, generalists and flexible specialists, there is a third group that remained invisible for our model but has important implications for network persistence and stability.
-It has been shown that species that are able to vary their interaction partners flexibly and their role in the network are more likely to persist in their community as environmental conditions vary [@gaiarsa_interaction_2019].
+Species that are able to vary their interaction partners flexibly and their role in the network are more likely to persist in their community as environmental conditions vary [@gaiarsa_interaction_2019].
 We propose this third group of is composed of specialists that are constrained to interact with partners of high trait-matching and therefore were not likely to be found in more than one community. 
-If species that are not flexible are unlikely to persist over temporal or spatial environmental gradients we can expect specialised communities that are highly constrained by trait-matching [like some plant-hummingbird networks; @vizentin-bugoni_processes_2014; @maruyama_morphological_2014] to be far more vulnerable to increased climate change-induced environmental stress and habitat degradation than communities where role and interaction flexibility are more prevalent.
+If species that are not flexible are unlikely to persist over temporal or spatial environmental gradients, we can expect specialised communities that are highly constrained by trait-matching [like some plant-hummingbird networks; @vizentin-bugoni_processes_2014; @maruyama_morphological_2014] to be far more vulnerable to increased climate change-induced environmental stress and habitat degradation than communities where role and interaction flexibility are more prevalent.
 
@@
 The increases on the stress that species are predicted to experience due to rapid environmental change might further erode the co-evolutionary history of specialist species.
-Communities as a whole might be set in a trajectory of even more diffuse co-evolution.
+Communities as a whole might be in a trajectory of even more diffuse co-evolution.
 For specialist species, at least, the longer-term benefits of being able to interact with multiple partners might be more important than the shorter-term benefits of interacting with partners of high trait matching.
@@
 However, it is plausible to expect that nestedness, and therefore network stability, might be reduced in the face of rapid environmental change.
-Determining exactly how the changes in degree caused by environmental stress is also reflected in systematic changes in network structure would be an interesting avenue of research. 
-This would require expanding our suitability analysis to all species in the community and compare the degree distribution of networks along a gradient of stress for the community as a whole.
+Determining exactly how the changes in degree caused by environmental stress reflect on systematic changes in network structure would be an interesting avenue of research. 
+Answering this question would require expanding our suitability analysis to all species in the community and compare the degree distribution of networks along a gradient of stress for the community as a whole.
 
-In conclusion, we show that the environment is able to affect the realised niche of plants and pollinators in systematic ways beyond community composition. 
+In conclusion, we show that the environment can affect the realised niche of plants and pollinators in systematic ways beyond community composition. 
 On the one hand, species that are inflexible with their interaction partners are unlikely to persist under more stressful environmental conditions. 

### 2019-11-17 paper/supp-info.Rmd
Loadd interaction citations in supp info
Spelling supp info

@@
 
-## Reducing taxononic uncertainty
+## Reducing taxonomic uncertainty
 
@@
 loadd(checked_sp_names, spp, manual_name_corrections, problematic_networks)
+loadd(interaction_citations)
 loadd(int_metadata)
@@
 
-Data was obtained from the Web of Life database [@fortuna_web_2014] which includes data from `r length(interaction_citations$BIBTEXKEY)` published studies `r all_int_cites`.
+Data were obtained from the Web of Life database [@fortuna_web_2014] which includes data from `r length(interaction_citations$BIBTEXKEY)` published studies `r all_int_cites`.
 
@@
 Therefore, we followed @zizka_coordinatecleaner_2019 and applied a series of simple filters and geographic heuristics to remove those of lower quality. 
-Specifically, we removed all occurrences with (*i*) a coordinate uncertainty larger than 100km; (*ii*) those recorded prior to 1945 (as records prior to this date have been shown to be often impreciseref); (*iii*) those in which the number of counts in the occurrence were registered was either zero (as that indicates that the species has not been recorded); and (*iv*) those occurrences in which the "basis of record" was not a human observation or a preserved specimen (as occirrences from unknown and fossil records are known to be highly unreliable).
+Specifically, we removed all occurrences with (*i*) a coordinate uncertainty larger than 100km; (*ii*) those recorded prior to 1945 (as records prior to this date have been shown to be often imprecise); (*iii*) those in which the number of counts in the occurrence was registered was either zero (as that indicates that the species has not been recorded); and (*iv*) those occurrences in which the "basis of record" was not a human observation or a preserved specimen (as occurrences from unknown and fossil records are known to be highly unreliable).
 We then used the R package `CoordinateCleaner` `r as.character(packageVersion('taxize'))` [@zizka_coordinatecleaner_2019] and land mass and country data from Natural Earth (https://www.naturalearthdata.com) with a 1:10,000,000 scale to further identify and remove problematic occurrences.

### 2019-11-17 paper/draft-info.Rmd
Add some stuff that I've done to draft info
Add to-do of checking warnings when filling environmental varibles
Update draft info

--- 2019-09-08 paper/draft-info.Rmd
@@
 
-## Requests to coauthors
-
-* Should I include more networks?
-Easy to get some more from other published studies.
-Could improve the manuscript but every new data set has to be cleaned independently.
-This could take around 2 days per network.
-* Should I increase the resolution of the bioclimatic variables?
-Currently working with 2.5' (~5km).
-Increasing to 30'' (~1km) might improve the analysis but we're talking about working with ~25GB+ of data instead of the 1GB used now.
-* Audrey: Could you please fill in the gaps in the rationale behind filtering out occurrences with potential low quality coordinates (\lr{rationale-occurrence-filtering})
-* I chose, rather arbitrarily, a mean absolute error of 10% for the sensitivity analysis. Does this choice sound appropiate to you?
-
 ## Done
 
-* Downloaded network data from the Web of Life and cleaned it.
-I didn't anticipated data needed SO MUCH work!
-I estimated three days to do this but took roughly 3 weeks to do it propperly and there is still some work to do.
-Quite a mess...
-* Downloaded bioclimatic and habitat data
-* Dowloaded species occurrences. Wasn't straightforward as there is a lot of species and lots of restrictions with the GBIF API. About a week getting this to work.
-* Calculated environmental niche size and the environmental suitability of species in their communities
-* Modelled the normalised degree of species as a proxy of eltonian niche size using a bayesian framework
+* Refocused the introduction
+* Moved details of taxonomic data cleaning process to supplementary materials
+* Moved details of occurrence data cleaning process to supplementary materials
+* Reorganised the results
+* Rewrote most of the discussion
+* Changed some details about how species are cleaned
+* Removed species generality and the breadth of the environmental niche from the model
 
@@
 
-* Manually fix the remaining species names that are incorrect and were not picked up by the automatic procedure. Doing 5-10 per day, so should be done in a couple months
-* Fix references. There are lots of mistakes re. author, years and publication venue particularly for those from which data was downloaded.
-
-<!-- Interactions are selected by species depending on the relative benefit they provide.
-The assumption goes that species with a large number of interactions are benefit relatively little from each of them, and species with a small number benefit largely with them, this is they focus in more optimal pollinators.
--->
-
-<!-- AND  -->
-
-<!-- We know that interactions are influenced by the environment.  -->
-
-<!-- BUT -->
-
-<!-- We don't know how exactly wether the enviroment influences the patterns of generalisation/specialization.  -->
-
-<!-- One option is that when species are in detrimental environmental conditions focus on most optimal partners and as such interact with a smaller number of species.  -->
-<!-- An alternative hypotheisis is that when species are in favourable environmental conditions they can afford to be more picky about their interactions and as such avoid those of less value, while individuals in unfavourable conditions must get rewards from whatever they can get.
--->
-
-<!-- THEREFORE -->
-
-<!-- We used a global dataset on plant pollinator interactions, species occurrence, and bioclimatic data to test these hypotheses.  -->
-<!-- If the first option is true we should see a negative relationship between environmental sutability and the relative degree of a species.  -->
-<!-- If the second option is true we should see the opposite, a positive relationship between environmental suitability and the relative degree of a species.  -->
-
-<!-- **Is my central topic turnover of interactions**? If yes then I should quanitify turnover accross high and low suitability areas.  -->
-
-<!-- **Continuation: compare the suitability of the species that species do not interact with vs those that interact (when a possible interaction occurs but is not realised)?** -->
-
-<!-- **Continuation: average suitability of all species.
-If avg.
-competitors suitability is low, species, facilitation more common and resource sharing should increase.
-If avg.
-suitability is high, the opposite should happen?** -->
-
-<!-- **Continuation: Should I use relative suitability instead of absolute? Is not total suitability what matters but that relative to other species?**  -->
-
-<!-- **Is smaller degree a smaller Eltonian niche?** Should I frame this as the relationship between Grinellian and Eltonian.
-A better position in the grinellian niche allows for a larger Realised Eltonian niche.
-A problem of stating the hypothesis in terms of niches is that there are many definitions of niche and people is picky -->
-
-<!-- *Previous state of the world: We know interactions change with the environment but we don't know beyond co-occurrence patterns* -->
-
-<!-- Notes: -->
-
-<!-- **From donoso et al 2017: ** Intro: It is generally agreed that both neutral and niche-driven processes contribute to the occurrence of pairwise mutualistic interactions and network structure.
-That is, whether or not two species interact can be thought of as the result of two sequential processes.
-First, there is a stochastic (neutral) process driven by the local abundances of interacting species, such that abundant species are more likely to encounter each other than are rare ones.
-Secondly, there is a deterministic process driven by a matching of traits (e.g., phenology, morphology, behavior, etc.) that finally permits the interaction between co- occurring species.
--->
-
-<!-- Intro: Mutualistic interactions are fundamentally dynamic, such that there is a turnover of species and individuals in space and time (Carnicer et al., 2009; Laliberté and Tylianakis, 2010; Hagen et al., 2012).
--->
-
-<!-- I would then add a thrird one that is dictated by the rewards provided by an interaction. Maybe? -->
-
-<!-- Conclusion: Overall we found that the assemblage of pairwise interactions depended on the neutral effects of interacting species abundances (the more abundant the species of fruit and frugivore, the more frequent their pairwise interaction) and on the local context of ecological neighborhoods.
--->
-
-<!-- **From Boulangeat et al 2012:** Intro: These drivers of species distributions may act at different spatial scales.
-For instance, frequent consideration is given to abiotic variables acting at large spatial scales.
-On the other hand, biotic interactions and consumer-resource dynamics are assumed to occur at smaller spatial scales.
--->
-
-<!-- Conclusion: Biotic inetractions are def important at determining abundace.
-They observed positive effects of biotic interactions at colder climates (low suitability for plants) -- suggest facilitation.
-and negative effects of interactions at warmer climates (high suitability) suggesting competition.
-*Should I calculate the suitability of other species and test this?* -->
-
-<!-- **From Dormann et al 2018:** Intro: Sometimes, an organism will be little affected by com- petitors, mutualists, pathogens or predators; a mature tree may appear to grow unfettered by its neighbours for decades.
-In other cases, an individual may struggle to survive the pressure of its community during every hour of its life; for example, a fish preying and escaping predators in a small river.
-Biotic interactions such as these can have major effects on local processes and population dynamics, and some, but not neces- sarily all, scale up to co-determining the range of a species (reviewed, e.g., by Wisz et al., 2013).
--->
-
-<!-- Most BI-SDMs assume that biotic interactions are constant in space and time.
-It is more likely, however, that interaction strengths are modulated by the biotic and abiotic environment.
-Experimental studies showed that rates of biological interactions depend on environmental conditions: rates of herbivory are temperature dependent (Burnside, Erhardt, Hammond, & Brown, 2014); mycorrhizal symbioses change with resource availability (Cox, Barsoum, Lilleskov, & Bidartondo, 2010; Johnson, Wilson, Bowker, Wilson, & Miller, 2010); and plant–plant interactions can shift from competitive to facilitative along a stress gra- dient (Bertness & Callaway, 1994).
-Additionally, environmental change can modulate biotic interactions via phenological mismatches, such as for plant–pollinator interactions (Berg et al., 2010; Elzinga et al., 2007).
-In these conditions, the model must also allow for the interplay of environmental and biotic interactions (Clark et al., 2011), which has only recently started to be explored in BI-SDMs (Tikhonov, Abrego, Dunson, & Ovaskainen, 2017).
--->
-
-<!-- **From Gravel et al.
-2018**: We apply this framework to host–parasite interactions across Europe and ind that two aspects of the environment (temperature and precipitation) exert a strong imprint on species co-occurrence, but not on species interactions.
-Even where species co-occur, interaction proves to be stochastic rather than deterministic, adding to variation in realized network structure.
-*Bingo: I show it's not completely stochastic and is likely to be determined by the suitability hehe* -- for real ( They test prob.
-of two co-occurring species to interact does not depend on environment.
-I test single species thingy).
-Should I do that?
-suit sp.1 and suit sp.
-2?
-It;s not about the environment, but about how the environment affect the species involved.
-Buya!
--->
-
-<!-- There is, however, ample evidence that interaction networks vary in space and time (Laliberté and Tylianakis 2010, Poisot et al.
-2012, 2016c, Schleuning et al.
-2012, Albouy et al.
-2014, Trøjelsgaard et al.
-2015), even though there is no common framework with which to generalize these results.
--->
-
-<!-- he occurrence and intensity of interactions could vary because of the environment, species abundance, and higher- order ecological interactions (Poisot et al.
-2015).
-*Well do I show that could vary because of more stuff?* -->
-
-<!-- Variation in community composition can be independent of variation of ecological interactions, suggesting that species and inter- ac tion distribution may well respond to diferent drivers (Poisot et al.
-2012).
--->
-
-<!-- Ecological interactions could also vary with the environment.
-Although it is rare to see a conditional representation of pairwise ecological interactions, experimental studies have frequently revealed interactions to be sensitive to the environment.
-For instance, McKinnon et al.
-(2010) showed that predation risks of shorebirds vary at the continental scale, decreasing from the south to the north.
-It is also common to see increasing top-down control with temperature (Shurin et al.
-2012, Gray et al.
-2016).
-Efects of the environment on interactions (Gibert and DeLong 2014) also propagate up the community and inluence net- work structure (Tylianakis et al.
-2007, Petchey et al.
-2010, Woodward et al.
-2010).
--->
-
-<!-- In terms of species interacting with each other, our analysis suggests that the environment leaves a detectable imprint on species co-occurrence, but only a slight mark on the occurrence of realized links among species in a speciic place: the prob- ability of inding a given combination of species at a higher and a lower trophic level at the same site was clearly afected by the environment, whereas the probability of observing an interaction between the two was, given co-occurrence, not signiicantly so.
--->
-
-<!-- This does not imply that species will always interact when they meet – **although this is a basic assumption in most documented metawebs to date** (Havens 1992, Wood et al. 2015).  -->
-
-<!-- Evidence that the structure of ecological networks does vary across habitats (Tylianakis et al.
-2007), over environmental gradients (Lurgi et al.
-2012) and in time (Simanonok and Burkle 2014) is accumulating rapidly.
--->
-
-<!-- **Devictor 2010:** I can use degree to quantify realised eltonian niche -->
-
-<!-- **Godsoe 2017**: Biogeographers and community ecologists have long debated the importance of biotic interactions (see Glossary) for species distributions and range limits [1–5].*But seldom the other way arround?* -->
-
-<!-- **Tylianakis 2017**: Interactions can change because of environment because environment and habitat can change encounter rate.  -->
-
-<!-- Specialist species (that lack flexibility in their choice of interaction partner) should theoretically be most vulnerable to phenological decoupling.
-However, one study of pollinator communities along an elevational gradient found that apparently specialized pollinators were facultatively more generalist than they appeared and could adapt their visitation patterns across sites as much as generalists to avoid phenological asynchrony (Benadi et al.
-2014).
-Similarly, duration of the fruiting season has been shown to predict the degree and strength of seed-dispersal interactions (Gonza ́ lez- Castro et al.
-2012), and a long-term study found no difference between specialist and generalist plant species in their interannual fluctuations in phenology and pollinator richness (Petanidou et al.
-2014).
-Although these findings suggest that the facultative generalism of pollination mutualisms may confer robustness to these networks in the face of altered phenology (see also discussion on rewiring above), this robustness may depend on the climate context and the diversity and specialization within the network (Hoiss et al.
-2015).
-Moreover, less-generalized interactions such as those between parasites and hosts may show less flexibility.
--->
-
-<!-- many trophic and mutualistic interactions are relatively generalized and potentially opportunistic (Pimm et al.
-1991).
-Thus, we may expect that ecological networks will comprise a mixture of interactions that persist over the long-term owing to trait matching of partners through coevolution (Go ́ mez et al.
-2010, Guimaraes et al.
-2011) and those that occur opportunistically, perhaps with inferior long-term fitness benefits (Aizen et al.
-2016).
-Increases in the frequency of the former will strengthen any pattern of phylogenetic congruence, whereas increases in the latter will erode it.
--->
-
-<!-- For example, environmental stressors could cause species to narrow their trophic breadth by increasing the search time to find alternative partners (Gauld 1987) or by imposing limits on the quality of interaction partners that can be used (i.e., using only resources to which a species is best adapted).
-Phylogenetic congruence becomes stronger in parasitoid–host networks with increasing temperature (Lavandero & Tylianakis 2013) and in plantation versus native forests (Peralta et al.
-2015), and such patterns appear consistent with a hy- pothesis of stress-induced reduction in trophic (phylogenetic) breadth (in the case of Lavandero & Tylianakis 2013, this occurred on genotype relatedness rather than between-species phylogenies).
-However, evidence for the hypothesized mechanism is still lacking, as experiments have revealed no change in the proportionate use of good or bad hosts when parasitoids are nutritionally stressed (Hopper et al.
-2013) or even decreased selectivity toward high-quality hosts under high levels of nutritional stress (Crespo et al.
-2015).
--->
-
-<!-- In addition to seasonal patterns, interaction turnover can be driven by environmental fac- tors, such as community changes during drought years (Alarco ́n et al.
-2008) or along land use or landscape intensity gradients (Gagic et al.
-2012, Laliberte ́ & Tylianakis 2010).
-The impact of environmental conditions on interaction turnover can, in turn, be constrained by species traits such as feeding morphology (Carnicer et al.
-2009) or body size (Laliberte ́ & Tylianakis 2010).
-To understand this balance, species interactions can be thought of as having both a niche-based or trait-based component and a random or neutral component determined by encounter probability (Bartomeus et al.
-2016, Vazquez et al.
-2009).
-Any environmental driver that sufficiently increases encounter probability (see Section 2.2) for all species could reduce the neutral barrier to inter- actions and allow species to consistently select their interaction partner with optimally matched traits.
-This enhanced expression of species preferences would result in reduced spatial or temporal variability because the same interactions would consistently be realized (i.e., network homogeniza- tion; Laliberte ́ & Tylianakis 2010).
-Reduction of the neutral component of interactions could also lead to exaggeration of patterns of trait matching and phylogenetic congruence (Carnicer et al.
-2009) (see Section 2.3).
-Alternatively, a driver that increases the abundance of a subset of species could result in their overrepresentation in interactions by allowing the neutral component of inter- actions to be overexpressed relative to the trait-based component (Carnicer et al.
-2009).
-Because individual species may differ in the extent to which they engage in neutral interactions, changes to the relative abundance of species can alter network architecture.
-For example, exotic birds can be less selective in the fruit species on which they feed (i.e., feeding more neutrally on species in proportion to their abundance), and this low selectivity can allow them to fill the gap left by rare or extinct native birds and maintain high network nestedness and connectance (Garcıa et al.
-2014).
--->
-
-<!-- **Peralta 2015:** Plantation forests (as opposed to native) habitat may impose stresses on parasitoids that constrain them to attack only host species for which they are best adapted.
--> Consistent with more stress less generalism.
--->
-
-<!-- Native herbivore–parasitoid combinations whose interac- tions contributed the most to the pattern of phylogenetic congruence were more abundant in plantations than in native forests.
-This stronger co-evolutionary signal in plantation forests suggests that parasitoids in disturbed habitats may only be able to utilize hosts that they have best evolved to attack.
-Analogously, climate warming has been shown to reduce the niche breadth plasticity of par- asitoids (Lavandero & Tylianakis 2013), suggesting that different environmental changes could reduce the ability of parasitoid communities to suppress a broad range of host species and genotypes in natural systems and biologi- cal control programmes.
--->
+* There are some warnings for when matching environmental variables to occurrences. I need to double check this is happeing correctly. 
+* Refine the supplementary results. 
+* Fix references

### 2019-11-17 paper/draft-info.Rmd
Check spelling draft info

@@
 title: "Draft information"
-subtitle: "version: draft-0.0"
-date: "20xx"
+subtitle: "version: draft-0.3"
+date: "2019-11"
 # bibliography: phd-bibliography/pollen-competition.bib
@@
 * Refocused the introduction
-* Moved details of taxonomic data cleaning process to supplementary materials
+* Moved details of the taxonomic data cleaning process to supplementary materials
 * Moved details of occurrence data cleaning process to supplementary materials
@@
 
-* There are some warnings for when matching environmental variables to occurrences. I need to double check this is happeing correctly. 
+* There are some warnings for when matching environmental variables to occurrences. I need to double-check this is happening correctly. 
 * Refine the supplementary results. 

### 2019-11-19 paper/manuscript.Rmd
Add loadd to interaction citations

@@
 loadd(abs_wordcount, msc_wordcount, n_displays, n_references, keywords, bibliography)
+loadd(interaction_citations)
 ```

### 2019-11-19 paper/manuscript.Rmd
Add loadd to config
Add loadd to interaction citations
update references
fix lines msc

@@
 loadd(abs_wordcount, msc_wordcount, n_displays, n_references, keywords, bibliography)
-loadd(interaction_citations)
+loadd(interaction_citations, config) 
 ```
@@
 There are multiple examples of species that interact with a large number of partners in a particular community or season, but with fewer in another. 
-
 Some of this variation can be attributed to environmental drivers. 
@@
 
-```{r}
+```{r occurrences-calcs}
 loadd(n_occurrences, n_cleaned_occurrences, n_dirty_occurrences, gbif_key_groups, org_ids, n_thinned_occurrences, complete_climate_cells, complete_filled_cells_1, complete_filled_cells_2)
@@
 After obtaining information about species occurrence and the environment, we then merged these two datasets such that a vector with details of our 37 bioclimatic and topographic variables characterised the location of each occurrence.
-
 Sets of occurrence data tend to be spatially aggregated due to sample bias (tendency to collect close to cities, certain countries). 
@@
 As we were interested in understanding whether the effect of habitat suitability is conditional on the species guild (plant or pollinator), we, therefore, included guild and its interaction with suitability in the model.
+
 We allowed the intercept of degree and slope of the suitability-degree relationship to vary among species. 

### 2019-11-19 paper/supp-info.Rmd
remove supp info extra space
add loadd sensitivity_species_name it was not called before

@@
 ```{r fig-sensitivity-analysis, fig.width = width('single'), fig.height = 2.2, fig.cap = fig_sensitivity_analysis_legend}
-
+loadd(sensitivity_species_name)
 fig_sensitivity_analysis_legend <- 

### 2019-11-19 paper/manuscript.Rmd
make results fig smaller
add first keywords
remove full model from table results

@@
 
-```{r fig-conditional-effects, fig.width = width('single'), fig.height = 2.2*3, fig.cap = fig_conditional_effects_legend}
+```{r fig-conditional-effects, fig.width = width('single'), fig.height = 2.2*1.5, fig.cap = fig_conditional_effects_legend}
 loadd(median_trials)
@@
   purrr::map(~.$estimates["waic", ]) %>% 
+  dplyr::filter(formula != "formula_full") %>%
   purrr::map_df(~tibble::tibble(estimate = .[1], se = .[2]), .id = "formula") %>%
@@
                caption = "Comparison in out of sample predictive power of the baseline model (bold) and their alternatives.
-We rank models by their expected log predictive density based on their leave-one-out cross-validation information criterion (LOO).
-The standard error of the LOO difference provides rough guidance to the uncertainty of the model ranking.
-We also show the Wanatabe-Akaike information criterion (WAIC) of each model for comparison.") %>%
+We rank models by their expected log predictive density based on their Wanatabe-Akaike information criterion (WAIC).") %>%
   kableExtra::kable_styling(font_size = 8) #%>%

### 2019-11-19 paper/manuscript.Rmd
update msc

@@
   purrr::map(~.$estimates["waic", ]) %>% 
+  purrr::map_df(~tibble::tibble(estimate = .[1], se = .[2]), .id = "formula") %>%
   dplyr::filter(formula != "formula_full") %>%
-  purrr::map_df(~tibble::tibble(estimate = .[1], se = .[2]), .id = "formula") %>%
   dplyr::mutate(formula = translate_model_formula(formula, "long-abv"), 

### 2019-11-20 paper/draft-info.Rmd
Add manual checks to TO-DO
update draft info

@@
 
-* There are some warnings for when matching environmental variables to occurrences. I need to double-check this is happening correctly. 
+* There are some unfamiliar warnings for when matching environmental variables to occurrences. I need to double-check this is all correct before submission. 
 * Refine the supplementary results. 
 * Fix references
+* Finish manual species checks
+
+## Comments
+
+* Jason, thanks for proposing the idea of calculating the suitability of the community as a whole.
+I think it would be super exciting but didn't pursue that path.
+Mainly because that would imply downloading the occurrences for all the species we know their correct name as opposed to just those that are in more than one community as we do now.
+Currently, the occurrence data for the latter group is ~50GB.
+Expanding the group will likely mean dealing with 3-5 times as much data.
+This exercise creates some new technical problems — all solvable but challenging enough to take longer than what I want to budget for it.
+
+* Appart from that, I think I followed most suggestions one way or another. **Thanks!**

### 2019-11-27 paper/manuscript.Rmd
Most changes to intro

@@
 Some of this variation can be attributed to environmental drivers. 
-However, how exactly the environment, specifically the stress it imposes on species, affects whether two species interact or not, and ultimately the number of partners a species has is still unknown. 
-Understanding how the number of partners—the species degree—is driven by the environment is crucial because it underpins the species role in its community and shapes the structure of the network of interactions.
+However, how exactly the environment, specifically the stress it imposes on species, affects whether two species interact or not, and ultimately the species' specialisation. 
+Understanding how the number of partners is driven by the environment is crucial because it underpins the species role in its community and shapes the structure of the network of interactions. 
 This structure, in turn, determines ecosystem function and stability.
@@
 
-One possible explanation for the seemingly contradictory evidence is that each species can have multiple partners. 
-Each of these partners, as well as the interactions with them, can be simultaneously affected by the environmental conditions. 
-Therefore environmental stress may affect the number of partners in different ways depending on its role in the community (for example its trophic guild) or even the species itself. 
-Previous research suggests that there might be two alternative hypotheses of how environmental stress may affect species degree [@tylianakis_ecological_2017]. 
+One possible explanation for the seemingly contradictory evidence is that different bioclimatic factors (like temperature or precipitation) can have contrasting effects on species and their partners. 
+Here we attempt to simplify this situation by reducing multiple factors into a single measure of environmental stress. 
+Previous research suggests that environmental stress may affect the number of partners in different ways depending on its role in the community (for example its trophic guild) or even the species itself.
+Specifically, we proporse two alternative hypotheses of how environmental stress may affect specialisation [@tylianakis_ecological_2017]. 
 On the one hand, it is possible that when species are under environmental stress, they might be "pressured" to focus on partners with which they are best adapted to interact. 
 For instance, @hoiss_altitude_2012 found increased phylogenetic clustering between plants and pollinators at higher altitudes; while @peralta_phylogenetic_2015 found that parasitoids in plantation forest, where environmental stress was higher than in native forests, were constrained to interact with hosts, they were best adapted to attack.
-Similarly, @lavandero_genotype_2013 found that environmental stress due to higher temperature reduced the breadth of the Eltonian niche of parasitoids.
+Similarly, @lavandero_genotype_2013 found that environmental stress due to higher temperature reduced the thropic niche breadth of parasitoids.
 
-On the other hand, it is also possible that when species are under environmental stress, they are forced to be more flexible in their interactions as higher environmental stress is likely to be reflected in greater energetic or reproductive costs.
+On the other hand, it is also possible that when species are under environmental stress, they are forced to be more flexible in their interactions.
+Higher environmental stress is likely to be reflected in greater energetic or reproductive costs. 
 Therefore they might not be able to sustain encounter rates with their preferred partners at sufficient levels. 
@@
 
-Here, we investigate whether, and how, environmental stress can systematically affect species degree. 
-Our main aim is to test the two competing hypotheses that relate environmental stress and species degree and investigate whether this changes across species or between trophic guilds. 
+Here, we investigate whether and how environmental stress can systematically affect specialisation.  
+Our main aim is to test the two aforementioned hypotheses that relate environmental stress and species' number of partners and investigate whether this changes across species or between trophic guilds.
 We propose that specialist species can become "facultative" generalists to reduce their vulnerability to the absence of preferred partners [for example, when variations in climate decouple phenologies; @benadi_specialization_2014].
-We therefore also expect that as environmental stress increases species with a relatively small number of partners are more likely to engage with more partners and broaden their trophic niche. 
-Species with a large number of partners, on the other hand, should have a larger pool of available partners and might, therefore, be more likely to narrow their niche under environmental stress by focusing on the most beneficial partners.
-Importantly, when testing these hypotheses, we control for the potential effects of the environment in community composition and the size of the species fundamental niche, both from an Eltonian (interactions) and Grinellian (environment) perspective.
-
+In other words we expect that, as environmental stress increases, specialists should be more likely to engage with more partners. 
+Species with a large number of partners, on the other hand, should have a larger pool of available partners and might, therefore, be more likely to specialise under environmental stress and focus on the most beneficial partners.
+Importantly, when testing these hypotheses, we control for the potential effects of the environment in community [which has been previously shown to be determinant factor; @gravel_bringing_2018]
 We test these hypotheses using data on plant-pollinator interactions. 
-We use the species' patterns of occurrence to estimate the environmental suitability in their communities as an indirect measure of the environmental stress they might experience. 
-Condensing the environmental variation over multiple factors (like temperature and precipitation) into a single metric is crucial to generalise our findings at a global scale.
+This system is a particularly interesting XX.
+We use the species' patterns of global occurrence to estimate the bioclimatic suitability of their communities and use this as an indirect measure of the environmental stress they might experience.
 

### 2019-11-27 paper/manuscript.Rmd
Improve title

@@
 ---
-title: "Environmental stress affects niche breadth in plant-pollinator communities"
+title: "Environment affects specialisation of plants and pollinators"
 author: 

### 2019-11-30 paper/manuscript.Rmd
Last couple sentences of introduction

@@
 We test these hypotheses using data on plant-pollinator interactions. 
-This system is a particularly interesting XX.
-We use the species' patterns of global occurrence to estimate the bioclimatic suitability of their communities and use this as an indirect measure of the environmental stress they might experience.
+These interactions provide a particularly interesting system to test these hypotheses because, due to the multiple trade-offs involved in the pollination service, there are multiple intuitive ways in which we could imagine species respond to environmental stress given the available partners.
+We estimate the stress species might experience in their community by calculating the the bioclimatic suitability of their communities given the species' patterns of global occurrence.
 

### 2019-11-30 paper/manuscript.Rmd
Fix typos and grammar in intro

@@
 However, how exactly the environment, specifically the stress it imposes on species, affects whether two species interact or not, and ultimately the species' specialisation. 
-Understanding how the number of partners is driven by the environment is crucial because it underpins the species role in its community and shapes the structure of the network of interactions. 
+Understanding how the environment drives the number of partners is crucial because it underpins the species role in its community and shapes the structure of the network of interactions. 
 This structure, in turn, determines ecosystem function and stability.
@@
 Previous research suggests that environmental stress may affect the number of partners in different ways depending on its role in the community (for example its trophic guild) or even the species itself.
-Specifically, we proporse two alternative hypotheses of how environmental stress may affect specialisation [@tylianakis_ecological_2017]. 
+Specifically, we propose two alternative hypotheses of how environmental stress may affect specialisation [@tylianakis_ecological_2017]. 
 On the one hand, it is possible that when species are under environmental stress, they might be "pressured" to focus on partners with which they are best adapted to interact. 
 For instance, @hoiss_altitude_2012 found increased phylogenetic clustering between plants and pollinators at higher altitudes; while @peralta_phylogenetic_2015 found that parasitoids in plantation forest, where environmental stress was higher than in native forests, were constrained to interact with hosts, they were best adapted to attack.
-Similarly, @lavandero_genotype_2013 found that environmental stress due to higher temperature reduced the thropic niche breadth of parasitoids.
+Similarly, @lavandero_genotype_2013 found that environmental stress due to higher temperature reduced the trophic niche breadth of parasitoids suggesting higher specialisation.
 
@@
 Here, we investigate whether and how environmental stress can systematically affect specialisation.  
-Our main aim is to test the two aforementioned hypotheses that relate environmental stress and species' number of partners and investigate whether this changes across species or between trophic guilds.
+Our main aim is to test the two hypotheses mentioned above that relate environmental stress and species' number of partners and investigate whether this changes across species or between trophic guilds.
 We propose that specialist species can become "facultative" generalists to reduce their vulnerability to the absence of preferred partners [for example, when variations in climate decouple phenologies; @benadi_specialization_2014].
-In other words we expect that, as environmental stress increases, specialists should be more likely to engage with more partners. 
+In other words, we expect that, as environmental stress increases, specialists should be more likely to engage with more partners. 
 Species with a large number of partners, on the other hand, should have a larger pool of available partners and might, therefore, be more likely to specialise under environmental stress and focus on the most beneficial partners.
-Importantly, when testing these hypotheses, we control for the potential effects of the environment in community [which has been previously shown to be determinant factor; @gravel_bringing_2018]
+Importantly, when testing these hypotheses, we control for the potential effects of the environment in community composition [which has been previously shown to be a determinant factor; @gravel_bringing_2018]
 We test these hypotheses using data on plant-pollinator interactions. 
 These interactions provide a particularly interesting system to test these hypotheses because, due to the multiple trade-offs involved in the pollination service, there are multiple intuitive ways in which we could imagine species respond to environmental stress given the available partners.
-We estimate the stress species might experience in their community by calculating the the bioclimatic suitability of their communities given the species' patterns of global occurrence.
+We estimate the stress species might experience in their community by calculating the bioclimatic suitability of their communities given the species' patterns of global occurrence.
 

### 2019-11-30 paper/manuscript.Rmd
Move world map to supplementary info
Simplify first part of the methods

@@
 This database contains datasets originating from `r length(interaction_citations$BIBTEXKEY)` studies published in the primary literature between `r int_citations_year_range[1]` and `r int_citations_year_range[2]`.
-Calculating the environmental stress of species in their community and their Eltonian niche breadth required us to reduce both the taxonomic and distributional/locational uncertainty.
+Calculating the environmental stress of species in their community and their potential partners required us to reduce both the taxonomic and distributional/locational uncertainty.
 A critical step towards reducing this uncertainty is to ensure that the names used to identify species are valid and unambiguous, which in turn allow us to obtain further information from biological databases and accurately match species across studies.
-Therefore, our first step was to ensure consistent spelling and standardisation of species names synonyms (See Supplementary Methods).
-This step ensured that the matching of species across studies was as accurate as possible. 
+Therefore, our first step was to ensure consistent spelling and standardisation of species names synonyms (see Supplementary Methods).
 The cleaning process resulted on a total of `r format(stats_clean_int$pla_id, big.mark = ",")` plants and `r format(stats_clean_int$ani_id, big.mark = ",")` pollinator species distributed across `r format(stats_clean_int$loc_id)` locations arround the globe (Figure \@ref(fig:fig-worldmap), \@ref(fig:fig-distribution-species-mult-locations)).
-
-```{r fig-worldmap, fig.width = width('single'), fig.cap ="Worldwide distribution of pollination communities included in this study"}
-readd(fig_worldmap)
-```
 
@@
 
-Second, we calculated the suitability of the environment for a species in a particular community as a proxy of environmental stress. 
-We assume that the environmental stress a species experience in a particular location is inversely related to the suitability of the average environmental conditions in that place. 
-Our third and final step was to relate the environmental suitability to the relative number of partners a species has in a community, as a proxy for Eltionian niche breadth. 
-To explore this relationship within and across species, we used a multilevel Bayesian model in which we controlled for the potential effects of the environment on co-occurrence.
+After matching species across studies as accurate as possible we carried on two more steps. 
+First, we calculated the envoronmental stress of species in their communitues.
+Second, we relate the species stress in their communitu with the number of partner species it has as a metric of their level of specialisation.
 

### 2019-11-30 paper/manuscript.Rmd
Edit suitability methods

@@
 
-Our next step was to determine the habitat suitability of the species as a proxy of the environmental stress they experience in their community.
-As we aim to compare the trophic niche for different suitability levels, we only do this for species that were present in at least `r numbers2words(readd(minimum_spp_locations))` communities.
-To calculate the suitability of a species in a particular location, we used a niche-factor analysis [@hirzel_ecological-niche_2002; @broennimann_measuring_2012]. 
+Our third and final step was to relate the environmental suitability to the relative number of partners a species has in a community, as a proxy for Eltionian niche breadth. 
+To explore this relationship within and across species, we used a multilevel Bayesian model in which we controlled for the potential effects of the environment on co-occurrence.
+
+We assume that stress a species experience in a particular location is inversely related to the suitability of the average environmental conditions in that place. 
+As we aim to compare specialisation levels for different levels of environmental stress, we only calculate bioclimatic suitability for species that were present in at least `r numbers2words(readd(minimum_spp_locations))` communities.
+To calculate the bioclimatic suitability of a species in a particular location, we used a niche-factor analysis [@hirzel_ecological-niche_2002; @broennimann_measuring_2012]. 
 This approach is based on the probability density function of species distribution in an environmental variable space. 
-In a nutshell, habitats (characterised by a collection of environmental variables) in which the species occurs most often are deemed to be suitable for the species than habitats in which the species has never been observed.
-This approach to estimating the habitat suitability requires two critical pieces of information. 
+Habitats are characterised by a collection of environmental variables. 
+In a nutshell, those habitats in which the species occurs more often are deemed to be more suitable for the species than habitats in which the species has never been observed. 
+As bioclimatic suitability is calculated in a scale from zero to one following the niche-factor analysis, for simplicity, we define environmental stress as one minus suitability.
+
+The niche factor analysis requires two critical pieces of information. 
 First, we require information about the occurrences of the species of interest.
 Second, we require information about the environmental conditions for all the locations in which the species occurs.
-
 We retrieved `r round(sum(n_occurrences$N)/1000000, digits = 1)` million occurrences from the Global Biodiversity Information Facility (GBIF; https://www.gbif.org). 
 Issues with data quality are a central issue hampering the use of publicly available species occurrence GBIF data in ecology and biogeography [@jetz_essential_2019]. 
-We, therefore we followed a series of filters and geographic heuristics to correct or remove erroneous and imprecise referencing records [See supplementary methods; @zizka_coordinatecleaner_2019] which allowed us to identify and remove `r round(sum(n_dirty_occurrences$N)/1000000, digits = 1)` million problematic occurrences from further analysis.
+We therefore followed a series of filters and geographic heuristics to correct or remove erroneous and imprecise referencing records [see supplementary methods; @zizka_coordinatecleaner_2019] which allowed us to identify and remove `r round(sum(n_dirty_occurrences$N)/1000000, digits = 1)` million potentially problematic occurrences from further analysis.
 We integrated the occurrences from our plant-pollinator communities to the cleaned occurrences retrieved from GBIF.
@@
 We then complemented data obtained from WorldClim with data from Envirem [@title_envirem_2017], which includes 16 extra bioclimatic and two topographic variables. 
-The additional set of variables from Envirem are relevant to ecological or physiological processes and as such, have the potential to improve our suitability estimation [@title_envirem_2018]. 
+The additional set of variables from Envirem are relevant to ecological or physiological processes and thus have the potential to improve our suitability estimation [@title_envirem_2018]. 
 We obtained all environmental data as rasters composed by cells of 2.5 arc-minutes. 
-We chose this resolution because it provides a reasonable match to the locational accuracy of the species occurrences found in GBIF, particularly those that come preserved specimens in museum collections.
+We chose this resolution because it provides a reasonable match to the locational accuracy of the species occurrences found in GBIF, particularly those that originate from preserved specimens in museum collections.
 
@@
 Sets of occurrence data tend to be spatially aggregated due to sample bias (tendency to collect close to cities, certain countries). 
-Spatial autocorrelation arises in ecological data because geographically clumped records tend to be more similar, in physical characteristics and/or species abundances, than are pairs of locations that are farther apart.
-To account for such spatial dependency in occurrence data, if a species had more than one occurrence records within one of the cells of the bioclimatic raster, we only included one of the occurrence records.
+Moreover, spatial autocorrelation arises in ecological data because geographically clumped records tend to be more similar in physical characteristics and/or species abundances than do pairs of locations that are farther apart.
+To account for such spatial dependency in occurrence data, we only included one occurrence record if a species had more than one within a cell of the bioclimatic raster. 
 We did this to avoid giving more weight to areas with a high number of occurrences, a common scenario in occurrence records collected opportunistically as the ones we use here. 
@@
 A common issue of terrestrial bioclimatic datasets is that the boundaries of the cells with information do not precisely match the landmass boundaries. 
-The result of this missmatch is that not all environmental variables was not available for `r format(complete_climate_cells[1], big.mark = ",")` of the raster cells with occurrences (`r scales::percent(complete_climate_cells[1]/sum(complete_climate_cells), accuracy = 0.1)` of the total).
+The result of this missmatch is that not all environmental variables were available for `r format(complete_climate_cells[1], big.mark = ",")` of the raster cells with occurrences (`r scales::percent(complete_climate_cells[1]/sum(complete_climate_cells), accuracy = 0.1)` of the total).
 As expected, the vast majority of these problematic cells were close to the shore. 
 To address this issue, we calculated the average value of environmental variables within an `r config$climate_buffer/1000`km buffer of the centre of the cell where the variable was missing and used it to approximate the value of the variable in that cell.
-Using this procedure, we were able to fill environmental variables for `r scales::percent(percent_filled_round_one, accuracy = 0.1)` of the cells were they were missing. 
+Using this procedure, we were able to fill environmental variables for `r scales::percent(percent_filled_round_one, accuracy = 0.1)` of the cells where they were missing. 
 To fill the remaining `r format(complete_filled_cells_1[1], big.mark= ",")` cells, we repeated the aforementioned procedure but instead using a `r config$climate_buffer*2/1000`km buffer. 
-We removed from further analysis occurrences located within the `r complete_filled_cells_2[1]` cells for which we were unable to fill environmental variables.
+We removed from further analysis occurrences located within the `r complete_filled_cells_2[1]` cells for which we were unable to fill environmental variables (`r scales::percent(complete_filled_cells_2[1]/sum(complete_filled_cells_2))` of the total).
 
@@
 To determine the environmental space, we use the first two components from a principal component analysis of the 37 bioclimatic variables associated with the species occurrences. 
-Specifically we use the `dudi.pca` function from the R package `ade4` `r as.character(packageVersion('ade4'))` [@dray_ade4_2007] and center and scale all bioclimatic variables to have a mean of 0 and a unit standard deviation.
+Specifically we use the `dudi.pca` function from the R package `ade4` `r as.character(packageVersion('ade4'))` [@dray_ade4_2007] and center and scale all bioclimatic variables to have a mean of zero and a unit standard deviation.
 We then determine the position of species occurrences in the environmental space and estimate their bivariate probability density function. 
@@
 We then determine the location in the environmental space of the plant-pollinator communities using the function `suprow` from `ade4`.
-The normalised density at that particular location corresponds to our suitability metric, which we calculate using the R package `raster` `r as.character(packageVersion('raster'))` [@hijmans_raster_2019].
-We use the kernel density method in the niche-factor analysis [@broennimann_measuring_2012] rather than the distance from the mode [@hirzel_ecological-niche_2002], as it has been proposed earlier, as it has been shown to reduce the procedure's sensitivity to sampling effort and the resolution of the environmental space.
+The normalised density at that particular location [which we calculate using the R package `raster` `r as.character(packageVersion('raster'))`; @hijmans_raster_2019] corresponds the bioclimatic suitability.
+We use the kernel density method in the niche-factor analysis [@broennimann_measuring_2012] rather than the distance from the mode [@hirzel_ecological-niche_2002], as it has been proposed earlier, because it has been shown to reduce the procedure's sensitivity to sampling effort and the resolution of the environmental space.
+The result of all these steps is the environmental stress which corresponds to one minus the bioclimatic suitability for a species of a particular location.
 

### 2019-11-30 paper/manuscript.Rmd
From suitability to stress
Edits to the methods

@@
 
-### Species suitability
+### Environmental stress
 
@@
 To determine the environmental space, we use the first two components from a principal component analysis of the 37 bioclimatic variables associated with the species occurrences. 
-Specifically we use the `dudi.pca` function from the R package `ade4` `r as.character(packageVersion('ade4'))` [@dray_ade4_2007] and center and scale all bioclimatic variables to have a mean of zero and a unit standard deviation.
+Specifically we use the `dudi.pca` function from the R package `ade4` `r as.character(packageVersion('ade4'))` [@dray_ade4_2007] and center and scale all bioclimatic variables to have a mean of zero and a unit variance.
 We then determine the position of species occurrences in the environmental space and estimate their bivariate probability density function. 
@@
 
-We then used a set of bayesian multilevel models to evaluate the impact of environmental suitability on the number of partners a species has. 
-Specifically, we use the normalised degree of species as our response variable; this is, the number of species it interacts with given the number of species in the opposite guild [@martin_gonzalez_centrality_2010].
-The normalised degree was modelled using a logit link function, and a binomial distribution in which the number of species interacts with is the number of successes, and the number of species in the opposite guild is the number of trials.
+We then used a set of Bayesian multilevel models to evaluate the impact of environmental stress on species specialisation. 
+Specifically, we use the normalised degree of species as our response variable; that is, the number of species it interacts with given the number of species in the opposite guild [@martin_gonzalez_centrality_2010].
+The normalised degree was modelled using a logit link function, and a binomial distribution in which the number of partner species a focal interacts with is the number of successes, and the number of species in the opposite guild is the number of trials.
 We are aware that whether species interact or not is not a Bernoulli process as species interactions are not strictly independent from each other. 
-However, a binomial distribution allows us to account for the differences in species richness across communities indirectly. 
-Importantly, however, results are qualitatively similar when we model species degree directly using a Poisson distribution and a logarithmic link function.
+However, the use of a binomial distribution allows us to account for the differences in species richness across communities indirectly. 
+Importantly, results are qualitatively similar when we model species degree directly using a Poisson distribution and a logarithmic link function.
 
-We evaluate four models to assess the relative importance of suitability. 
-A first model, our baseline model, included three population-level predictors and two grouping levels, species and the community.
-The population-level predictors in the baseline model, commonly called fixed effects, were the habitat suitability, the species guild (plant or a pollinator), and its number of known possible partners.
-We included the number of known possible partners as a predictor in our models as it allows us to control for the environmental effects on species co-occurrence. 
+We evaluated four models to assess the relative importance of suitability. 
+A first model, our baseline model, included five variables. 
+<!-- fixed variables (population-level predictors) and two random variables (grouping levels). -->
+The predictors in the baseline model were the environmental stress, its number of known possible partners in the commuynity, and both the species guild (plant or a pollinator) and its interaction with environmental stress.
+We included the number of known possible partners as a predictor in our models as it allows us to control for the effects of the environment on community composition, effectively accounting for species co-occurrence.
 We calculate this metric by determining the number of partners with which the species is known to interact in any other community.
-Controlling for the number of potential partners makes our model a particularly stringent test of our environmental stress hypotheses because this variable could explain a large proportion of variance.
-Often the potential and the actual number of partners is the same or very close to each other, especially for rare species present only in a few communities.
-As we were interested in understanding whether the effect of habitat suitability is conditional on the species guild (plant or pollinator), we, therefore, included guild and its interaction with suitability in the model.
+Controlling for the number of potential partners makes our model a particularly stringent test of our environmental-stress hypotheses because this variable could explain a large proportion of variance.
+Often, the potential and the actual number of partners is the same or very close to each other, especially for rare species present only in a few communities.
 
-We allowed the intercept of degree and slope of the suitability-degree relationship to vary among species. 
+We allowed the intercept and slope of the stress-specialisation relationship to vary among species. 
 This approach allowed us to investigate two questions. 
-First, it allows us to inspect the extent to which suitability is a population or a group level effect. 
-Second, by investigating the correlation between the intercept and the slope as a model parameter, it allowed us to inspect the extent by which species with a small or large number of interactions respond to increasing levels of environmental stress.
-To account for unmeasured differences between communities, like sampling effort, sampling method, or diversity, we also calculated an intercept for each community in our study.
-To facilitate model interpretation and convergence, we scaled all continuous variables to have a mean of zero and a unit standard deviation.
+First, it allows us to inspect the extent to which environmental stress affects species in a similar fashion. 
+Second, by investigating the correlation between the intercept and the slope as a model parameter, it allowed us to inspect the extent by which species with a small or large number of partner species respond to increasing levels of environmental stress.
+To account for unmeasured differences between communities, like sampling effort, sampling method, or diversity, we also allowed the model intercept to be different for each community in our study.
+To facilitate model interpretation and convergence, we scaled all continuous variables to have a mean of zero and a unit variance
 
-We compared this baseline model with three alternative models in which we remove one predictor at a time.
+We compared this baseline model with three alternative models in which we removed one predictor at a time.
 To quantify the difference between models, in terms of their expected out-of-sample performance, we use the Wanatabe-Akaike information criterion (WAIC).
-All models were fitted under a bayesian framework using the R package `brms` `r as.character(packageVersion('brms'))` [@burkner_brms_2017; @burkner_advanced_2018] as an interface for Stan [@carpenter_stan_2017].
+All models were fitted under a Bayesian framework using the R package `brms` `r as.character(packageVersion('brms'))` [@burkner_brms_2017; @burkner_advanced_2018] as an interface for Stan [@carpenter_stan_2017].
 For each model, we used four Markov chains of 4,000 iterations each; we used half of the iterations for warmup.

### 2019-11-30 paper/manuscript.Rmd
Fix typos and grammar Methods

@@
 
-After matching species across studies as accurate as possible we carried on two more steps. 
-First, we calculated the envoronmental stress of species in their communitues.
-Second, we relate the species stress in their communitu with the number of partner species it has as a metric of their level of specialisation.
+After matching species across studies as accurate as possible, we carried on two more steps. 
+First, we calculated the environmental stress of species in their communities.
+Second, we relate the species stress in their community with the number of partner species it has as a metric of their level of specialisation.
 
@@
 Issues with data quality are a central issue hampering the use of publicly available species occurrence GBIF data in ecology and biogeography [@jetz_essential_2019]. 
-We therefore followed a series of filters and geographic heuristics to correct or remove erroneous and imprecise referencing records [see supplementary methods; @zizka_coordinatecleaner_2019] which allowed us to identify and remove `r round(sum(n_dirty_occurrences$N)/1000000, digits = 1)` million potentially problematic occurrences from further analysis.
+We, therefore, followed a series of filters and geographic heuristics to correct or remove erroneous and imprecise referencing records [see supplementary methods; @zizka_coordinatecleaner_2019] which allowed us to identify and remove `r round(sum(n_dirty_occurrences$N)/1000000, digits = 1)` million potentially problematic occurrences from further analysis.
 We integrated the occurrences from our plant-pollinator communities to the cleaned occurrences retrieved from GBIF.
@@
 The normalised density at that particular location [which we calculate using the R package `raster` `r as.character(packageVersion('raster'))`; @hijmans_raster_2019] corresponds the bioclimatic suitability.
-We use the kernel density method in the niche-factor analysis [@broennimann_measuring_2012] rather than the distance from the mode [@hirzel_ecological-niche_2002], as it has been proposed earlier, because it has been shown to reduce the procedure's sensitivity to sampling effort and the resolution of the environmental space.
+We use the kernel density method in the niche-factor analysis [@broennimann_measuring_2012] rather than the distance from the mode [@hirzel_ecological-niche_2002], as it has been proposed earlier because it has been shown to reduce the procedure's sensitivity to sampling effort and the resolution of the environmental space.
 The result of all these steps is the environmental stress which corresponds to one minus the bioclimatic suitability for a species of a particular location.
@@
 <!-- fixed variables (population-level predictors) and two random variables (grouping levels). -->
-The predictors in the baseline model were the environmental stress, its number of known possible partners in the commuynity, and both the species guild (plant or a pollinator) and its interaction with environmental stress.
+The predictors in the baseline model were the environmental stress, its number of known possible partners in the community, and both the species guild (plant or a pollinator) and its interaction with environmental stress.
 We included the number of known possible partners as a predictor in our models as it allows us to control for the effects of the environment on community composition, effectively accounting for species co-occurrence.
@@
 This approach allowed us to investigate two questions. 
-First, it allows us to inspect the extent to which environmental stress affects species in a similar fashion. 
+First, it allows us to inspect the extent to which environmental stress affects species similarly. 
 Second, by investigating the correlation between the intercept and the slope as a model parameter, it allowed us to inspect the extent by which species with a small or large number of partner species respond to increasing levels of environmental stress.
 To account for unmeasured differences between communities, like sampling effort, sampling method, or diversity, we also allowed the model intercept to be different for each community in our study.
-To facilitate model interpretation and convergence, we scaled all continuous variables to have a mean of zero and a unit variance
+To facilitate model interpretation and convergence, we scaled all continuous variables to have a mean of zero and a unit variance.
 

### 2019-11-30 paper/manuscript.Rmd
Sensitivity analysis figure back to the main text for thesis

@@
 \@ref(fig:fig-median-suitability)).
+```{r fig-sensitivity-analysis, fig.width = width('single'), fig.height = 2.2, fig.cap = fig_sensitivity_analysis_legend}
+loadd(sensitivity_species_name)
+fig_sensitivity_analysis_legend <- 
+  paste0("Sensitivity analysis of environmental stress error. ",
+         "The number of independent occurrences retrieved from GBIF is inversely related to the error of bioclimatic suitability for our plant-pollinator networks.", 
+         "The sensitivity analysis was performed by subsampling occurrences of", 
+         " *", sensitivity_species_name$canonicalName, "* ", 
+         "the species in our dataset with the largest number of occurrences in GBIF, which was recorded in two of our communities.")
+
+readd(fig_sensitivity_analysis)
+```
 

### 2019-11-30 paper/supp-info.Rmd
Move world map to supplementary info
Sensitivity analysis figure back to the main text for thesis

--- 2019-11-17 paper/supp-info.Rmd
@@
 
+```{r fig-worldmap, fig.width = width('single'), fig.cap ="Worldwide distribution of pollination communities included in this study"}
+readd(fig_worldmap)
+```
+
 ## Reducing location uncertainty
@@
 
-```{r fig-sensitivity-analysis, fig.width = width('single'), fig.height = 2.2, fig.cap = fig_sensitivity_analysis_legend}
-
-fig_sensitivity_analysis_legend <- 
-  paste0("Sensitivity analysis of environmental suitability error. ",
-         "The number of independent occurrences retrieved from GBIF is inversely related to the error of environmental suitability for our plant-pollinator networks.", 
-         "The sensitivity analysis was performed by subsampling occurrences of", 
-         " *", sensitivity_species_name$canonicalName, "* ", 
-         "the species in our dataset with the largest number of occurrences in GBIF, which was recorded in two of our communities.")
-
-readd(fig_sensitivity_analysis)
-```
-
 ```{r fig-median-suitability, fig.width = width('single'), fig.height = 2.2*1.5, fig.cap = "Median habitat suitability of communities in our dataset.

### 2019-11-30 code/figures.R

@@ -152,7 +152,7 @@ plot_sensitivity_analysis <- function(error_subsamples, min_suitability_error,
           legend.title = element_blank()) +
     labs(x = "number of GBIF occurrences",
          y = "mean absolute error",
-         title = "error of environmental suitability of communities",
+         title = "error of bioclimatic suitability",
          subtitle = "for a species present in two plant-pollinator communities ")
 
   # ggsave("plot.pdf", p,  width = unit(width("single"), "in"), height = unit(2.2, "in"))

### 2019-11-30 paper/manuscript.Rmd
Error based on selected approach to suitability

@@
 
-After performing our sensitivity analysis, we found that we need roughly `r readd(min_occurrences_factor)` independent occurrences for each community for which we calculated a suitability value in order to obtain a mean absolute error below `r config$min_suitability_error` (Fig.
-\@ref(fig:fig-sensitivity-analysis)).
-We, therefore, removed from further analyses `r n_spp_not_enough_occ` species for which we did not have enough occurrences to obtain robust estimates.
-When inspecting the suitability values of the analysed species, we found that most communities included species for which habitat suitability was low and species for which it was high (Fig.
-\@ref(fig:fig-median-suitability)).
+```{r sensitivity-results}
+loadd(approach_suitability)
+threshold_type <- ifelse(approach_suitability == "independent_suitability", "single_species", "all_species")
+```
+After performing our sensitivity analysis, we found that, for a species, we need roughly `r readd(min_occurrences_factor)[[threshold_type]]` independent occurrences for each community for which we aim to estimate the environmental stress.
 ```{r fig-sensitivity-analysis, fig.width = width('single'), fig.height = 2.2, fig.cap = fig_sensitivity_analysis_legend}

### 2019-11-30 paper/manuscript.Rmd
Improve wording sensitivity analysis in Methods

@@
 
-We used a sensitivity analysis to determine the minimum number of occurrences that are necessary to have robust environmental suitability values in our communities. 
-For that we used the species with most occurrences available, *`r sensitivity_species_name$canonicalName`*, and calculated the mean absolute error of the suitability values obtained with `r numbers2words(config$n_subsamples)` subsamples from the `r format(n_occ_sensitivity_species, big.mark  =",")`  occurrences available from GBIF.
+We used a sensitivity analysis to determine the minimum number of occurrences that are necessary to have robust environmental stress estimations. 
+For that we used the species with most occurrences available, *`r sensitivity_species_name$canonicalName`*, and calculated the mean absolute error of the bioclimatic suitability values obtained with `r numbers2words(config$n_subsamples)` subsamples from the `r format(n_occ_sensitivity_species, big.mark  =",")`  occurrences available from GBIF.
 

### 2019-11-30 paper/manuscript.Rmd
Adjust legend figure conditional effects

@@
 fig_conditional_effects_legend <- 
-  paste0("Conditional effects of predictors in our baseline model. The predicted values of the number of interacting species are based on a hypothetical community with ",
+  paste0("Conditional effects of predictors in our baseline model. The shown values are based on predictions for a hypothetical community with ",
          median_n_pla, " plants and ", 
@@
          ".
-These values correspond to the median number of species in each guild, respectively.
-In each panel, we condition on the mean values of all other predictors in the model.
+These values correspond to the median number of species in each guild across communities.
+In each panel, we condition on the mean value of the other predictor in the model.
 We indicate mean values for each predictor with a vertical dashed line.
-For model fitting, we scaled all predictors to have a mean of zero and unit variance.
-However, except for environmental niche size, here we show the unscaled predictors to facilitate interpretation.
+For model fitting, we scaled all predictors to have a mean of zero and unit variance; however, here we show the unscaled predictors to facilitate interpretation.
 To illustrate the uncertainty around the fitted estimates, we plot the fits of 100 independent draws from the posterior distribution.
 The thick lines indicate the mean values of the response distribution.
-As there was no interaction between guild and generality or the number of possible interactions, for these two predictors, we only show conditional the conditional effect of pollinators.")
+As there was no interaction between guild and the number of possible interactions, we only show the conditional effect of pollinators.")
 

### 2019-11-30 paper/manuscript.Rmd
Order WAIC table

@@
   purrr::map_df(~tibble::tibble(estimate = .[1], se = .[2]), .id = "formula") %>%
+  dplyr::arrange(dplyr::desc(estimate)) %>%
   dplyr::filter(formula != "formula_full") %>%

### 2019-11-30 paper/manuscript.Rmd
More edits to results

@@
 ```
+
 After performing our sensitivity analysis, we found that, for a species, we need roughly `r readd(min_occurrences_factor)[[threshold_type]]` independent occurrences for each community for which we aim to estimate the environmental stress.
+This is the number of occurrences necessary to maintain the mean absolute error of bioclimatic suitability below `r config$min_suitability_error` (Fig. \@ref(fig:fig-sensitivity-analysis)). 
+We therefore removed from further analyses `r n_spp_not_enough_occ` species for which we did not have enough occurrences to obtain robust estimates.
+<!-- When inspecting the suitability values of the analysed species, we found that most communities included species for which habitat suitability was low and species for which it was high (Fig.
+\@ref(fig:fig-median-suitability)).
+-->
+
 ```{r fig-sensitivity-analysis, fig.width = width('single'), fig.height = 2.2, fig.cap = fig_sensitivity_analysis_legend}
@@
 Our models performed relatively well.
-The bayesian R-squared for our baseline model was `r round(bayesian_r2_baseline[1], digits = 2)`, which indicates our models were able to capture a large proportion of the variability on the data. 
-Overall we found that environmental suitability does not show a consistent pattern across species. 
-Indeed, when looking at the population level effects, suitability has virtually no relationship with the normalised degree, neither for plants or pollinators (Figure \@ref(fig:fig-conditional-effects)b).
-However, suitability is an important predictor as the WAIC difference between our baseline model and that that did not include suitability was `r round(waic_diff_suitability)` ± `r round(waic_se_diff_suitability)` (Table \@ref(tab:tab-model-comparison)).
-This apparent discrepancy can be explained by the variability of the suitability-degree relationship across species.
+The Bayesian R^2^ for our baseline model was `r round(bayesian_r2_baseline[1], digits = 2)`, which indicates our models were able to capture a large proportion of the variability on the data. 
+Overall, we found that environmental stress does not have a consistent effect across species. 
+Indeed, when looking at the fixed effects, stress has virtually no relationship with the normalised degree—our metric of specialisation (Figure \@ref(fig:fig-conditional-effects)a). 
+However, environmental stress was still an important predictor in our model. 
+The difference in WAIC between our baseline model and the model that did not include environmental stress was `r round(waic_diff_suitability)` ± `r round(waic_se_diff_suitability)` (Table \@ref(tab:tab-model-comparison)).
+This apparent discrepancy can be explained by the variability of the specialisation-stress relationship across species.
 
@@
 
-While for some species there is a strong negative relationship between suitability and normalised degree, for some others with a strong positive relationship (Figure \@ref(fig:fig-random-effects)a). 
-Interestingly, the slope of this relationship correlates negatively with the species' intercept in the model (Figure \@ref(fig:fig-random-effects)b). 
+For some species there is a strong negative relationship between stress and specialisation, while for others there is a strong positive relationship (Figure \@ref(fig:fig-random-effects)a). 
+Interestingly, the slope of this relationship correlates positively with the species' intercept in the model (Figure \@ref(fig:fig-random-effects)b and c). 
 The mean correlation coefficient was `r round(random_cor$Estimate, 2)` [`r round(random_cor$Q2.5, 2)`, `r round(random_cor$Q97.5, 2)`].
-In other words, the slope of the suitability-degree relationship was more likely to be positive for species with a smaller number of partners in lower-suitability and negative for species with a larger number of partners in lower-suitability conditions.
+In other words, the slope of the stress-specialisation relationship was more likely to be positive for species with a smaller number of partners in and negative for species with a larger number of partners in lower-suitability conditions.
 

### 2019-11-30 main.R
Use stress instead of suitability in models

@@ -281,8 +281,11 @@ suitability_vs_generalism_plan <- drake::drake_plan(
   nets = ints_as_nets(interactions_org),
   possible_interactions = get_possible_interactions(interactions_org),
   org_degree = calc_org_degree(possible_interactions, interactions_org),
-  datasets = list(independent_suitability = independent_suitability,
+  datasets_suitability = list(independent_suitability = independent_suitability,
                   collective_suitability = collective_suitability),
+  # Using 1 - because I want stress not suitability
+  datasets = purrr::map(datasets_suitability, 
+                        ~dplyr::mutate(., suitability = 1 - suitability)),
   analysis_frames = purrr::map(datasets,
                               ~build_analysis_frame(
                                  org_degree, .,

### 2019-12-01 paper/manuscript.Rmd
More changes to results

@@
 The thick lines indicate the mean values of the response distribution.
-As there was no interaction between guild and the number of possible interactions, we only show the conditional effect of pollinators.")
+As there was no interaction between the guild and the number of possible interactions, we only show the conditional effect of pollinators.")
 
@@
 
-For some species there is a strong negative relationship between stress and specialisation, while for others there is a strong positive relationship (Figure \@ref(fig:fig-random-effects)a). 
-Interestingly, the slope of this relationship correlates positively with the species' intercept in the model (Figure \@ref(fig:fig-random-effects)b and c). 
+For some species, there is a strong negative relationship between stress and specialisation, while for others, there is a strong positive relationship (Figure \@ref(fig:fig-random-effects)a). 
+Interestingly, the slope of this relationship correlates negatively with the species' intercept in the model (Figure \@ref(fig:fig-random-effects)b and c). 
 The mean correlation coefficient was `r round(random_cor$Estimate, 2)` [`r round(random_cor$Q2.5, 2)`, `r round(random_cor$Q97.5, 2)`].
-In other words, the slope of the stress-specialisation relationship was more likely to be positive for species with a smaller number of partners in and negative for species with a larger number of partners in lower-suitability conditions.
+In other words, the slope of the stress-specialisation relationship was more likely to be positive for species with a smaller number of partners in low-stress conditions (and negative for species with a larger number of partners).
 
@@
 (a) Conditional effect of suitability for individual species.
-To facilitate visualization we show only species for which there is suitability information in at least six communities (",
+To facilitate visualisation we show only species for which there is suitability information in at least six communities (",
          n_random_pla, " plants and ", 
@@
 As expected, we found a strong and positive relationship between the number of possible interactions and the number of realised interactions in the community. 
-There was a large difference on WAIC between the model that included this predictor and that that excluded it. 
-This result indicates that the availability of potential partners accounts for a large proportion of the variability on species degree.  
-Importantly, our findings of the suitability-degree relationship were qualitatively unchanged whether we included this variable or not.
+There was also a large difference on WAIC between the model that included this predictor and that that excluded it. 
+This result indicates that the availability of potential partners—this is, community composition—accounts for a large proportion of the variability in species degree. 
+Importantly, our findings relating to the variability of the stress-specialisation relationship were qualitatively unchanged, whether we included this variable or not.
 
-The group-level variation among communities was larger than that among species which further indicates the importance of the local context when determining species degree.
-Specifically, the standard deviation (in the parameters scale) of the community intercepts was `r round(sd_loc_id$Estimate, 2)` [`r round(sd_loc_id$Q2.5, 2)`, `r round(sd_loc_id$Q97.5, 2)`] while the standard deviation of the species intercept was `r round(sd_org_id$Estimate, 2)` [`r round(sd_org_id$Q2.5, 2)`, `r round(sd_org_id$Q97.5, 2)`], and that of the species' suitability slope was `r round(sd_org_id_suitability$Estimate, 2)` [`r round(sd_org_id_suitability$Q2.5, 2)`, `r round(sd_org_id_suitability$Q97.5, 2)`] (95% credible intervals shown within square brakets).
+The standard deviation (in the parameters scale) of the community intercepts was `r round(sd_loc_id$Estimate, 2)` [`r round(sd_loc_id$Q2.5, 2)`, `r round(sd_loc_id$Q97.5, 2)`] which indicates the importance of the local context when determining specialisation.
+The standard deviation of the species intercept was `r round(sd_org_id$Estimate, 2)` [`r round(sd_org_id$Q2.5, 2)`, `r round(sd_org_id$Q97.5, 2)`], and that of the species' suitability slope was `r round(sd_org_id_suitability$Estimate, 2)` [`r round(sd_org_id_suitability$Q2.5, 2)`, `r round(sd_org_id_suitability$Q97.5, 2)`] (95% credible intervals shown within square brakets).
 

### 2019-12-01 paper/manuscript.Rmd
Improve figure 2

@@
 fig_random_effects_legend <- 
-  paste0("Species-level effects of suitability.
-(a) Conditional effect of suitability for individual species.
-To facilitate visualisation we show only species for which there is suitability information in at least six communities (",
+  paste0("Species-level effects of environmental stress (a) Conditional effect of stress for individual species.
+Each line corresponds to the median relationship for each species.
+Although we included in the analysis of all species that are present in two or core communities, to facilitate visualisation here, we show only species for which there is suitability information in at least six communities (",
          n_random_pla, " plants and ", 
@@
 ",
-         "(b) The correlation between the species' intercept and the species' slope of suitability was negatively correlated.")
+         "(b and c) The correlation between the species' intercept and the species' slope of suitability was negative.
+The species' intercept can be interpreted as the relative difference between the number of partners a species has under zero environmental stress and the mean number of partners across all species.
+Positive values of species' slope indicate a positive relationship between stress and the number of partners and vice-versa.")
 

### 2019-12-01 code/figures.R

@@ -261,9 +261,9 @@ plot_ranf <- function(random_species_draws, random_correlation_posterior, random
     pub_theme() +
     coord_cartesian(expand = F) +
     theme(legend.position = "none") +
-    labs(y = "# interactions",
-         x = "environmental suitability",
-         title = "(a) effect of suitability on individual species")
+    labs(y = "# partners",
+         x = "environmental stress",
+         title = "(a) effect of stress on individual species")
 
   mean_correlation <- random_correlation_posterior %>%
     dplyr::summarise_all(mean) %$%
@@ -321,8 +321,8 @@ plot_ranf <- function(random_species_draws, random_correlation_posterior, random
     pub_theme() +
     theme(legend.position = "none") +
     labs(x = "species' intercept",
-         y = "species' suitability slope",
-         title = "(b) species' specific intercept and suitability slope",
+         y = "species' slope",
+         title = "(b) species' specific intercept and slope",
          subtitle = "all values in parameter space")
 
   plot_left <- conditional_effects_plot

### 2019-12-01 paper/manuscript.Rmd
Changes in the disussion

@@
 
-We set out to explore whether and how environmental stress can systematically affect species degree. 
-After accounting for the pool of potential partners, we found that indeed environmental conditions contribute to determining whether a species is a generalist or a specialist in their community. 
-However, we also found that the particular effect of the environment is strongly dependent on the species.
-We proposed two alternative hypotheses of how environmental stress may affect the degree, and we found evidence for both of them.
+We set out to explore whether and how environmental stress can systematically affect specialisation. 
+After accounting for the pool of potential partners, we found that environmental conditions contribute to determining whether a species is a generalist or a specialist *in their community*. 
+We also found that the particular effect of the environment is strongly dependent on the species.
+Based on existing literature, we proposed two alternative hypotheses of how environmental stress may affect species' specialisation, and we found evidence for both of them.
 Species with a large number of partners in low-stress communities were more likely to have a negative relationship and hence reduce the number of partners as stress increases. 
 Contrastingly, species in our datasets with a small number of partners in low-stress communities were more likely to have a larger number of partners in more stressful communities.
-In summary, environmental stress pushes species that are flexible enough to change their interaction partners towards intermediate levels of degree, a so-called "regression towards the mean".
+In summary, environmental stress pushes species that are flexible enough to change their interaction partners towards intermediate levels of specialisation, a so-called "regression towards the mean".
 
@@
 However, they also show that, for a large number of species, the environment may also play a substantial role in determining their realised (Eltonian) niche. 
-While previous research has recognised that environmental factors may help explain the changes in network structure along environmental gradients that cannot be explained by community composition [@tylianakis_habitat_2007], how these two factors were linked had been elusive so far [@gravel_bringing_2018].
-We believe that part of this difficulty could have arisen because species, and ultimately network structure, can respond in multiple and contrasting, ways depending on the particular bioclimatic variable examined (e.g.
+Previous research has recognised that environmental factors may help explain the changes in network structure along environmental gradients that cannot be explained by community composition [@tylianakis_habitat_2007].
+However, how these two factors were linked had been elusive so far [@gravel_bringing_2018]. 
+We believe that part of this difficulty could have arisen because species, and ultimately network structure, can respond in multiple, and contrasting, ways depending on the particular bioclimatic variable examined (e.g.
 temperature or precipitation).
@@
 
-Although both niche and neutral processes are relevant at determining species interactions, our model suggests that niche processes may be the predominant mechanism through which the environment *systematically* affect species degree.
+Although both niche and neutral processes are relevant in determining species interactions, our model suggests that niche processes may be the predominant mechanism through which the environment *systematically* affect species degree.
 First, it is unlikely that environmental suitability correlates to local species abundances [@pearce_practical_2001; @sagarin_moving_2006]. 

### 2019-12-01 paper/manuscript.Rmd
Using 95% CI for slopes and intercepts

@@
 
+```{r}
+loadd(random_slope_intercepts)
+# random_slope_intercepts <- readRDS("rsi.rds")
+
+species_types <- random_slope_intercepts %>%
+  # dplyr::rename_all(stringr::str_replace, "Q75", "Q97.5") %>%
+  # dplyr::rename_all(stringr::str_replace, "Q25", "Q2.5") %>%
+  # = Q75, Q2.5 = Q25) %>%
+  dplyr::mutate(intercept_sig = dplyr::case_when(Intercept_Q2.5 > 0 ~ "positive", Intercept_Q97.5 < 0 ~ "negative", TRUE ~ "indeterminate"), 
+                slope_sig = dplyr::case_when(scaled_suitability_Q2.5 > 0 ~ "positive", scaled_suitability_Q97.5 < 0 ~ "negative", TRUE ~ "indeterminate"), 
+                int_slo = interaction(intercept_sig, slope_sig), 
+                int_slo = dplyr::case_when(int_slo == "indeterminate.indeterminate" ~ "neither generalist or specialist", int_slo == "positive.indeterminate" ~ "true generalist", int_slo == "negative.indeterminate" ~ "true specialist", int_slo %in% c("positive.positive", "negative.negative") ~ "flexible species", TRUE ~ "flexible species") ) %>%
+  dplyr::mutate(int_slo = forcats::fct_infreq(int_slo))
+
+species_types %>%
+  dplyr::count(int_slo, guild) %>%
+  tidyr::spread(guild, n)
+
+  # dplyr::filter(intercept_sig != "indeterminate") %>%
+  # table(slope_sig, intercept_sig)
+
+library(ggplot2)
+species_types %>%  # 
+  ggplot(aes(x = int_slo, fill = guild)) +
+  geom_bar() +
+  coord_flip()
+```
+
 ```{r fig-random-effects, fig.width = width('double'), fig.height = 2.2*2, fig.cap = fig_random_effects_legend, out.width = "6.81in", out.height = "4.4in", out.extra="center"}

### 2019-12-01 code/model_predictions.R

@@ -168,7 +168,7 @@ get_pos_random_params <- function(baseline_model){
                                              start = 20,
                                              end = -2L))
 
-  c("Estimate", "Q25", "Q75") %>%
+  c("Estimate", "Q2.5", "Q97.5") %>%
     purrr::map_dfc(~ spread_post_summary(tall_posterior, .)) %>%
     dplyr::inner_join(sp_properties, by = "org_id")
 

### 2019-12-01 paper/manuscript.Rmd
Edit discussion

@@
 Our results suggest that changes in community composition are indeed the primary channel through which the environment determines changes interaction probability. 
-However, they also show that, for a large number of species, the environment may also play a substantial role in determining their realised (Eltonian) niche. 
+However, they also show that, for a large number of species, the environment may also play a substantial role in determining their level of specialisation. 
 Previous research has recognised that environmental factors may help explain the changes in network structure along environmental gradients that cannot be explained by community composition [@tylianakis_habitat_2007].
@@
 
-Although both niche and neutral processes are relevant in determining species interactions, our model suggests that niche processes may be the predominant mechanism through which the environment *systematically* affect species degree.
-First, it is unlikely that environmental suitability correlates to local species abundances [@pearce_practical_2001; @sagarin_moving_2006]. 
-Second, even if there is a relationship between suitability and abundances, a particular environmental gradient could have a positive effect on the abundance of some species and a negative effect on others.
-Indeed, we show that within a community there is a wide range of suitability values, even for the relatively limited number of species we were able to include in our analysis.
+Although both niche and neutral processes are relevant in determining species interactions, our model suggests that niche processes may be the predominant mechanism through which the environment *systematically* affects specialisation.
+First, it is unlikely that environmental stress correlates to local species abundances [@pearce_practical_2001; @sagarin_moving_2006]. 
+Second, even if there is a relationship between stress and abundances, a particular environmental gradient could have a positive effect on the abundance of some species and a negative effect on others.
+Indeed, we find that within a community there is a wide range of stress values, even for the relatively limited number of species we were able to include in our analysis.
 
@@
 Our results add two important nuances to these findings. 
-First, because generalists seem to focus on a smaller number of partners as environmental conditions deteriorate, we show that trait matching might still play a role in determining the interactions of generalist species.
-Second, we demonstrate that rewiring is not exclusive to generalists.
-At least a fraction of the species that appear to be specialist in their communities might be as flexible, if not more, than generalist species, effectively behaving as facultative generalists in the face of environmental change.
-These flexible specialists might, therefore, have a more significant role in network persistence than previously expected.
+First, because "generalists" seem to focus on a smaller number of partners as environmental conditions deteriorate, we show that trait matching might still play a role in determining the interactions of generalist species.
+Second, and most importantly, our results suggest that actually only a small proportion of species are "true generalists" or "true specialists" this is, species that interact with a large or small number of partners regardless of the environmental stress, respectively.
+This implies that rewiring is not exclusive of species with a large number of partners. 
+Instead, at least a fraction of the species that appear to be specialist *in their communities* might be as flexible, if not more, than those with a large number of partners, effectively behaving as facultative generalists in the face of environmental change.
+These flexible "specialists" might therefore have a more significant role in network persistence than previously expected.
 
-While our model detected how the environment affects the interactions of two types of species, generalists and flexible specialists, there is a third group that remained invisible for our model but has important implications for network persistence and stability.
+In our model we can roughly divide species between true specialists, true generalists, and flexible species. 
+However, there is a fourth group that remained invisible for our model but has important implications for network persistence and stability.
 Species that are able to vary their interaction partners flexibly and their role in the network are more likely to persist in their community as environmental conditions vary [@gaiarsa_interaction_2019].
-We propose this third group of is composed of specialists that are constrained to interact with partners of high trait-matching and therefore were not likely to be found in more than one community. 
+We propose this fourth group of is composed of true specialists that are constrained to interact with partners of high trait-matching and therefore were not likely to be found in more than one community.
 If species that are not flexible are unlikely to persist over temporal or spatial environmental gradients, we can expect specialised communities that are highly constrained by trait-matching [like some plant-hummingbird networks; @vizentin-bugoni_processes_2014; @maruyama_morphological_2014] to be far more vulnerable to increased climate change-induced environmental stress and habitat degradation than communities where role and interaction flexibility are more prevalent.
@@
 Communities as a whole might be in a trajectory of even more diffuse co-evolution.
-For specialist species, at least, the longer-term benefits of being able to interact with multiple partners might be more important than the shorter-term benefits of interacting with partners of high trait matching.
+For specialist, at least, the longer-term benefits of being able to interact with multiple partners might be more important than the shorter-term benefits of interacting with partners of high trait matching.
 
@@
 
-In conclusion, we show that the environment can affect the realised niche of plants and pollinators in systematic ways beyond community composition. 
-On the one hand, species that are inflexible with their interaction partners are unlikely to persist under more stressful environmental conditions. 
-On the other, species that are flexible with their interactions partners experience a regression towards intermediate levels of degree, where generalist species tend to interact with fewer, presumably more effective, partners and specialist tend to interact with more partners.
+In conclusion, we show that the environment can affect the specialisation level of plants and pollinators in systematic ways beyond community composition. 
+Species that are inflexible with their interaction partners are unlikely to persist under more stressful environmental conditions. 
+However, we show that many species are flexible in regards of their specialisation levels and therefore are not inherently generalists or specialists. 
+Instead, species' level of specialisation/generalisation should be considered on a relative scale depending on where they are found and the environmental conditions at that location.
 

### 2019-12-01 code/figures.R
Add vline to show mean stress levels in random eff. figure

@@ -220,7 +220,11 @@ plot_conditional_effect_guild <- function(data, pal, mean_val, log_transformed =
     labs(y = "# interactions")
 }
 
-plot_ranf <- function(random_species_draws, random_correlation_posterior, random_sp_names, random_slope_intercepts){
+plot_ranf <- function(random_species_draws, 
+                      random_correlation_posterior, 
+                      random_sp_names, 
+                      random_slope_intercepts, 
+                      mean_suitability){
 
   suppressPackageStartupMessages({
     require(ggplot2)
@@ -236,6 +240,7 @@ plot_ranf <- function(random_species_draws, random_correlation_posterior, random
     dplyr::left_join(random_sp_names, by = "org_id") %>%
     ggplot(aes(x = var, y = .value, colour = guild)) +
     geom_line(aes(group = org_id, alpha = highlight, size = highlight), stat = "summary",fun.y = "mean") +
+    geom_vline(xintercept = mean_suitability, size = 0.25, linetype = 2) +
     geom_mark_circle(aes(group = org_id,
                          filter = highlight & mark,
                           label = sp_name),

### 2019-12-01 main.R

@@ -369,7 +369,8 @@ figures_plan <- drake_plan(
   fig_random_effects = plot_ranf(random_species_draws,
                                  random_correlation_posterior,
                                  random_sp_names,
-                                 random_slope_intercepts),
+                                 random_slope_intercepts, 
+                                 mean_suitability = mean_parameter_values$suitability),
  fig_median_suitability = plot_suitability(median_suitability)
 )
 

### 2019-12-01 paper/manuscript.Rmd
Order WAIC table ascending

@@
   purrr::map_df(~tibble::tibble(estimate = .[1], se = .[2]), .id = "formula") %>%
-  dplyr::arrange(dplyr::desc(estimate)) %>%
+  dplyr::arrange(estimate) %>%
   dplyr::filter(formula != "formula_full") %>%

### 2019-12-01 paper/manuscript.Rmd
Remove quantification of true generalist and true specialists. Doing it properly will take time

@@
 
-```{r}
-loadd(random_slope_intercepts)
-# random_slope_intercepts <- readRDS("rsi.rds")
-
-species_types <- random_slope_intercepts %>%
-  # dplyr::rename_all(stringr::str_replace, "Q75", "Q97.5") %>%
-  # dplyr::rename_all(stringr::str_replace, "Q25", "Q2.5") %>%
-  # = Q75, Q2.5 = Q25) %>%
-  dplyr::mutate(intercept_sig = dplyr::case_when(Intercept_Q2.5 > 0 ~ "positive", Intercept_Q97.5 < 0 ~ "negative", TRUE ~ "indeterminate"), 
-                slope_sig = dplyr::case_when(scaled_suitability_Q2.5 > 0 ~ "positive", scaled_suitability_Q97.5 < 0 ~ "negative", TRUE ~ "indeterminate"), 
-                int_slo = interaction(intercept_sig, slope_sig), 
-                int_slo = dplyr::case_when(int_slo == "indeterminate.indeterminate" ~ "neither generalist or specialist", int_slo == "positive.indeterminate" ~ "true generalist", int_slo == "negative.indeterminate" ~ "true specialist", int_slo %in% c("positive.positive", "negative.negative") ~ "flexible species", TRUE ~ "flexible species") ) %>%
-  dplyr::mutate(int_slo = forcats::fct_infreq(int_slo))
-
-species_types %>%
-  dplyr::count(int_slo, guild) %>%
-  tidyr::spread(guild, n)
-
-  # dplyr::filter(intercept_sig != "indeterminate") %>%
-  # table(slope_sig, intercept_sig)
-
-library(ggplot2)
-species_types %>%  # 
-  ggplot(aes(x = int_slo, fill = guild)) +
-  geom_bar() +
-  coord_flip()
-```
-
 ```{r fig-random-effects, fig.width = width('double'), fig.height = 2.2*2, fig.cap = fig_random_effects_legend, out.width = "6.81in", out.height = "4.4in", out.extra="center"}

### 2019-12-01 paper/manuscript.Rmd
Explain better what the intercept means in text

@@
 For some species, there is a strong negative relationship between stress and specialisation, while for others, there is a strong positive relationship (Figure \@ref(fig:fig-random-effects)a). 
-Interestingly, the slope of this relationship correlates negatively with the species' intercept in the model (Figure \@ref(fig:fig-random-effects)b and c). 
+Interestingly, the slope of this relationship correlates with the species' intercept in the model (Figure \@ref(fig:fig-random-effects)b and c).
+Recall that the model estimates the intercept at the mean value for stress across communities (`r round(readd(mean_parameter_values)$suitability, 2)`).
 The mean correlation coefficient was `r round(random_cor$Estimate, 2)` [`r round(random_cor$Q2.5, 2)`, `r round(random_cor$Q97.5, 2)`].
-In other words, the slope of the stress-specialisation relationship was more likely to be positive for species with a smaller number of partners in low-stress conditions (and negative for species with a larger number of partners).
+Therefore, the slope of the stress-specialisation relationship was more likely to be positive for species with a large number of partners under average stress conditions (and negative for species with a smaller number of partners).
+Extrapolating to no-stress conditions: species that would interact with a small number of partners under no stress are more likely to interact with more partners as stress increases, whereas those that would interact with a large number of partners are more likely to interact with less.
 

### 2019-12-01 paper/manuscript.Rmd
Explain intercept better in figure caption

@@
          "(b and c) The correlation between the species' intercept and the species' slope of suitability was negative.
-The species' intercept can be interpreted as the relative difference between the number of partners a species has under zero environmental stress and the mean number of partners across all species.
+The species' intercept can be interpreted as the relative difference between the number of partners a species has under mean levels of environmental stress and the mean number of partners across all species.
 Positive values of species' slope indicate a positive relationship between stress and the number of partners and vice-versa.")

### 2019-12-01 paper/manuscript.Rmd
Typos and grammar discussion

@@
 First, because "generalists" seem to focus on a smaller number of partners as environmental conditions deteriorate, we show that trait matching might still play a role in determining the interactions of generalist species.
-Second, and most importantly, our results suggest that actually only a small proportion of species are "true generalists" or "true specialists" this is, species that interact with a large or small number of partners regardless of the environmental stress, respectively.
-This implies that rewiring is not exclusive of species with a large number of partners. 
+Second, and most importantly, our results suggest that only a small proportion of species are "true generalists" or "true specialists" this is, species that interact with a large or small number of partners regardless of the environmental stress, respectively.
+This pattern implies that rewiring is not exclusive of species with a large number of partners. 
 Instead, at least a fraction of the species that appear to be specialist *in their communities* might be as flexible, if not more, than those with a large number of partners, effectively behaving as facultative generalists in the face of environmental change.
@@
 
-In our model we can roughly divide species between true specialists, true generalists, and flexible species. 
-However, there is a fourth group that remained invisible for our model but has important implications for network persistence and stability.
-Species that are able to vary their interaction partners flexibly and their role in the network are more likely to persist in their community as environmental conditions vary [@gaiarsa_interaction_2019].
-We propose this fourth group of is composed of true specialists that are constrained to interact with partners of high trait-matching and therefore were not likely to be found in more than one community.
+In our model, we can roughly divide species between true specialists, true generalists, and flexible species. 
+However, there is a fourth group that remained invisible to our model but has important implications for network persistence and stability.
+Species that can vary their interaction partners flexibly and their role in the network are more likely to persist in their community as environmental conditions vary [@gaiarsa_interaction_2019].
+We propose this fourth group is composed of true specialists that are constrained to interact with partners of high trait-matching and therefore were not likely to be found in more than one community.
 If species that are not flexible are unlikely to persist over temporal or spatial environmental gradients, we can expect specialised communities that are highly constrained by trait-matching [like some plant-hummingbird networks; @vizentin-bugoni_processes_2014; @maruyama_morphological_2014] to be far more vulnerable to increased climate change-induced environmental stress and habitat degradation than communities where role and interaction flexibility are more prevalent.
@@
 Species that are inflexible with their interaction partners are unlikely to persist under more stressful environmental conditions. 
-However, we show that many species are flexible in regards of their specialisation levels and therefore are not inherently generalists or specialists. 
-Instead, species' level of specialisation/generalisation should be considered on a relative scale depending on where they are found and the environmental conditions at that location.
+However, we show that many species are flexible in regards to their specialisation levels and therefore are not inherently generalists or specialists. 
+Instead, the species' level of specialisation/generalisation should be considered on a relative scale depending on where they are found and the environmental conditions at that location.
 

### 2019-12-01 paper/supp-info.Rmd
Fix author names in supp info
Fix typo supp info

@@
 subtitle: "Supplementary information"
-author: "E. Fernando Cagua, Hugo J. Marrero, Jason M. Tylianakis, Daniel B. Stouffer"
+author: "E. Fernando Cagua, Audrey Lustig, Jason M. Tylianakis, Daniel B. Stouffer"
 bibliography: 
@@
 We removed occurrences for which their coordinates (*v*) fell outside the borders of the country where they were recorded; (*vi*) those around a country capital or the centroid of the country and province centroids; (*vii*) those around a biodiversity institution; and (*viii*) those located within oceans.
-Thorugh this cleaning process, we removed with `r round(sum(n_dirty_occurrences$N)/1000000, digits = 1)` million occurrences distributed accross `r n_species_with_dirty_occurrences` species.
-
-# Supplementary results
+Through this cleaning process, we removed with `r round(sum(n_dirty_occurrences$N)/1000000, digits = 1)` million occurrences distributed across `r n_species_with_dirty_occurrences` species.
 

### 2019-12-01 code/plotting-and-formatting.R
Use x instead of * to show model terms in model table

@@ -128,12 +128,12 @@ translate_model_formula <- function(x, type = "short"){
     )
   } else if(type == "long-abv"){
     dplyr::case_when(
-      x == "formula_base" ~ "Suit. * Guild + Pot.",
+      x == "formula_base" ~ "Suit. x Guild + Pot.",
       # x == "formula_no_grinell_niche_size" ~ "Suit. + Gen. + Pot.",
       # x == "formula_no_generalism" ~ "Suit. + Pot. + Env.",
       x == "formula_no_suitability" ~ "Guild + Pot.",
       # x == "formula_no_possible_partners_generalism" ~ "Suit. + Env.",
-      x == "formula_no_possible_partners" ~ "Suit. * Guild",
+      x == "formula_no_possible_partners" ~ "Suit. x Guild",
       x == "formula_full" ~ "FULL",
       x == "formula_no_guild" ~ "Suit. + Pot.",
       TRUE ~ "unknown"

### 2019-12-01 paper/draft-info.Rmd
Add to do. Need to quantify numbers in species types
Update draft info

@@
 title: "Draft information"
-subtitle: "version: draft-0.3"
-date: "2019-11"
+subtitle: "version: draft-0.4"
+date: "2019-12-01"
 # bibliography: phd-bibliography/pollen-competition.bib
@@
 * Removed species generality and the breadth of the environmental niche from the model
+* Language is now centered on stress and specialisation. Mentioning bioclimatic suitability only when needed in the methods.
 
@@
 * Finish manual species checks
+* Quantify number of "true specialists", "true generalists" and flexible species.
 

### 2019-12-03 paper/manuscript.Rmd
update paper when bibliography changes
Correct more typos and grammar

@@
 loadd(interaction_citations, config) 
+loadd(bibliography)
 ```
@@
 However, how exactly the environment, specifically the stress it imposes on species, affects whether two species interact or not, and ultimately the species' specialisation. 
-Understanding how the environment drives the number of partners is crucial because it underpins the species role in its community and shapes the structure of the network of interactions. 
+Understanding how the environment drives the number of partners is crucial because it underpins the species' role in its community and shapes the structure of the network of interactions. 
 This structure, in turn, determines ecosystem function and stability.
@@
 For instance, @hoiss_altitude_2012 found increased phylogenetic clustering between plants and pollinators at higher altitudes; while @peralta_phylogenetic_2015 found that parasitoids in plantation forest, where environmental stress was higher than in native forests, were constrained to interact with hosts, they were best adapted to attack.
-Similarly, @lavandero_genotype_2013 found that environmental stress due to higher temperature reduced the trophic niche breadth of parasitoids suggesting higher specialisation.
+Similarly, @lavandero_genotype_2013 showed that environmental stress due to higher temperature reduced the trophic niche breadth of parasitoids suggesting higher specialisation.
 
@@
 Species with a large number of partners, on the other hand, should have a larger pool of available partners and might, therefore, be more likely to specialise under environmental stress and focus on the most beneficial partners.
-Importantly, when testing these hypotheses, we control for the potential effects of the environment in community composition [which has been previously shown to be a determinant factor; @gravel_bringing_2018]
+Importantly, when testing these hypotheses, we control for the potential effects of the environment in community composition [which has been previously shown to be a determinant factor; @gravel_bringing_2018].
 We test these hypotheses using data on plant-pollinator interactions. 
@@
        most_popular_species$sp_name[1], 
-       "*, which was sampled on ", 
+       "*, which was sampled at ", 
        most_popular_species$n_locations[1], 
@@
        most_popular_species$sp_name[2], 
-       "*, which was sampled on ", 
+       "*, which was sampled at ", 
        most_popular_species$n_locations[2], 
@@
 
-### Environmental stress
+## Environmental stress
 
@@
 The niche factor analysis requires two critical pieces of information. 
-First, we require information about the occurrences of the species of interest.
-Second, we require information about the environmental conditions for all the locations in which the species occurs.
+First, it requires information about the occurrences of the species of interest.
+Second, the method requires information about the environmental conditions for all the locations in which the species occurs.
 We retrieved `r round(sum(n_occurrences$N)/1000000, digits = 1)` million occurrences from the Global Biodiversity Information Facility (GBIF; https://www.gbif.org). 
@@
 As expected, the vast majority of these problematic cells were close to the shore. 
-To address this issue, we calculated the average value of environmental variables within an `r config$climate_buffer/1000`km buffer of the centre of the cell where the variable was missing and used it to approximate the value of the variable in that cell.
+To address this issue, we calculated the average value of environmental variables within a `r config$climate_buffer/1000`km buffer of the centre of the cell where the variable was missing and used it to approximate the value of the variable in that cell.
 Using this procedure, we were able to fill environmental variables for `r scales::percent(percent_filled_round_one, accuracy = 0.1)` of the cells where they were missing. 
 To fill the remaining `r format(complete_filled_cells_1[1], big.mark= ",")` cells, we repeated the aforementioned procedure but instead using a `r config$climate_buffer*2/1000`km buffer. 
-We removed from further analysis occurrences located within the `r complete_filled_cells_2[1]` cells for which we were unable to fill environmental variables (`r scales::percent(complete_filled_cells_2[1]/sum(complete_filled_cells_2))` of the total).
+We removed from further analysis occurrences located within the `r complete_filled_cells_2[1]` cells for which we were unable to fill environmental variables (`r scales::percent(complete_filled_cells_2[1]/sum(complete_filled_cells_2), 0.01)` of the total).
 
@@
 We included the number of known possible partners as a predictor in our models as it allows us to control for the effects of the environment on community composition, effectively accounting for species co-occurrence.
-We calculate this metric by determining the number of partners with which the species is known to interact in any other community.
+We calculated this metric by determining the number of partners with which the species is known to interact in any other community.
 Controlling for the number of potential partners makes our model a particularly stringent test of our environmental-stress hypotheses because this variable could explain a large proportion of variance.
@@
 As expected, we found a strong and positive relationship between the number of possible interactions and the number of realised interactions in the community. 
-There was also a large difference on WAIC between the model that included this predictor and that that excluded it. 
+There was also a large difference of WAIC between the model that included this predictor and that that excluded it. 
 This result indicates that the availability of potential partners—this is, community composition—accounts for a large proportion of the variability in species degree. 
@@
 The standard deviation (in the parameters scale) of the community intercepts was `r round(sd_loc_id$Estimate, 2)` [`r round(sd_loc_id$Q2.5, 2)`, `r round(sd_loc_id$Q97.5, 2)`] which indicates the importance of the local context when determining specialisation.
-The standard deviation of the species intercept was `r round(sd_org_id$Estimate, 2)` [`r round(sd_org_id$Q2.5, 2)`, `r round(sd_org_id$Q97.5, 2)`], and that of the species' suitability slope was `r round(sd_org_id_suitability$Estimate, 2)` [`r round(sd_org_id_suitability$Q2.5, 2)`, `r round(sd_org_id_suitability$Q97.5, 2)`] (95% credible intervals shown within square brakets).
+The standard deviation of the species intercept was `r round(sd_org_id$Estimate, 2)` [`r round(sd_org_id$Q2.5, 2)`, `r round(sd_org_id$Q97.5, 2)`], and that of the species' stress slope was `r round(sd_org_id_suitability$Estimate, 2)` [`r round(sd_org_id_suitability$Q2.5, 2)`, `r round(sd_org_id_suitability$Q97.5, 2)`] (95% credible intervals shown within square brakets).
 
@@
 Similarly, if the patterns we see in our models have also played a role during the evolutionary history of pollination communities, our results also help explain why only a small fraction of plant-pollinator interactions show a strong signature of deep co-evolutionary history [@hutchinson_cophylogenetic_2017].
-The increases on the stress that species are predicted to experience due to rapid environmental change might further erode the co-evolutionary history of specialist species.
+The increases in the stress that species are predicted to experience due to rapid environmental change might further erode the co-evolutionary history of specialist species.
 Communities as a whole might be in a trajectory of even more diffuse co-evolution.
-For specialist, at least, the longer-term benefits of being able to interact with multiple partners might be more important than the shorter-term benefits of interacting with partners of high trait matching.
+For specialists, at least, the longer-term benefits of being able to interact with multiple partners might be more important than the shorter-term benefits of interacting with partners of high trait matching.
 

### 2019-12-03 code/figures.R
Use # partners instead of # interactons in figures

@@ -185,8 +185,8 @@ plot_all_conditional_effect <- function(cond_draws, mean_parameter_values){
 
   possible_plot <- cond_draws$possible %>%
     plot_conditional_effect_guild(pal, mean_parameter_values$possible) +
-    labs(title = "(b) possible number of interactions",
-         x = "# possible interactions")
+    labs(title = "(b) possible number of partners",
+         x = "# possible partners")
 
   p <- cowplot::plot_grid(#grinell_niche_size_plot,
                           suitability_plot,
@@ -217,7 +217,7 @@ plot_conditional_effect_guild <- function(data, pal, mean_val, log_transformed =
     pub_theme() +
     coord_cartesian(expand = F) +
     theme(legend.position = "none") +
-    labs(y = "# interactions")
+    labs(y = "# partners")
 }
 
 plot_ranf <- function(random_species_draws, 

### 2019-12-03 paper/manuscript.Rmd
Remove old text that stayed there who knows why

@@
 
-Our third and final step was to relate the environmental suitability to the relative number of partners a species has in a community, as a proxy for Eltionian niche breadth. 
-To explore this relationship within and across species, we used a multilevel Bayesian model in which we controlled for the potential effects of the environment on co-occurrence.
-
-We assume that stress a species experience in a particular location is inversely related to the suitability of the average environmental conditions in that place. 
+We calculated the environmental stress of species in their communities.
+We assume that stress a species experiences in a particular location is inversely related to the suitability of the average environmental conditions in that place. 
 As we aim to compare specialisation levels for different levels of environmental stress, we only calculate bioclimatic suitability for species that were present in at least `r numbers2words(readd(minimum_spp_locations))` communities.

### 2019-12-03 paper/manuscript.Rmd
Reorder paraphaph in the methods to improve clarity

@@
 
-Next, we calculate the probability density function of the species distribution in environmental space. 
-To determine the environmental space, we use the first two components from a principal component analysis of the 37 bioclimatic variables associated with the species occurrences. 
-Specifically we use the `dudi.pca` function from the R package `ade4` `r as.character(packageVersion('ade4'))` [@dray_ade4_2007] and center and scale all bioclimatic variables to have a mean of zero and a unit variance.
-We then determine the position of species occurrences in the environmental space and estimate their bivariate probability density function. 
-We use a kernel method to estimate this density and normalise it such that it ranges between zero and one. 
-Specifically, to calculate the probability density function we use `ecospat.grid.clim.dyn` from the R package `ecospat` `r as.character(packageVersion('ecospat'))` [@broennimann_ecospat_2018] with a grid resolution of 200.
-We then determine the location in the environmental space of the plant-pollinator communities using the function `suprow` from `ade4`.
-The normalised density at that particular location [which we calculate using the R package `raster` `r as.character(packageVersion('raster'))`; @hijmans_raster_2019] corresponds the bioclimatic suitability.
-We use the kernel density method in the niche-factor analysis [@broennimann_measuring_2012] rather than the distance from the mode [@hirzel_ecological-niche_2002], as it has been proposed earlier because it has been shown to reduce the procedure's sensitivity to sampling effort and the resolution of the environmental space.
+Next, we calculated the probability density function of the species distribution in environmental space. 
+To determine the environmental space, we used the first two components from a principal component analysis of the 37 bioclimatic variables associated with the species occurrences. 
+Specifically we used the `dudi.pca` function from the R package `ade4` `r as.character(packageVersion('ade4'))` [@dray_ade4_2007] and center and scale all bioclimatic variables to have a mean of zero and a unit variance.
+We then determined the position of species occurrences in the environmental space and estimate their bivariate probability density function. 
+We used a kernel method to estimate this density and normalised it such that it ranges between zero and one. 
+We used the kernel density method in the niche-factor analysis [@broennimann_measuring_2012] rather than the distance from the mode [@hirzel_ecological-niche_2002] (as it has been proposed earlier) because it has been shown to reduce the procedure's sensitivity to sampling effort and the resolution of the environmental space.
+Specifically, to calculate the probability density function we used `ecospat.grid.clim.dyn` from the R package `ecospat` `r as.character(packageVersion('ecospat'))` [@broennimann_ecospat_2018] with a grid resolution of 200.
+We then determined the location in the environmental space of the plant-pollinator communities using the function `suprow` from `ade4`.
+The normalised density at that particular location [which we calculated using the R package `raster` `r as.character(packageVersion('raster'))`; @hijmans_raster_2019] corresponds the bioclimatic suitability.
 The result of all these steps is the environmental stress which corresponds to one minus the bioclimatic suitability for a species of a particular location.

### 2019-12-03 main.R
Output data was going to the wrong dir

@@ -400,7 +400,7 @@ file_out_plan <- drake_plan(
     random_sp_names = random_sp_names,
     random_slope_intercepts = random_slope_intercepts,
     mean_suitability = mean_parameter_values$suitability),
-  target(saveRDS(fig_random_effects_data, "fig_random_effects_data.rds"))
+  target(saveRDS(fig_random_effects_data, "data/processed/fig_random_effects_data.rds"))
 )
 
 # Manuscript --------------------------------------------------------------

### 2019-12-04 paper/manuscript.Rmd
Note about missing species

@@
 This is the number of occurrences necessary to maintain the mean absolute error of bioclimatic suitability below `r config$min_suitability_error` (Fig. \@ref(fig:fig-sensitivity-analysis)). 
-We therefore removed from further analyses `r n_spp_not_enough_occ` species for which we did not have enough occurrences to obtain robust estimates.
+We therefore removed from further analyses (NOTE XXX) `r n_spp_not_enough_occ` species for which we did not have enough occurrences to obtain robust estimates.
 <!-- When inspecting the suitability values of the analysed species, we found that most communities included species for which habitat suitability was low and species for which it was high (Fig.

### 2019-12-05 paper/manuscript.Rmd
Fix species number
Some format changes for Biorxiv

@@
 # classoption: a4paper
-geometry: 
-  - textwidth=33em
-  - textheight=48\baselineskip
+# geometry: 
+  # - textwidth=33em
+  # - textheight=48\baselineskip
 header-includes:
@@
 
-**Running title:** XX
+<!-- **Running title:** XX -->
 
-**Keywords:** `r keywords`
+<!-- **Type of article:** XX -->
 
-**Type of article:** XX
+<!-- **Number of words:** `r abs_wordcount$n_words_stri` in abstract; `r format(round(msc_wordcount$n_words_stri), big.mark = ",")` in main text. -->
 
-**Number of words:** `r abs_wordcount$n_words_stri` in abstract; `r format(round(msc_wordcount$n_words_stri), big.mark = ",")` in main text.
+<!-- **Number of displays:** `r n_displays$figures` figures; `r n_displays$tables` tables; `r n_displays$text_boxes` text boxes. -->
 
-**Number of displays:** `r n_displays$figures` figures; `r n_displays$tables` tables; `r n_displays$text_boxes` text boxes.
-
-**Number of references:** `r n_references + nrow(interaction_citations)`
+<!-- **Number of references:** `r n_references + nrow(interaction_citations)` -->
 
@@
 
-**Data accessibility:** Data supporting the results will be accessible in an appropriate data repository after publication. We will include the DOI here.
+<!-- **Data accessibility:** Data supporting the results will be accessible in an appropriate data repository after publication. We will include the DOI here. -->
 
-**Author contributions:** XX
+<!-- **Author contributions:** XX -->
 
@@
 `r paste(drake::readd(abstract), collapse = "")`
+
+**Keywords:** `r keywords`
 
@@
 
-n_spp_not_enough_occ <- nrow(n_thinned_occurrences) - nrow(n_enough_occurrences)
+n_spp_not_enough_occ <- nrow(n_thinned_occurrences) - nrow(n_enough_occurrences$single_species)
 ```

### 2019-12-05 code/plotting-and-formatting.R
Do not abbrebiate terms table

@@ -128,14 +128,14 @@ translate_model_formula <- function(x, type = "short"){
     )
   } else if(type == "long-abv"){
     dplyr::case_when(
-      x == "formula_base" ~ "Suit. x Guild + Pot.",
+      x == "formula_base" ~ "stress x guild + # possible partners",
       # x == "formula_no_grinell_niche_size" ~ "Suit. + Gen. + Pot.",
       # x == "formula_no_generalism" ~ "Suit. + Pot. + Env.",
-      x == "formula_no_suitability" ~ "Guild + Pot.",
+      x == "formula_no_suitability" ~ "guild + # possible partners",
       # x == "formula_no_possible_partners_generalism" ~ "Suit. + Env.",
-      x == "formula_no_possible_partners" ~ "Suit. x Guild",
+      x == "formula_no_possible_partners" ~ "stress x guild",
       x == "formula_full" ~ "FULL",
-      x == "formula_no_guild" ~ "Suit. + Pot.",
+      x == "formula_no_guild" ~ "stress + # possible partners",
       TRUE ~ "unknown"
     )
   }

### 2019-12-05 paper/manuscript.Rmd
Remove note

@@
 This is the number of occurrences necessary to maintain the mean absolute error of bioclimatic suitability below `r config$min_suitability_error` (Fig. \@ref(fig:fig-sensitivity-analysis)). 
-We therefore removed from further analyses (NOTE XXX) `r n_spp_not_enough_occ` species for which we did not have enough occurrences to obtain robust estimates.
+We therefore removed from further analyses `r n_spp_not_enough_occ` species for which we did not have enough occurrences to obtain robust estimates.
 <!-- When inspecting the suitability values of the analysed species, we found that most communities included species for which habitat suitability was low and species for which it was high (Fig.

### 2019-12-05 paper/manuscript.Rmd
Fix ugly figure reference

@@
 Therefore, our first step was to ensure consistent spelling and standardisation of species names synonyms (see Supplementary Methods).
-The cleaning process resulted on a total of `r format(stats_clean_int$pla_id, big.mark = ",")` plants and `r format(stats_clean_int$ani_id, big.mark = ",")` pollinator species distributed across `r format(stats_clean_int$loc_id)` locations arround the globe (Figure \@ref(fig:fig-worldmap), \@ref(fig:fig-distribution-species-mult-locations)).
+The cleaning process resulted on a total of `r format(stats_clean_int$pla_id, big.mark = ",")` plants and `r format(stats_clean_int$ani_id, big.mark = ",")` pollinator species distributed across `r format(stats_clean_int$loc_id)` locations arround the globe (Figure \@ref(fig:fig-distribution-species-mult-locations) and  \@ref(fig:fig-worldmap)).
 

### 2020-03-09 paper/manuscript.Rmd
Better title
Change citation style

@@
 ---
-title: "Environment affects specialisation of plants and pollinators"
+title: "Environmental stress drives intermediate plant and pollinator specialisation"
 author: 
@@
   - int-bibliography.bib
-# csl: pnas.csl
+csl: ecology-letters.csl
 output: #word_document

### 2020-03-09 paper/manuscript.Rmd
Title page to conform to EL requirements

@@
 
-<!-- **Running title:** XX -->
+**Running title:** Environmental stress drives specialisation.
 
-<!-- **Type of article:** XX -->
+**Keywords:** `r keywords`
 
-<!-- **Number of words:** `r abs_wordcount$n_words_stri` in abstract; `r format(round(msc_wordcount$n_words_stri), big.mark = ",")` in main text. -->
+**Type of article:** Letter.
 
-<!-- **Number of displays:** `r n_displays$figures` figures; `r n_displays$tables` tables; `r n_displays$text_boxes` text boxes. -->
+**Number of words:** `r abs_wordcount$n_words_stri` in abstract; `r format(round(msc_wordcount$n_words_stri), big.mark = ",")` in main text.
 
-<!-- **Number of references:** `r n_references + nrow(interaction_citations)` -->
+**Number of displays:** `r n_displays$figures` figures; `r n_displays$tables` tables; `r n_displays$text_boxes` text boxes.
+
+**Number of references:** `r n_references + nrow(interaction_citations)`
 
@@
 
-<!-- **Data accessibility:** Data supporting the results will be accessible in an appropriate data repository after publication. We will include the DOI here. -->
+**Data accessibility:** Data supporting the results will be accessible in an appropriate data repository after publication. We will include the DOI here.
 
-<!-- **Author contributions:** XX -->
+**Author contributions:** EFC conceived the study. EFC and AL compiled cleaned the data. EFC analysed the data. All authors contributed to the writing of the manuscript and study design.
 
@@
 `r paste(drake::readd(abstract), collapse = "")`
-
-**Keywords:** `r keywords`
 

### 2020-03-29 paper/manuscript.Rmd
changes to first paragraph of introduction

@@
 
-Species interactions are known to vary widely across space and time. 
-There are multiple examples of species that interact with a large number of partners in a particular community or season, but with fewer in another. 
-Some of this variation can be attributed to environmental drivers. 
-However, how exactly the environment, specifically the stress it imposes on species, affects whether two species interact or not, and ultimately the species' specialisation. 
-Understanding how the environment drives the number of partners is crucial because it underpins the species' role in its community and shapes the structure of the network of interactions. 
-This structure, in turn, determines ecosystem function and stability.
+Species interactions are known to vary widely across space and time [@laliberte_cascading_2012; @trojelsgaard_geographical_2015; @schleuning_specialization_2012; @poisot_beyond_2015]. 
+There are multiple examples of species that interact with a large number of partners in a particular community or season, but with fewer in another [@olesen_temporal_2008; @dupont_spatio-temporal_2009; @olesen_strong_2011; @rabeling_seasonal_2019; @benadi_specialization_2014].
+Some of this variation can be attributed to environmental drivers [@tylianakis_ecological_2017]. 
+However, it remains unknown how generalisable characteristics of the environment, specifically the stress it imposes on species, affects whether two species interact, and, ultimately, the species' specialisation.
+Understanding how the environment drives the number of partners is crucial because it underpins the species' role in its community and shapes the structure of the network of interactions [@cirtwill_review_2018].
+This structure, in turn, determines ecosystem function and stability [@thebault_stability_2010].
 

### 2020-04-11 paper/manuscript.Rmd
changes to second paragraph of intro:

@@
 
-Species interactions are determined in part by niche processes (the matching of traits) and partly by neutral processes (more abundant species are more likely to encounter each other and, thus, interact).
-The environment can influence both of these processes. 
-It is, therefore, not surprising that, despite limitations on the spatial extent or the number of environmental gradients considered, multiple studies have been able to show how changes to interactions can be related to environmental change [@tylianakis_ecological_2017].
-For instance, some studies suggest that the strength of some trophic interactions, like predation [@mckinnon_lower_2010; @vucic-pestic_warming_2011] and herbivory [@baskett_latitudinal_2018], can increase with temperature but might decrease with precipitation [@pires_predicted_2016].
-Some other studies, however, have shown either no effect (on average) or non-linear effects of temperature or precipitation on plant-pollinator interactions [@devoto_patterns_2005; @gravel_bringing_2018].
+Species interactions are determined in part by niche processes (the matching of traits) and partly by neutral processes (more abundant species are more likely to encounter each other and, thus, interact) [@vazquez_evaluating_2009; @vazquez_uniting_2009].
+The environment can influence both of these processes [@godsoe_integrating_2017]. 
+It is, therefore, not surprising that, despite limitations on the spatial extent or the number of environmental gradients considered, multiple studies have shown how changes to interactions can be related to environmental change [@tylianakis_ecological_2017].
+Despite widespread evidence that species interactions and their networks can change along environmental gradients, the direction of change can be variable [@pires_predicted_2016; @baskett_latitudinal_2018; @devoto_patterns_2005], such that until now it has been impossible to extrapolate previous findings to new kinds of gradients.
 Overall, while it looks clear that pairwise interactions respond to environmental drivers, there is high variability in the response [@tylianakis_global_2008].

### 2020-04-11 paper/manuscript.Rmd
finish off edits to intro

@@
 
-One possible explanation for the seemingly contradictory evidence is that different bioclimatic factors (like temperature or precipitation) can have contrasting effects on species and their partners. 
-Here we attempt to simplify this situation by reducing multiple factors into a single measure of environmental stress. 
-Previous research suggests that environmental stress may affect the number of partners in different ways depending on its role in the community (for example its trophic guild) or even the species itself.
-Specifically, we propose two alternative hypotheses of how environmental stress may affect specialisation [@tylianakis_ecological_2017]. 
-On the one hand, it is possible that when species are under environmental stress, they might be "pressured" to focus on partners with which they are best adapted to interact. 
-For instance, @hoiss_altitude_2012 found increased phylogenetic clustering between plants and pollinators at higher altitudes; while @peralta_phylogenetic_2015 found that parasitoids in plantation forest, where environmental stress was higher than in native forests, were constrained to interact with hosts, they were best adapted to attack.
-Similarly, @lavandero_genotype_2013 showed that environmental stress due to higher temperature reduced the trophic niche breadth of parasitoids suggesting higher specialisation.
+One possible explanation for the seemingly contradictory evidence is that different bioclimatic factors (like temperature or precipitation) can have contrasting effects on species and their partners, such that we lack a common currency with which to derive general responses to the environment.
+Here we attempt to overcome these barriers to deriving general rules by reducing multiple factors into a single measure of environmental stress. 
+Previous research suggests that environmental stress may affect the number of interaction partners a species has in different ways depending on the species' role in the community (for example its trophic guild) [@tylianakis_ecological_2017].
+Specifically, we propose two alternative hypotheses of how environmental stress may affect specialisation. 
+First, species under environmental stress, might be "pressured" to focus on partners with which they are best adapted to interact. 
+For instance, @hoiss_altitude_2012 found increased phylogenetic clustering between plants and pollinators at higher altitudes; while @peralta_phylogenetic_2015 found that parasitoids in plantation forest, where environmental stress was higher than in native forests, constrained their host use to those with which phylogenetic matching was strongest.
+Similarly, @lavandero_genotype_2013 showed that environmental stress due to higher temperature reduced the trophic niche breadth (range of host genotypes used) of parasitoids, suggesting higher specialisation.
 
-On the other hand, it is also possible that when species are under environmental stress, they are forced to be more flexible in their interactions.
+Alternatively, it is also possible that when species are under environmental stress, they are forced to be more flexible in their interactions.
 Higher environmental stress is likely to be reflected in greater energetic or reproductive costs. 
-Therefore they might not be able to sustain encounter rates with their preferred partners at sufficient levels. 
+Therefore, they might not be able to sustain encounter rates with their preferred partners at sufficient levels. 
 In line with this hypothesis, @hoiss_interactive_2015 found that the specialisation of plant-pollinator networks decreased both with elevation and after extreme drought events.
@@
 Here, we investigate whether and how environmental stress can systematically affect specialisation. 
-Our main aim is to test the two hypotheses mentioned above that relate environmental stress and species' number of partners and investigate whether this changes across species or between trophic guilds.
+Our main aim is to test the two hypotheses mentioned above that relate environmental stress with a species' number of partners and investigate whether this changes systematically across species or between trophic guilds.
 We propose that specialist species can become "facultative" generalists to reduce their vulnerability to the absence of preferred partners [for example, when variations in climate decouple phenologies; @benadi_specialization_2014].
 In other words, we expect that, as environmental stress increases, specialists should be more likely to engage with more partners. 
-Species with a large number of partners, on the other hand, should have a larger pool of available partners and might, therefore, be more likely to specialise under environmental stress and focus on the most beneficial partners.
-Importantly, when testing these hypotheses, we control for the potential effects of the environment in community composition [which has been previously shown to be a determinant factor; @gravel_bringing_2018].
+Species with many partners, conversely, should have a larger pool of available partners and might, therefore, be more likely to specialise on the most benefitial partners under environmental stress. 
+Importantly, when testing these hypotheses, we control for the potential effects of the environment on community composition [which has been previously shown to be a determinant factor; @gravel_bringing_2018].
 We test these hypotheses using data on plant-pollinator interactions. 
-These interactions provide a particularly interesting system to test these hypotheses because, due to the multiple trade-offs involved in the pollination service, there are multiple intuitive ways in which we could imagine species respond to environmental stress given the available partners.
-We estimate the stress species might experience in their community by calculating the bioclimatic suitability of their communities given the species' patterns of global occurrence.
+These interactions provide a particularly interesting system to test these hypotheses because, due to the multiple trade-offs involved in the pollination service, there are multiple intuitive ways in which we could imagine species responding to environmental stress given the available partners.
+We estimate the stress species might experience a given community by calculating its bioclimatic suitability based on the species' patterns of global occurrence.
 

### 2020-04-11 paper/manuscript.Rmd
minor spellchecking intro

@@
 Specifically, we propose two alternative hypotheses of how environmental stress may affect specialisation. 
-First, species under environmental stress, might be "pressured" to focus on partners with which they are best adapted to interact. 
+First, species under environmental stress might be "pressured" to focus on partners with which they are best adapted to interact. 
 For instance, @hoiss_altitude_2012 found increased phylogenetic clustering between plants and pollinators at higher altitudes; while @peralta_phylogenetic_2015 found that parasitoids in plantation forest, where environmental stress was higher than in native forests, constrained their host use to those with which phylogenetic matching was strongest.
@@
 In other words, we expect that, as environmental stress increases, specialists should be more likely to engage with more partners. 
-Species with many partners, conversely, should have a larger pool of available partners and might, therefore, be more likely to specialise on the most benefitial partners under environmental stress. 
+Species with many partners, conversely, should have a larger pool of available partners and might, therefore, be more likely to specialise on the most beneficial partners under environmental stress. 
 Importantly, when testing these hypotheses, we control for the potential effects of the environment on community composition [which has been previously shown to be a determinant factor; @gravel_bringing_2018].

### 2020-04-14 paper/manuscript.Rmd
Corrections to the Methods

@@
 Calculating the environmental stress of species in their community and their potential partners required us to reduce both the taxonomic and distributional/locational uncertainty.
-A critical step towards reducing this uncertainty is to ensure that the names used to identify species are valid and unambiguous, which in turn allow us to obtain further information from biological databases and accurately match species across studies.
-Therefore, our first step was to ensure consistent spelling and standardisation of species names synonyms (see Supplementary Methods).
+A critical step towards reducing this uncertainty is to ensure that the names used to identify species are valid and unambiguous, which in turn allows us to obtain further information from biological databases and accurately match species across studies.
+Therefore, our first step was to ensure consistent spelling and standardisation of species names and synonyms (see Supplementary Methods).
 The cleaning process resulted on a total of `r format(stats_clean_int$pla_id, big.mark = ",")` plants and `r format(stats_clean_int$ani_id, big.mark = ",")` pollinator species distributed across `r format(stats_clean_int$loc_id)` locations arround the globe (Figure \@ref(fig:fig-distribution-species-mult-locations) and  \@ref(fig:fig-worldmap)).
@@
 
-After matching species across studies as accurate as possible, we carried on two more steps. 
+After matching species across studies as accurately as possible, we performed two more steps. 
 First, we calculated the environmental stress of species in their communities.
-Second, we relate the species stress in their community with the number of partner species it has as a metric of their level of specialisation.
+Second, we relate each species' stress in its community with the number of partner species it has as a metric of its level of specialisation.
 
-## Environmental stress
+## Environmental stressdispla
 
@@
 We calculated the environmental stress of species in their communities.
-We assume that stress a species experiences in a particular location is inversely related to the suitability of the average environmental conditions in that place. 
+We assume that the stress a species experiences in a particular location is inversely related to the suitability of the average environmental conditions in that place. 
 As we aim to compare specialisation levels for different levels of environmental stress, we only calculate bioclimatic suitability for species that were present in at least `r numbers2words(readd(minimum_spp_locations))` communities.
@@
 Second, the method requires information about the environmental conditions for all the locations in which the species occurs.
-We retrieved `r round(sum(n_occurrences$N)/1000000, digits = 1)` million occurrences from the Global Biodiversity Information Facility (GBIF; https://www.gbif.org). 
+We retrieved `r round(sum(n_occurrences$N)/1000000, digits = 1)` million occurrences of our focal species from the Global Biodiversity Information Facility (GBIF; https://www.gbif.org). 
 Issues with data quality are a central issue hampering the use of publicly available species occurrence GBIF data in ecology and biogeography [@jetz_essential_2019]. 
 We, therefore, followed a series of filters and geographic heuristics to correct or remove erroneous and imprecise referencing records [see supplementary methods; @zizka_coordinatecleaner_2019] which allowed us to identify and remove `r round(sum(n_dirty_occurrences$N)/1000000, digits = 1)` million potentially problematic occurrences from further analysis.
-We integrated the occurrences from our plant-pollinator communities to the cleaned occurrences retrieved from GBIF.
+We integrated the occurrence records from our plant-pollinator communities to the cleaned occurrences retrieved from GBIF.
 
@@
 To determine the environmental space, we used the first two components from a principal component analysis of the 37 bioclimatic variables associated with the species occurrences. 
-Specifically we used the `dudi.pca` function from the R package `ade4` `r as.character(packageVersion('ade4'))` [@dray_ade4_2007] and center and scale all bioclimatic variables to have a mean of zero and a unit variance.
-We then determined the position of species occurrences in the environmental space and estimate their bivariate probability density function. 
+Specifically we used the `dudi.pca` function from the R package `ade4` `r as.character(packageVersion('ade4'))` [@dray_ade4_2007] and centered and scaled all bioclimatic variables to have a mean of zero and a unit variance.
+We then determined the position of species occurrences in the environmental space and estimated their bivariate probability density function. 
 We used a kernel method to estimate this density and normalised it such that it ranges between zero and one. 
-We used the kernel density method in the niche-factor analysis [@broennimann_measuring_2012] rather than the distance from the mode [@hirzel_ecological-niche_2002] (as it has been proposed earlier) because it has been shown to reduce the procedure's sensitivity to sampling effort and the resolution of the environmental space.
+We used the kernel density method in the niche-factor analysis [@broennimann_measuring_2012] rather than the distance from the mode [@hirzel_ecological-niche_2002] (as has been proposed earlier) because it has been shown to reduce the procedure's sensitivity to sampling effort and the resolution of the environmental space.
 Specifically, to calculate the probability density function we used `ecospat.grid.clim.dyn` from the R package `ecospat` `r as.character(packageVersion('ecospat'))` [@broennimann_ecospat_2018] with a grid resolution of 200.
 We then determined the location in the environmental space of the plant-pollinator communities using the function `suprow` from `ade4`.
-The normalised density at that particular location [which we calculated using the R package `raster` `r as.character(packageVersion('raster'))`; @hijmans_raster_2019] corresponds the bioclimatic suitability.
-The result of all these steps is the environmental stress which corresponds to one minus the bioclimatic suitability for a species of a particular location.
+The normalised density at that particular location [which we calculated using the R package `raster` `r as.character(packageVersion('raster'))`; @hijmans_raster_2019] corresponds with the bioclimatic suitability.
+The result of all these steps is the generation of a value of environmental stress, which corresponds to one minus the bioclimatic suitability for a species of a particular location.
 
@@
 Specifically, we use the normalised degree of species as our response variable; that is, the number of species it interacts with given the number of species in the opposite guild [@martin_gonzalez_centrality_2010].
-The normalised degree was modelled using a logit link function, and a binomial distribution in which the number of partner species a focal interacts with is the number of successes, and the number of species in the opposite guild is the number of trials.
+The normalised degree was modelled using a logit link function and a binomial distribution in which the number of partner species a focal species interacts with is the number of successes, and the number of species in the opposite guild is the number of trials.
 We are aware that whether species interact or not is not a Bernoulli process as species interactions are not strictly independent from each other. 
@@
 
-We evaluated four models to assess the relative importance of suitability. 
+We evaluated four models to assess the relative importance of stress for each focal species.  
 A first model, our baseline model, included five variables. 
 <!-- fixed variables (population-level predictors) and two random variables (grouping levels). -->
-The predictors in the baseline model were the environmental stress, its number of known possible partners in the community, and both the species guild (plant or a pollinator) and its interaction with environmental stress.
+The predictors in the baseline model were the environmental stress of the community for each focal species, the species' number of known possible partners in the community, and both the species guild (plant or a pollinator) and its interaction with environmental stress.
 We included the number of known possible partners as a predictor in our models as it allows us to control for the effects of the environment on community composition, effectively accounting for species co-occurrence.
-We calculated this metric by determining the number of partners with which the species is known to interact in any other community.
+We calculated this metric by determining the number of partners with which the species is known to interact in any other community and assessing how mant of these potential partners are present in the local community.
 Controlling for the number of potential partners makes our model a particularly stringent test of our environmental-stress hypotheses because this variable could explain a large proportion of variance.

### 2020-04-14 paper/manuscript.Rmd
Move sensitivity analysis results to the methods

@@
 
+```{r sensitivity-results}
+loadd(approach_suitability)
+threshold_type <- ifelse(approach_suitability == "independent_suitability", "single_species", "all_species")
+```
+
 We used a sensitivity analysis to determine the minimum number of occurrences that are necessary to have robust environmental stress estimations. 
 For that we used the species with most occurrences available, *`r sensitivity_species_name$canonicalName`*, and calculated the mean absolute error of the bioclimatic suitability values obtained with `r numbers2words(config$n_subsamples)` subsamples from the `r format(n_occ_sensitivity_species, big.mark  =",")`  occurrences available from GBIF.
+This analysis indicated that, for a species, we need roughly `r readd(min_occurrences_factor)[[threshold_type]]` independent occurrences for each community for which we aim to estimate the environmental stress.
+This is the number of occurrences necessary to maintain the mean absolute error of bioclimatic suitability below `r config$min_suitability_error` (Fig. \@ref(fig:fig-sensitivity-analysis)). 
+We therefore removed from further analyses `r n_spp_not_enough_occ` species for which we did not have enough occurrences to obtain robust estimates.
+
+```{r fig-sensitivity-analysis, fig.width = width('single'), fig.height = 2.2, fig.cap = fig_sensitivity_analysis_legend}
+loadd(sensitivity_species_name)
+fig_sensitivity_analysis_legend <- 
+  paste0("Sensitivity analysis of environmental stress error. ",
+         "The number of independent occurrences retrieved from GBIF is inversely related to the error of bioclimatic suitability for our plant-pollinator networks. ", 
+         "The sensitivity analysis was performed by subsampling occurrences of", 
+         " *", sensitivity_species_name$canonicalName, "*, ", 
+         "the species in our dataset with the largest number of occurrences in GBIF, which was recorded in two of our communities.")
+
+readd(fig_sensitivity_analysis)
+```
 
@@
 # Results
-
-```{r sensitivity-results}
-loadd(approach_suitability)
-threshold_type <- ifelse(approach_suitability == "independent_suitability", "single_species", "all_species")
-```
-
-After performing our sensitivity analysis, we found that, for a species, we need roughly `r readd(min_occurrences_factor)[[threshold_type]]` independent occurrences for each community for which we aim to estimate the environmental stress.
-This is the number of occurrences necessary to maintain the mean absolute error of bioclimatic suitability below `r config$min_suitability_error` (Fig. \@ref(fig:fig-sensitivity-analysis)). 
-We therefore removed from further analyses `r n_spp_not_enough_occ` species for which we did not have enough occurrences to obtain robust estimates.
-<!-- When inspecting the suitability values of the analysed species, we found that most communities included species for which habitat suitability was low and species for which it was high (Fig.
-\@ref(fig:fig-median-suitability)).
--->
-
-```{r fig-sensitivity-analysis, fig.width = width('single'), fig.height = 2.2, fig.cap = fig_sensitivity_analysis_legend}
-loadd(sensitivity_species_name)
-fig_sensitivity_analysis_legend <- 
-  paste0("Sensitivity analysis of environmental stress error. ",
-         "The number of independent occurrences retrieved from GBIF is inversely related to the error of bioclimatic suitability for our plant-pollinator networks.", 
-         "The sensitivity analysis was performed by subsampling occurrences of", 
-         " *", sensitivity_species_name$canonicalName, "* ", 
-         "the species in our dataset with the largest number of occurrences in GBIF, which was recorded in two of our communities.")
-
-readd(fig_sensitivity_analysis)
-```
 

### 2020-04-14 paper/manuscript.Rmd
Updates to the results

@@
 This analysis indicated that, for a species, we need roughly `r readd(min_occurrences_factor)[[threshold_type]]` independent occurrences for each community for which we aim to estimate the environmental stress.
-This is the number of occurrences necessary to maintain the mean absolute error of bioclimatic suitability below `r config$min_suitability_error` (Fig. \@ref(fig:fig-sensitivity-analysis)). 
+This is the number of occurrences necessary to maintain the mean absolute error of bioclimatic suitability below `r config$min_suitability_error` (Figure \@ref(fig:fig-sensitivity-analysis)). 
 We therefore removed from further analyses `r n_spp_not_enough_occ` species for which we did not have enough occurrences to obtain robust estimates.
@@
 Our models performed relatively well.
-The Bayesian R^2^ for our baseline model was `r round(bayesian_r2_baseline[1], digits = 2)`, which indicates our models were able to capture a large proportion of the variability on the data. 
+The Bayesian R^2^ for our baseline model was `r round(bayesian_r2_baseline[1], digits = 2)`, which indicates that our models were able to capture a large proportion of the variability on the data. 
 Overall, we found that environmental stress does not have a consistent effect across species. 
@@
 For some species, there is a strong negative relationship between stress and specialisation, while for others, there is a strong positive relationship (Figure \@ref(fig:fig-random-effects)a). 
-Interestingly, the slope of this relationship correlates with the species' intercept in the model (Figure \@ref(fig:fig-random-effects)b and c).
-Recall that the model estimates the intercept at the mean value for stress across communities (`r round(readd(mean_parameter_values)$suitability, 2)`).
-The mean correlation coefficient was `r round(random_cor$Estimate, 2)` [`r round(random_cor$Q2.5, 2)`, `r round(random_cor$Q97.5, 2)`].
-Therefore, the slope of the stress-specialisation relationship was more likely to be positive for species with a large number of partners under average stress conditions (and negative for species with a smaller number of partners).
-Extrapolating to no-stress conditions: species that would interact with a small number of partners under no stress are more likely to interact with more partners as stress increases, whereas those that would interact with a large number of partners are more likely to interact with less.
+Interestingly, the slope of this relationship was correlated with the species' specialisation intercept in the model (Figure \@ref(fig:fig-random-effects)b and c; the mean correlation coefficient was `r round(random_cor$Estimate, 2)` [`r round(random_cor$Q2.5, 2)`, `r round(random_cor$Q97.5, 2)`]).
+This correlation indicates that the slope of the stress-specialisation relationship was more likely to be positive for species with many partners under average stress conditions (and negative for species fewer partners).
+Recall that the model estimates the intercept of the number of partners for each species at the mean value for stress across communities (`r round(readd(mean_parameter_values)$suitability, 2)`).
+Extrapolating to no-stress conditions this means that species that would interact with few partners under no stress are more likely to interact with more partners as stress increases, whereas those that would interact with many partners are more likely to interact fewer.
 
@@
 Each line corresponds to the median relationship for each species.
-Although we included in the analysis of all species that are present in two or core communities, to facilitate visualisation here, we show only species for which there is suitability information in at least six communities (",
+Although we included in the analysis all species that are present in two or more communities, to facilitate visualisation here, we show only species present in at least six communities (",
          n_random_pla, " plants and ", 
@@
 ",
-         "(b and c) The correlation between the species' intercept and the species' slope of suitability was negative.
-The species' intercept can be interpreted as the relative difference between the number of partners a species has under mean levels of environmental stress and the mean number of partners across all species.
-Positive values of species' slope indicate a positive relationship between stress and the number of partners and vice-versa.")
+         "(b and c) There was a positive correlation between the species' intercept and the species' stress-specialisation slope.
+The species' intercept can be interpreted as the number of partners a species would have under mean levels of environmental stress.")
 
@@
 
-As expected, we found a strong and positive relationship between the number of possible interactions and the number of realised interactions in the community. 
+As expected, we found a strong and positive relationship between the number of possible interactions and the number of realised interactions in the community (i.e.
+species that were capable of being generalists tended to realise this generality at all locations).
 There was also a large difference of WAIC between the model that included this predictor and that that excluded it. 
 This result indicates that the availability of potential partners—this is, community composition—accounts for a large proportion of the variability in species degree. 
-Importantly, our findings relating to the variability of the stress-specialisation relationship were qualitatively unchanged, whether we included this variable or not.
+Importantly, our findings relating to the variability of the stress-specialisation relationship were qualitatively unchanged, whether we accounted for community composition or not.
 
 The standard deviation (in the parameters scale) of the community intercepts was `r round(sd_loc_id$Estimate, 2)` [`r round(sd_loc_id$Q2.5, 2)`, `r round(sd_loc_id$Q97.5, 2)`] which indicates the importance of the local context when determining specialisation.
-The standard deviation of the species intercept was `r round(sd_org_id$Estimate, 2)` [`r round(sd_org_id$Q2.5, 2)`, `r round(sd_org_id$Q97.5, 2)`], and that of the species' stress slope was `r round(sd_org_id_suitability$Estimate, 2)` [`r round(sd_org_id_suitability$Q2.5, 2)`, `r round(sd_org_id_suitability$Q97.5, 2)`] (95% credible intervals shown within square brakets).
+The standard deviation of the species intercept was `r round(sd_org_id$Estimate, 2)` [`r round(sd_org_id$Q2.5, 2)`, `r round(sd_org_id$Q97.5, 2)`], and that of the species' stress slope was `r round(sd_org_id_suitability$Estimate, 2)` [`r round(sd_org_id_suitability$Q2.5, 2)`, `r round(sd_org_id_suitability$Q97.5, 2)`] (95% credible intervals shown within square brackets).
 

### 2020-04-17 paper/manuscript.Rmd
corrections to discussion

@@
 After accounting for the pool of potential partners, we found that environmental conditions contribute to determining whether a species is a generalist or a specialist *in their community*. 
-We also found that the particular effect of the environment is strongly dependent on the species.
-Based on existing literature, we proposed two alternative hypotheses of how environmental stress may affect species' specialisation, and we found evidence for both of them.
-Species with a large number of partners in low-stress communities were more likely to have a negative relationship and hence reduce the number of partners as stress increases. 
-Contrastingly, species in our datasets with a small number of partners in low-stress communities were more likely to have a larger number of partners in more stressful communities.
-In summary, environmental stress pushes species that are flexible enough to change their interaction partners towards intermediate levels of specialisation, a so-called "regression towards the mean".
+We also found that the particular effect of the environment dependends strongly on the species' inherent tendency to be a specialist or generalist.
+Based on existing literature, we proposed two alternative hypotheses of how environmental stress may affect species' specialisation, and we found evidence for both.
+Species with many partners in low-stress communities were more likely to have a negative relationship and hence reduce the number of partners as stress increases. 
+Contrastingly, species in our datasets with few partners in low-stress communities were more likely to interact with more partners in more stressful communities.
 
-Our results suggest that changes in community composition are indeed the primary channel through which the environment determines changes interaction probability. 
+Our results suggest that changes in community composition are indeed the primary channel through which the environment determines changes interaction probability, and this is a common mechanism through which ecological networks respond to environmental change [@tylianakis_ecological_2017].
 However, they also show that, for a large number of species, the environment may also play a substantial role in determining their level of specialisation. 
@@
 
-Although both niche and neutral processes are relevant in determining species interactions, our model suggests that niche processes may be the predominant mechanism through which the environment *systematically* affects specialisation.
-First, it is unlikely that environmental stress correlates to local species abundances [@pearce_practical_2001; @sagarin_moving_2006]. 
-Second, even if there is a relationship between stress and abundances, a particular environmental gradient could have a positive effect on the abundance of some species and a negative effect on others.
-Indeed, we find that within a community there is a wide range of stress values, even for the relatively limited number of species we were able to include in our analysis.
-
 Recent research suggests that species are continuously changing their interaction partners wherever environmental conditions change in space or time [@raimundo_adaptive_2018].
@@
 Our results add two important nuances to these findings. 
-First, because "generalists" seem to focus on a smaller number of partners as environmental conditions deteriorate, we show that trait matching might still play a role in determining the interactions of generalist species.
+First, because "generalists" seem to focus on fewer partners as environmental conditions deteriorate, we show that trait matching might still play a role in determining the  less-flexible core interactions of generalist species.
 Second, and most importantly, our results suggest that only a small proportion of species are "true generalists" or "true specialists" this is, species that interact with a large or small number of partners regardless of the environmental stress, respectively.
-This pattern implies that rewiring is not exclusive of species with a large number of partners. 
+This pattern implies that rewiring is not exclusive to species with many partners. 
 Instead, at least a fraction of the species that appear to be specialist *in their communities* might be as flexible, if not more, than those with a large number of partners, effectively behaving as facultative generalists in the face of environmental change.
@@
 
-Similarly, if the patterns we see in our models have also played a role during the evolutionary history of pollination communities, our results also help explain why only a small fraction of plant-pollinator interactions show a strong signature of deep co-evolutionary history [@hutchinson_cophylogenetic_2017].
+Similarly, if the patterns we see in our models have also played a role during the evolutionary history of pollination communities, our results also help to explain why only a small fraction of plant-pollinator interactions shows a strong signature of deep co-evolutionary history [@hutchinson_cophylogenetic_2017].
 The increases in the stress that species are predicted to experience due to rapid environmental change might further erode the co-evolutionary history of specialist species.
@@
 However, it is plausible to expect that nestedness, and therefore network stability, might be reduced in the face of rapid environmental change.
-Determining exactly how the changes in degree caused by environmental stress reflect on systematic changes in network structure would be an interesting avenue of research. 
-Answering this question would require expanding our suitability analysis to all species in the community and compare the degree distribution of networks along a gradient of stress for the community as a whole.
+Determining exactly how the changes in degree caused by environmental stress are reflected by systematic changes in network structure would be an interesting avenue of research. 
+Answering this question would require expanding our suitability analysis to all species in the community and comparing the degree distribution of networks along a gradient of stress for the community as a whole.
 
@@
 However, we show that many species are flexible in regards to their specialisation levels and therefore are not inherently generalists or specialists. 
-Instead, the species' level of specialisation/generalisation should be considered on a relative scale depending on where they are found and the environmental conditions at that location.
+Instead, the species' level of specialisation/generalisation should be considered on a relative scale depending on environmental stress at a given location.
 

### 2020-04-18 paper/supp-info.Rmd
Update title in supp. info
Edits to the supplementary materials

@@
 ---
-title: "Environmental stress affects niche breadth in plant-pollinator communities"
+title: "Environment affects specialisation of plants and pollinators"
 subtitle: "Supplementary information"
@@
 Interaction data from the included studies included `r format(n_sp_names, big.mark = ",")` unique organism names. 
-From these `r format(n_names_in_multiple_references_orig, big.mark = ",")` were present in more than one study.
+From these, `r format(n_names_in_multiple_references_orig, big.mark = ",")` were present in more than one study.
 From the total number of organisms, `r format(n_sp_names_subsp_level, big.mark = ",")` were identified to the subspecies or variety level, `r format(n_sp_names_sp_level_no_subsp, big.mark = ",")` to the species level, `r format(n_sp_names_gen_level, big.mark = ",")` to the genus level, whereas the remaining `r format(n_no_tax_info, big.mark = ",")` were unidentified.
@@
 
-All together, from the `r format(n_sp_names_sp_level - n_sp_correct_in_data, big.mark = ",")` names we were unable to validate, it was not possible to automatically correct or find synonyms `r format(n_sp_not_found, big.mark = ",")` of them.
+All together, from the `r format(n_sp_names_sp_level - n_sp_correct_in_data, big.mark = ",")` names we were unable to validate, it was not possible to automatically correct or find synonyms for `r format(n_sp_not_found, big.mark = ",")` of them.
 We then manually consulted multiple online databases, chiefly Wikispecies (https://species.wikimedia.org/), and looked for canonical names that both, resembled the unvalidated names and matched the geographic and taxonomic expectations.
@@
 
-```{r tab-manual-name-corrections}
+```{r tab-manual-name-corrections, eval = FALSE}
 loadd(spp, manual_name_corrections)
@@
 
-This cleaning process allowed us to match further `r n_sp_names - n_sp_ids` names across data sources and, by doing so, identify another `r n_names_in_multiple_references_after - n_names_in_multiple_references_orig` species that were present in more than one study.
+This cleaning process allowed us to match a further `r n_sp_names - n_sp_ids` names across data sources and, by doing so, identify another `r n_names_in_multiple_references_after - n_names_in_multiple_references_orig` species that were present in more than one study.
 The process also allowed us to identify `r numbers2words(length(problematic_networks))` problematic data sources in which some names were included as both plants and pollinators. 
 These data sources were removed from further analysis. 
-In `r numbers2words(n_data_sources_mult_nets)` of our data sources interaction data was recorded at multiple points in time. 
+In `r numbers2words(n_data_sources_mult_nets)` of our data sources, interaction data were recorded at multiple points in time. 
 When this was the case, we combined interaction data into one single interaction network.
@@
 Specifically, for each species, we only requested occurrences for which the coordinates of the observation were available and that had no known geospatial issue in the GBIF database.
-Roughly, we downloaded `r round(sum(n_occurrences$N)/1000000, digits = 1)` million occurrences for the `r format(n_species_with_occurrences, big.mark = ",")` species we were interested on. 
-This occurrences, however, contain observations of mixed quality. 
+We downloaded roughly `r round(sum(n_occurrences$N)/1000000, digits = 1)` million occurrences for the `r format(n_species_with_occurrences, big.mark = ",")` species in which we were interested. 
+These occurrences, however, contain observations of mixed quality. 
 Therefore, we followed @zizka_coordinatecleaner_2019 and applied a series of simple filters and geographic heuristics to remove those of lower quality. 
-Specifically, we removed all occurrences with (*i*) a coordinate uncertainty larger than 100km; (*ii*) those recorded prior to 1945 (as records prior to this date have been shown to be often imprecise); (*iii*) those in which the number of counts in the occurrence was registered was either zero (as that indicates that the species has not been recorded); and (*iv*) those occurrences in which the "basis of record" was not a human observation or a preserved specimen (as occurrences from unknown and fossil records are known to be highly unreliable).
+Specifically, we removed all occurrences with (*i*) a coordinate uncertainty larger than 100km; (*ii*) those recorded prior to 1945 (as records prior to this date have been shown to be often imprecise); (*iii*) those in which the number of counts in the occurrence was registered as zero (as that indicates that the species has not been recorded); and (*iv*) those occurrences in which the "basis of record" was not a human observation or a preserved specimen (as occurrences from unknown and fossil records are known to be highly unreliable).
 We then used the R package `CoordinateCleaner` `r as.character(packageVersion('taxize'))` [@zizka_coordinatecleaner_2019] and land mass and country data from Natural Earth (https://www.naturalearthdata.com) with a 1:10,000,000 scale to further identify and remove problematic occurrences.

### 2020-04-18 paper/manuscript.Rmd
Add gbif citations

--- 2020-04-17 paper/manuscript.Rmd
@@
   - int-bibliography.bib
+  - occurrence_bibliography.bib
 csl: ecology-letters.csl
@@
 loadd(interaction_citations, config) 
-loadd(bibliography)
+loadd(bibliography, occurrence_refs)
 ```
@@
 
+```{r occurrence-citations}
+occ_cit <- occurrence_refs %>%
+  purrr::map_chr(names) %>%
+  paste0("@", .) %>%
+  paste(collapse = "; ") %>%
+  paste0("[", ., "]")
+```
+
 The niche factor analysis requires two critical pieces of information. 
@@
 Second, the method requires information about the environmental conditions for all the locations in which the species occurs.
-We retrieved `r round(sum(n_occurrences$N)/1000000, digits = 1)` million occurrences of our focal species from the Global Biodiversity Information Facility (GBIF; https://www.gbif.org). 
+We retrieved `r round(sum(n_occurrences$N)/1000000, digits = 1)` million occurrences of our focal species from the Global Biodiversity Information Facility `r occ_cit`. 
 Issues with data quality are a central issue hampering the use of publicly available species occurrence GBIF data in ecology and biogeography [@jetz_essential_2019]. 

### 2020-04-18 code/occurrence_bibliography.R

@@ -1,0 +1,36 @@
+# Save a bib file for a list of dois from GBIF
+get_occurrence_refs <- function(dois){
+  
+  occurrences_bib <- RefManageR::GetBibEntryWithDOI(dois)
+  
+  # update GBIF name cause its ugly
+  change_author_familyname <- function(x, new_name){
+    x$author$family <- new_name
+    x
+  }
+  
+  update_ref_key <- function(x){
+    names(x) <- basename(names(x)) %>%
+      paste0("gbif_", .)
+    x
+  }
+  
+  occurrences_bib %>%
+    purrr::map(change_author_familyname,
+               new_name = "GBIF.org") %>%
+    purrr::map(update_ref_key)
+  
+}
+
+write_bib <- function(references, bib_file){
+  
+  # start fresh if the file already exists
+  if (file.exists(bib_file))
+    file.remove(bib_file)
+  
+  ocurrences_bib_clean %>%
+    purrr::walk(RefManageR::WriteBib, 
+                file = bib_file, 
+                append = TRUE)
+}
+

### 2020-04-18 main.R

@@ -416,6 +416,10 @@ reporting_plan <- drake_plan(
                                file_out("paper/int-bibliography.bib"),
                                biblio_download_date)
   ),
+  occurrence_refs = get_occurrence_refs(gbif_download_info$doi), 
+  occurrence_bibliography = target(
+    command = write_bib(occurrence_refs, 
+                        file_out("paper/interaction_bibliography.bib"))),
   interaction_citations = bib2df::bib2df(file_in("paper/int-bibliography.bib")),
   abstract = readLines(file_in("./paper/abstract.md")),
   keywords = process_keywords(file_in("./paper/keywords.md")),

### 2020-04-18 paper/draft-info.Rmd
Add to-do
Update draft info

--- 2019-11-17 paper/draft-info.Rmd
@@
 title: "Draft information"
-subtitle: "version: draft-0.3"
-date: "2019-11"
+subtitle: "version: draft-0.5"
+date: "2020-04-18"
 # bibliography: phd-bibliography/pollen-competition.bib
@@
 
-* Refocused the introduction
-* Moved details of the taxonomic data cleaning process to supplementary materials
-* Moved details of occurrence data cleaning process to supplementary materials
-* Reorganised the results
-* Rewrote most of the discussion
-* Changed some details about how species are cleaned
-* Removed species generality and the breadth of the environmental niche from the model
+* Included feedback to paper (thanks Jason)
+* Added many references including some to GBIF datasets
+* Minor adjustments to figure captions
+* Tidied up the supplementary materials
 
@@
 
-* There are some warnings for when matching environmental variables to occurrences. I need to double-check this is happening correctly. 
-* Refine the supplementary results. 
-* Fix references
+* Fix a couple of references
+* Add a few references to the methods justifying occurrence cleaning approach (thanks Audrey)
+
+## Won't-do
+
+* Finish the manual checks for species names that we were unable to correct automatically.
+It takes ~5-10 mins per species and we have ~600.
+Given the amount of data we already have it probably won't make much of a difference.
+
+## Comments
+
+* Jason, one of your comments was: *"I can't remember if I've raised this before, but if species are near to the boundaries of number of partners (close to zero or close to N, where N is the number of species in a community), a random change in the number of partners is more likely to bring them towards the mean because they can't go any higher than N or lower than 0.
+Is there any way to deal with this?"*.
+That certainly might be happening for species with few partners.
+I try to address that in the discussion (see \lr{regression-to-the-mean}).
+I don't think it happens for species with many partners because very few of the species analysed are close to N (only ~2% of plants and ~3% of animals have a normalised degree > 0.5, ~0.5% of both have a normalised degree > 0.75).
+To avoid confusion I've removed the "regression to the mean" statements in the discussion.
+* Appart from that, I think I followed most suggestions one way or another. **Thanks!**

### 2020-04-18 paper/manuscript.Rmd
Update draft info

@@
 
-In our model, we can roughly divide species between true specialists, true generalists, and flexible species. 
+\R{regression-to-the-mean}In our model, we can roughly divide species between true specialists, true generalists, and flexible species. 
 However, there is a fourth group that remained invisible to our model but has important implications for network persistence and stability.

### 2020-04-18 main.R
Fix occ bibio file name

@@ -419,7 +419,7 @@ reporting_plan <- drake_plan(
   occurrence_refs = get_occurrence_refs(gbif_download_info$doi), 
   occurrence_bibliography = target(
     command = write_bib(occurrence_refs, 
-                        file_out("paper/interaction_bibliography.bib"))),
+                        file_out("paper/occurrence_bibliography.bib"))),
   interaction_citations = bib2df::bib2df(file_in("paper/int-bibliography.bib")),
   abstract = readLines(file_in("./paper/abstract.md")),
   keywords = process_keywords(file_in("./paper/keywords.md")),

### 2020-04-18 paper/supp-info.Rmd
Produce manual fix after all

@@
 
-```{r tab-manual-name-corrections, eval = FALSE}
+```{r tab-manual-name-corrections}
 loadd(spp, manual_name_corrections)

### 2020-04-18 paper/draft-info.Rmd
Update draft info
Add ref to manuscript

@@
 
-* Fix a couple of references
 * Add a few references to the methods justifying occurrence cleaning approach (thanks Audrey)
@@
 That certainly might be happening for species with few partners.
-I try to address that in the discussion (see \lr{regression-to-the-mean}).
+I try to address that in the discussion (see \lr{M-regression-to-the-mean}).
 I don't think it happens for species with many partners because very few of the species analysed are close to N (only ~2% of plants and ~3% of animals have a normalised degree > 0.5, ~0.5% of both have a normalised degree > 0.75).

### 2020-05-10 paper/manuscript.Rmd
Try to improve exceptionally messy section in intro

@@
 We test these hypotheses using data on plant-pollinator interactions. 
-These interactions provide a particularly interesting system to test these hypotheses because, due to the multiple trade-offs involved in the pollination service, there are multiple intuitive ways in which we could imagine species responding to environmental stress given the available partners.
-We estimate the stress species might experience a given community by calculating its bioclimatic suitability based on the species' patterns of global occurrence.
+These interactions provide a particularly interesting system to test these hypotheses. 
+Due to the multiple trade-offs involved in the pollination service, there are several ways in which species could respond to environmental stress given the available partners.
+We estimate the stress species might experience in a given community based on the species' patterns of global occurrence.
 

### 2020-05-12 paper/manuscript.Rmd
Fix heading in methods
More of daniel's suggestions

@@
 
-## Environmental stressdispla
+## Environmental stress
 
@@
 Second, the method requires information about the environmental conditions for all the locations in which the species occurs.
-We retrieved `r round(sum(n_occurrences$N)/1000000, digits = 1)` million occurrences of our focal species from the Global Biodiversity Information Facility `r occ_cit`. 
+To obtain the first kind type of information, we retrieved `r round(sum(n_occurrences$N)/1000000, digits = 1)` million occurrences of our focal species from the Global Biodiversity Information Facility `r occ_cit`.
 Issues with data quality are a central issue hampering the use of publicly available species occurrence GBIF data in ecology and biogeography [@jetz_essential_2019]. 
@@
 
-We retrieved environmental data from WorldClim V2.0, which includes 19 bioclimatic variables commonly used in species distribution modelling [@fick_worldclim_2017]. 
+To obtain the second type of information, we retrieved environmental data from WorldClim V2.0, which includes 19 bioclimatic variables commonly used in species distribution modelling [@fick_worldclim_2017].
 We then complemented data obtained from WorldClim with data from Envirem [@title_envirem_2017], which includes 16 extra bioclimatic and two topographic variables. 
@@
 We obtained all environmental data as rasters composed by cells of 2.5 arc-minutes.
-We chose this resolution because it provides a reasonable match to the locational accuracy of the species occurrences found in GBIF, particularly those that originate from preserved specimens in museum collections.
 
@@
 We included the number of known possible partners as a predictor in our models as it allows us to control for the effects of the environment on community composition, effectively accounting for species co-occurrence.
-We calculated this metric by determining the number of partners with which the species is known to interact in any other community and assessing how mant of these potential partners are present in the local community.
+We determined the number of possible partners in a particular community by counting the number of species in the opposite guild with which the species interacted in any other community in our interaction dataset.
 Controlling for the number of potential partners makes our model a particularly stringent test of our environmental-stress hypotheses because this variable could explain a large proportion of variance.
@@
 To account for unmeasured differences between communities, like sampling effort, sampling method, or diversity, we also allowed the model intercept to be different for each community in our study.
-To facilitate model interpretation and convergence, we scaled all continuous variables to have a mean of zero and a unit variance.
+To facilitate model interpretation and convergence, we scaled all continuous predictor variables to have a mean of zero and a unit variance.
 
 We compared this baseline model with three alternative models in which we removed one predictor at a time.
-To quantify the difference between models, in terms of their expected out-of-sample performance, we use the Wanatabe-Akaike information criterion (WAIC).
+To quantify the difference between models, in terms of their expected out-of-sample performance, we use the Wanatabe-Akaike information criterion (WAIC); as with other information criteria, the smaller the WAIC the better the performance.
 All models were fitted under a Bayesian framework using the R package `brms` `r as.character(packageVersion('brms'))` [@burkner_brms_2017; @burkner_advanced_2018] as an interface for Stan [@carpenter_stan_2017].
@@
 These values correspond to the median number of species in each guild across communities.
-In each panel, we condition on the mean value of the other predictor in the model.
+In each panel, we condition on the mean value of the other predictors in the model.
 We indicate mean values for each predictor with a vertical dashed line.
@@
 For some species, there is a strong negative relationship between stress and specialisation, while for others, there is a strong positive relationship (Figure \@ref(fig:fig-random-effects)a). 
-Interestingly, the slope of this relationship was correlated with the species' specialisation intercept in the model (Figure \@ref(fig:fig-random-effects)b and c; the mean correlation coefficient was `r round(random_cor$Estimate, 2)` [`r round(random_cor$Q2.5, 2)`, `r round(random_cor$Q97.5, 2)`]).
-This correlation indicates that the slope of the stress-specialisation relationship was more likely to be positive for species with many partners under average stress conditions (and negative for species fewer partners).
+Interestingly, the slope of this relationship was correlated with the species' specialisation intercept in the model (Figure \@ref(fig:fig-random-effects)b and c).
+The mean correlation coefficient was `r round(random_cor$Estimate, 2)` [`r round(random_cor$Q2.5, 2)`, `r round(random_cor$Q97.5, 2)`] (95% credible intervals shown within square brackets).
+This correlation indicates that the slope of the stress-specialisation relationship was more likely to be positive for species with many partners under average stress conditions (and more likely to be negative for species fewer partners).
 Recall that the model estimates the intercept of the number of partners for each species at the mean value for stress across communities (`r round(readd(mean_parameter_values)$suitability, 2)`).
-Extrapolating to no-stress conditions this means that species that would interact with few partners under no stress are more likely to interact with more partners as stress increases, whereas those that would interact with many partners are more likely to interact fewer.
+Extrapolating to no-stress conditions this means that species that would interact with few partners under no stress are more likely to interact with more partners as stress increases, whereas those that would interact with many partners are more likely to interact with fewer.
 
@@
 ",
-         "(b and c) There was a positive correlation between the species' intercept and the species' stress-specialisation slope.
-The species' intercept can be interpreted as the number of partners a species would have under mean levels of environmental stress.")
+         "(b and c) There was a positive correlation between the species' intercept and the species' stress-specialisation slope.")
 
@@
 The standard deviation (in the parameters scale) of the community intercepts was `r round(sd_loc_id$Estimate, 2)` [`r round(sd_loc_id$Q2.5, 2)`, `r round(sd_loc_id$Q97.5, 2)`] which indicates the importance of the local context when determining specialisation.
-The standard deviation of the species intercept was `r round(sd_org_id$Estimate, 2)` [`r round(sd_org_id$Q2.5, 2)`, `r round(sd_org_id$Q97.5, 2)`], and that of the species' stress slope was `r round(sd_org_id_suitability$Estimate, 2)` [`r round(sd_org_id_suitability$Q2.5, 2)`, `r round(sd_org_id_suitability$Q97.5, 2)`] (95% credible intervals shown within square brackets).
+The standard deviation of the species intercept was `r round(sd_org_id$Estimate, 2)` [`r round(sd_org_id$Q2.5, 2)`, `r round(sd_org_id$Q97.5, 2)`], and that of the species' stress slope was `r round(sd_org_id_suitability$Estimate, 2)` [`r round(sd_org_id_suitability$Q2.5, 2)`, `r round(sd_org_id_suitability$Q97.5, 2)`] .
 
@@
 
-Our results suggest that changes in community composition are indeed the primary channel through which the environment determines changes interaction probability, and this is a common mechanism through which ecological networks respond to environmental change [@tylianakis_ecological_2017].
+Our results suggest that changes in community composition are indeed the primary channel through which the environment determines changes in interaction probability, and this is a common mechanism through which ecological networks respond to environmental change [@tylianakis_ecological_2017].
 However, they also show that, for a large number of species, the environment may also play a substantial role in determining their level of specialisation. 
@@
 First, because "generalists" seem to focus on fewer partners as environmental conditions deteriorate, we show that trait matching might still play a role in determining the  less-flexible core interactions of generalist species.
-Second, and most importantly, our results suggest that only a small proportion of species are "true generalists" or "true specialists" this is, species that interact with a large or small number of partners regardless of the environmental stress, respectively.
+Second, and most importantly, our results suggest that only a small proportion of species are "true generalists" or "true specialists"; that is, species that interact with a large or small number of partners regardless of the environmental stress, respectively.
 This pattern implies that rewiring is not exclusive to species with many partners. 
 Instead, at least a fraction of the species that appear to be specialist *in their communities* might be as flexible, if not more, than those with a large number of partners, effectively behaving as facultative generalists in the face of environmental change.
-These flexible "specialists" might therefore have a more significant role in network persistence than previously expected.
+These "flexible specialists" might therefore have a more significant role in network persistence than previously expected.
 
@@
 Species that are inflexible with their interaction partners are unlikely to persist under more stressful environmental conditions. 
-However, we show that many species are flexible in regards to their specialisation levels and therefore are not inherently generalists or specialists. 
+However, we show that many species are flexible with regards to their specialisation levels and therefore are not inherently generalists or specialists. 
 Instead, the species' level of specialisation/generalisation should be considered on a relative scale depending on environmental stress at a given location.

### 2020-05-12 paper/manuscript.Rmd
Get bibliography as yaml

@@
 bibliography: 
-  - bibliography.bib
+  - bibliography.yaml
   - int-bibliography.bib

### 2020-05-12 main.R

@@ -407,8 +407,8 @@ file_out_plan <- drake_plan(
 
 reporting_plan <- drake_plan(
   bibliography = target(
-    command = get_bibliography("https://raw.githubusercontent.com/efcaguab/phd-bibliography/master/interactions%2Bsdm_manuscript.bib",
-                               file_out("paper/bibliography.bib"),
+    command = get_bibliography("https://raw.githubusercontent.com/efcaguab/phd-bibliography/master/interactions%2Bsdm_manuscript.yaml",
+                               file_out("paper/bibliography.yaml"),
                                biblio_download_date)
   ),
   interaction_bibliography = target(

### 2020-05-12 paper/manuscript.Rmd
Add refs for occurrence cleaning

@@
 After obtaining information about species occurrence and the environment, we then merged these two datasets such that a vector with details of our 37 bioclimatic and topographic variables characterised the location of each occurrence.
-Sets of occurrence data tend to be spatially aggregated due to sample bias (tendency to collect close to cities, certain countries). 
-Moreover, spatial autocorrelation arises in ecological data because geographically clumped records tend to be more similar in physical characteristics and/or species abundances than do pairs of locations that are farther apart.
-To account for such spatial dependency in occurrence data, we only included one occurrence record if a species had more than one within a cell of the bioclimatic raster. 
+Sets of occurrence data tend to be spatially aggregated due to sample bias [tendency to collect close to cities, certain countries; @jetz_essential_2019]. 
+Moreover, spatial autocorrelation arises in ecological data because geographically clumped records tend to be more similar in physical characteristics and/or species abundances than do pairs of locations that are farther apart [@elith_species_2009; @dormann_methods_2007].
+To account for such spatial dependency in occurrence data, we only included one occurrence record if a species had more than one within a cell of the bioclimatic raster [@torres_using_2018; @elith_species_2009].
 We did this to avoid giving more weight to areas with a high number of occurrences, a common scenario in occurrence records collected opportunistically as the ones we use here. 
@@
 
-A common issue of terrestrial bioclimatic datasets is that the boundaries of the cells with information do not precisely match the landmass boundaries. 
+A common issue of terrestrial bioclimatic datasets is that the boundaries of the cells with information do not precisely match the landmass boundaries [@zizka_coordinatecleaner_2019]. 
 The result of this missmatch is that not all environmental variables were available for `r format(complete_climate_cells[1], big.mark = ",")` of the raster cells with occurrences (`r scales::percent(complete_climate_cells[1]/sum(complete_climate_cells), accuracy = 0.1)` of the total).

### 2020-05-24 paper/manuscript.Rmd
Update title

@@
 ---
-title: "Environmental stress drives intermediate plant and pollinator specialisation"
+title: "Environmental stress drives plant and pollinator specialisation"
 author: 
-  - "E. Fernando Cagua^1^ ([efc29@uclive.ac.nz](mailto:efc29@uclive.ac.nz))"
   - "Audrey Lustig^2^ ([audrey.lustig@canterbury.ac.nz](audrey.lustig@canterbury.ac.nz))"

### 2020-05-24 paper/manuscript.Rmd
I'm first author. R: please stop saying otherwise
Make Fig 1 a inverse cumulative distribution

--- 2020-05-12 paper/manuscript.Rmd
@@
 ---
-title: "Environmental stress drives intermediate plant and pollinator specialisation"
+title: "Environmental stress drives plant and pollinator specialisation"
 author: 
@@
 fig_dist_species_multiple_locations_legend <- 
-  paste0("Frequency distribution of the number of locations in which a species is present. The most common pollinator species was *", 
+  paste0("Inverse cummulative distribution of the number of locations in which a species is present. The most common pollinator species was *", 
        most_popular_species$sp_name[1], 

### 2020-05-24 code/figures.R

@@ -35,34 +35,38 @@ plot_species_location_distribution <- function(dist_species_multiple_locations_d
   pal <- cgm()$pal_el_green[c(4,7)]
 
    p <- dist_species_multiple_locations_data %>%
-    ggplot(aes(x = n_locations, y = n_species, fill = guild)) +
-    geom_line(aes(colour = guild), linetype = 3, size = 0.5) +
-    geom_point(shape = 21, size = 1) +
-    # geom_text_repel(data = distribution_data_highlight, aes(label = sp_name)) +
-    geom_mark_circle(aes(label = sp_name, filter = !is.na(sp_name), group = sp_name),
-                     expand = unit(0.1, "mm"),
-                     alpha = 0.1,
-                     colour = NA,
-                     label.fontsize = 7,
-                     label.buffer = unit(5, "mm"),
-                     label.minwidth = unit(10, "mm"),
-                     label.margin = margin(0.5, 0.5, 0.5, 0.5, "mm"),
-                     label.fontface = "italic",
-                     con.size = 0.25,
-                     con.cap = unit(1, "mm"),
-                     con.type = "straight") +
-    scale_fill_manual(values = pal, aesthetics = c("fill", "colour"),
-                      labels = c("animals", "plants")) +
-    scale_y_log10(labels = scales::number_format(big.mark = ",")) +
-    scale_x_log10(breaks = c(1,2, 4, 8, 16, 32)) +
-    pub_theme() +
-    theme(legend.position = c(0.95,0.95),
-          legend.justification = c(1,1),
-          legend.title = element_blank()) +
-    labs(x = "number of locations",
-         y = "frequency (# species)",
-         title = "number of species at multiple locations",
-         subtitle = "frequency distribution")
+     dplyr::arrange(guild, desc(n_locations)) %>%
+     dplyr::mutate(cn = cumsum(n_species), 
+                   p = cn / max(cn)) %>% 
+     ggplot(aes(n_locations, cn, fill = guild)) +
+     geom_line(aes(colour = guild), linetype = 3, size = 0.5) +
+     geom_point(shape = 21, size = 1) +
+     # geom_text_repel(data = distribution_data_highlight, aes(label = sp_name)) +
+     geom_mark_circle(aes(label = sp_name, filter = !is.na(sp_name), group = sp_name),
+                      expand = unit(0.1, "mm"),
+                      alpha = 0.1,
+                      colour = NA,
+                      label.fontsize = 7,
[…]

### 2020-06-17 paper/manuscript.Rmd
Actual and potential number of partners aren't actually that close
Updates to intro based on Chris feedback

@@
 First, species under environmental stress might be "pressured" to focus on partners with which they are best adapted to interact. 
-For instance, @hoiss_altitude_2012 found increased phylogenetic clustering between plants and pollinators at higher altitudes; while @peralta_phylogenetic_2015 found that parasitoids in plantation forest, where environmental stress was higher than in native forests, constrained their host use to those with which phylogenetic matching was strongest.
+In other words under environmental stress they are more specialised than otherwise. 
+For instance, @hoiss_altitude_2012 found increased phylogenetic clustering between plants and pollinators at higher altitudes compared to lower altitudes; while @peralta_phylogenetic_2015 found that parasitoids in plantation forest, where environmental stress was higher than in native forests, constrained their host use to those with which phylogenetic matching was strongest.
 Similarly, @lavandero_genotype_2013 showed that environmental stress due to higher temperature reduced the trophic niche breadth (range of host genotypes used) of parasitoids, suggesting higher specialisation.
@@
 These interactions provide a particularly interesting system to test these hypotheses. 
-Due to the multiple trade-offs involved in the pollination service, there are several ways in which species could respond to environmental stress given the available partners.
+Plant-pollinator interactions are loose enough detect a signal of flexibility and partner preference but strong enough to drive coevolutionary processes [@hutchinson_cophylogenetic_2017]. 
 We estimate the stress species might experience in a given community based on the species' patterns of global occurrence.
@@
 Controlling for the number of potential partners makes our model a particularly stringent test of our environmental-stress hypotheses because this variable could explain a large proportion of variance.
-Often, the potential and the actual number of partners is the same or very close to each other, especially for rare species present only in a few communities.
 

### 2020-06-17 paper/manuscript.Rmd
Minor changes to Methods based on Chris' comments
Chris sugestions for the Methods

--- 2020-05-24 paper/manuscript.Rmd
@@
 The Bayesian R^2^ for our baseline model was `r round(bayesian_r2_baseline[1], digits = 2)`, which indicates that our models were able to capture a large proportion of the variability on the data. 
-Overall, we found that environmental stress does not have a consistent effect across species. 
+Environmental stress was still an important predictor in our model. 
+The difference in WAIC between our baseline model and the model that did not include environmental stress was `r round(waic_diff_suitability)` ± `r round(waic_se_diff_suitability)` (Table \@ref(tab:tab-model-comparison)).
+
+We found that some species, there is a strong negative relationship between stress and specialisation, while for others, there is a strong positive relationship (Figure \@ref(fig:fig-random-effects)a).
+Interestingly, the slope of these relationships was correlated with the species' specialisation intercepts in the model (Figure \@ref(fig:fig-random-effects)b and c).
+The mean correlation coefficient was `r round(random_cor$Estimate, 2)` [`r round(random_cor$Q2.5, 2)`, `r round(random_cor$Q97.5, 2)`] (95% credible intervals shown within square brackets).
+This correlation indicates that the slope of the stress-specialisation relationship was more likely to be positive for species with many partners under average stress conditions (and more likely to be negative for species fewer partners).
+Recall that the model estimates the intercept of the number of partners for each species at the mean value for stress across communities (`r round(readd(mean_parameter_values)$suitability, 2)`).
+Species that would interact with few partners  under no stress are more likely to interact with more partners as stress increases, whereas those that would interact with many partners are more likely to interact with fewer.
+
+```{r fig-random-effects, fig.width = width('double'), fig.height = 2.2*2, fig.cap = fig_random_effects_legend, out.width = "6.81in", out.height = "4.4in", out.extra="center"}
+loadd(random_species_draws)
+
+n_random_species <- random_species_draws %>%
+  dplyr::group_by(guild) %>%
+  dplyr::summarise(n_sp = dplyr::n_distinct(org_id))
+
+n_random_pla <- n_random_species %>%
+  dplyr::filter(guild == "pla_id") %$%
+  n_sp
+
+n_random_ani <- n_random_species %>%
+  dplyr::filter(guild == "ani_id") %$%
+  n_sp
+
+fig_random_effects_legend <- 
+  paste0("Species-level effects of environmental stress (a) Conditional effect of stress for individual species.
+Each line corresponds to the median relationship for each species.
+Although we included in the analysis all species that are present in two or more communities, to facilitate visualisation here, we show only species present in at least six communities (",
+         n_random_pla, " plants and ", 
+         n_random_ani, " pollinators).
+As in the previous figure, fitted values assume a hypothetical community of median size.
+In each panel, we highlight two species for which the relationship between environmental suitability and the normalised degree was particularly strong.
+",
+         "(b and c) There was a positive correlation between the species' intercept and the species' stress-specialisation slope.")
+
+readd(fig_random_effects)
+```
+
+The the variability of the specialisation-stress relationship across species was also evident when looking at overall patterns. 
+We found that environmental stress does not have a consistent effect across species. 
 Indeed, when looking at the fixed effects, stress has virtually no relationship with the normalised degree—our metric of specialisation (Figure \@ref(fig:fig-conditional-effects)a).
-However, environmental stress was still an important predictor in our model. 
-The difference in WAIC between our baseline model and the model that did not include environmental stress was `r round(waic_diff_suitability)` ± `r round(waic_se_diff_suitability)` (Table \@ref(tab:tab-model-comparison)).
-This apparent discrepancy can be explained by the variability of the specialisation-stress relationship across species.
 
@@
 
-For some species, there is a strong negative relationship between stress and specialisation, while for others, there is a strong positive relationship (Figure \@ref(fig:fig-random-effects)a). 
-Interestingly, the slope of this relationship was correlated with the species' specialisation intercept in the model (Figure \@ref(fig:fig-random-effects)b and c).
-The mean correlation coefficient was `r round(random_cor$Estimate, 2)` [`r round(random_cor$Q2.5, 2)`, `r round(random_cor$Q97.5, 2)`] (95% credible intervals shown within square brackets).
-This correlation indicates that the slope of the stress-specialisation relationship was more likely to be positive for species with many partners under average stress conditions (and more likely to be negative for species fewer partners).
-Recall that the model estimates the intercept of the number of partners for each species at the mean value for stress across communities (`r round(readd(mean_parameter_values)$suitability, 2)`).
-Extrapolating to no-stress conditions this means that species that would interact with few partners under no stress are more likely to interact with more partners as stress increases, whereas those that would interact with many partners are more likely to interact with fewer.
-
-```{r fig-random-effects, fig.width = width('double'), fig.height = 2.2*2, fig.cap = fig_random_effects_legend, out.width = "6.81in", out.height = "4.4in", out.extra="center"}
-loadd(random_species_draws)
-
-n_random_species <- random_species_draws %>%
-  dplyr::group_by(guild) %>%
-  dplyr::summarise(n_sp = dplyr::n_distinct(org_id))
-
-n_random_pla <- n_random_species %>%
-  dplyr::filter(guild == "pla_id") %$%
-  n_sp
-
-n_random_ani <- n_random_species %>%
-  dplyr::filter(guild == "ani_id") %$%
-  n_sp
-
-fig_random_effects_legend <- 
-  paste0("Species-level effects of environmental stress (a) Conditional effect of stress for individual species.
-Each line corresponds to the median relationship for each species.
-Although we included in the analysis all species that are present in two or more communities, to facilitate visualisation here, we show only species present in at least six communities (",
-         n_random_pla, " plants and ", 
-         n_random_ani, " pollinators).
-As in the previous figure, fitted values assume a hypothetical community of median size.
-In each panel, we highlight two species for which the relationship between environmental suitability and the normalised degree was particularly strong.
-",
-         "(b and c) There was a positive correlation between the species' intercept and the species' stress-specialisation slope.")
-
-readd(fig_random_effects)
-```
-
 As expected, we found a strong and positive relationship between the number of possible interactions and the number of realised interactions in the community (i.e.
@@
 The standard deviation (in the parameters scale) of the community intercepts was `r round(sd_loc_id$Estimate, 2)` [`r round(sd_loc_id$Q2.5, 2)`, `r round(sd_loc_id$Q97.5, 2)`] which indicates the importance of the local context when determining specialisation.
-The standard deviation of the species intercept was `r round(sd_org_id$Estimate, 2)` [`r round(sd_org_id$Q2.5, 2)`, `r round(sd_org_id$Q97.5, 2)`], and that of the species' stress slope was `r round(sd_org_id_suitability$Estimate, 2)` [`r round(sd_org_id_suitability$Q2.5, 2)`, `r round(sd_org_id_suitability$Q97.5, 2)`] .
+The standard deviation of the species intercepts was `r round(sd_org_id$Estimate, 2)` [`r round(sd_org_id$Q2.5, 2)`, `r round(sd_org_id$Q97.5, 2)`], and that of the species' stress slope was `r round(sd_org_id_suitability$Estimate, 2)` [`r round(sd_org_id_suitability$Q2.5, 2)`, `r round(sd_org_id_suitability$Q97.5, 2)`] .
 

### 2020-06-17 paper/manuscript.Rmd

@@
 This approach allowed us to investigate two questions. 
-First, it allows us to inspect the extent to which environmental stress affects species similarly. 
+First, it allows us to inspect the extent to which environmental stress affects species in a similar way. 
 Second, by investigating the correlation between the intercept and the slope as a model parameter, it allowed us to inspect the extent by which species with a small or large number of partner species respond to increasing levels of environmental stress.

### 2020-06-17 paper/manuscript.Rmd
Typo
Reorder WAIC table

@@
 The Bayesian R^2^ for our baseline model was `r round(bayesian_r2_baseline[1], digits = 2)`, which indicates that our models were able to capture a large proportion of the variability on the data. 
-Environmental stress was still an important predictor in our model. 
+Environmental stress was an important predictor in our model. 
 The difference in WAIC between our baseline model and the model that did not include environmental stress was `r round(waic_diff_suitability)` ± `r round(waic_se_diff_suitability)` (Table \@ref(tab:tab-model-comparison)).
 
-We found that some species, there is a strong negative relationship between stress and specialisation, while for others, there is a strong positive relationship (Figure \@ref(fig:fig-random-effects)a).
+```{r tab-model-comparison}
+model_ranking$waic %>%
+  purrr::map(~.$estimates["waic", ]) %>% 
+  purrr::map_df(~tibble::tibble(estimate = .[1], se = .[2]), .id = "formula") %>%
+  dplyr::arrange(estimate) %>%
+  dplyr::filter(formula != "formula_full") %>%
+  dplyr::mutate(formula = translate_model_formula(formula, "long-abv"), 
+                formula = kableExtra::cell_spec(formula, format = "latex", 
+                                                bold =nchar(formula) == max(nchar(formula)))) %>% 
+  knitr::kable("latex", 
+               booktabs = TRUE, 
+               digits = c(0,0,0), 
+               format.args = list(big.mark = ","), 
+               col.names = c("predictors", "WAIC", "SE"),
+               escape = FALSE,
+               linesep = "",
+               caption = "Comparison in out of sample predictive power of the baseline model (bold) and their alternatives.
+We rank models by their expected log predictive density based on their Wanatabe-Akaike information criterion (WAIC).") %>%
+  kableExtra::kable_styling(font_size = 8) #%>%
+```
+
+We found that for some species, there is a strong negative relationship between stress and specialisation, while for others, there is a strong positive relationship (Figure \@ref(fig:fig-random-effects)a).
 Interestingly, the slope of these relationships was correlated with the species' specialisation intercepts in the model (Figure \@ref(fig:fig-random-effects)b and c). 
@@
 
-The the variability of the specialisation-stress relationship across species was also evident when looking at overall patterns. 
+The variability of the specialisation-stress relationship across species was also evident when looking at overall patterns.
 We found that environmental stress does not have a consistent effect across species.
@@
 readd(fig_conditional_effects)
-```
-
-```{r tab-model-comparison}
-model_ranking$waic %>%
-  purrr::map(~.$estimates["waic", ]) %>% 
-  purrr::map_df(~tibble::tibble(estimate = .[1], se = .[2]), .id = "formula") %>%
-  dplyr::arrange(estimate) %>%
-  dplyr::filter(formula != "formula_full") %>%
-  dplyr::mutate(formula = translate_model_formula(formula, "long-abv"), 
-                formula = kableExtra::cell_spec(formula, format = "latex", 
-                                                bold =nchar(formula) == max(nchar(formula)))) %>% 
-  knitr::kable("latex", 
-               booktabs = TRUE, 
-               digits = c(0,0,0), 
-               format.args = list(big.mark = ","), 
-               col.names = c("predictors", "WAIC", "SE"),
-               escape = FALSE,
-               linesep = "",
-               caption = "Comparison in out of sample predictive power of the baseline model (bold) and their alternatives.
-We rank models by their expected log predictive density based on their Wanatabe-Akaike information criterion (WAIC).") %>%
-  kableExtra::kable_styling(font_size = 8) #%>%
 ```

### 2020-06-17 paper/manuscript.Rmd
Add written consideration of why 4th group of pollinators

@@
 We propose this fourth group is composed of true specialists that are constrained to interact with partners of high trait-matching and therefore were not likely to be found in more than one community.
+Unfortunately it is not straigtforward to explicitly account for this fourth group.
+Accounting for these species would require information that allow us to determine the communities in which the species is not present due to the lack of interaction partners even if climatic conditions are otherwise favourable.
+How to distinguish these two processes (often termed Eltonian and Grinellian, niches respectively) is stil an open area of res [@gravel_bringing_2018]
 If species that are not flexible are unlikely to persist over temporal or spatial environmental gradients, we can expect specialised communities that are highly constrained by trait-matching [like some plant-hummingbird networks; @vizentin-bugoni_processes_2014; @maruyama_morphological_2014] to be far more vulnerable to increased climate change-induced environmental stress and habitat degradation than communities where role and interaction flexibility are more prevalent.

### 2020-06-17 paper/manuscript.Rmd
Remove speculative paragraph about regression to the mean

@@
 
-The structural implications of the "regression towards the mean" that environmental stress promotes are less clear. 
-However, it is plausible to expect that nestedness, and therefore network stability, might be reduced in the face of rapid environmental change.
-Determining exactly how the changes in degree caused by environmental stress are reflected by systematic changes in network structure would be an interesting avenue of research. 
-Answering this question would require expanding our suitability analysis to all species in the community and comparing the degree distribution of networks along a gradient of stress for the community as a whole.
-
 In conclusion, we show that the environment can affect the specialisation level of plants and pollinators in systematic ways beyond community composition. 

### 2020-06-18 paper/manuscript.Rmd
Include explanations for using degree

@@
 Specifically, we use the normalised degree of species as our response variable; that is, the number of species it interacts with given the number of species in the opposite guild [@martin_gonzalez_centrality_2010].
-The normalised degree was modelled using a logit link function and a binomial distribution in which the number of partner species a focal species interacts with is the number of successes, and the number of species in the opposite guild is the number of trials.
+We use degree mainly because it is a simple approximation of specialisation from the "eltonian niche" perspective. 
+Importantly quantifying specialisation using degree does not require quantitative information about the interactions. 
+This crucial feature allowed us to include many more communities and, ultimately, minimise the possible over-representation of common and cosmopolitan species in our model.
+In our model, the normalised degree was modelled using a logit link function and a binomial distribution in which the number of partner species a focal species interacts with is the number of successes, and the number of species in the opposite guild is the number of trials.
 We are aware that whether species interact or not is not a Bernoulli process as species interactions are not strictly independent from each other. 

### 2020-06-18 paper/manuscript.Rmd
Explain inclusion of known possible partners

@@
 We evaluated four models to assess the relative importance of stress for each focal species.
+
 A first model, our baseline model, included five variables. 
-<!-- fixed variables (population-level predictors) and two random variables (grouping levels). -->
 The predictors in the baseline model were the environmental stress of the community for each focal species, the species' number of known possible partners in the community, and both the species guild (plant or a pollinator) and its interaction with environmental stress.
-We included the number of known possible partners as a predictor in our models as it allows us to control for the effects of the environment on community composition, effectively accounting for species co-occurrence.
+We included the number of known possible partners as a predictor in our models. 
+We included this predictor as we would expect an increase in the number of actual partners merely due to an increase in the number of available partners.
+From a community ecology perspective, this is justified because our response variable can be interpreted as the "realised" portion of the niche, and the number of potential partners is a rough approximation to the "fundamental" niche.
+From a biogeographic perspective, including the number of potential partners is an attempt to control for the effects of the environment on community composition and species co-occurrence. 
 We determined the number of possible partners in a particular community by counting the number of species in the opposite guild with which the species interacted in any other community in our interaction dataset.
-Controlling for the number of potential partners makes our model a particularly stringent test of our environmental-stress hypotheses because this variable could explain a large proportion of variance.
 
